### 2014-01-31 ms.tex
biblio.bib

\documentclass{emulateapj}

\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{natbib}
%\usepackage{lscape}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{array}
\usepackage{appendix}
\usepackage{comment}

\bibliographystyle{apj}

\def\plotonesc#1{\centering \leavevmode
\includegraphics[clip=, width=1.70\columnwidth]{#1}}
\def\plotoneh#1{\centering \leavevmode
\includegraphics[clip=, width=.95\columnwidth]{#1}}
\def\plotone#1{\centering \leavevmode
\includegraphics[clip=, width=.85\columnwidth]{#1}}
\def\plotoneShrinkSmall#1{\centering \leavevmode
\includegraphics[clip=, width=.49\columnwidth]{#1}}
\def\plotoneShrinkMed#1{\centering \leavevmode
\includegraphics[clip=, width=.55\columnwidth]{#1}}
\def\plotoneShrinkBig#1{\centering \leavevmode
\includegraphics[clip=, width=.65\columnwidth]{#1}}
\def\plottwo#1#2{\centering \leavevmode
\includegraphics[width=.45\columnwidth]{#1} \hfil
\includegraphics[width=.45\columnwidth]{#2}}
\def\plottwob#1#2{\centering \leavevmode
\includegraphics[width=.49\columnwidth]{#1} \hfil
\includegraphics[width=.49\columnwidth]{#2}}
\def\plottwor#1#2{\centering \leavevmode
\includegraphics[width=.55\columnwidth,angle=90]{#1} \hfil
\includegraphics[width=.55\columnwidth,angle=90]{#2}}
\def\plotthree#1#2#3{\centering \leavevmode
\includegraphics[width=.3\columnwidth]{#1} \hfil
\includegraphics[width=.3\columnwidth]{#2} \hfil
\includegraphics[width=.3\columnwidth]{#3}}

\newcommand{\cN}[1]{\mathcal{N}}
\newcommand{\pn}[1]{\mbox{$(#1)$}}
\newcommand{\spa}{\mbox{ }}
\def\gsim{\;\rlap{\lower 2.5pt
 \hbox{$\sim$}}\raise 1.5pt\hbox{$>$}\;}
\def\lsim{\;\rlap{\lower 2.5pt
   \hbox{$\sim$}}\raise 1.5pt\hbox{$<$}\;}

% set formatting properties
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.8in}
\setlength{\hoffset}{0.0in}
\setlength{\voffset}{-0.4in}
%\setlength{\voffset}{0.3in}
\parindent 0.2in
\parskip 0.1in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THE DOCUMENT BEGINS HERE                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\slugcomment{Submitted to ApJ, 20 October 2011}

\begin{document}

%%% Begin front material
%\twocolumn[%%% Begin front material

\title{Red-Giant Hot Jupiters: Brilliant Radio Beacons}

\author{
%
David S. Spiegel\altaffilmark{1} \\
%
and some order: \\
%
Nikku Madhusudhan\altaffilmark{?} [Add correct affiliation] \\
%
Mehrdad Mirbabayi\altaffilmark{1} \\
%
Aaron Parsons\altaffilmark{?} [Add correct affiliation] \\
%
Tony Mroczkowski\altaffilmark{?} [Add correct affiliation]
}

\affil{$^1$Astrophysics Department, Institute for Advanced Study,
  Princeton, NJ 08540}

\affil{$^?$Astronomy Department, University of Cambridge, UK}

\affil{$^?$Astronomy Department, UC Berkeley}

\affil{$^?$Naval Research Laboratory}

\vspace{0.5\baselineskip}

\email{
dave@ias.edu
}

\begin{abstract}
  Red-giant hot Jupiters are jovian planets orbiting red-giant-branch
  or asymptotic-giant-branch (AGB) stars.  Post-main-sequence stars
  lose mass at much higher rates than main-sequence stars.  A jovian
  planet passing through the dense winds of its AGB host can capture
  stellar wind in its magnetosphere.  The cyclotron frequency of
  electrons from the stellar wind accreting onto the planet scales as
  100~MHz~$(B/3 {\rm~Gauss})$.  Such a planet might generate a radio
  luminosity that would be visible from kiloparsec distances.
\end{abstract}

\keywords{planets and satellites: Jupiter --- Sun: evolution ---
  planetary systems --- radiative transfer --- stars: evolution ---
  stars: AGB and post-AGB}
%]%%% End front material

\section{Introduction}
\label{sec:intro}

% fix
Roughly 20\% of the more than 700 currently known
exoplanets\footnote{See online catalogs such as
  http://www.openexoplanetcatalogue.com/ \citep{rein2012},
  http://exoplanet.eu \citep{schneider_et_al2011}, or
  http://exoplanets.org \citep{wright_et_al2011} for up-to-date
  lists.} have masses greater than half of Jupiter's, orbital radii
greater than 1~AU, and will become hot Jupiters (i.e., for the present
purposes, this means they will receive at least as much irradiation as
the hot Neptune

The cyclotron frequency is
\begin{equation}
f_{\rm cyclotron} = \frac{eB}{2\pi m_e c} \approx 3 {\rm~MHz} \left( \frac{B}{1 \rm~G} \right) \, .
\label{eq:cyc}
\end{equation}
For magnetic field strengths in the vicinity of $\sim$25-50~Gauss (G),
the cyclotron frequency will be in the range $\sim$75-150~MHz.

\citep{spiegel2008}

\citep{lecavelier_et_al2013}

\citep{janhunen_et_al2003}

\citep{zarka1992, zarka1998}

\citep{farrell_et_al2004}

\citep{lazio+farrell2007}: likelihood function, tau Boo search

\citep{lecavelier_et_al2009}

\citep{spiegel2012}

\citep{nordhaus+spiegel2013}

\citep{spiegel+madhusudhan2012}

\citep{jiang+jin1996}: 12cm radio of Jupiter during Shoemake-Levy-9

\citep{morin2012, morin_et_al2013}

\citep{christensen_et_al2009, christensen2010}

\citep{saar2001}: Inverse rossby number scaling of magnetic field: $B
\sim 60 {\rm~G} \times Ro^{-1.2}$.  Here, he takes $Ro = \tau_c/P_{\rm
  rot}$, where $\tau_c$ is the convective turnover time = ?
\citep{gilliland1986}.  Well, $F \sim \rho v_c^3 \sim \rho
(H/\tau_c)^3$, so $\tau_c \sim H (\rho / F)^{1/3} = H / (\sigma T_{\rm
  eff}^4 / \rho)^{1/3}$.  Alternatively, $\tau_{\rm conv} \sim (M R^2
/ L)^{1/3}$.

On dimensional grounds, the convective turnover time goes as
$\tau_{\rm conv} \sim (M R^2 / L)^{1/3}$.  According to
\citet{burrows_et_al2001}, radius $R$ and luminosity scale with time
as $R \sim R_J$, where $R_J$ is the radius of Jupiter, and
\begin{equation}
\frac{L}{10^{-9} L_\odot} \sim \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
\label{eq:burrowsLum}
\end{equation}
So,
%\begin{eqnarray}
%\nonumber \tau_{\rm conv} & \sim & 3 {\rm~days} \times \left( \frac{M}{M_J} \right)^{1/3} \left( \frac{R}{R_J} \right)^{2/3} \left( \frac{L}{L_\odot} \right)^{-1/3} \\
% & = & 
%\end{eqnarray}
\begin{eqnarray}
\nonumber \tau_c & \sim & 3 {\rm~hrs} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{L}{10^{-9} L_\odot} \right)^{1/3}} \\
 & = & 3 {\rm~hrs} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_J} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}} \\
\end{eqnarray}
So the Rossby number $Ro = \tau_c/P_{\rm rot}$ is
\begin{eqnarray}
Ro & = & \frac{\tau_c}{P_{\rm rot}} \\
 & = & \left( \frac{P_{\rm rot}}{3 \rm~hrs} \right)^{-1} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_J} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}}
\end{eqnarray}

\citep{hallinan_et_al2013}

\citep{desch+kaiser1984} radiometric Bode's law

Noting that
\begin{equation}
\dot{M}_* = 4\pi r^2 \rho[r] v \, ,
\label{eq:mdot
}\end{equation}
so $\rho[r] = \dot{M}_*/(4\pi r^2 v)$,
\begin{eqnarray}
\frac{\rho v^2}{2} = \frac{B^2}{8\pi} \sim \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-3} \, ,
\end{eqnarray}
where $B_0$ is the field strength at a distance $d_0$ from the planet.
\begin{eqnarray}
\frac{\rho v^2}{2} & \sim & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
\frac{\dot{M}_* v}{8\pi a^2} & = & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
\frac{\dot{M}_* v}{r^2} & = & B_0^2 \left( \frac{d}{d_0} \right)^{-6} \\
d^6 & = & \frac{d_0^6 B_0^2 r^2}{\dot{M}_* v} \\
d_A & = & d_0 \left( \frac{B_0^2 r^2}{\dot{M}_* v} \right)^{1/6} \\
  & \sim & 4 R_J \left( \frac{d_0}{R_J}\right) \left\{ \frac{\left( \frac{B}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^2}{\left( \frac{\dot{M}_*}{10^{-6} M_\odot/\rm yr} \right) \left( \frac{v}{20 \rm~km/s} \right)} \right\}^{1/6}
\label{eq:Chapman-Ferraro}
\end{eqnarray}
In the above, $d_A$ is the distance away from the planet where the
magnetic energy density equals the kinetic energy density in the
stellar wind, if $B_0$ is the magnetic field strength at distance
$d_0$.

The escape speed is
\begin{equation}
v_{\rm esc}^* = \sqrt{\frac{2 G M_*}{R_*}} \, ,
\end{equation}
so if the stellar wind speed is a factor $C$ times the escape speed, then ...

The power incident on the planet within $d_A$ is
\begin{eqnarray}
P_{\rm inc} & = & \frac{\rho v^3}{2} \times \pi d_A^2 \\
\frac{\rho v^2}{2} & \sim & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
d_A^6 & = & d_0^6 \frac{B_0^2}{4\pi \rho v^2} \\
d_A^2 & = & d_0^2 \left( \frac{B_0^2}{4\pi \rho v^2}\right)^{1/3} \\
\pi d_A^2 \frac{\rho v^3}{2} & = & \frac{d_0^2}{2} \left( \frac{\pi^2 \rho^2 v^7 B_0^2}{4} \right)^{1/3} \\
P_{\rm inc} & = & d_0^2 \left( \frac{\pi^2 \rho^2 v^7 B_0^2}{32} \right)^{1/3} 
%\frac{\dot{M}_* v}{8\pi a^2} & = & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
%\frac{\dot{M}_* v}{r^2} & = & B_0^2 \left( \frac{d}{d_0} \right)^{-6} \\
%d^6 & = & \frac{d_0^6 B_0^2 r^2}{\dot{M}_* v} \\
%d_A & = & d_0 \left( \frac{B_0^2 r^2}{\dot{M}_* v} \right)^{1/6} \\
%  & \sim & 4 d_0 \left\{ \frac{\left( \frac{B}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^2}{\left( \frac{\dot{M}_*}{10^{-6} M_\odot/\rm yr} \right) \left( \frac{v}{20 \rm~km/s} \right)} \right\}^{1/6}
\end{eqnarray}
Note that $\rho v = \dot{M}_*/4\pi r^2$.  Therefore,
\begin{eqnarray}
P_{\rm inc} & = & d_0^2 \left( \frac{\pi^2 \rho^2 v^7 B_0^2}{32} \right)^{1/3} \\
 & = & d_0^2 \left( \frac{\dot{M}_*^2 v^5 B_0^2}{512 r^4} \right)^{1/3} \\
 & = & \frac{d_0^2}{8} \left( \frac{\dot{M}_*^2 v^5 B_0^2}{r^4} \right)^{1/3} \\
\nonumber  & \sim & 2 \times 10^{18} {\rm~W} \left( \frac{d_0}{R_J} \right)^2 \left( \frac{\dot{M}_*}{10^{-5} M_\odot / {\rm yr}} \right)^2 \\
 & & \times \left( \frac{v}{20 \rm~km/s} \right)^5 \left( \frac{B_0}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^{-4}
\end{eqnarray}

The power incident on the planet is

%\citep{lunine_et_al1989} -- error?

% http://kiss.caltech.edu/workshops/magnetic2013/presentations/winterhalter.pdf

%ftp://ftp.iwf.oeaw.ac.at/pub/Scherf/PRE-CD%20V2/pre6/nigl.pdf

\section{Conclusions}
\label{sec:conc}

\vspace{0.5in}

%\acknowledgements

{\sc Acknowledgments}

We thank many people for useful discussions, in particular Tony
Mroczkowzki.  DSS gratefully acknowledges support from a fellowship
from the AMIAS group.  NM acknowledges support from [???].

\newpage

\bibliography{biblio.bib}

\clearpage

\end{document}

### 2014-03-29 ms.tex
added my name
recent change

@@
 %
-and some order: \\
+{\bf and some order:} \\
 %
@@
   electrons from the stellar wind accreting onto the planet scales as
-  100~MHz~$(B/3 {\rm~Gauss})$.  Such a planet might generate a radio
+  100~MHz~$(B/30 {\rm~Gauss})$.  Such a planet might generate a radio
   luminosity that would be visible from kiloparsec distances.
@@
 % fix
+When stars less than $\sim$8~$M_\sun$ evolve off the main sequence,
+they go through stages on the red-giant branch (RGB) and the
+asymptotic-giant branch (AGB) when their radii and luminosities
+increase by orders of magnitude.  Jovian planets in orbit around such
+stars can be transiently heated to hot-Jupiter temperatures
+($\sim$1000~K or more) at distances out to tens of AU, depending on
+the star's mass.  These planets' existence was predicted by
+\citet{spiegel+madhusudhan2012} and we will refer to them as
+``red-giant hot Jupiters'' (RGHJs).
+
 Roughly 20\% of the more than 700 currently known
@@
 \begin{equation}
-f_{\rm cyclotron} = \frac{eB}{2\pi m_e c} \approx 3 {\rm~MHz} \left( \frac{B}{1 \rm~G} \right) \, .
+f_{\rm cyclotron} = \frac{eB}{2\pi m_e c} \approx 2.8 {\rm~MHz} \left( \frac{B}{1 \rm~G} \right) \, .
 \label{eq:cyc}
@@
 \end{eqnarray}
-In the above, $d_A$ is the distance away from the planet where the
-magnetic energy density equals the kinetic energy density in the
-stellar wind, if $B_0$ is the magnetic field strength at distance
-$d_0$.
+In the above, $d_A$ is the distance from the planet to the Alfven
+point, where the magnetic energy density $u_B = B^2 / 8\pi$ equals the
+kinetic energy density in the stellar wind $u_w = \rho v^2/2$, and
+$B_0$ is the magnetic field strength at distance $d_0$.
 
@@
 
+mehrdad
+\newpage
 \bibliography{biblio.bib}

### 2015-03-22 ms.tex
authors
fixed typo
Added Project Florida Labs to my affiliation.

@@
 %
-David S. Spiegel\altaffilmark{1} \\
+David S. Spiegel\altaffilmark{1, 2} \\
 %
@@
 %
-Nikku Madhusudhan\altaffilmark{?} [Add correct affiliation] \\
+Jason Nordhaus\altaffilmark{3} \\
+%
+Nikku Madhusudhan\altaffilmark{4} \\
 %
@@
 %
-Aaron Parsons\altaffilmark{?} [Add correct affiliation] \\
+Aaron Parsons\altaffilmark{5} \\
 %
-Tony Mroczkowski\altaffilmark{?} [Add correct affiliation]
+Tony Mroczkowski\altaffilmark{6} \\
+%
+Neil Zimmerman\altaffilmark{7}
 }
@@
 
-\affil{$^?$Astronomy Department, University of Cambridge, UK}
+\affil{$^2$Research \& Development, Project Florida Labs,
+  New York, NY  10001}
 
-\affil{$^?$Astronomy Department, UC Berkeley}
+\affil{$^2$Department of Mathematics, Rochester Institute of Technology}
 
-\affil{$^?$Naval Research Laboratory}
+\affil{$^3$Astronomy Department, University of Cambridge, UK}
+
+\affil{$^4$Astronomy Department, UC Berkeley}
+
+\affil{$^5$Naval Research Laboratory}
+
+\affil{$^6$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
 

### 2015-03-31 ms.tex
updated

@@
 \usepackage{comment}
+\usepackage{color}
 
 \bibliographystyle{apj}
+
+\def\memo#1{\color{red}$[${\bf #1}$]$ \color{black}}
 
@@
 
-\title{Red-Giant Hot Jupiters: Brilliant Radio Beacons}
+\title{Red-Giant Hot Jupiters: Brilliant Radio Emitter?}
 
@@
 
+Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
+It has been known that Jupiter emits radio wave around 20 MHz due to the interaction with plasmas from the satellite Io \memo{?}, and 100-3000 MHz, which is cyclotron radiation from electrons that are accelerated in Jupiter's magnetic field \memo{?}.
+Similarly, large exoplanets can emit radio waves, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons. 
+Radio emission from exoplanets have been estimated taking account of several possible processes \citep{griebmeier2007}, and the search for these radio signatures are being conducted. 
+%In general, there are four proposed models for a planet to emit radio wave \citep{griebmeier2007}: 1) the magnetic energy model, 2) kinetic energy model, 3) CME model, and 4) the unipolar interaction model.
+%The search for these radio emissions from extrasolar Jovian planets has been performed. 
+While some indications were obtained \memo{?} \citep{lecavelier_et_al2013},  there is no clear detection claimed so far.
+
+%It has been predicted that
 % fix
@@
 asymptotic-giant branch (AGB) when their radii and luminosities
-increase by orders of magnitude.  Jovian planets in orbit around such
+increase by orders of magnitude.
+
+Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} \memo{How these values are observationally obtained?} \memo{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memo{cite more papers?}.
+Jovian planets in orbit around such
 stars can be transiently heated to hot-Jupiter temperatures
@@
 ``red-giant hot Jupiters'' (RGHJs). 
+When massive stellar wind reach the planetary magnetosphere standoff points  \memo{??}, they presumably deposit part of their energy generating bright radio emission. 
+In this paper, we examine the radio brightness of RGHJs.
 
-Roughly 20\% of the more than 700 currently known
-exoplanets\footnote{See online catalogs such as
-  http://www.openexoplanetcatalogue.com/ \citep{rein2012},
-  http://exoplanet.eu \citep{schneider_et_al2011}, or
-  http://exoplanets.org \citep{wright_et_al2011} for up-to-date
-  lists.} have masses greater than half of Jupiter's, orbital radii
-greater than 1~AU, and will become hot Jupiters (i.e., for the present
-purposes, this means they will receive at least as much irradiation as
-the hot Neptune
+%Red giants lose their masses at a high rate, typically $\sim  10^{-5} M_{\odot }/yr $ through massive stellar wind. These stellar wind particle can
+
+%Roughly 20\% of the more than 700 \memo{check!} currently known exoplanets around main-sequence stars \footnote{See online catalogs such as http://www.openexoplanetcatalogue.com/ \citep{rein2012}, http://exoplanet.eu \citep{schneider_et_al2011}, or http://exoplanets.org \citep{wright_et_al2011} for up-to-date lists.} have masses greater than half of Jupiter's, orbital radii greater than 1~AU, and will become hot Jupiters (i.e., for the present purposes, this means they will receive at least as much irradiation as the currently known hot Jupiters/Neptunes \citep{spiegel+madhusudhan2012}.
+
+\section{Assumpsions}
+
+\subsection{Mechanisms}
+
+\subsection{Properties for Stellar Wind of RGs}
+
+The mass loss rate of the stellar wind can be estimated from observation \memo{How?}.
+For the known red giants, the values are typically $\dot M \sim 10^{-8} M_{\odot}$/yr, significantly greater than the solar mass-loss rate $\sim 10^{-14} M_{\odot}$/yr.
+\begin{equation}
+\frac{\dot M}{\dot M_{\odot}} \sim 10^6
+\end{equation}
+
+The stellar wind velocity is smaller because of the small escape velocity (due to expanded stellar radius)\footnote{Escape velocity is $\sqrt{2GM/r}$.}.
+Assuming that the stellar wind scales as the escape velocity, RGs with radius $R=100R_{\odot}$ have 10 times as slow stellar wind as that at the main sequence.
+\begin{equation}
+\frac{v}{v_{\odot}} \sim 10^{-1}
+\end{equation}
+
+The temperature of stellar wind of RGs is expected to be 2 orders of magnitude lower than their main sequence counterparts, mainly because the sound speed of hot corona exceeds the escape speed, i.e., hot corona cannot be confined in the stellar atmosphere \citep{suzuki2008}.
+\begin{equation}
+\frac{T}{T_{\odot}} \sim 10^{-2}
+\end{equation}
+
+\subsection{Properties for Planetary Magnetic Field}
+
+Scaling of magnetic field is found at
+\citet{griebmeier2007}
+\citet{griebmeier2004}
+
+Unlike usual hot jupiters, RGHJs are not subject to tidal lock, because the gravitational effects of their host star does not change even if the star evolves into red giants.
+
+For the moment, let us assume Jovian magnetic field strength.
+
+\section{Estimates of Radio Emission from RGHJ}
+
+\subsection{Estimates of frequency}
 
@@
 \begin{equation}
-f_{\rm cyclotron} = \frac{eB}{2\pi m_e c} \approx 2.8 {\rm~MHz} \left( \frac{B}{1 \rm~G} \right) \, .
+f_{\rm cyclotron} = \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \, .
 \label{eq:cyc}
@@
 the cyclotron frequency will be in the range $\sim$75-150~MHz.
+
+The emission is observable only when the maximum frequency is larger than the plasma frequency of the surrounding stellar wind. 
+The plasma frequency is 
+\begin{eqnarray}
+f_{\rm plasma} &=& \frac{1}{2\pi} \sqrt{\frac{ne^2}{\epsilon _0 m_e}} \\
+&\approx & 4\mbox{MHz} \left( \frac{\dot M}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
+\end{eqnarray}
+
+...OK!\memo{double-check}
+
+\subsection{Estimates of intensity}
+
+According to \citet{griebmeier2007} \memo{The following equations are quoted from the paper. Needs to elaborate. }
+\begin{enumerate}
+\item kinetic energy model
+\begin{equation}
+P_{\rm inp} \propto n v^3 r_s ^2 \label{eq:Pinp_kin}
+\end{equation}
+\item magnetic energy model:
+\begin{equation}
+P_{\rm inp} \propto v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag}
+\end{equation}
+\item CME model\\
+Not sure about CME for red giants. We don't consider?
+\item the unipolar interaction model\\
+??
+\end{enumerate}
+where $n$ and $v$ are density and velocity of stellar wind, respectively,  $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of magnetic standoff point.
+
+$r_s$ is determined by the balance between the magnetic pressure of planetary magnetosphere and kinetic pressure of stellar wind\footnote{Precisely, the magnetic standoff point is described by equation (9) of \citet{griebmeier2007}, which is.
+\begin{equation}
+r_s = \left[ \frac{\mu_0 f_0^2 \mathcal{M}}{8\pi^2 (m_p n(d) v(d)^2 + 2 n(d) k_B T)} \right]^{1/6}
+\end{equation}
+where $\mathcal{M}$ is the planetary magnetic moment and $m_p$ is the proton mass. 
+In the following arguments based on Dave's sketch, the second term in the denominator is ignored.
+This is valid for Solar wind where the first term is larger than the second term by 2 orders of magnitude.
+\memo{check!}}.
+Thus,
+\begin{equation}
+\frac{m_p n v ^2}{2} = \frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6} 
+\end{equation}
+Therefore,
+\begin{eqnarray}
+r_s &=& R_p \left( \frac{B^2}{\pi \dot M v (1/4\pi d^2)} \right)^{1/6} = R_p \left( \frac{4 B^2 d^2}{\dot M v } \right)^{1/6} \\
+&\approx & 5 R_J \left(\frac{B}{10 \mbox{[G]}}\right)^{1/3} \left(\frac{\dot M}{10^6 \dot M_{\odot}}\right)^{-1/6}\\
+&& \;\;\;\;\; \;\;\;\;\; \times \left(\frac{v}{10^{-1} v_{\odot}}\right)^{-1/6}  \left(\frac{d}{5 \mbox{[AU]}}\right)^{1/3} 
+\end{eqnarray}
+
+Therefore, the radio emission expected from kinetic energy model (equation (\ref{eq:Pinp_kin})) is 
+\begin{eqnarray}
+P_{\rm inp} &=& P_{\rm inp, J} \left(\frac{\dot M }{\dot M_{\odot }} \right) \left(\frac{v}{v_{\odot}} \right) ^2 \left(\frac{d}{5 \rm{AU}} \right) ^{-2}  \left(\frac{r_s}{r_{s, {\rm J}}} \right)^2 \\
+&=& P_{\rm inp, J} \left(\frac{\dot M }{\dot M_{\odot }} \right)^{\frac{2}{3}} \left(\frac{v}{v_{\odot}} \right) ^{\frac{5}{3}} \left(\frac{d}{5 \rm{AU}} \right) ^{-2} \left(\frac{B}{B_J} \right)^{\frac{2}{3}} \\
+&\approx& 200 P_{\rm inp, J} \left(\frac{\dot M }{10^6 \dot M_{\odot }} \right)^{\frac{2}{3}} \left(\frac{v}{10^{-1} v_{\odot}} \right) ^{\frac{5}{3}} \\
+&& \;\;\;\;\; \;\;\;\;\; \times \left(\frac{d}{5 \rm{[AU]}} \right) ^{-4/3} \left(\frac{B}{10 \mbox{[G]}} \right)^{\frac{2}{3}} \
+\end{eqnarray}
+
+\memo{Following arguments are based on \citep{griebmeier2007}. }
+Assuming $P_{\rm inp, J} = 2.1\times 10^{11}$ W \citep{griebmeier2007}, observed RGHJ radio emission at distance $l$ is
+\begin{eqnarray}
+P_{\rm ons} &=& \frac{P_{\rm radio}}{\Omega l^2 f_{\rm cyclotron}} \\
+&\approx & 5\times 10^{-6} \mbox{Jy} \left( \frac{P_{\rm radio}}{P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{[pc]}} \right)^{-2} \left( \frac{B}{10\mbox{[G]}} \right) ^{-1} \\
+&\approx & 10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{[pc]}} \right)^{-2} \left( \frac{B}{10\mbox{[G]}} \right) ^{-1}
+\end{eqnarray}
+where $\Omega $ is the solid angle of emission, which is assumed $\Omega = 1.6$.
+
+\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section{Discussion on Observability}
+
+\subsection{Radio emission from red giants stars}
+
+(Jason)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\citet{gorman2013}
+
+\subsection{Expected population of RGHJ in the observable volume}
+
+\section{Dave's sketch}
 
@@
 \citep{nordhaus+spiegel2013}
-
-\citep{spiegel+madhusudhan2012}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
@@
 mehrdad
+
 \newpage
+
 \bibliography{biblio.bib}

### 2015-03-31 ms.tex
Changed spacing slightly and added memo about AGB mass-loss rate.

@@
 
-\def\memo#1{\color{red}$[${\bf #1}$]$ \color{black}}
+\def\memoYF#1{\color{red}$[${\bf #1}$]$ \color{black}}
+
+\def\memoDS#1{\color{blue}$[${\bf #1}$]$ \color{black}}
 
@@
 Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
-It has been known that Jupiter emits radio wave around 20 MHz due to the interaction with plasmas from the satellite Io \memo{?}, and 100-3000 MHz, which is cyclotron radiation from electrons that are accelerated in Jupiter's magnetic field \memo{?}.
+It has been known that Jupiter emits radio wave around 20 MHz due to the interaction with plasmas from the satellite Io \memoYF{?}, and 100-3000 MHz, which is cyclotron radiation from electrons that are accelerated in Jupiter's magnetic field \memoYF{?}.
 Similarly, large exoplanets can emit radio waves, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons. 
@@
 %The search for these radio emissions from extrasolar Jovian planets has been performed. 
-While some indications were obtained \memo{?} \citep{lecavelier_et_al2013},  there is no clear detection claimed so far.
+While some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013},  there is no clear detection claimed so far.
 
@@
 
-Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} \memo{How these values are observationally obtained?} \memo{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memo{cite more papers?}.
+Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} \memoYF{How these values are observationally obtained?} \memoYF{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memoYF{cite more papers?}.
 Jovian planets in orbit around such
@@
 ``red-giant hot Jupiters'' (RGHJs). 
-When massive stellar wind reach the planetary magnetosphere standoff points  \memo{??}, they presumably deposit part of their energy generating bright radio emission. 
+When massive stellar wind reach the planetary magnetosphere standoff points  \memoYF{??}, they presumably deposit part of their energy generating bright radio emission. 
 In this paper, we examine the radio brightness of RGHJs.
@@
 
-%Roughly 20\% of the more than 700 \memo{check!} currently known exoplanets around main-sequence stars \footnote{See online catalogs such as http://www.openexoplanetcatalogue.com/ \citep{rein2012}, http://exoplanet.eu \citep{schneider_et_al2011}, or http://exoplanets.org \citep{wright_et_al2011} for up-to-date lists.} have masses greater than half of Jupiter's, orbital radii greater than 1~AU, and will become hot Jupiters (i.e., for the present purposes, this means they will receive at least as much irradiation as the currently known hot Jupiters/Neptunes \citep{spiegel+madhusudhan2012}.
+%Roughly 20\% of the more than 700 \memoYF{check!} currently known exoplanets around main-sequence stars \footnote{See online catalogs such as http://www.openexoplanetcatalogue.com/ \citep{rein2012}, http://exoplanet.eu \citep{schneider_et_al2011}, or http://exoplanets.org \citep{wright_et_al2011} for up-to-date lists.} have masses greater than half of Jupiter's, orbital radii greater than 1~AU, and will become hot Jupiters (i.e., for the present purposes, this means they will receive at least as much irradiation as the currently known hot Jupiters/Neptunes \citep{spiegel+madhusudhan2012}.
 
@@
 
-The mass loss rate of the stellar wind can be estimated from observation \memo{How?}.
+The mass loss rate of the stellar wind can be estimated from observation \memoYF{How?}.
 For the known red giants, the values are typically $\dot M \sim 10^{-8} M_{\odot}$/yr, significantly greater than the solar mass-loss rate $\sim 10^{-14} M_{\odot}$/yr.
+\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.
+I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
 \begin{equation}
@@
 
-...OK!\memo{double-check}
+...OK!\memoYF{double-check}
 
@@
 
-According to \citet{griebmeier2007} \memo{The following equations are quoted from the paper. Needs to elaborate. }
+According to \citet{griebmeier2007} \memoYF{The following equations are quoted from the paper. Needs to elaborate. }
 \begin{enumerate}
@@
 This is valid for Solar wind where the first term is larger than the second term by 2 orders of magnitude.
-\memo{check!}}.
+\memoYF{check!}}.
 Thus,
@@
 
-\memo{Following arguments are based on \citep{griebmeier2007}. }
+\memoYF{Following arguments are based on \citep{griebmeier2007}. }
 Assuming $P_{\rm inp, J} = 2.1\times 10^{11}$ W \citep{griebmeier2007}, observed RGHJ radio emission at distance $l$ is

### 2015-04-13 ms.tex
Explained how to estimate magnetic field of RGHJs.

--- 2015-03-31 ms.tex
@@
 
-Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} \memo{How these values are observationally obtained?} \memo{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memo{cite more papers?}.
+Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} for RGs \memo{How these values are observationally obtained?}.
+\memo{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memo{cite more papers?}.
 Jovian planets in orbit around such
@@
 When massive stellar wind reach the planetary magnetosphere standoff points  \memo{??}, they presumably deposit part of their energy generating bright radio emission.
-In this paper, we examine the radio brightness of RGHJs.
+
+In this paper, we examine the radio brightness of RGHJs, taking account of the increased stellar wind.
 
@@
 The mass loss rate of the stellar wind can be estimated from observation \memo{How?}.
-For the known red giants, the values are typically $\dot M \sim 10^{-8} M_{\odot}$/yr, significantly greater than the solar mass-loss rate $\sim 10^{-14} M_{\odot}$/yr.
+For the known red giants, the values are typically $\dot M \sim 10^{-8} M_{\odot}$/yr, and can be as much as $\sim  10^{-5} M_{\odot }$/yr for AGB stars, significantly greater than the solar mass-loss rate: $\sim 10^{-14} M_{\odot}$/yr.
 \begin{equation}
@@
 
-The stellar wind velocity is smaller because of the small escape velocity (due to expanded stellar radius)\footnote{Escape velocity is $\sqrt{2GM/r}$.}.
+The stellar wind velocity becomes smaller because of the small escape velocity (due to expanded stellar radius)\footnote{Escape velocity is $\sqrt{2GM/r}$.}.
 Assuming that the stellar wind scales as the escape velocity, RGs with radius $R=100R_{\odot}$ have 10 times as slow stellar wind as that at the main sequence.
@@
 
-Scaling of magnetic field is found at
-\citet{griebmeier2007}
-\citet{griebmeier2004}
+Theoretically, the magnetic moment of gaseous planets are expressed with the following scaling relationship \citep{griebmeier2004}:
+%%%%%%%%%% 
+\begin{equation}
+\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
+\end{equation}
+%%%%%%%%%%
+where $\omega $ is the spin angular velocity, $\rho _c$, $r_c$ and $\sigma $ are the density, the radius, and the conductivity of the ``dynamo region'' where the density is high enough for hydrogen to be metallic, respectively.
+The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$.
+In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}.
+\memo{validity?}
 
 Unlike usual hot jupiters, RGHJs are not subject to tidal lock, because the gravitational effects of their host star does not change even if the star evolves into red giants.
+Without no physical insights of the typical spin period, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
 
-For the moment, let us assume Jovian magnetic field strength.
+In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of gaseous planets.
+We simply use the same model as \citet{griebmeier2004}, where the density as a function of radius from the center is described as:
+%%%%%%%%%% 
+\begin{equation}
+\rho (r) = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left( \pi \frac{r}{R_p} \right)}{\left( \pi \frac{r}{R_p} \right)} \label{eq:rho_r}
+\end{equation}
+%%%%%%%%%%
+and assume that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$.
+The density of the metallic core is obtained by averaging the density in the core.
+
+We assume that the conductivity $\sigma $ is the same as Jupiter \memo{?}.
 
@@
 The cyclotron frequency is
-\begin{equation}
-f_{\rm cyclotron} = \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \, .
-\label{eq:cyc}
-\end{equation}
+\begin{eqnarray}
+f_{\rm cyclotron} &=& \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \, ,
+\label{eq:cyc} \\
+B &=& \frac{\mu_0}{2\pi}\frac{\mathcal{M}}{R_p^3} \\
+&\sim & 9.1 \mbox{[G]} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right) \left( \frac{R_p}{R_{p, J}} \right)^{-3}. 
+\end{eqnarray}
+%where $\mathcal{M}_J = 1.56 \times 10^{27} \mbox{A m}^2$. 
 For magnetic field strengths in the vicinity of $\sim$25-50~Gauss (G),
 the cyclotron frequency will be in the range $\sim$75-150~MHz.
+
+Since the 
+Figure \ref{fig:f_cyclotron} shows
 
@@
 f_{\rm plasma} &=& \frac{1}{2\pi} \sqrt{\frac{ne^2}{\epsilon _0 m_e}} \\
-&\approx & 4\mbox{MHz} \left( \frac{\dot M}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
+&\approx & 4\mbox{[MHz]} \left( \frac{\dot M}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
 \end{eqnarray}
@@
 \begin{eqnarray}
-P_{\rm inp} &=& P_{\rm inp, J} \left(\frac{\dot M }{\dot M_{\odot }} \right) \left(\frac{v}{v_{\odot}} \right) ^2 \left(\frac{d}{5 \rm{AU}} \right) ^{-2}  \left(\frac{r_s}{r_{s, {\rm J}}} \right)^2 \\
-&=& P_{\rm inp, J} \left(\frac{\dot M }{\dot M_{\odot }} \right)^{\frac{2}{3}} \left(\frac{v}{v_{\odot}} \right) ^{\frac{5}{3}} \left(\frac{d}{5 \rm{AU}} \right) ^{-2} \left(\frac{B}{B_J} \right)^{\frac{2}{3}} \\
-&\approx& 200 P_{\rm inp, J} \left(\frac{\dot M }{10^6 \dot M_{\odot }} \right)^{\frac{2}{3}} \left(\frac{v}{10^{-1} v_{\odot}} \right) ^{\frac{5}{3}} \\
+P_{\rm radio} &=& P_{\rm radio, J} \left(\frac{\dot M }{\dot M_{\odot }} \right) \left(\frac{v}{v_{\odot}} \right) ^2 \left(\frac{d}{5 \rm{AU}} \right) ^{-2}  \left(\frac{r_s}{r_{s, {\rm J}}} \right)^2 \\
+&=& P_{\rm radio, J} \left(\frac{\dot M }{\dot M_{\odot }} \right)^{\frac{2}{3}} \left(\frac{v}{v_{\odot}} \right) ^{\frac{5}{3}} \left(\frac{d}{5 \rm{AU}} \right) ^{-2} \left(\frac{B}{B_J} \right)^{\frac{2}{3}} \\
+&\approx& 200 P_{\rm radio, J} \left(\frac{\dot M }{10^6 \dot M_{\odot }} \right)^{\frac{2}{3}} \left(\frac{v}{10^{-1} v_{\odot}} \right) ^{\frac{5}{3}} \\
 && \;\;\;\;\; \;\;\;\;\; \times \left(\frac{d}{5 \rm{[AU]}} \right) ^{-4/3} \left(\frac{B}{10 \mbox{[G]}} \right)^{\frac{2}{3}} \
@@
 \begin{eqnarray}
-P_{\rm ons} &=& \frac{P_{\rm radio}}{\Omega l^2 f_{\rm cyclotron}} \\
+P_{\rm obs} &=& \frac{P_{\rm radio}}{\Omega l^2 f_{\rm cyclotron}} \\
 &\approx & 5\times 10^{-6} \mbox{Jy} \left( \frac{P_{\rm radio}}{P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{[pc]}} \right)^{-2} \left( \frac{B}{10\mbox{[G]}} \right) ^{-1} \\

### 2015-04-13 ms.tex

@@
 
-Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} for RGs \memo{How these values are observationally obtained?}.
-\memo{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memo{cite more papers?}.
+Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} \memoYF{How these values are observationally obtained?} \memoYF{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memoYF{cite more papers?}.
+
 Jovian planets in orbit around such
@@
 ``red-giant hot Jupiters'' (RGHJs). 
-When massive stellar wind reach the planetary magnetosphere standoff points  \memo{??}, they presumably deposit part of their energy generating bright radio emission.
+When massive stellar wind reach the planetary magnetosphere standoff points  \memoYF{??}, they presumably deposit part of their energy generating bright radio emission.
 
@@
 
-The mass loss rate of the stellar wind can be estimated from observation \memo{How?}.
-For the known red giants, the values are typically $\dot M \sim 10^{-8} M_{\odot}$/yr, and can be as much as $\sim  10^{-5} M_{\odot }$/yr for AGB stars, significantly greater than the solar mass-loss rate: $\sim 10^{-14} M_{\odot}$/yr.
+The mass loss rate of the stellar wind can be estimated from observation \memoYF{How?}.
+For the known red giants, the values are typically $\dot M \sim 10^{-8} M_{\odot}$/yr, and can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases, significantly greater than the solar mass-loss rate $\sim 10^{-14} M_{\odot}$/yr.
+
+%\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
+%>>>>>>> e6e562d36dff6e5bb10b57fdd066ee5edd32b496
 \begin{equation}
@@
 In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}.
-\memo{validity?}
+\memoYF{validity?}
 
@@
 
-We assume that the conductivity $\sigma $ is the same as Jupiter \memo{?}.
+We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
 

### 2015-04-13 ms.tex
Figures are temporarily added.

@@
 %
+Yuka Fujii\altaffilmark{0} \\
+%
 David S. Spiegel\altaffilmark{1, 2} \\
@@
 }
+
+\affil{$^0$Earth-Life Science Institute, Tokyo Institute of Technology, 
+  Tokyo, JAPAN, 152-8550}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
 \label{sec:intro}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Assumpsions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Assumptions}
+\label{s:assumptions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Mechanisms}
+\label{ss:mechanisms}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+According to \citet{griebmeier2007} \memoYF{The following equations are quoted from the paper. Needs to elaborate. }
+\begin{enumerate}
+\item kinetic energy model
+\begin{equation}
+P_{\rm inp} \propto n v^3 r_s ^2 \label{eq:Pinp_kin}
+\end{equation}
+\item magnetic energy model:
+\begin{equation}
+P_{\rm inp} \propto v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag}
+\end{equation}
+\item CME model\\
+Not sure about CME for red giants. We don't consider?
+\item the unipolar interaction model\\
+??
+\end{enumerate}
+where $n$ and $v$ are density and velocity of stellar wind, respectively,  $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of magnetic standoff point.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Properties for Stellar Wind of RGs}
+\label{ss:stellarwind}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Properties for Planetary Magnetic Field}
+\label{ss:planetarymagnetic}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%
-and assume that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$.
-The density of the metallic core is obtained by averaging the density in the core.
-
+where
+%%%%%%%%%% 
+\begin{equation}
+R_p (M_p) = \frac{(\alpha M_p)^{1/3}}{1+\left( \frac{M_p}{M_{\rm max}} \right)} \label{eq:Rp}
+\end{equation}
+%%%%%%%%%%
+with $\alpha =6/1 \times 10^{-4}$ \citep{griebmeier2007}. 
+We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$.
+The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
 We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Estimates of Radio Emission from RGHJ}
+\label{s:estimate}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Estimates of frequency}
+\label{ss:frequency}
 
@@
 
-Since the 
-Figure \ref{fig:f_cyclotron} shows
+Figure \ref{fig:f_cyclotron} shows the cyclotron frequency of the planetary magnetic field.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                                                                                                                               
+\begin{figure}[!h]
+\begin{center}
+\includegraphics[width=0.7\hsize]{test_fcycrotron.eps}
+\end{center}
+\caption{Cyclotron frequency. (May be deleted eventually.)}
+\label{fig:f_cyclotron}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-...OK!\memoYF{double-check}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                                                                                                                               
+\begin{figure}[!h]
+\begin{center}
+\includegraphics[width=0.9\hsize]{test_observability.eps}
+\end{center}
+\caption{Where condition $f_{cyclotron}>f_{plasma}$. (May be deleted eventually.)}
+\label{fig:f_cyclotron}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Estimates of intensity}
-
-According to \citet{griebmeier2007} \memoYF{The following equations are quoted from the paper. Needs to elaborate. }
-\begin{enumerate}
-\item kinetic energy model
-\begin{equation}
-P_{\rm inp} \propto n v^3 r_s ^2 \label{eq:Pinp_kin}
-\end{equation}
-\item magnetic energy model:
-\begin{equation}
-P_{\rm inp} \propto v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag}
-\end{equation}
-\item CME model\\
-Not sure about CME for red giants. We don't consider?
-\item the unipolar interaction model\\
-??
-\end{enumerate}
-where $n$ and $v$ are density and velocity of stellar wind, respectively,  $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of magnetic standoff point.
+\label{ss:intensity}
 
@@
 
+Figure \ref{fig:radio} shows the intensity of radio emission from RGHJs. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                                                                                                                               
+\begin{figure}[!h]
+\begin{center}
+\includegraphics[width=0.9\hsize]{test_radio.eps}
+\end{center}
+\caption{Intensity of radio emission. }
+\label{fig:radio}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
+\label{ss:offset}
 
@@
 \newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion on Observability}
+\label{s:discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Radio emission from red giants stars}
+\label{ss:RGradio}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \citet{gorman2013}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Expected population of RGHJ in the observable volume}
+\label{ss:number}
+
+\newpage
 

### 2015-04-15 ms.tex
introduction elaborated

@@
 Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
-It has been known that Jupiter emits radio wave around 20 MHz due to the interaction with plasmas from the satellite Io \memoYF{?}, and 100-3000 MHz, which is cyclotron radiation from electrons that are accelerated in Jupiter's magnetic field \memoYF{?}.
-Similarly, large exoplanets can emit radio waves, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons. 
-Radio emission from exoplanets have been estimated taking account of several possible processes \citep{griebmeier2007}, and the search for these radio signatures are being conducted. 
+It has been known that Jupiter emits radio emission from the radiation belt and auroral region due to the acceleration of the plasmas.
+\memoYF{?}.
+Potentially, large exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
+stellar wind particles and particles from Io-like moons.
+Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001,griebmeier2007,noyola2013}.
+Although the search for these radio signatures are being conducted, there is no clear detection claimed so far, while some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013}. 
 %In general, there are four proposed models for a planet to emit radio wave \citep{griebmeier2007}: 1) the magnetic energy model, 2) kinetic energy model, 3) CME model, and 4) the unipolar interaction model.
 %The search for these radio emissions from extrasolar Jovian planets has been performed.
-While some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013},  there is no clear detection claimed so far.
 
@@
 they go through stages on the red-giant branch (RGB) and the
-asymptotic-giant branch (AGB) when their radii and luminosities
-increase by orders of magnitude.
+asymptotic-giant branch (AGB) where their radii and luminosities increase by orders of magnitude. 
+Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass \citet{spiegel+madhusudhan2012}.
+At the same time, they are subject to massive stellar wind, because the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991}.
+\memoYF{How these values are observationally obtained?} \memoYF{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memoYF{cite more papers?}.
+On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could generate bright radio emission.
 
-Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} \memoYF{How these values are observationally obtained?} \memoYF{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memoYF{cite more papers?}.
+In this paper we propose the potential to detect planetary companions around evolved stars through the brightness of their radio emission. 
+The search for such emission could tell us the population of companions around evolved stars, including those were originally A or O stars.
 
-Jovian planets in orbit around such
-stars can be transiently heated to hot-Jupiter temperatures
-($\sim$1000~K or more) at distances out to tens of AU, depending on
-the star's mass. These planets' existence was predicted by
-\citet{spiegel+madhusudhan2012} and we will refer to them as
-``red-giant hot Jupiters'' (RGHJs). 
-When massive stellar wind reach the planetary magnetosphere standoff points  \memoYF{??}, they presumably deposit part of their energy generating bright radio emission.
-
-In this paper, we examine the radio brightness of RGHJs, taking account of the increased stellar wind.
+In \S2, we discuss the assumption we make in this paper. 
+\S3, we provide the estimates. 
+\S4, we examine the possible obstacles to detect radio emission from the companion, taking account of the intrinsic radio emission of the evolved stars...
+% based on the number of targets in the observable volumes
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Radio emission intensity of Solar System giant planets are known to be proportional to the kinetic energy or the magnetic energy of the solar wind,  which interacts with planetary magnetic field at the magnetic standoff cross section\memoYF{``radio Bode's law'': cite something}.
+
+Unfortunately, the detail of the mechanism of energy transport from the energy source into the radio emission.
 

### 2015-04-16 ms.tex
Descriptions are updated. Figures of main result are updated.

@@
 stellar wind particles and particles from Io-like moons.
-Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001,griebmeier2007,noyola2013}.
+Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001,griebmeier2007,noyola2014}.
 Although the search for these radio signatures are being conducted, there is no clear detection claimed so far, while some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013}. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Assumptions}
+\section{Model}
 \label{s:assumptions}
@@
 
+\subsection{Frequency of Radio Emission}
+
+%Radio emission intensity of Solar System giant planets are empirically shown to be proportional to the kinetic energy or the magnetic energy of the solar wind,  which interacts with planetary magnetic field at the magnetic standoff cross section\citep[``radio Bode's law''; ][]{desch+kaiser1984}.
+%The detail of the mechanism of energy transport from the energy source into the radio emission.
+
+%\subsection{}
+The peak of the auroral radio emission is around the cyclotron frequency, of the planetary magnetic field $f_{\rm cyc}$: 
+%In our assumption, the frequency band width is assumed to be scaled with the cyclotron frequency, $f_{\rm cyc}$: 
+%%%
+\begin{eqnarray}
+f_{\rm cyc} &=& \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \, ,
+\label{eq:cyc} \\
+B &=& \frac{\mu_0}{2\pi}\frac{\mathcal{M}}{R_p^3} \\
+&\sim & 9.1{\rm~G} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right) \left( \frac{R_p}{R_{p, J}} \right)^{-3}. 
+\end{eqnarray}
+%%%
+%where $\mathcal{M}_J = 1.56 \times 10^{27} \mbox{A m}^2$. 
+For magnetic field strengths in the vicinity of $\sim$25-50~Gauss (G),
+the cyclotron frequency will be in the range $\sim$75-150~MHz.
+
+Note that the emission is observable from ground only when the maximum frequency is larger than the plasma frequency of the Earth's ionosphere, $f_{\rm c1}\sim 10$~MHz {\it and} the maximum plasma frequency along the line of sight, $f_{\rm c2}$.
+At the favorable condition where the planet is in the near side of the spherical plane, the maximum plasma frequency corresponds to that in the vicinity of the planet, $f_{\rm plasma}$. Therefore, 
+%%%
+\begin{eqnarray}
+f_{\rm c2} &=& f_{\rm plasma} = \frac{1}{2\pi} \sqrt{\frac{ne^2}{\epsilon _0 m_e}} \\
+&\approx & 4{\rm~MHz} \left( \frac{\dot M}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
+\end{eqnarray}
+%%%
+
+\subsection{Flux of Radio Emission}
+
+The auroral radio flux of exoplanets observed at the Earth, $F_{\rm obs}$ can be expressed by:
+%Assuming $P_{\rm inp, J} = 2.1\times 10^{11}$ W \citep{griebmeier2007}, observed RGHJ radio emission at distance $l$ is
+%%%
+\begin{equation}
+F_{\rm obs} = \frac{P_{\rm radio}}{\Omega l^2 \Delta f}
+\end{equation}
+%%%
+where $P_{\rm radio}$ is the energy that is deposited as radio emission of considered frequency range, $\Omega $ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta f$ is frequency band width.
+
+We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, following the procedure of \citet{griebmeier2007}. 
+This is based on the empirical good correlation between the radio emission intensity of Solar System giant planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}.
+The scaling factors depend on the properties of the stellar wind and the planetary magnetic field, which are examined in \S\ref{ss:mechanisms}, \S\ref{ss:stellarwind}, and \S\ref{ss:magneticfield}. 
+%The detailed mechanism of auroral radio emission is not fully understand,
+
+We assume that the solid angle of the emission is same as the Jupiter's one for all of the exoplanets.
+In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim 1.6$, $\sim $6.3, and $\sim $3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission.
+
+The band width, $\Delta f$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griebmeier2007}.
+
+%Therefore, assuming that the solid angle of emission is same for all of the planets \citep{??}, 
+%%%
+%\begin{equation}
+%F_{\rm obs} = 3.76 \cdot 10^{-14}F_{\rm J, \oplus} \left( \frac{P_{\rm radio}}{P_{\rm radio,\,J}} \right) \left( \frac{l}{100\mbox{[pc]}} \right)^{-2} \left( \frac{f_{\rm cycs}}{f_{\rm cyc,\,J}} \right)^{-1}
+%\end{equation}
+%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Mechanisms}
+\subsection{Assumptions for Radio Emission Scaling}
 \label{ss:mechanisms}
@@
 
-Radio emission intensity of Solar System giant planets are known to be proportional to the kinetic energy or the magnetic energy of the solar wind,  which interacts with planetary magnetic field at the magnetic standoff cross section\memoYF{``radio Bode's law'': cite something}.
+Although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
+observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$:
+%%%
+\begin{eqnarray}
+P_{\rm k,\,inp} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
+P_{\rm m,\,inp} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
+\end{eqnarray}
+%%%
+where $n$ and $v$ are density and velocity of stellar wind, respectively, $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point.
+In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
+It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
+Because... \memoYF{I want to justify not to consider the magnetic case.}, we assume that the radio emission is scaled with the input kinetic energy, $P_{\rm k,\,inp}$.
 
-Unfortunately, the detail of the mechanism of energy transport from the energy source into the radio emission.
+The radius of the magnetic stand-off point, $r_s$, is determined by the balance between the stellar wind pressure and the planetary magnetic pressure: 
+%%%
+\begin{eqnarray}
+m_p n v ^2 &\sim& \frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \\
+&=& \frac{1}{2\pi }\left( \frac{\mu _0}{2\pi } \frac{\mathcal{M}}{r_s^3} \right)^2 %\frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6} 
+\end{eqnarray}
+%%%
+or, 
+%%%
+\begin{equation}
+r_s \sim \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2}
+\right)^{1/6}   
+\end{equation}
+%\begin{eqnarray}
+%r_s &\sim& \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2} \right)^{1/6} \\
+%&=& 4.6 R_J \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{1/3} \left( \frac{\dot M}{\dot M_{\odot }} \right)^{-1/6} \left( \frac{v}{v_{\odot }} \right)^{-1/6}  
+%\end{eqnarray}
+%%%
 
-According to \citet{griebmeier2007} \memoYF{The following equations are quoted from the paper. Needs to elaborate. }
-\begin{enumerate}
-\item kinetic energy model
-\begin{equation}
-P_{\rm inp} \propto n v^3 r_s ^2 \label{eq:Pinp_kin}
-\end{equation}
-\item magnetic energy model:
-\begin{equation}
-P_{\rm inp} \propto v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag}
-\end{equation}
-\item CME model\\
-Not sure about CME for red giants. We don't consider?
-\item the unipolar interaction model\\
-??
-\end{enumerate}
-where $n$ and $v$ are density and velocity of stellar wind, respectively,  $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of magnetic standoff point.
+Thus, the radio emission, $P_{\rm radio}$, or equivalently the input kinetic energy, $P_{\rm k,\,inp}$, are estimated with $n$, $v$, and $\mathcal{M}$, which should be specified by assuming the properties of the stellar wind and the planetary magnetic field.
+In the following, we describe our assumptions for these properties.
+
+%Thus, 
+%r_s = \left[ \frac{\mu_0 f_0^2 \mathcal{M}}{8\pi^2 (m_p n(d) v(d)^2 + 2 n(d) k_B T)} \right]^{1/6}. 
+%\end{equation}
+%%%
+%where $\mathcal{M}$ is the planetary magnetic moment and $m_p$ is the proton mass.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Properties for Stellar Wind of RGs}
+\subsection{Assumptions for Stellar Wind}
 \label{ss:stellarwind}
@@
 
-The mass loss rate of the stellar wind can be estimated from observation \memoYF{How?}.
-For the known red giants, the values are typically $\dot M \sim 10^{-8} M_{\odot}$/yr, and can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases, significantly greater than the solar mass-loss rate $\sim 10^{-14} M_{\odot}$/yr.
-
+The stellar wind density, $n$ in equation \ref{eq:Pinp_kin} are estimated by
+%%%
+\begin{equation}
+n = \frac{\dot M}{4\pi d^2 m_p v}
+\end{equation}
+%%%
+where $\dot M$ is the mass loss rate, $d$ is the orbital distance from the star and $m_p$ is proton mass. 
+The mass loss rate of red giants are typically $\dot M \sim 10^{-8} M_{\odot}$/yr based on observation \memoYF{How?}.
+The rate can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases, significantly greater than the solar mass-loss rate $\dot M_{\odot } \sim 10^{-14} M_{\odot}$/yr.
+Therefore, we have
 %\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
-%>>>>>>> e6e562d36dff6e5bb10b57fdd066ee5edd32b496
 \begin{equation}
-\frac{\dot M}{\dot M_{\odot}} \sim 10^6
+\frac{\dot M}{\dot M_{\odot}} \sim 10^6 - 10^9
 \end{equation}
 
-The stellar wind velocity becomes smaller because of the small escape velocity (due to expanded stellar radius)\footnote{Escape velocity is $\sqrt{2GM/r}$.}.
+On the other hand, the stellar wind velocity becomes smaller because of the small escape velocity (due to expanded stellar radius)\footnote{Escape velocity is $\sqrt{2GM/r}$.}.
 Assuming that the stellar wind scales as the escape velocity, RGs with radius $R=100R_{\odot}$ have 10 times as slow stellar wind as that at the main sequence.
+\memoYF{Estimate in more detail?}
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Properties for Planetary Magnetic Field}
-\label{ss:planetarymagnetic}
+\subsection{Assumptions for Planetary Magnetic Field}
+\label{ss:magneticfield}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{It may be better to consider Cristensen's scaling, taking account of the age. But I have not followed the theory yet.}
 
@@
 
-Unlike usual hot jupiters, RGHJs are not subject to tidal lock, because the gravitational effects of their host star does not change even if the star evolves into red giants.
+Unlike usual hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
 Without no physical insights of the typical spin period, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Estimates of Radio Emission from RGHJ}
-\label{s:estimate}
+%\subsection{Cut-off frequency}
+%\label{ss:cutoff}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Estimates of frequency}
-\label{ss:frequency}
+\section{Results}
+\label{s:result}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The cyclotron frequency is
+On the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows: 
+%%%
 \begin{eqnarray}
-f_{\rm cyclotron} &=& \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \, ,
-\label{eq:cyc} \\
-B &=& \frac{\mu_0}{2\pi}\frac{\mathcal{M}}{R_p^3} \\
-&\sim & 9.1 \mbox{[G]} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right) \left( \frac{R_p}{R_{p, J}} \right)^{-3}. 
+P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2} \right)^{1/3}  \\
+&=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3}
 \end{eqnarray}
-%where $\mathcal{M}_J = 1.56 \times 10^{27} \mbox{A m}^2$. 
-For magnetic field strengths in the vicinity of $\sim$25-50~Gauss (G),
-the cyclotron frequency will be in the range $\sim$75-150~MHz.
+%%%
 
-Figure \ref{fig:f_cyclotron} shows the cyclotron frequency of the planetary magnetic field.
+Therefore, 
+%%%
+\begin{eqnarray}
+F_{\rm obs} &=& \frac{P_{\rm radio}}{\Omega l^2 f_{\rm cyclotron}} \\
+&=& P_{\rm radio,\,J} \\
+&\approx & 5\times 10^{-8} \mbox{Jy} \left( \frac{l}{100\mbox{~pc}} \right)^{-2}  \\
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{R_p}{R_{p, J}} \right)^{3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3} \\
+&\approx & 10^{-5} \mbox{Jy} \left( \frac{l}{100\mbox{~pc}} \right)^{-2}  \\
+&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{R_p}{R_{p, J}} \right)^{3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3} %\\
+%&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\
+%&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1} \left( \frac{R_p}{R_{p, J}} \right)^{3}
+\end{eqnarray}
+%%%
+Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}.
+
+%If we consider an AGB star with mass loss rate $\dot M \sim 10^{-5} M_{\odot }\mbox{/yr}~ (=10^9 \dot M_{\odot})$, then the flux goes up to $\sim 1 \mbox{~mJy}$. 
+%As the current detection limit of radio wave at $\sim 30 \mbox{~MHz}$ with Long Wavelength Array (LWA), for instance, is $\sim 1\mbox{~mJy}$ \memoYF{cite something}, this indicates that as the Sun evolves to ARB stage our Jupiter will eventually become so brilliant in radio wave that it can be detected from 100 pc away!
+%\memoYF{only if $v \sim 10^{-1} v_{\odot}$. Is this validated???}
+% <---- No, in this case f_plasma > 30 MHz
+
+Using the scaling relation of magnetic moment described in \S\ref{ss:magneticfield}, radio emission of planetary companions with varying mass and orbital distance can be estimated. 
+Figure \ref{fig:radio} shows the intensity of radio emission from RGHJs at 100 pc in the plane of companion mass and orbital distance, as well as their cyclotron frequency.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
+\begin{figure*}[bp]
+ \begin{minipage}{0.5\hsize}
   \begin{center}
-\includegraphics[width=0.7\hsize]{test_fcycrotron.eps}
+   \includegraphics[width=\hsize]{radio_emission_Mdot1e-8.eps}
   \end{center}
-\caption{Cyclotron frequency. (May be deleted eventually.)}
-\label{fig:f_cyclotron}
-\end{figure}
+ \end{minipage}
+ \begin{minipage}{0.5\hsize}
+  \begin{center}
+   \includegraphics[width=\hsize]{radio_emission_Mdot1e-5.eps}
+  \end{center} 
+ \end{minipage}
+   \caption{Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
+The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere.
+The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion.
+Bottom panel: cyclotron frequency, i.e., the frequency of radio emission.
+}
+  \label{fig:two}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The emission is observable only when the maximum frequency is larger than the plasma frequency of the surrounding stellar wind. 
-The plasma frequency is 
-\begin{eqnarray}
-f_{\rm plasma} &=& \frac{1}{2\pi} \sqrt{\frac{ne^2}{\epsilon _0 m_e}} \\
-&\approx & 4\mbox{[MHz]} \left( \frac{\dot M}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
-\end{eqnarray}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                                                                                                                               
-\begin{figure}[!h]
-\begin{center}
-\includegraphics[width=0.9\hsize]{test_observability.eps}
-\end{center}
-\caption{Where condition $f_{cyclotron}>f_{plasma}$. (May be deleted eventually.)}
-\label{fig:f_cyclotron}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Estimates of intensity}
-\label{ss:intensity}
-
-$r_s$ is determined by the balance between the magnetic pressure of planetary magnetosphere and kinetic pressure of stellar wind\footnote{Precisely, the magnetic standoff point is described by equation (9) of \citet{griebmeier2007}, which is.
-\begin{equation}
-r_s = \left[ \frac{\mu_0 f_0^2 \mathcal{M}}{8\pi^2 (m_p n(d) v(d)^2 + 2 n(d) k_B T)} \right]^{1/6}
-\end{equation}
-where $\mathcal{M}$ is the planetary magnetic moment and $m_p$ is the proton mass. 
-In the following arguments based on Dave's sketch, the second term in the denominator is ignored.
-This is valid for Solar wind where the first term is larger than the second term by 2 orders of magnitude.
-\memoYF{check!}}.
-Thus,
-\begin{equation}
-\frac{m_p n v ^2}{2} = \frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6} 
-\end{equation}
-Therefore,
-\begin{eqnarray}
-r_s &=& R_p \left( \frac{B^2}{\pi \dot M v (1/4\pi d^2)} \right)^{1/6} = R_p \left( \frac{4 B^2 d^2}{\dot M v } \right)^{1/6} \\
-&\approx & 5 R_J \left(\frac{B}{10 \mbox{[G]}}\right)^{1/3} \left(\frac{\dot M}{10^6 \dot M_{\odot}}\right)^{-1/6}\\
-&& \;\;\;\;\; \;\;\;\;\; \times \left(\frac{v}{10^{-1} v_{\odot}}\right)^{-1/6}  \left(\frac{d}{5 \mbox{[AU]}}\right)^{1/3} 
-\end{eqnarray}
-
-Therefore, the radio emission expected from kinetic energy model (equation (\ref{eq:Pinp_kin})) is 
-\begin{eqnarray}
-P_{\rm radio} &=& P_{\rm radio, J} \left(\frac{\dot M }{\dot M_{\odot }} \right) \left(\frac{v}{v_{\odot}} \right) ^2 \left(\frac{d}{5 \rm{AU}} \right) ^{-2}  \left(\frac{r_s}{r_{s, {\rm J}}} \right)^2 \\
-&=& P_{\rm radio, J} \left(\frac{\dot M }{\dot M_{\odot }} \right)^{\frac{2}{3}} \left(\frac{v}{v_{\odot}} \right) ^{\frac{5}{3}} \left(\frac{d}{5 \rm{AU}} \right) ^{-2} \left(\frac{B}{B_J} \right)^{\frac{2}{3}} \\
-&\approx& 200 P_{\rm radio, J} \left(\frac{\dot M }{10^6 \dot M_{\odot }} \right)^{\frac{2}{3}} \left(\frac{v}{10^{-1} v_{\odot}} \right) ^{\frac{5}{3}} \\
-&& \;\;\;\;\; \;\;\;\;\; \times \left(\frac{d}{5 \rm{[AU]}} \right) ^{-4/3} \left(\frac{B}{10 \mbox{[G]}} \right)^{\frac{2}{3}} \
-\end{eqnarray}
-
-\memoYF{Following arguments are based on \citep{griebmeier2007}. }
-Assuming $P_{\rm inp, J} = 2.1\times 10^{11}$ W \citep{griebmeier2007}, observed RGHJ radio emission at distance $l$ is
-\begin{eqnarray}
-P_{\rm obs} &=& \frac{P_{\rm radio}}{\Omega l^2 f_{\rm cyclotron}} \\
-&\approx & 5\times 10^{-6} \mbox{Jy} \left( \frac{P_{\rm radio}}{P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{[pc]}} \right)^{-2} \left( \frac{B}{10\mbox{[G]}} \right) ^{-1} \\
-&\approx & 10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{[pc]}} \right)^{-2} \left( \frac{B}{10\mbox{[G]}} \right) ^{-1}
-\end{eqnarray}
-where $\Omega $ is the solid angle of emission, which is assumed $\Omega = 1.6$.
-
-Figure \ref{fig:radio} shows the intensity of radio emission from RGHJs. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                                                                                                                               
-\begin{figure}[!h]
-\begin{center}
-\includegraphics[width=0.9\hsize]{test_radio.eps}
-\end{center}
-\caption{Intensity of radio emission. }
-\label{fig:radio}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
-\label{ss:offset}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion on Observability}
+\section{Discussions}
 \label{s:discussion}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Radio emission from red giants stars}
+\subsection{Intrinsic radio emission of red giants stars}
 \label{ss:RGradio}
@@
 (Jason)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
+\label{ss:offset}
 

### 2015-04-20 ms.tex
bibliography updated
comparison with canonical hot jupiters

@@
 &=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3}
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp}
 \end{eqnarray}
 %%%
+In order to compare the canonical hot jupiters and red giant hot jupiters, equation (\ref{eq:Pkinp}) can be re-normalized as 
+%%%
+\begin{eqnarray}
+P_{\rm k,\,inp} 
+&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
+&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
+&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{d}{0.05~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
+\end{eqnarray}
+%%%
+\memoYF{what is the typical wind velocity of AGB stars?}
+Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as typical hot Jupiters.
+In other words, we could search for radio signal from these stars in $50^3 = 125000$ times as large volume as the canonical hot jupiters.
 

### 2015-04-20 ms.tex
replaced d by a, l by d

--- 2015-04-16 ms.tex
@@
 \begin{equation}
-n = \frac{\dot M}{4\pi d^2 m_p v}
+n = \frac{\dot M}{4\pi a^2 m_p v}
 \end{equation}
 %%%
-where $\dot M$ is the mass loss rate, $d$ is the orbital distance from the star and $m_p$ is proton mass. 
+where $\dot M$ is the mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass. 
 The mass loss rate of red giants are typically $\dot M \sim 10^{-8} M_{\odot}$/yr based on observation \memoYF{How?}.
@@
 &=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3}
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp}
 \end{eqnarray}
 %%%
+In order to compare the canonical hot jupiters and red giant hot jupiters, equation (\ref{eq:Pkinp}) can be re-normalized as 
+%%%
+\begin{eqnarray}
+P_{\rm k,\,inp} 
+&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
+&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
+&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
+\end{eqnarray}
+%%%
+\memoYF{what is the typical wind velocity of AGB stars?}
+Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as typical hot Jupiters.
+In other words, we could search for radio signal from these stars in $50^3 = 125000$ times as large volume as the canonical hot jupiters.
 
@@
 \begin{eqnarray}
-F_{\rm obs} &=& \frac{P_{\rm radio}}{\Omega l^2 f_{\rm cyclotron}} \\
+F_{\rm obs} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
 &=& P_{\rm radio,\,J} \\
-&\approx & 5\times 10^{-8} \mbox{Jy} \left( \frac{l}{100\mbox{~pc}} \right)^{-2}  \\
+&\approx & 5\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{R_p}{R_{p, J}} \right)^{3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3} \\
-&\approx & 10^{-5} \mbox{Jy} \left( \frac{l}{100\mbox{~pc}} \right)^{-2}  \\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{R_p}{R_{p, J}} \right)^{3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
+&\approx & 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
 && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{R_p}{R_{p, J}} \right)^{3} \left( \frac{d}{5.2~\mbox{AU}} \right)^{-4/3} %\\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{R_p}{R_{p, J}} \right)^{3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} %\\
 %&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\

### 2015-04-20 ms.tex
equivalent distance for RGHJs are corrected
Changed affiliation: Project Florida -> Sum

@@
 
-\affil{$^2$Research \& Development, Project Florida Labs,
+\affil{$^2$Research \& Development, Sum Labs,
   New York, NY  10001}
@@
 Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as typical hot Jupiters.
-In other words, we could search for radio signal from these stars in $50^3 = 125000$ times as large volume as the canonical hot jupiters.
+In other words, we could search for radio signal from these stars in $(\sqrt{50})^3 = 353$ times as large volume as the canonical hot jupiters.
 

### 2015-04-20 ms.tex
Discussion about the radio brightness of giants are added

@@
 \usepackage{comment}
-\usepackage{color}
+\usepackage[dvipdfmx]{color}
+%\usepackage[dvipdfmx]{graphicx}
 
@@
 
-\affil{$^2$Research \& Development, Sum Labs,
+\affil{$^2$Research \& Development, Project Florida Labs,
   New York, NY  10001}
@@
 \memoYF{what is the typical wind velocity of AGB stars?}
-Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as typical hot Jupiters.
+Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as canonical hot Jupiters.
 In other words, we could search for radio signal from these stars in $(\sqrt{50})^3 = 353$ times as large volume as the canonical hot jupiters.
@@
 Using the scaling relation of magnetic moment described in \S\ref{ss:magneticfield}, radio emission of planetary companions with varying mass and orbital distance can be estimated. 
-Figure \ref{fig:radio} shows the intensity of radio emission from RGHJs at 100 pc in the plane of companion mass and orbital distance, as well as their cyclotron frequency.
+Figure \ref{fig:radio} shows the intensity of radio emission from RGHJs at 10~pc in the plane of companion mass and orbital distance, as well as their cyclotron frequency.
 
@@
 }
-  \label{fig:two}
+  \label{fig:radio}
 \end{figure*}
@@
 
-(Jason)
+(Jason?)
+
+In the radio range, the brightness source of the radio emission is Rayleigh-Jeans tail of the Planck function, i.e., $S_{\nu } = 2kT\nu^2/c^2$.
+Recent observations revealed that this dependence on $\nu$ ($f \propto \nu^{\alpha }$ where $\alpha $ is 2) can approximately be extended as low frequency as 1 GHz \citet{gorman2013}, presumably as a result of the wavelength dependence of the opacity (at longer wavelength we see the region further from the center of the stars) and the decreased temperature as the distance from the stars increases.
+In this paper, we simply assume that the radio emission from the red giants themselves are approximated as a black body radiation. Therefore, the flux from the giants are:
+%%%
+\begin{eqnarray}
+f_{\star } (\nu ) &=& \frac{2R_{\star }^2 k_B T \nu^2}{c^2 d^2}  \\
+&\approx & 1.4 \times 10^{-9} ~\mbox{Jy} \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2} \\
+&& \times \left( \frac{R_{\star }}{10 R_{\odot }} \right)^2 \left( \frac{T_{\star }}{10^{4}~\mbox{K}} \right) \left( \frac{\nu}{1 ~\mbox{GHz}} \right)^2 
+\end{eqnarray}
+%%%
+Therefore, for stars with $R_{\star } < 50 R_{\odot}$, companions around the stars are typically brighter than their hosts.
 

### 2015-04-24 ms.tex
Radius is assumed to be constant

@@
 In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of gaseous planets. 
-We simply use the same model as \citet{griebmeier2004}, where the density as a function of radius from the center is described as:
+First, we assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}.
+For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
 %%%%%%%%%% 
 \begin{equation}
-\rho (r) = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left( \pi \frac{r}{R_p} \right)}{\left( \pi \frac{r}{R_p} \right)} \label{eq:rho_r}
+\rho (r) = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left( \pi \frac{r}{R_p} \right)}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
 \end{equation}
 %%%%%%%%%%
-where
-%%%%%%%%%% 
-\begin{equation}
-R_p (M_p) = \frac{(\alpha M_p)^{1/3}}{1+\left( \frac{M_p}{M_{\rm max}} \right)} \label{eq:Rp}
-\end{equation}
-%%%%%%%%%%
-with $\alpha =6/1 \times 10^{-4}$ \citep{griebmeier2007}. 
 We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$.
@@
 We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htdp]
+\caption{Canonical Parameters of 2 types of hot jupiters.}
+\begin{center}
+\begin{tabular}{c|ccc} \hline \hline
+& mass & orbital distance &  spin period \\ \hline
+canonical HJ & $M_J$ & 0.05 AU & 4 days \\
+RGHJ & $M_J$ & 5 AU &  0.4 days \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:comp_HJ}
+\end{table}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%
-In order to compare the canonical hot jupiters and red giant hot jupiters, equation (\ref{eq:Pkinp}) can be re-normalized as 
+
+It would be illustrative to compare radio emission power of canonical hot jupiters and that of red giant hot jupiters.
+We adopt canonical values for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}.
+Then, equation (\ref{eq:Pkinp}) can be re-normalized as
 %%%
@@
 &\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
+&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
 &\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
-&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
+&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
+&\approx & 100 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \\
 \end{eqnarray}
@@
 \memoYF{what is the typical wind velocity of AGB stars?}
-Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as canonical hot Jupiters.
+Thus, the jupiters to the AGB stars are intrinsically 50 times as bright as canonical hot Jupiters.
 In other words, we could search for radio signal from these stars in $(\sqrt{50})^3 = 353$ times as large volume as the canonical hot jupiters.

### 2015-04-24 ms.tex
Rotation period of canonical hot jupiter is assumed to be 1/10 of our Jupiter. Radio emission is thus reduced.
F_obs => F_nu

@@
 
-The auroral radio flux of exoplanets observed at the Earth, $F_{\rm obs}$ can be expressed by:
+The auroral radio spectral flux of exoplanets observed at the Earth, $F_{\nu}$ can be expressed by:
 %Assuming $P_{\rm inp, J} = 2.1\times 10^{11}$ W \citep{griebmeier2007}, observed RGHJ radio emission at distance $l$ is
@@
 \begin{equation}
-F_{\rm obs} = \frac{P_{\rm radio}}{\Omega l^2 \Delta f}
+F_{\nu} = \frac{P_{\rm radio}}{\Omega l^2 \Delta f}
 \end{equation}
@@
 \begin{eqnarray}
-P_{\rm k,\,inp} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
-P_{\rm m,\,inp} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
+P_{\rm radio} &\propto & P_{\rm inp} \\
+P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
+P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
 \end{eqnarray}
@@
 It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
-Because... \memoYF{I want to justify not to consider the magnetic case.}, we assume that the radio emission is scaled with the input kinetic energy, $P_{\rm k,\,inp}$.
+Because... \memoYF{I want to justify not to consider the magnetic case.}, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.
 
@@
 \begin{tabular}{c|ccc} \hline \hline
-& mass & orbital distance &  spin period \\ \hline
+& mass & orbital distance &  spin period \\ 
+& $M_p$ & $a$ & $\omega $ \\ \hline
 canonical HJ & $M_J$ & 0.05 AU & 4 days \\
@@
 
-It would be illustrative to compare radio emission power of canonical hot jupiters and that of red giant hot jupiters.
+It is illustrative to compare radio emission power of canonical hot jupiters and that of red giant hot jupiters.
 We adopt canonical values for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}.
@@
 \memoYF{what is the typical wind velocity of AGB stars?}
-Thus, the jupiters to the AGB stars are intrinsically 50 times as bright as canonical hot Jupiters.
-In other words, we could search for radio signal from these stars in $(\sqrt{50})^3 = 353$ times as large volume as the canonical hot jupiters.
+Thus, the jupiters to the AGB stars are intrinsically 200 times as bright as canonical hot Jupiters.
+In other words, we could search for radio signal from these stars in $(\sqrt{200})^3 \approx 3000$ times as large volume as the canonical hot jupiters.
 
-Therefore, 
+We now turn to the energy distribution of 
 %%%
 \begin{eqnarray}
-F_{\rm obs} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
+F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
 &=& P_{\rm radio,\,J} \\

### 2015-04-24 ms.tex
Rp dependence of F_nu is omitted.

@@
 
-We now turn to the energy distribution of 
+We now turn to the spectral radio flux observed at the Earth. 
 %%%
@@
 F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
-&=& P_{\rm radio,\,J} \\
+%&=& P_{\rm radio,\,J} \\
 &\approx & 5\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{R_p}{R_{p, J}} \right)^{3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3}  \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
 &\approx & 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
 && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{R_p}{R_{p, J}} \right)^{3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} %\\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} %\\
 %&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\

### 2015-04-24 ms.tex
P_radio and F_nu are nomalized at 5AU, not 5.2AU.

@@
 P_{\rm k,\,inp} 
-&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
-&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
+&\approx & 230 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \\
+&\approx & 2.3 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
+&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \\
 &\approx & 100 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{2/3} \\
@@
 %&=& P_{\rm radio,\,J} \\
-&\approx & 5\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
+&\approx & 5.3\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3}  \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
-&\approx & 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \\
+&\approx & 1.0 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
 && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} %\\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} %\\
 %&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\

### 2015-04-24 ms.tex
figure replaced

--- 2015-04-24 ms.tex
@@
 \begin{eqnarray}
-f_{\rm cyc} &=& \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \, ,
+f_{\rm cyc} &=& \frac{eB}{2\pi m_e} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \, ,
 \label{eq:cyc} \\
@@
 
-Note that the emission is observable from ground only when the maximum frequency is larger than the plasma frequency of the Earth's ionosphere, $f_{\rm c1}\sim 10$~MHz {\it and} the maximum plasma frequency along the line of sight, $f_{\rm c2}$.
+Note that the emission is observable from ground only when the maximum frequency is larger than the plasma frequency of the Earth's ionosphere,
+%%%
+\begin{equation}
+f_{\rm c1}\sim 10~\mbox{MHz}
+\end{equation}
+%%%
+{\it and} the maximum plasma frequency along the line of sight, $f_{\rm c2}$. 
 At the favorable condition where the planet is in the near side of the spherical plane, the maximum plasma frequency corresponds to that in the vicinity of the planet, $f_{\rm plasma}$. Therefore, 
@@
 f_{\rm c2} &=& f_{\rm plasma} = \frac{1}{2\pi} \sqrt{\frac{ne^2}{\epsilon _0 m_e}} \\
-&\approx & 4{\rm~MHz} \left( \frac{\dot M}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
+&\approx & 13{\rm~MHz} \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \notag \\
+&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
 \end{eqnarray}
@@
 Unlike usual hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
-Without no physical insights of the typical spin period, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
+Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
+\memoYF{Would their spin rate become higher or lower??}
 
@@
 \begin{equation}
-\rho (r) = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left( \pi \frac{r}{R_p} \right)}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
+\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
 \end{equation}
@@
 & mass & orbital distance &  spin period \\ 
-& $M_p$ & $a$ & $\omega $ \\ \hline
+& $M_p$ & $a$ &  \\ \hline
 canonical HJ & $M_J$ & 0.05 AU & 4 days \\
@@
 P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2} \right)^{1/3}  \\
-&=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp}
+&=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
 \end{eqnarray}
@@
 P_{\rm k,\,inp} 
-&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
-&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
-&\approx & 100 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{2/3} \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \\
+&\approx & 230 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
+&\approx & 2.3 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
+&\approx & 100 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} 
 \end{eqnarray}
@@
 %&=& P_{\rm radio,\,J} \\
-&\approx & 5\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
+&\approx & 5.4\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3}  \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
-&\approx & 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
-&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} %\\
+&\approx & 1.0 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} 
+%\\
 %&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\
@@
   \begin{center}
-   \includegraphics[width=\hsize]{radio_emission_Mdot1e-8.eps}
+   \includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.eps}
   \end{center}
@@
   \begin{center}
-   \includegraphics[width=\hsize]{radio_emission_Mdot1e-5.eps}
+   \includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.eps}
   \end{center} 

### 2015-04-24 ms.tex
compare F_nu of RGHJs with F_nu of canonical HJs

@@
 \begin{eqnarray}
-f_{\rm cyc} &=& \frac{eB}{2\pi m_e} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \, ,
+f_{\rm cyc} &=& \frac{eB}{2\pi m_e} \approx 25.4 {\rm~MHz} \left( \frac{B}{9.1 \rm~G} \right) \, ,
 \label{eq:cyc} \\
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htdp]
-\caption{Canonical Parameters of 2 types of hot jupiters.}
-\begin{center}
-\begin{tabular}{c|ccc} \hline \hline
-& mass & orbital distance &  spin period \\ 
-& $M_p$ & $a$ &  \\ \hline
-canonical HJ & $M_J$ & 0.05 AU & 4 days \\
-RGHJ & $M_J$ & 5 AU &  0.4 days \\ \hline
-\end{tabular}
-\end{center}
-\label{tab:comp_HJ}
-\end{table}%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{s:result}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Estimate of Radio emission of RGHJs in comparison with canonical HJs}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We now turn to the spectral radio flux observed at the Earth. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htdp]
+\caption{Canonical Parameters of 2 types of hot jupiters.}
+\begin{center}
+\begin{tabular}{c|ccc} \hline \hline
+& mass & orbital distance &  spin period \\ 
+& $M_p$ & $a$ &  \\ \hline
+canonical HJ & $M_J$ & 0.05 AU & 4 days \\
+RGHJ & $M_J$ & 5 AU &  0.4 days \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:comp_HJ}
+\end{table}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%If we consider an AGB star with mass loss rate $\dot M \sim 10^{-5} M_{\odot }\mbox{/yr}~ (=10^9 \dot M_{\odot})$, then the flux goes up to $\sim 1 \mbox{~mJy}$. 
+%As the current detection limit of radio wave at $\sim 30 \mbox{~MHz}$ with Long Wavelength Array (LWA), for instance, is $\sim 1\mbox{~mJy}$ \memoYF{cite something}, this indicates that as the Sun evolves to ARB stage our Jupiter will eventually become so brilliant in radio wave that it can be detected from 100 pc away!
+%\memoYF{only if $v \sim 10^{-1} v_{\odot}$. Is this validated???}
+% <---- No, in this case f_plasma > 30 MHz
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Observable spectral radio emission of RGHJs with varying mass and orbital distance}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We now turn to the spectral radio flux observed at the Earth: 
 %%%
@@
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+%%%
 &\approx & 1.0 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} 
+&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
+%%%
+&\approx & 1.0 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
+%%%
+&\approx & 4.6 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&&\times \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs}
 %\\
@@
 Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}. 
+\memoYF{Spectral radio flux decreases as the magnetic moment increases. Is this true?}
 
-%If we consider an AGB star with mass loss rate $\dot M \sim 10^{-5} M_{\odot }\mbox{/yr}~ (=10^9 \dot M_{\odot})$, then the flux goes up to $\sim 1 \mbox{~mJy}$. 
-%As the current detection limit of radio wave at $\sim 30 \mbox{~MHz}$ with Long Wavelength Array (LWA), for instance, is $\sim 1\mbox{~mJy}$ \memoYF{cite something}, this indicates that as the Sun evolves to ARB stage our Jupiter will eventually become so brilliant in radio wave that it can be detected from 100 pc away!
-%\memoYF{only if $v \sim 10^{-1} v_{\odot}$. Is this validated???}
-% <---- No, in this case f_plasma > 30 MHz
+Combining equation (\ref{eq:F_nu}) with the scaling relation of magnetic moment described in \S\ref{ss:magneticfield}, we estimate the spectral radio flux of planetary companions with varying masses and orbital distances as shown in Figure \ref{fig:radio}.
+Here we assumed that the target system is located at a distance of 10~pc from the Earth.
+The flux can be scaled by the distance as explicitly written in equation (\ref{eq:F_nu}).
 
-Using the scaling relation of magnetic moment described in \S\ref{ss:magneticfield}, radio emission of planetary companions with varying mass and orbital distance can be estimated. 
-Figure \ref{fig:radio} shows the intensity of radio emission from RGHJs at 10~pc in the plane of companion mass and orbital distance, as well as their cyclotron frequency.
+%The hashed regions are not observable due to the plasma cutoff at Earth's ionosphere (hashed region with vertical lines) and in the vicinity of companions (hashed region with horizontal lines).
+Given the stellar mass-loss rate $\dot M$ and planetary mass $M_p$, the minimum orbital distance $a$ to let radio emission escape from the target system is determined by $f_{\rm cyc} = f_{\rm plasma}$.
+Therefore,
+%%%
+%\begin{eqnarray}
+%25.4 ~\mbox{MHz} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right) &=& 12.6 ~\mbox{MHz} \left( \frac{a_{\rm min}}{5~\mbox{AU}} \right) \notag \\ 
+%&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/2} \left( \frac{v}{v_{\odot}} \right)^{-1/2} \\
+%\end{eqnarray}
+%%%
 

### 2015-05-10 ms.tex
Added memo comment. I think it would be a good idea to convert all eps figures to pdf with epstopdf.
Replaced .eps figures with .pdf figures in ms.tex

@@
 \memoYF{Would their spin rate become higher or lower??}
+\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}
 
@@
   \begin{center}
-   \includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.eps}
+   \includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
   \end{center}
@@
   \begin{center}
-   \includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.eps}
+   \includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
   \end{center} 

### 2015-05-11 ms.tex
Fixed color memos and figures.
I didn't remember which part I edited but apparently I made some change 10 days ago.

--- 2015-04-24 ms.tex
@@
 asymptotic-giant branch (AGB) where their radii and luminosities increase by orders of magnitude. 
-Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass \citet{spiegel+madhusudhan2012}.
-At the same time, they are subject to massive stellar wind, because the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991}.
+Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass \citep{spiegel+madhusudhan2012}.
+At the same time, they are subject to massive stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991}.
+The mass-loss rate can be as high as $\sim  10^{-5} M_{\odot }$/yr for AGB stars.
 \memoYF{How these values are observationally obtained?} \memoYF{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memoYF{cite more papers?}.
@@
 
-In this paper we propose the potential to detect planetary companions around evolved stars through the brightness of their radio emission. 
+In this paper we estimate the potential to detect planetary companions around evolved stars through the brightness of their radio emission. 
 The search for such emission could tell us the population of companions around evolved stars, including those were originally A or O stars.
@@
 
-The stellar wind density, $n$ in equation \ref{eq:Pinp_kin} are estimated by
+The stellar wind density, $n$ in equation (\ref{eq:Pinp_kin}) are estimated byt
 %%%
@@
 
-\memoYF{It may be better to consider Cristensen's scaling, taking account of the age. But I have not followed the theory yet.}
+In order to estimate the planetary magnetic field of general planets, we adopt simple scaling relation between the magnetic field and planetary properties. 
+Several relationships have been proposed so far by \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griebmeier2004} or \citet{christensen2010} for the summary).
+
+They are compared with numerical simulations in \citep{christensen2010}.
+We employ the following relationship \citep{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
+%%%%%%%%%% 
+\begin{equation}
+B^2 \propto \rho_c r_c^{4/3} q_c^{2/3},% \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
+\end{equation}
+%%%%%%%%%%
+where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux.
+
+In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
+In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}.
+For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
+%%%%%%%%%% 
+\begin{equation}
+\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
+\end{equation}
+%%%%%%%%%%
+We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$ \memoYF{cite something!}.
+The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
+In the case of Jupiter, $r_{c, J} = 0.85 R_{\rm J}$. 
+%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
+
+The convected heat flux $q_c$ is estimated
 
@@
 && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
 &\approx & 2.3 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
 &\approx & 100 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} 
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
 \end{eqnarray}
@@
 \memoYF{what is the typical wind velocity of AGB stars?}
-Thus, the jupiters to the AGB stars are intrinsically 200 times as bright as canonical hot Jupiters.
+
+%Thus, the jupiters to the AGB stars are intrinsically 200 times as bright as canonical hot Jupiters.
 In other words, we could search for radio signal from these stars in $(\sqrt{200})^3 \approx 3000$ times as large volume as the canonical hot jupiters.
@@
 &&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
 %%%
@@
 && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
 %%%
@@
 && \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
 %%%
@@
 &&\times \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs}
+&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
 %\\
@@
 
-Combining equation (\ref{eq:F_nu}) with the scaling relation of magnetic moment described in \S\ref{ss:magneticfield}, we estimate the spectral radio flux of planetary companions with varying masses and orbital distances as shown in Figure \ref{fig:radio}.
+Combining equation (\ref{eq:F_nu})-(\ref{eq:F_nu_RGHJs}) with the scaling relation of magnetic moment described in \S\ref{ss:magneticfield}, we estimate the spectral radio flux of planetary companions with varying masses and orbital distances as shown in Figure \ref{fig:radio}.
 Here we assumed that the target system is located at a distance of 10~pc from the Earth.
@@
 \newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+\label{sec:conc}
+
+\vspace{0.5in}
+
+%\acknowledgements
+
+{\sc Acknowledgments}
+
+We thank many people for useful discussions, in particular Tony
+Mroczkowzki.  DSS gratefully acknowledges support from a fellowship
+from the AMIAS group.  NM acknowledges support from [???].
+
+%\newpage
+
+%mehrdad
+
+%\newpage
+
+\bibliography{biblio.bib}
+
+\clearpage
+
+%\end{document}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Assumptions for Planetary Magnetic Field}
+\label{ss:magneticfield}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-\label{sec:conc}
+\memoYF{It may be better to consider Cristensen's scaling, taking account of the age. But I have not followed the theory yet.}
 
-\vspace{0.5in}
+Theoretically, the magnetic moment of gaseous planets are expressed with the following scaling relationship \citep{griebmeier2004}:
+%%%%%%%%%% 
+\begin{equation}
+\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
+\end{equation}
+%%%%%%%%%%
+where $\omega $ is the spin angular velocity, $\rho _c$, $r_c$ and $\sigma $ are the density, the radius, and the conductivity of the ``dynamo region'' where the density is high enough for hydrogen to be metallic, respectively.
+The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$.
+In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}.
+\memoYF{validity?}
 
-%\acknowledgements
+Unlike usual hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
+Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
+\memoYF{Would their spin rate become higher or lower??}
 
-{\sc Acknowledgments}
-
-We thank many people for useful discussions, in particular Tony
-Mroczkowzki.  DSS gratefully acknowledges support from a fellowship
-from the AMIAS group.  NM acknowledges support from [???].
-
-\newpage
-
-mehrdad
-
-\newpage
-
-\bibliography{biblio.bib}
-
-\clearpage
+In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of gaseous planets. 
+First, we assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}.
+For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
+%%%%%%%%%% 
+\begin{equation}
+\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
+\end{equation}
+%%%%%%%%%%
+We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$.
+The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
+We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
 

### 2015-05-16 ms.tex
Changed back to latex, with .eps figures.
planetary magnetic field is now estimated based on Christensen 2010

@@
 \usepackage{comment}
-\usepackage[dvipdfmx]{color}
+\usepackage{color}
+%\usepackage[dvipdfmx]{color}
 %\usepackage[dvipdfmx]{graphicx}
@@
 %%%%%%%%%%
-where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux.
+where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region.
 
@@
 The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
-In the case of Jupiter, $r_{c, J} = 0.85 R_{\rm J}$. 
+In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$. 
 %We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
 
-The convected heat flux $q_c$ is estimated
+The convected heat flux $q_c$ is estimated from the numerical simulation of \citep[e.g.][]{burrows_et_al2001,marley2007}. 
+According to \citet{burrows_et_al2001}, the luminosity scale with time as
+%%%%%%%%%%
+\begin{equation}
+L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
+\label{eq:burrowsLum}
+\end{equation}
+%%%%%%%%%%
+\memoYF{Burrows et al. 2001 implies $10^{-9} L_\odot $, but looks to me like it is actually $10^{-8} L_\odot $}. 
+We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$. 
+The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}, which is used for the scaling of planetary magnetic fields.
 
-Theoretically, the magnetic moment of gaseous planets are expressed with the following scaling relationship \citep{griebmeier2004}:
+There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
+In particular, \citet{griebmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
 %%%%%%%%%% 
@@
 %%%%%%%%%%
-where $\omega $ is the spin angular velocity, $\rho _c$, $r_c$ and $\sigma $ are the density, the radius, and the conductivity of the ``dynamo region'' where the density is high enough for hydrogen to be metallic, respectively.
+where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
 The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
-In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}.
-\memoYF{validity?}
-
-Unlike usual hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
+%In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}
+%
+Unlike usual hot jupiters, RGHJsEst are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
 Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
 \memoYF{Would their spin rate become higher or lower??}
-
-In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of gaseous planets. 
-First, we assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}.
-For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
-%%%%%%%%%% 
-\begin{equation}
-\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
-\end{equation}
-%%%%%%%%%%
-We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$.
-The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
-We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
+\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Estimate of Planetary Magnetic Field}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[bp]
+   \plotonesc{contour_B.pdf}
+   \caption{Planetary magnetic field as a function of age and planetary mass, based on \citet{christensen2010}. }
+  \label{fig:radio}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{figure*}[bp]
- \begin{minipage}{0.5\hsize}
-  \begin{center}
-   \includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.eps}
-  \end{center}
- \end{minipage}
- \begin{minipage}{0.5\hsize}
-  \begin{center}
-   \includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.eps}
-  \end{center} 
- \end{minipage}
+ %\begin{minipage}{0.5\hsize}
+  %\begin{center}
+   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-8_constRp.pdf}
+  %\end{center}
+ %\end{minipage}
+ %\begin{minipage}{0.5\hsize}
+   %\begin{center}
+   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-5_constRp.pdf}
+  %\end{center} 
+ %\end{minipage}
    \caption{Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
@@
 \label{sec:conc}
+
+In this paper, we propose that ``hot Jupiters'' around evolved stars (RGHJ) may be bright radio wave emitters, on the assumption of the simple empirical correlation between the radio emission and the kinetic input energy.
+Due to the massive stellar wind, the input kinetic energy into magnetospheres of distant Jovian planets around red giants and AGB stars can be comparable to or by far greater than canonical hot Jupiters in close-in orbits, which could lead to the intrinsic bright radio emission.
+
+The maximum radio emission we can expect to observe is limited by the plasma cut-off frequency of the stellar wind in the vicinity of the planets. 
+For a planet with the same magnetic moment as Jupiter, the maximum radio emission from the planets which can penetrate through the surrounding plasma is $\sim 10^{-3}$ Jy or $\sim 10^{-5}$ Jy at 10 pc and 100 pc, respectively.
+This energy level would be detectable with LWA between 10~MHz abd 100~MHz or with SKA between 100~MHz and 1~GHz.
+
+The planetary magnetic moment is computed based on the simple scaling relationship given by \citep{christensen2010}.
+
+The radio emission due to the interaction between the planetary companion and the stellar wind would be brighter than the intrinsic radio emission from the host star.
+
+The candidate radio detectors sensitive to the radio emission from 10~MHz to 1~GHz are LWA are SKA. For LWA,
+
+This is above the detection limit of the
+
+Non-detection
+
+For planets around AGB stars, be
+, which provides us to
 

### 2015-05-16 ms.tex
figure is updated
description added

@@
 \begin{equation}
-B^2 \propto \rho_c r_c^{4/3} q_c^{2/3},% \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
+B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} % \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta } 
 \end{equation}
@@
 %%%%%%%%%%
-We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$ \memoYF{cite something!}.
+We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}.
 The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Estimate of Planetary Magnetic Field}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Estimate of Planetary Magnetic Field and Maximum Frequency}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s
+
+First, we estimate the strength of planetary magnetic field based on the scaling relation of equation (\ref{eq:Bscaling}) and assumptions described in \S\ref{ss:magneticfield}. 
+Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_c$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_c$), as functions of planetary mass and the age.
+Planetary magnetic field is expected to become stronger as planet becomes larger because all of $r_c$, $\rho _c$, and $q_c$ in equation (\ref{eq:Bscaling}) increase with planetary mass.
+
+The cyclotron frequency Jovian planets older than 10~Gyr typically larger than 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
+In this regime, there are a number of current and near-future radio wave detectors including UTR-2, LOFAR, LWA, and SKA.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[bp]
-   \plotonesc{contour_B.pdf}
+\begin{figure}[htbp]
+%   \plotoneh{r_c.pdf}
+%   \plotoneh{rho_c.pdf}
+   \plotoneh{model_planetaryB.pdf}
    \caption{Planetary magnetic field as a function of age and planetary mass, based on \citet{christensen2010}. }
-  \label{fig:radio}
+  \label{fig:planetaryB}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Estimate of Radio emission of RGHJs in comparison with canonical HJs}
+\subsection{Estimate of Radio Intensity of RGHJs in comparison with canonical HJs}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Assumptions for Planetary Magnetic Field}
-\label{ss:magneticfield}
+%\label{ss:magneticfield}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-05-17 ms.tex
text elaborated

@@
 %%%
-\begin{eqnarray}
-f_{\rm cyc} &=& \frac{eB}{2\pi m_e} \approx 25.4 {\rm~MHz} \left( \frac{B}{9.1 \rm~G} \right) \, ,
-\label{eq:cyc} \\
-B &=& \frac{\mu_0}{2\pi}\frac{\mathcal{M}}{R_p^3} \\
-&\sim & 9.1{\rm~G} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right) \left( \frac{R_p}{R_{p, J}} \right)^{-3}. 
-\end{eqnarray}
+\begin{equation}
+f_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:cyc} 
+%\\
+%B &=& \frac{\mu_0}{2\pi}\frac{\mathcal{M}}{R_p^3} \\
+%&\sim & 9.1{\rm~G} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right) \left( \frac{R_p}{R_{p, J}} \right)^{-3}. 
+\end{equation}
 %%%
 %where $\mathcal{M}_J = 1.56 \times 10^{27} \mbox{A m}^2$. 
-For magnetic field strengths in the vicinity of $\sim$25-50~Gauss (G),
-the cyclotron frequency will be in the range $\sim$75-150~MHz.
+%For magnetic field strengths in the vicinity of $\sim$25-50~Gauss (G),
+%the cyclotron frequency will be in the range $\sim$75-150~MHz.
 
@@
 %%%
-\begin{eqnarray}
-m_p n v ^2 &\sim& \frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \\
-&=& \frac{1}{2\pi }\left( \frac{\mu _0}{2\pi } \frac{\mathcal{M}}{r_s^3} \right)^2 %\frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6} 
-\end{eqnarray}
+\begin{equation}
+m_p n v ^2 \sim \frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6}  
+\end{equation}
 %%%
-or, 
+and therefore
 %%%
 \begin{equation}
-r_s \sim \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2}
+r_s \sim \left( \frac{B^2}{2\pi m_{\rm p}nv^2}
 \right)^{1/6}   
 \end{equation}
+%%%
 %\begin{eqnarray}
@@
 Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_c$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_c$), as functions of planetary mass and the age.
-Planetary magnetic field is expected to become stronger as planet becomes larger because all of $r_c$, $\rho _c$, and $q_c$ in equation (\ref{eq:Bscaling}) increase with planetary mass.
+Because $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
+%%%%%%%%%% 
+\begin{eqnarray}
+B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \\
+f_c &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} 
+\end{eqnarray}
+%%%%%%%%%%
+under this model.
 
-The cyclotron frequency Jovian planets older than 10~Gyr typically larger than 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
+Note that the cyclotron frequency Jovian planets older than 1~Gyr is typically larger than 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
 In this regime, there are a number of current and near-future radio wave detectors including UTR-2, LOFAR, LWA, and SKA.
@@
 
-On the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows: 
+Based on the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows: 
 %%%
 \begin{eqnarray}
-P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2} \right)^{1/3}  \\
-&=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
+P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
+&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
@@
 
-It is illustrative to compare radio emission power of canonical hot jupiters and that of red giant hot jupiters.
-We adopt canonical values for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}.
-Then, equation (\ref{eq:Pkinp}) can be re-normalized as
+Now, we compare radio emission power of canonical hot jupiters and that of red giant hot jupiters. 
+Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}. 
+Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows. 
 %%%
@@
 P_{\rm k,\,inp} 
-&\approx & 230 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
-&\approx & 2.3 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
-&\approx & 100 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx & 460 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
@@
 %%%
+Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
+Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission will be even weaker.
+\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
 \memoYF{what is the typical wind velocity of AGB stars?}
-
-%Thus, the jupiters to the AGB stars are intrinsically 200 times as bright as canonical hot Jupiters.
-In other words, we could search for radio signal from these stars in $(\sqrt{200})^3 \approx 3000$ times as large volume as the canonical hot jupiters.
 
@@
 \begin{center}
-\begin{tabular}{c|ccc} \hline \hline
-& mass & orbital distance &  spin period \\ 
-& $M_p$ & $a$ &  \\ \hline
-canonical HJ & $M_J$ & 0.05 AU & 4 days \\
-RGHJ & $M_J$ & 5 AU &  0.4 days \\ \hline
+\begin{tabular}{c|cccc} \hline \hline
+& mass & magnetic field & orbit &  spin period \\ 
+& $M_p$ & B & $a$ &  \\ \hline
+canonical HJ & $M_J$ & $B_J$ & 0.05 AU & 4 days \\
+RGHJ & $M_J$ & $B_J$ & 5 AU &  0.4 days \\ \hline
 \end{tabular}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Observable spectral radio emission of RGHJs with varying mass and orbital distance}
+%\subsection{Observable spectral radio emission of RGHJs with varying mass and orbital distance}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-We now turn to the spectral radio flux observed at the Earth: 
+Then, spectral radio flux observed at the Earth is:
 %%%
@@
 &\approx & 5.4\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
@@
 %%%
-&\approx & 1.0 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&\approx & 1.2 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
 && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
@@
 %%%
-&\approx & 1.0 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
-&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&\approx & 1.2 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
 && \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
@@
 %%%
-&\approx & 4.6 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
-&&\times \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&\approx & 2.5 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
@@
 Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}. 
-\memoYF{Spectral radio flux decreases as the magnetic moment increases. Is this true?}
+Therefore, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.
 
-Combining equation (\ref{eq:F_nu})-(\ref{eq:F_nu_RGHJs}) with the scaling relation of magnetic moment described in \S\ref{ss:magneticfield}, we estimate the spectral radio flux of planetary companions with varying masses and orbital distances as shown in Figure \ref{fig:radio}.
-Here we assumed that the target system is located at a distance of 10~pc from the Earth.
-The flux can be scaled by the distance as explicitly written in equation (\ref{eq:F_nu}).
+%Note that the spectral radio flux increases as the magnetic moment decreases.
 
-%The hashed regions are not observable due to the plasma cutoff at Earth's ionosphere (hashed region with vertical lines) and in the vicinity of companions (hashed region with horizontal lines).
-Given the stellar mass-loss rate $\dot M$ and planetary mass $M_p$, the minimum orbital distance $a$ to let radio emission escape from the target system is determined by $f_{\rm cyc} = f_{\rm plasma}$.
-Therefore,
+However, observed energy flux is limited by the plasma cut-off frequency in the vicinity of the planets. 
+This condition is:
 %%%
-%\begin{eqnarray}
-%25.4 ~\mbox{MHz} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right) &=& 12.6 ~\mbox{MHz} \left( \frac{a_{\rm min}}{5~\mbox{AU}} \right) \notag \\ 
-%&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/2} \left( \frac{v}{v_{\odot}} \right)^{-1/2} \\
+\begin{equation}
+ f_{cyc} > f_{c2}
+\end{equation} 
+%%%
+or, 
+%%%
+\begin{eqnarray}
+ \left( \frac{B}{10~\mbox{G}} \right) &>& 2.2 \left( \frac{a}{5~\mbox{AU}} \right)^{-1} \\
+ && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
+\end{eqnarray}
+%%%
+or, 
+%%%
+\begin{eqnarray}
+ \left( \frac{M_p}{M_{p,J}} \right) &> & 1.8 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
+ && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
+\end{eqnarray}
+%%%
+% 
+% \left( \frac{a}{5~\mbox{[AU]}} \right)  \\
+%&&> 2.2 \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
 %\end{eqnarray}
 %%%
+Therefore, given any orbital distance, there is a lower mass limit for a planet to be able to release the  radio wave out of the system.
+
+Substituting equation (\ref{eq:Ba_limit}) into equation (\ref{eq:F_nu_RGHJ}) leads to the maximum spectral radio flux at given orbital period:
+%%%
+\begin{eqnarray}
+F_{\nu} &<& 8 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right) \\
+&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{-1}  \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/6} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
+\end{eqnarray}
+%%%
+Since the dependence of the mass-loss rate is weak, even for evolved stars with significant mass loss rate (e.g.
+AGB stars), the upper limit of the stellar flux would not be changed by orders of magnitude.
+Thus, we may consider that the radio-brightest planetary systems at 10 pc would emit $\sim 10^{-2}$ Jy.
+
+Figure \ref{fig:radio} shows the contours of spectral radio flux of planetary companions at 4.5~Gyr with varying masses and orbital distances.
+Here we assumed that the target system is located at a distance of 10~pc from the Earth.
+The flux can be scaled by the distance as a quadratic function.
+The hashed regions indicate the parameter spaces where the radio emission from the planet cannot be observed due to the plasma cut-off frequency of the Earth's ionosphere as well as that of the target planetary system.
 
@@
 \label{ss:RGradio}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 f_{\star } (\nu ) &=& \frac{2R_{\star }^2 k_B T \nu^2}{c^2 d^2}  \\
-&\approx & 1.4 \times 10^{-9} ~\mbox{Jy} \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2} \\
+&\approx & 1.4 \times 10^{-7} ~\mbox{Jy} \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2} \\
 && \times \left( \frac{R_{\star }}{10 R_{\odot }} \right)^2 \left( \frac{T_{\star }}{10^{4}~\mbox{K}} \right) \left( \frac{\nu}{1 ~\mbox{GHz}} \right)^2 
@@
 We thank many people for useful discussions, in particular Tony
-Mroczkowzki.  DSS gratefully acknowledges support from a fellowship
+Mroczkowzki.  YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science. 
+DSS gratefully acknowledges support from a fellowship
 from the AMIAS group.  NM acknowledges support from [???].

### 2015-05-18 ms.tex
figures compared

@@
 
-The stellar wind density, $n$ in equation (\ref{eq:Pinp_kin}) are estimated byt
+The stellar wind density, $n$ in equation (\ref{eq:Pinp_kin}) is estimated by
 %%%
@@
    \plotoneh{model_planetaryB.pdf}
-   \caption{Planetary magnetic field as a function of age and planetary mass, based on \citet{christensen2010}. }
+   \caption{Planetary magnetic field as a function of age and planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of internal heat of \citet{burrows_et_al2001}.
+}
   \label{fig:planetaryB}
@@
    %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
+  %\end{center}
+ %\end{minipage}
+ %\begin{minipage}{0.5\hsize}
+   %\begin{center}
+   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-5_constRp_christensen.pdf}
+  %\end{center} 
+ %\end{minipage}
+   \caption{[{\bf New version: based on scaling relationship of Christensen 2010}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
+The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere.
+The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion.
+Bottom panel: cyclotron frequency, i.e., the frequency of radio emission.
+}
+  \label{fig:radio}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[bp]
+ %\begin{minipage}{0.5\hsize}
+  %\begin{center}
+   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
    \plotonesc{radio_emission_Mdot1e-8_constRp.pdf}
@@
  %\end{minipage}
-   \caption{Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
+   \caption{[{\bf Old version: based on scaling relationship of Sano 1993}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
 The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere.
@@
 In the radio range, the brightness source of the radio emission is Rayleigh-Jeans tail of the Planck function, i.e., $S_{\nu } = 2kT\nu^2/c^2$.
-Recent observations revealed that this dependence on $\nu$ ($f \propto \nu^{\alpha }$ where $\alpha $ is 2) can approximately be extended as low frequency as 1 GHz \citet{gorman2013}, presumably as a result of the wavelength dependence of the opacity (at longer wavelength we see the region further from the center of the stars) and the decreased temperature as the distance from the stars increases.
-In this paper, we simply assume that the radio emission from the red giants themselves are approximated as a black body radiation. Therefore, the flux from the giants are:
+Recent observations revealed that this dependence on $\nu$ ($f \propto \nu^{\alpha }$ where $\alpha $ is 2) can approximately be extended as low frequency as 1 GHz \citep{gorman2013}, presumably as a result of the wavelength dependence of the opacity (at longer wavelength we see the region further from the center of the stars) and the decreased temperature as the distance from the stars increases.
+In this paper, we simply assume that the radio emission from the red giants themselves is approximated as a black body radiation at 1000~GHz and proportional to $\nu ^2$. 
+Thus, the flux from the giants is:
 %%%
@@
 f_{\star } (\nu ) &=& \frac{2R_{\star }^2 k_B T \nu^2}{c^2 d^2}  \\
-&\approx & 1.4 \times 10^{-7} ~\mbox{Jy} \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2} \\
+&\approx & 1.4 \times 10^{-5} ~\mbox{Jy} \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2} \\
 && \times \left( \frac{R_{\star }}{10 R_{\odot }} \right)^2 \left( \frac{T_{\star }}{10^{4}~\mbox{K}} \right) \left( \frac{\nu}{1 ~\mbox{GHz}} \right)^2 
@@
 %%%
-Therefore, for stars with $R_{\star } < 50 R_{\odot}$, companions around the stars are typically brighter than their hosts.
+The brightest emission due to interaction with planetary companion would overwhelm radio emission from their host (evolved) star in the 10-100~MHz range (in the 100-1000~MHz range) if the stellar radius $R_{\star }$ is smaller than $\sim 1000R_{\odot }$ ($\sim 100R_{\odot }$).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Detectability} 
+\label{ss:detectability}
+
+Figure \ref{fig:} displays the detection limit of current and near-future radio wave detectors.
+Between 10~MHz and 100~MHz the detection limit is $\sim 10^{-3}$~Jy.
+Therefore, Jovian planets around the nearest evolved stars would be within reach.
+On the other hand, between 100~MHz and 1~GHz where the cyclotron frequency of massive Jovian planets resides, SKA potentially achieve $10^{-5}$ Jy.
+In this range, massive planetary companion as far as 100 pc away would be marginally within the scope.
+
+We estimate the population of RGHJs within 100 pc to be order of 1000, based on the photometric dataset of Hipparcos. Thus,
+
+\newpage
 
@@
 \citet{gorman2013}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Expected population of RGHJ in the observable volume}
-\label{ss:number}
-
-\newpage
 

### 2015-05-18 ms.tex
Added spiegel+burrows2012

@@
 In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
-In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}.
+In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007, spiegel+burrows2012}.
 For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
@@
    %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
-   \plotonesc{radio_emission_Mdot1e-8_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-8_constRp.eps}
   %\end{center}
@@
    %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
-   \plotonesc{radio_emission_Mdot1e-5_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-5_constRp.eps}
   %\end{center} 

### 2015-05-18 ms.tex
the order of subsections in Section 2 is changed

--- 2015-05-18 ms.tex
@@
 
-\title{Red-Giant Hot Jupiters: Brilliant Radio Emitter?}
+\title{Red-Giant Hot Jupiters: Brilliant Radio Beacons?}
 
@@
 Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass \citep{spiegel+madhusudhan2012}.
-At the same time, they are subject to massive stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991}.
+At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991}.
 The mass-loss rate can be as high as $\sim  10^{-5} M_{\odot }$/yr for AGB stars. 
-\memoYF{How these values are observationally obtained?} \memoYF{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memoYF{cite more papers?}.
+\memoYF{to Jason: how these values are observationally obtained? Suggestions for relevant references?} 
+%stellar wind \citep{suzuki2008} \memoYF{To Jason: references?}. 
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could generate bright radio emission.
@@
 In this paper we estimate the potential to detect planetary companions around evolved stars through the brightness of their radio emission. 
-The search for such emission could tell us the population of companions around evolved stars, including those were originally A or O stars.
-
-In \S2, we discuss the assumption we make in this paper. 
-\S3, we provide the estimates. 
-\S4, we examine the possible obstacles to detect radio emission from the companion, taking account of the intrinsic radio emission of the evolved stars...
+%The search for such emission could tell us the population of companions around evolved stars, including those were originally A or O stars. 
+In \S2, we describe our assumptions for the scaling of planetary radio emission, stellar wind, and planetary magnetosphere.  
+\S3 estimates spectral radio intensity from RGHJs and compare them that from canonical hot Jupiters. 
+\S4 discusses possible obstacles to detect radio emission from RGHJs, in particular the effects of intrinsic radio emission of evolved stars and the  offsetting effect of the electrons spiraling down along the planetary magnetic field.
+Observability with current and near-future instruments is also examined in \S4.
+Finally, \S5 concludes the paper with a brief summary. 
 % based on the number of targets in the observable volumes
@@
 
+Before estimating the frequency of planetary radio emission and the spectral radio intensity, we specify the property of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}, and that of planetary magnetic field in \S\ref{ss:magneticfield}.
+Then, we discuss the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Assumptions for Stellar Wind}
+\label{ss:stellarwind}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+One important factor in modeling the radio emission due to the interaction with stellar wind and the planetary magnetic field is the density and velocity of stellar wind. 
+The number density of stellar wind, $n$, can be expressed as
+%%%
+\begin{equation}
+n = \frac{\dot M}{4\pi a^2 m_p v}
+\end{equation}
+%%%
+where $\dot M$ is the mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.
+
+While the solar mass loss rate, $\dot M_{\odot }$, is $\dot M_{\odot } \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is significantly greater, typically $\dot M \sim 10^{-8} M_{\odot}$/yr based on observation \memoYF{to Jason: reference?}.
+The rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
+Therefore, we have
+%\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
+\begin{equation}
+\frac{\dot M}{\dot M_{\odot}} \sim 10^6 - 10^9
+\end{equation}
+
+On the other hand, the stellar wind velocity becomes smaller because of the small escape velocity (due to expanded stellar radius).
+%\footnote{Escape velocity is $\sqrt{2GM/r}$.}
+Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_p/R}$ ($G$ is the gravitational constant, $M_p$ is the planetary mass, and $R$ is the planetary radius), a RG with radius $R=100R_{\odot}$ has 10 times as slow stellar wind as that at the main sequence.
+\memoYF{Estimate in more detail?} Thus,
+\begin{equation}
+\frac{v}{v_{\odot}} \sim 10^{-1}
+\end{equation}
+where $v_{\odot} \sim 4.0 \times 10^5 $ km/sec.
+
+%The temperature of stellar wind of RGs is expected to be 2 orders of magnitude lower than their main sequence counterparts, mainly because the sound speed of hot corona exceeds the escape speed, i.e., hot corona cannot be confined in the stellar atmosphere \citep{suzuki2008}.
+%\begin{equation}
+%\frac{T}{T_{\odot}} \sim 10^{-2}
+%\end{equation}
+%where $T_{\odot } \sim 10^6$ K.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Assumptions for Planetary Magnetic Field}
+\label{ss:magneticfield}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to estimate the planetary magnetic field of general planets, we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.
+
+Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griebmeier2004} or \citet{christensen2010} for the summary).
+%
+They are compared with numerical simulations in \citet{christensen2010}.
+We employ the following relationship from \citet{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
+%%%%%%%%%% 
+\begin{equation}
+B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} % \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta } 
+\end{equation}
+%%%%%%%%%%
+where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region.
+
+In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
+In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, because the numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
+For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
+%%%%%%%%%% 
+\begin{equation}
+\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
+\end{equation}
+%%%%%%%%%%
+We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}.
+The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
+In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$. 
+%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
+
+The convected heat flux, $q_c$, is estimated by dividing the time-dependent net planetary luminosity by the surface area of the core region ($4\pi r_c^2$). 
+The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
+%%%%%%%%%%
+\begin{equation}
+L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
+\label{eq:burrowsLum}
+\end{equation}
+%%%%%%%%%%
+\memoYF{Burrows et al. 2001 says $10^{-9} L_\odot $, but it looks to me like it is actually $10^{-8} L_\odot $}. 
+%We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$. 
+The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}, which is used for the scaling of planetary magnetic fields.
+
+\memoYF{I am not sure if the following paragraph is needed.}
+There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
+In particular, \citet{griebmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
+%%%%%%%%%% 
+\begin{equation}
+\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
+\end{equation}
+%%%%%%%%%%
+where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
+The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
+%In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}
+%
+Unlike usual hot jupiters, RGHJsEst are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
+Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
+\memoYF{Would their spin rate become higher or lower??}
+\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Cut-off frequency}
+%\label{ss:cutoff}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Frequency of Radio Emission}
+\label{ss:model_frequency}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %\subsection{}
-The peak of the auroral radio emission is around the cyclotron frequency, of the planetary magnetic field $f_{\rm cyc}$: 
+The peak of the auroral radio emission is around the cyclotron frequency of the planetary magnetic field, $f_{\rm cyc}$: 
 %In our assumption, the frequency band width is assumed to be scaled with the cyclotron frequency, $f_{\rm cyc}$: 
@@
 \begin{equation}
-f_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:cyc} 
+f_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:cyc} 
 %\\
@@
 %%%
+where $e$ is the elementary charge ($=1.60\times10^{-19}$ C) and $m_e$ is the electron mass ($=9.10\times 10^{-31}$ kg).
+
 %where $\mathcal{M}_J = 1.56 \times 10^{27} \mbox{A m}^2$. 
@@
 
-Note that the emission is observable from ground only when the maximum frequency is larger than the plasma frequency of the Earth's ionosphere,
+Radio emission from the planet is observable from ground only when the maximum frequency is larger than the plasma frequency of Earth's ionosphere,
 %%%
@@
 {\it and} the maximum plasma frequency along the line of sight, $f_{\rm c2}$. 
-At the favorable condition where the planet is in the near side of the spherical plane, the maximum plasma frequency corresponds to that in the vicinity of the planet, $f_{\rm plasma}$. Therefore, 
+At the favorable condition where the planet is in the near side of the spherical plane, the maximum plasma frequency corresponds to that in the vicinity of the planet. Therefore, 
 %%%
 \begin{eqnarray}
-f_{\rm c2} &=& f_{\rm plasma} = \frac{1}{2\pi} \sqrt{\frac{ne^2}{\epsilon _0 m_e}} \\
-&\approx & 13{\rm~MHz} \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \notag \\
+f_{\rm c2} &=& \frac{1}{2\pi} \sqrt{\frac{ne^2}{\epsilon _0 m_e}} \\
+&=& \frac{1}{2\pi} \sqrt{\frac{\dot M }{4\pi a^2 m_p v}\frac{e^2}{\epsilon _0 m_e}} 
+\end{eqnarray}
+%%%
+where $\epsilon _0$ is the permittivity of vacuum ($=8.85$~F/m). 
+%
+Using solar mass $M_{\odot } = 1.99\times 10^{30}$~kg, solar mass-loss rate $\dot M_{\odot } = 2.0 \times 10^{-14}~M_{\odot }$/yr, and the typical velocity  of solar wind $v_{\odot }=400 $~km/sec, we scale this frequency as
+%%%
+\begin{eqnarray}
+f_{\rm c2} &\approx & 14.7{\rm~MHz} \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \notag \\
 && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Flux of Radio Emission}
+\label{ss:model_intensity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, following the procedure of \citet{griebmeier2007}. 
-This is based on the empirical good correlation between the radio emission intensity of Solar System giant planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}.
-The scaling factors depend on the properties of the stellar wind and the planetary magnetic field, which are examined in \S\ref{ss:mechanisms}, \S\ref{ss:stellarwind}, and \S\ref{ss:magneticfield}. 
-%The detailed mechanism of auroral radio emission is not fully understand,
-
-We assume that the solid angle of the emission is same as the Jupiter's one for all of the exoplanets.
-In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim 1.6$, $\sim $6.3, and $\sim $3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission.
-
-The band width, $\Delta f$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griebmeier2007}.
-
-%Therefore, assuming that the solid angle of emission is same for all of the planets \citep{??}, 
-%%%
-%\begin{equation}
-%F_{\rm obs} = 3.76 \cdot 10^{-14}F_{\rm J, \oplus} \left( \frac{P_{\rm radio}}{P_{\rm radio,\,J}} \right) \left( \frac{l}{100\mbox{[pc]}} \right)^{-2} \left( \frac{f_{\rm cycs}}{f_{\rm cyc,\,J}} \right)^{-1}
-%\end{equation}
-%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Assumptions for Radio Emission Scaling}
-\label{ss:mechanisms}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
-observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$:
+We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission with the input energy from stellar wind, in the same manner as \citet{griebmeier2007}.
+%, following the procedure of \citet{griebmeier2007}. 
+This is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
+%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
+%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
 %%%
@@
 %%%
-where $n$ and $v$ are density and velocity of stellar wind, respectively, $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point.
+where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
 In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Assumptions for Stellar Wind}
-\label{ss:stellarwind}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We assume that the solid angle of the emission is same as the Jupiter's one for all of the exoplanets.
+In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim 1.6$, $\sim $6.3, and $\sim $3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission.
 
-The stellar wind density, $n$ in equation (\ref{eq:Pinp_kin}) is estimated by
-%%%
-\begin{equation}
-n = \frac{\dot M}{4\pi a^2 m_p v}
-\end{equation}
-%%%
-where $\dot M$ is the mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass. 
-The mass loss rate of red giants are typically $\dot M \sim 10^{-8} M_{\odot}$/yr based on observation \memoYF{How?}.
-The rate can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases, significantly greater than the solar mass-loss rate $\dot M_{\odot } \sim 10^{-14} M_{\odot}$/yr.
-Therefore, we have
-%\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
-\begin{equation}
-\frac{\dot M}{\dot M_{\odot}} \sim 10^6 - 10^9
-\end{equation}
-
-On the other hand, the stellar wind velocity becomes smaller because of the small escape velocity (due to expanded stellar radius)\footnote{Escape velocity is $\sqrt{2GM/r}$.}.
-Assuming that the stellar wind scales as the escape velocity, RGs with radius $R=100R_{\odot}$ have 10 times as slow stellar wind as that at the main sequence.
-\memoYF{Estimate in more detail?}
-\begin{equation}
-\frac{v}{v_{\odot}} \sim 10^{-1}
-\end{equation}
-
-The temperature of stellar wind of RGs is expected to be 2 orders of magnitude lower than their main sequence counterparts, mainly because the sound speed of hot corona exceeds the escape speed, i.e., hot corona cannot be confined in the stellar atmosphere \citep{suzuki2008}.
-\begin{equation}
-\frac{T}{T_{\odot}} \sim 10^{-2}
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Assumptions for Planetary Magnetic Field}
-\label{ss:magneticfield}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In order to estimate the planetary magnetic field of general planets, we adopt simple scaling relation between the magnetic field and planetary properties. 
-Several relationships have been proposed so far by \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griebmeier2004} or \citet{christensen2010} for the summary).
-
-They are compared with numerical simulations in \citep{christensen2010}.
-We employ the following relationship \citep{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
-%%%%%%%%%% 
-\begin{equation}
-B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} % \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta } 
-\end{equation}
-%%%%%%%%%%
-where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region.
-
-In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
-In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}.
-For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
-%%%%%%%%%% 
-\begin{equation}
-\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
-\end{equation}
-%%%%%%%%%%
-We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}.
-The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
-In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$. 
-%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
-
-The convected heat flux $q_c$ is estimated from the numerical simulation of \citep[e.g.][]{burrows_et_al2001,marley2007}. 
-According to \citet{burrows_et_al2001}, the luminosity scale with time as
-%%%%%%%%%%
-\begin{equation}
-L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
-\label{eq:burrowsLum}
-\end{equation}
-%%%%%%%%%%
-\memoYF{Burrows et al. 2001 implies $10^{-9} L_\odot $, but looks to me like it is actually $10^{-8} L_\odot $}. 
-We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$. 
-The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}, which is used for the scaling of planetary magnetic fields.
-
-There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
-In particular, \citet{griebmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
-%%%%%%%%%% 
-\begin{equation}
-\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
-\end{equation}
-%%%%%%%%%%
-where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
-The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
-%In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}
-%
-Unlike usual hot jupiters, RGHJsEst are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
-Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
-\memoYF{Would their spin rate become higher or lower??}
-\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Cut-off frequency}
-%\label{ss:cutoff}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The band width, $\Delta f$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griebmeier2007}.
 

### 2015-05-18 ms.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Assumptions for Stellar Wind}
+\label{ss:stellarwind}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The stellar wind density, $n$ in equation (\ref{eq:Pinp_kin}) is estimated by
+%%%
+\begin{equation}
+n = \frac{\dot M}{4\pi a^2 m_p v}
+\end{equation}
+%%%
+where $\dot M$ is the mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass. 
+The mass loss rate of red giants are typically $\dot M \sim 10^{-8} M_{\odot}$/yr based on observation \memoYF{How?}.
+The rate can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases, significantly greater than the solar mass-loss rate $\dot M_{\odot } \sim 10^{-14} M_{\odot}$/yr.
+Therefore, we have
+%\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
+\begin{equation}
+\frac{\dot M}{\dot M_{\odot}} \sim 10^6 - 10^9
+\end{equation}
+
+On the other hand, the stellar wind velocity becomes smaller because of the small escape velocity (due to expanded stellar radius)\footnote{Escape velocity is $\sqrt{2GM/r}$.}.
+Assuming that the stellar wind scales as the escape velocity, RGs with radius $R=100R_{\odot}$ have 10 times as slow stellar wind as that at the main sequence.
+\memoYF{Estimate in more detail?}
+\begin{equation}
+\frac{v}{v_{\odot}} \sim 10^{-1}
+\end{equation}
+
+The temperature of stellar wind of RGs is expected to be 2 orders of magnitude lower than their main sequence counterparts, mainly because the sound speed of hot corona exceeds the escape speed, i.e., hot corona cannot be confined in the stellar atmosphere \citep{suzuki2008}.
+\begin{equation}
+\frac{T}{T_{\odot}} \sim 10^{-2}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Assumptions for Planetary Magnetic Field}
+\label{ss:magneticfield}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to estimate the planetary magnetic field of general planets, we adopt simple scaling relation between the magnetic field and planetary properties. 
+Several relationships have been proposed so far by \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griebmeier2004} or \citet{christensen2010} for the summary).
+
+They are compared with numerical simulations in \citep{christensen2010}.
+We employ the following relationship \citep{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
+%%%%%%%%%% 
+\begin{equation}
+B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} % \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta } 
+\end{equation}
+%%%%%%%%%%
+where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region.
+
+In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
+In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007, spiegel+burrows2012}.
+For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
+%%%%%%%%%% 
+\begin{equation}
+\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
+\end{equation}
+%%%%%%%%%%
+We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}.
+The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
+In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$. 
+%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
+
+The convected heat flux $q_c$ is estimated from the numerical simulation of \citep[e.g.][]{burrows_et_al2001,marley2007}. 
+According to \citet{burrows_et_al2001}, the luminosity scale with time as
+%%%%%%%%%%
+\begin{equation}
+L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
+\label{eq:burrowsLum}
+\end{equation}
+%%%%%%%%%%
+\memoYF{Burrows et al. 2001 implies $10^{-9} L_\odot $, but looks to me like it is actually $10^{-8} L_\odot $}. 
+We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$. 
+The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}, which is used for the scaling of planetary magnetic fields.
+
+There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
+In particular, \citet{griebmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
+%%%%%%%%%% 
+\begin{equation}
+\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
+\end{equation}
+%%%%%%%%%%
+where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
+The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
+%In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}
+%
+Unlike usual hot jupiters, RGHJsEst are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
+Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
+\memoYF{Would their spin rate become higher or lower??}
+\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Cut-off frequency}
+%\label{ss:cutoff}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+>>>>>>> c540a35c06ae4ad467ac103fe5b2e2b7605650a9
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}

### 2015-05-18 ms.tex
doubled sections are removed
numbers are re-checked...

--- 2015-05-18 ms.tex
@@
 
+\memoYF{In the end the number of significant decimal digits is set to 1 or 2.}
+
 Before estimating the frequency of planetary radio emission and the spectral radio intensity, we specify the property of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}, and that of planetary magnetic field in \S\ref{ss:magneticfield}.
@@
 where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
+Magnetic field of planets are estimated by scaling Jovian magnetic field $B_J \sim 10$~G by equation (\ref{eq:Bscaling}).
 
@@
 %We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$. 
-The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}, which is used for the scaling of planetary magnetic fields.
+%The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}; this leads to the Jovian magnetic field $B_J \sim $
+is used for the scaling of planetary magnetic fields.
 
@@
 Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
-\memoYF{Would their spin rate become higher or lower??}
-\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}
+%\memoYF{Would their spin rate become higher or lower??}
+%\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}
 
@@
 where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
+%
 In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
@@
 P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
-&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
+&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.20~\mbox{AU}} \right)^{-4/3}  \notag \\
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
@@
 P_{\rm k,\,inp} 
-&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
-&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
-&\approx & 460 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
@@
 %&=& P_{\rm radio,\,J} \\
-&\approx & 5.4\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 5.22\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
@@
 %%%
-&\approx & 1.2 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
@@
 %%%
-&\approx & 1.2 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 1.12 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
@@
 %%%
-&\approx & 2.5 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 2.42 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
@@
 %%%
-Since the dependence of the mass-loss rate is weak, even for evolved stars with significant mass loss rate (e.g.
+%Since the dependence of the mass-loss rate is weak, even for evolved stars with significant mass loss rate (e.g.
 AGB stars), the upper limit of the stellar flux would not be changed by orders of magnitude.
-Thus, we may consider that the radio-brightest planetary systems at 10 pc would emit $\sim 10^{-2}$ Jy.
+%Thus, we may consider that the radio-brightest planetary systems at 10 pc would emit $\sim 10^{-2}$ Jy.
 

### 2015-05-18 ms.tex
estimate for radio brightness of RGs is updated

@@
 Recent observations revealed that this dependence on $\nu$ ($f \propto \nu^{\alpha }$ where $\alpha $ is 2) can approximately be extended as low frequency as 1 GHz \citep{gorman2013}, presumably as a result of the wavelength dependence of the opacity (at longer wavelength we see the region further from the center of the stars) and the decreased temperature as the distance from the stars increases.
-In this paper, we simply assume that the radio emission from the red giants themselves is approximated as a black body radiation at 1000~GHz and proportional to $\nu ^2$. 
+In this paper, we simply assume that the radio emission from the red giants themselves is approximated as a black body radiation at 1000~GHz and proportional to $\nu ^{5/3}$. 
 Thus, the flux from the giants is:
@@
 f_{\star } (\nu ) &=& \frac{2R_{\star }^2 k_B T \nu^2}{c^2 d^2}  \\
-&\approx & 1.4 \times 10^{-5} ~\mbox{Jy} \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2} \\
-&& \times \left( \frac{R_{\star }}{10 R_{\odot }} \right)^2 \left( \frac{T_{\star }}{10^{4}~\mbox{K}} \right) \left( \frac{\nu}{1 ~\mbox{GHz}} \right)^2 
+&\approx & 1.56 \times 10^{-6} ~\mbox{Jy} \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2} \\
+&& \times \left( \frac{R_{\star }}{10 R_{\odot }} \right)^2 \left( \frac{T_{\star }}{10^{4}~\mbox{K}} \right) \left( \frac{\nu}{1~\mbox{GHz}} \right)^{5/3} 
 \end{eqnarray}
 %%%
-The brightest emission due to interaction with planetary companion would overwhelm radio emission from their host (evolved) star in the 10-100~MHz range (in the 100-1000~MHz range) if the stellar radius $R_{\star }$ is smaller than $\sim 1000R_{\odot }$ ($\sim 100R_{\odot }$).
+The brightest emission due to interaction with planetary companion to the RGB stars would therefore overwhelm the radio emission from their host stars in the 10-100~MHz range (in the 100-1000~MHz range) unless the stellar radius $R_{\star }$ is larger than $\sim 2000R_{\odot }$ ($\sim 300R_{\odot }$).
 

### 2015-05-19 ms.tex
slight edit of conclusion to clean up

@@
 \label{ss:offset}
-
-\citet{gorman2013}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The radio emission due to the interaction between the planetary companion and the stellar wind would be brighter than the intrinsic radio emission from the host star.
-
-The candidate radio detectors sensitive to the radio emission from 10~MHz to 1~GHz are LWA are SKA. For LWA,
-
-This is above the detection limit of the
-
-Non-detection
-
-For planets around AGB stars, be
-, which provides us to
+-about detectability
+-number of evolved stars within 100pc $\sim 1000$.
 

### 2015-05-20 ms.tex
references for mass-loss rate added

@@
 Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass \citep{spiegel+madhusudhan2012}.
-At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991}.
-The mass-loss rate can be as high as $\sim  10^{-5} M_{\odot }$/yr for AGB stars. 
-\memoYF{to Jason: how these values are observationally obtained? Suggestions for relevant references?} 
+At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_{\odot }$/yr to $\sim  10^{-5} M_{\odot }$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975,schild1989,vassiliadis1993,schoier2001,vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_{\odot }$/yr.
+%\memoYF{to Jason: how these values are observationally obtained? Suggestions for relevant references?} 
 %stellar wind \citep{suzuki2008} \memoYF{To Jason: references?}. 

### 2015-05-22 ms.tex
Mehrdad's draft is incorporated

@@
 
-While the solar mass loss rate, $\dot M_{\odot }$, is $\dot M_{\odot } \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is significantly greater, typically $\dot M \sim 10^{-8} M_{\odot}$/yr based on observation \memoYF{to Jason: reference?}.
-The rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
+While the solar mass loss rate, $\dot M_{\odot }$, is $\dot M_{\odot } \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is typically $\dot M \sim 10^{-8}-10^{-7} M_{\odot}$/yr, ant the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
 Therefore, we have
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
+\subsection{Back-reaction of a plasma flowing into a magnetic field}
 \label{ss:offset}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$.
+The particles make a spiral motion inside the magnetic field and partially cancel the initial field.
+The canceling field $B_c$ can be estimated as follows.
+
+A single charged particle moving perpendicular to the magnetic field moves in a circular orbit of radius 
+%%%
+\begin{equation}
+r=\frac{mv}{eB}.
+\end{equation}
+%%%
+This creates a magnetic dipole
+%%%
+\begin{equation}
+\mu = \frac{e}{2\pi r/v} \pi r^2 = \frac{1}{2} e r v.
+\end{equation}
+%%%
+The volume integral of the magnetic field generated by a single dipole $\mu$ is
+%%%
+\begin{equation}
+\int d^3{\boldsymbol r} B = \frac{8\pi}{3} \mu.
+\end{equation}
+%%%
+Hence, for a number density $n$ of these charged particles the canceling field is
+%%%
+\begin{equation}
+B_c = \frac{n(mv^2/2)}{3 B^2/8\pi}= \frac{\rho_K}{3\rho_B},
+\end{equation}
+%%%
+where $\rho_K$ and $\rho_B$ are respectively the kinetic energy density and the magnetic energy density.
+If the initial velocity is not perpendicular to the magnetic field, $v$ must everywhere be replaced by its perpendicular component.
+
+For a plasma of protons and electrons in solar wind the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.
 

### 2015-05-24 ms.tex
miscellaneous edits...

--- 2015-05-20 ms.tex
@@
 \begin{equation}
-n = \frac{\dot M}{4\pi a^2 m_p v}
+n = \frac{\dot M_{\star }}{4\pi a^2 m_p v}
 \end{equation}
 %%%
-where $\dot M$ is the mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.
+where $\dot M_{\star }$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.
 
-While the solar mass loss rate, $\dot M_{\odot }$, is $\dot M_{\odot } \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is significantly greater, typically $\dot M \sim 10^{-8} M_{\odot}$/yr based on observation \memoYF{to Jason: reference?}.
-The rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
+While the solar mass loss rate, $\dot M_{\odot }$, is $\dot M_{\odot } \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is typically $\dot M_{\star } \sim 10^{-8}-10^{-7} M_{\odot}$/yr, ant the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
 Therefore, we have
@@
 \begin{equation}
-\frac{\dot M}{\dot M_{\odot}} \sim 10^6 - 10^9
+\frac{\dot M_{\star }}{\dot M_{\odot}} \sim 10^6 - 10^9
 \end{equation}
@@
 \begin{equation}
-L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
+L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{1~M_J} \right)^{2.64} \, .
 \label{eq:burrowsLum}
@@
 f_{\rm c2} &=& \frac{1}{2\pi} \sqrt{\frac{ne^2}{\epsilon _0 m_e}} \\
-&=& \frac{1}{2\pi} \sqrt{\frac{\dot M }{4\pi a^2 m_p v}\frac{e^2}{\epsilon _0 m_e}} 
+&=& \frac{1}{2\pi} \sqrt{\frac{\dot M_{\star } }{4\pi a^2 m_p v}\frac{e^2}{\epsilon _0 m_e}} 
 \end{eqnarray}
@@
 f_{\rm c2} &\approx & 14.7{\rm~MHz} \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \notag \\
-&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
+&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
 \end{eqnarray}
@@
 \begin{equation}
-m_p n v ^2 \sim \frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6}  
+m_p n v ^2 \sim \frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \label{eq:stand-off}
 \end{equation}
@@
 r_s \sim \left( \frac{B^2}{2\pi m_{\rm p}nv^2}
-\right)^{1/6}   
+\right)^{1/6}   \label{eq:stand-off-radius}
 \end{equation}
@@
 \begin{eqnarray}
-B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \\
-f_c &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} 
+B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
+f_c &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
 \end{eqnarray}
@@
 &=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.20~\mbox{AU}} \right)^{-4/3}  \notag \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
+&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
 \end{eqnarray}
@@
 &\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
+&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
 &\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
+&& \times \left( \frac{\dot M_{\star }}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
 &\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
@@
 &&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
+&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
@@
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
+&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
@@
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
+&& \times \left( \frac{\dot M_{\star }}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
@@
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
+&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
@@
  \left( \frac{B}{10~\mbox{G}} \right) &>& 2.2 \left( \frac{a}{5~\mbox{AU}} \right)^{-1} \\
- && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
+ && \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
 \end{eqnarray}
@@
  \left( \frac{M_p}{M_{p,J}} \right) &> & 1.8 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
- && \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
+ && \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
 \end{eqnarray}
@@
 F_{\nu} &<& 8 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right) \\
-&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{-1}  \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/6} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
+&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{-1}  \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{1/6} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
 \end{eqnarray}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[bp]
+%\begin{figure*}[bp]
  %\begin{minipage}{0.5\hsize}
@@
    %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
-   \plotonesc{radio_emission_Mdot1e-8_constRp.eps}
+%   \plotonesc{radio_emission_Mdot1e-8_constRp.eps}
   %\end{center}
@@
    %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
-   \plotonesc{radio_emission_Mdot1e-5_constRp.eps}
+%   \plotonesc{radio_emission_Mdot1e-5_constRp.eps}
   %\end{center} 
  %\end{minipage}
-   \caption{[{\bf Old version: based on scaling relationship of Sano 1993}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
+%   \caption{[{\bf Old version: based on scaling relationship of Sano 1993}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
 The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere.
@@
 }
-  \label{fig:radio}
-\end{figure*}
+%  \label{fig:radio}
+%\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Observability}
+\label{s:observability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from actual red giants in the case that they have planetary companions around them.
+
+For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets \memoYF{cite something} to compute the distance.
+
+For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
+%%%
+\begin{equation}
+\dot M_{\star } \sim \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_{\star }}{M_{\odot }} \right)^{-1}
+\end{equation}
+%%%
+where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are radius, luminosity, and mass of the star. 
+The velocity of stellar wind is assumed to scale with the escape velocity, hence
+%%%
+\begin{equation}
+v \propto \sqrt{\frac{2GM_{\star }}{R_{\star }}}
+\end{equation}
+%%%
+Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity by specifying the magnetic field and orbital distance of a hypothetical planetary companion.
+Here, we consider two cases: (a) a Jupiter-twin at 5.2~AU whose cyclotron frequency is $\sim 30$~MHz, and (b) a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old at 5.2~AU whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).
+
+Figure \ref{fig:observability} displays the estimated radio intensity and the maximum frequency (i.e., cyclotron frequency) of red giants within 100~pc.  
+The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{model_planetaryB.pdf}
+   \caption{.}
+  \label{fig:observability}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{discussion about detectability}
+
+%Figure \ref{fig:} displays the detection limit of current and near-future radio wave detectors.
+Between 10~MHz and 100~MHz the detection limit is $\sim 10^{-3}$~Jy.
+Therefore, Jovian planets around the nearest evolved stars would be within reach.
+%On the other hand, between 100~MHz and 1~GHz where the cyclotron frequency of massive Jovian planets resides, SKA potentially achieve $10^{-5}$ Jy.
+In this range, massive planetary companion as far as 100 pc away would be marginally within the scope.
+%We estimate the population of RGHJs within 100 pc to be order of 1000, based on the photometric dataset of Hipparcos. Thus,
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Detectability} 
-\label{ss:detectability}
-
-Figure \ref{fig:} displays the detection limit of current and near-future radio wave detectors.
-Between 10~MHz and 100~MHz the detection limit is $\sim 10^{-3}$~Jy.
-Therefore, Jovian planets around the nearest evolved stars would be within reach.
-On the other hand, between 100~MHz and 1~GHz where the cyclotron frequency of massive Jovian planets resides, SKA potentially achieve $10^{-5}$ Jy.
-In this range, massive planetary companion as far as 100 pc away would be marginally within the scope.
-
-We estimate the population of RGHJs within 100 pc to be order of 1000, based on the photometric dataset of Hipparcos. Thus,
-
 \newpage
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
+\subsection{Back-reaction of a plasma flowing into a magnetic field}
 \label{ss:offset}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+One might expect that the plasma flowing into a magnetic field could generate the magnetic field that partially cancel the intrinsic planetary magnetic field. 
+To estimate this possibility, consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$, spiraling along the initial magnetic field. 
+%The particles make a spiral motion inside the magnetic field and partially cancel the initial field. 
+%The canceling field $B_c$ can be estimated as follows. 
+A single charged particle moving perpendicular to the magnetic field moves in a circular orbit of radius 
+%%%
+\begin{equation}
+r=\frac{mv}{eB}.
+\end{equation}
+%%%
+which creates a magnetic dipole
+%%%
+\begin{equation}
+\mu = \frac{e}{2\pi r/v} \pi r^2 = \frac{1}{2} e r v = \frac{mv^2}{2B}.
+\end{equation}
+%%%
+The volume integral of the canceling magnetic field $B_c$ generated by a single dipole $\mu$ is
+%%%
+\begin{equation}
+\int d^3{\boldsymbol r} B_c = \frac{8\pi}{3} \mu.
+\end{equation}
+%%%
+Hence, for a number density $n$ of these charged particles, the fraction of canceling field to the background magnetic field is
+%%%
+\begin{equation}
+\frac{B_c}{B} = \frac{n(mv^2/2)}{3 B^2/8\pi}= \frac{\rho_K}{3\rho_B},
+\end{equation}
+%%%
+where $\rho_K$ and $\rho_B$ are the kinetic energy density and the magnetic energy density, respectively.
+If the initial velocity is not perpendicular to the magnetic field, $v$ must everywhere be replaced by its perpendicular component.
+
+%
+At the magnetic stand-off point, 
+%%%
+\begin{equation}
+m_p n(r_s) v^2 = \frac{B(r_s)^2}{2\pi }
+\end{equation}
+%%%
+and thus $\rho_K \sim \rho _B$. When the particle spirals into the planet, the kinetic energy of the moment is
+%%%
+\begin{equation}
+\frac{mv^2}{2} \propto \frac{1}{r}
+\end{equation}
+%%%
+while magnetic pressures increases (by beaming?) by 
+%%%
+\begin{equation}
+\frac{B^2}{8\pi } \propto \frac{1}{r^6}
+\end{equation}
+%%%
+therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.
+
+%Since by definition $\rho_K/\rho_B < 1$ inside the magnetic stand-off point where the auroral emission is from, the canceling magnetic field is much smaller than the canceling magnetic field.
+
+Note that that for a plasma of protons and electrons in solar wind the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.
+\memoYF{necessary to mention?}
 
@@
 In this paper, we propose that ``hot Jupiters'' around evolved stars (RGHJ) may be bright radio wave emitters, on the assumption of the simple empirical correlation between the radio emission and the kinetic input energy.
-Due to the massive stellar wind, the input kinetic energy into magnetospheres of distant Jovian planets around red giants and AGB stars can be comparable to or by far greater than canonical hot Jupiters in close-in orbits, which could lead to the intrinsic bright radio emission.
+Massive stellar wind of red giants and AGB stars would put the kinetic energy into magnetospheres of distant Jovian planets, which could lead to the intrinsic bright radio emission, which is comparable to or by far greater than canonical hot Jupiters in close-in orbits.
 
@@
 For a planet with the same magnetic moment as Jupiter, the maximum radio emission from the planets which can penetrate through the surrounding plasma is $\sim 10^{-3}$ Jy or $\sim 10^{-5}$ Jy at 10 pc and 100 pc, respectively.
-This energy level would be detectable with LWA between 10~MHz abd 100~MHz or with SKA between 100~MHz and 1~GHz.
+\memoYF{comment on observability!!}
 
-The planetary magnetic moment is computed based on the simple scaling relationship given by \citep{christensen2010}.
+Admittedly, uncertainties exist both in the scaling of planetary magnetic field  and the scaling of radio emission of Jovian planets in relation to the input energy. 
+Alternatively, once we detect both the gravitational perturbation and radio emission of Jovian planets, these models will be contested.
+The viability of these scaling relations will be examined in the future.
 
--about detectability
--number of evolved stars within 100pc $\sim 1000$.
+%The planetary magnetic moment is computed based on the simple scaling relationship given by \citep{christensen2010}. 
+%-about detectability
+%-number of evolved stars within 100pc $\sim 1000$.
 

### 2015-05-24 ms.tex
figures of radio emission from actual M-type RGs are added

@@
 \begin{equation}
-\dot M_{\star } \sim \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_{\star }}{M_{\odot }} \right)^{-1}
+\dot M_{\star } [M_{\odot }{\rm /yr}] \sim 4 \times 10^{-13} \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_{\star }}{M_{\odot }} \right)^{-1}
 \end{equation}
@@
 Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity by specifying the magnetic field and orbital distance of a hypothetical planetary companion.
-Here, we consider two cases: (a) a Jupiter-twin at 5.2~AU whose cyclotron frequency is $\sim 30$~MHz, and (b) a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old at 5.2~AU whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).
+Here, we consider two cases: (a) a Jupiter-twin at 5~AU whose cyclotron frequency is $\sim 30$~MHz, and (b) a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old at 5~AU whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).
 
@@
 \begin{figure}[htbp]
+   \plotoneh{model_planetaryB.pdf}
    \plotoneh{model_planetaryB.pdf}

### 2015-05-24 ms.tex
eps figures are converted to pdf
figures are updated and moved.
Added memo about dumm1988, changed duplicate labels, slightly reworded Mehrdad's section.

@@
 In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from actual red giants in the case that they have planetary companions around them.
-
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets \memoYF{cite something} to compute the distance.
+\memods{Dumm1988 is not in the biblio.bib file.}
 
@@
 \begin{figure}[htbp]
-   \plotoneh{model_planetaryB.pdf}
-   \plotoneh{model_planetaryB.pdf}
+   \plotoneh{radio_1Mp_5AU.pdf}
+   \plotoneh{radio_5Mp_5AU.pdf}
    \caption{.}
@@
 
-One might expect that the plasma flowing into a magnetic field could generate the magnetic field that partially cancel the intrinsic planetary magnetic field. 
-To estimate this possibility, consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$, spiraling along the initial magnetic field. 
+One might expect that plasma flowing into a region permeated by a magnetic field would, by spiraling around the field lines, generate an opposing magnetic field that partially cancels the intrinsic planetary magnetic field.
+To estimate the strength of this effect, consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$, spiraling along the initial magnetic field.
 %The particles make a spiral motion inside the magnetic field and partially cancel the initial field. 
@@
 \frac{L}{10^{-9} L_\odot} \sim \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
-\label{eq:burrowsLum}
+\label{eq:burrowsLum_2}
 \end{equation}
@@
 \dot{M}_* = 4\pi r^2 \rho[r] v \, ,
-\label{eq:mdot
-}\end{equation}
+\label{eq:mdot}
+\end{equation}
 so $\rho[r] = \dot{M}_*/(4\pi r^2 v)$,
@@
 \begin{equation}
-\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
+\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r_2}
 \end{equation}

### 2015-05-24 ms.tex
memods -> memoDS
memoDS Question about canonical HJ separation scaling.

@@
 %%%
+\memoDS{Why scale canonical HJs distances to 5 AU?}
 Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[bp]
+ %\begin{minipage}{0.5\hsize}
+  %\begin{center}
+   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
+  %\end{center}
+ %\end{minipage}
+ %\begin{minipage}{0.5\hsize}
+   %\begin{center}
+   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-5_constRp_christensen.pdf}
+  %\end{center} 
+ %\end{minipage}
+   \caption{[{\bf New version: based on scaling relationship of Christensen 2010}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
+The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere.
+The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion.
+Bottom panel: cyclotron frequency, i.e., the frequency of radio emission.
+}
+  \label{fig:radio}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[bp]
- %\begin{minipage}{0.5\hsize}
-  %\begin{center}
-   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
-   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
-  %\end{center}
- %\end{minipage}
- %\begin{minipage}{0.5\hsize}
-   %\begin{center}
-   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
-   \plotonesc{radio_emission_Mdot1e-5_constRp_christensen.pdf}
-  %\end{center} 
- %\end{minipage}
-   \caption{[{\bf New version: based on scaling relationship of Christensen 2010}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
-The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere.
-The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion.
-Bottom panel: cyclotron frequency, i.e., the frequency of radio emission.
-}
-  \label{fig:radio}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\begin{figure*}[bp]
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tbhp]
+   \plotoneh{radio_1Mp_5AU.pdf}
+   \plotoneh{radio_5Mp_5AU.pdf}
+   \caption{.}
+  \label{fig:observability}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from actual red giants in the case that they have planetary companions around them.
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets \memoYF{cite something} to compute the distance.
-\memods{Dumm1988 is not in the biblio.bib file.}
+\memoDS{Dumm1988 is not in the biblio.bib file.}
 
@@
 The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-   \plotoneh{radio_1Mp_5AU.pdf}
-   \plotoneh{radio_5Mp_5AU.pdf}
-   \caption{.}
-  \label{fig:observability}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-05-24 ms.tex
citation of @ARTICLE{1998NewA....3..137D,

--- 2015-05-24 ms.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[bp]
+ %\begin{minipage}{0.5\hsize}
+  %\begin{center}
+   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
+  %\end{center}
+ %\end{minipage}
+ %\begin{minipage}{0.5\hsize}
+   %\begin{center}
+   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
+   \plotonesc{radio_emission_Mdot1e-5_constRp_christensen.pdf}
+  %\end{center} 
+ %\end{minipage}
+   \caption{[{\bf New version: based on scaling relationship of Christensen 2010}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
+The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere.
+The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion.
+Bottom panel: cyclotron frequency, i.e., the frequency of radio emission.
+}
+  \label{fig:radio}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %If we consider an AGB star with mass loss rate $\dot M \sim 10^{-5} M_{\odot }\mbox{/yr}~ (=10^9 \dot M_{\odot})$, then the flux goes up to $\sim 1 \mbox{~mJy}$. 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tbhp]
+   \plotoneh{radio_1Mp_5AU.pdf}
+   \plotoneh{radio_5Mp_5AU.pdf}
+   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$ and 5$M_J$ at 1 AU and 5AU.
+Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet.
+}
+  \label{fig:observability}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from actual red giants in the case that they have planetary companions around them.
 
-For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets \memoYF{cite something} to compute the distance.
+For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS} to compute thes distance.
 
@@
 The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-   \plotoneh{model_planetaryB.pdf}
-   \plotoneh{model_planetaryB.pdf}
-   \caption{.}
-  \label{fig:observability}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-05-24 ms.tex
test edit

--- 2015-05-24 ms.tex
@@
 %\usepackage[dvipdfmx]{graphicx}
+
+% test edit
 
@@
    \plotoneh{radio_5Mp_5AU.pdf}
-   \caption{.}
+   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$ and 5$M_J$ at 1 AU and 5AU.
+Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet.
+}
   \label{fig:observability}
@@
 In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from actual red giants in the case that they have planetary companions around them.
-For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets \memoYF{cite something} to compute the distance.
-\memoDS{Dumm1988 is not in the biblio.bib file.}
+For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS} to compute thes distance.
 

### 2015-05-25 ms.tex
removed test edit
Added description of counterintuitive effect to Abstract and changed .tex document layout of Abstract.

@@
 %\usepackage[dvipdfmx]{graphicx}
-
-% test edit
 
@@
 \begin{abstract}
-  Red-giant hot Jupiters are jovian planets orbiting red-giant-branch
-  or asymptotic-giant-branch (AGB) stars.  Post-main-sequence stars
-  lose mass at much higher rates than main-sequence stars.  A jovian
-  planet passing through the dense winds of its AGB host can capture
-  stellar wind in its magnetosphere.  The cyclotron frequency of
-  electrons from the stellar wind accreting onto the planet scales as
-  100~MHz~$(B/30 {\rm~Gauss})$.  Such a planet might generate a radio
-  luminosity that would be visible from kiloparsec distances.
+  Red-giant hot Jupiters (RGHJs) are jovian planets orbiting red-giant-branch or asymptotic-giant-branch (AGB) stars.
+  Post-main-sequence stars lose mass at much higher rates than main-sequence stars.
+  A jovian planet passing through the dense winds of its RGB or AGB host can capture stellar wind in its magnetosphere, leading to cyclotron emission from electrons spiraling in the magnetic field.
+  The cyclotron frequency of electrons from the stellar wind accreting onto the planet scales as 100~MHz~$(B/30 {\rm~Gauss})$.
+  Counterintuitively, a plausible toy model suggests that a stronger planetary magnetic field leads to lower spectral flux density, and might therefore make objects more challenging to observe.
+  Still, for a range of planetary and stellar parameters, a RGHJ might generate a radio luminosity that would be visible from kiloparsec distances.
 \end{abstract}

### 2015-05-25 ms.tex
typo corrected --canonical hot jupiter is set at 0.05 AU

--- 2015-05-24 ms.tex
@@
 \memoDS{Why scale canonical HJs distances to 5 AU?}
+\memoYF{??}
 Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
@@
 &\approx & 2.42 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
-&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
 && \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\

### 2015-05-25 ms.tex
Added description of counterintuitive effect to Intro and to its own subsection.

--- 2015-05-25 ms.tex
@@
 Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
-It has been known that Jupiter emits radio emission from the radiation belt and auroral region due to the acceleration of the plasmas.
-\memoYF{?}.
+It has been known that Jupiter emits radio emission from the radiation belt and auroral region due to the acceleration of the plasmas. \memoYF{?}.
 Potentially, large exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.
-Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001,griebmeier2007,noyola2014}.
+Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001, griebmeier2007, hallinan_et_al2013, noyola2014}.
 Although the search for these radio signatures are being conducted, there is no clear detection claimed so far, while some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013}. 
@@
 Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass \citep{spiegel+madhusudhan2012}.
-At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_{\odot }$/yr to $\sim  10^{-5} M_{\odot }$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975,schild1989,vassiliadis1993,schoier2001,vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_{\odot }$/yr.
+At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_{\odot }$/yr to $\sim  10^{-5} M_{\odot }$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_{\odot }$/yr.
 %\memoYF{to Jason: how these values are observationally obtained? Suggestions for relevant references?} 
@@
 In \S2, we describe our assumptions for the scaling of planetary radio emission, stellar wind, and planetary magnetosphere.
-\S3 estimates spectral radio intensity from RGHJs and compare them that from canonical hot Jupiters. 
+\S3 presents a simple estimate of the spectral radio intensity of RGHJs and compares them with what might be expected from canonical hot Jupiters.
+\S3 also describes the surprising result that, although the planetary magnetic field is crucial to the generation of radio emission at all, there might be an important region in parameter space in which planets with stronger magnetic fields are less easily observable.
 \S4 discusses possible obstacles to detect radio emission from RGHJs, in particular the effects of intrinsic radio emission of evolved stars and the offsetting effect of the electrons spiraling down along the planetary magnetic field.
@@
 \subsection{Estimate of Planetary Magnetic Field and Maximum Frequency}
+\label{ss:Bplanet}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s
@@
 \subsection{Estimate of Radio Intensity of RGHJs in comparison with canonical HJs}
+\label{ss:brightness}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Now, we compare radio emission power of canonical hot jupiters and that of red giant hot jupiters. 
+Now, we compare radio emission power of canonical hot Jupiters and that of red giant hot Jupiters.
 Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}.
@@
 
-Then, spectral radio flux observed at the Earth is:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Brighter Implies Harder to See: Greater $B$ Produces Lower $F_\nu$}
+\label{ss:counterintuitive}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Per Eq.~(\ref{eq:Pkinp}), the total emitted power scales with $B^(2/3)$.
+In detail, it is not obvious how the power spectral density scales with a planet's surface magnetic field, because the emission process involves electrons passing through a wide range of magnetic field conditions (dipolar field strength drops off as $r^{-3}$, and only in an idealized model is a planet a perfect magnetic dipole).
+Nevertheless, a reasonable ansatz is that the radio emission is spread over a range of wavelengths in an approximately scale-independent way.
+In other words, the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.
+Since $f_{\rm cyclotron}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
+Planets that are intrinsically brighter, owing to a greater magnetic field strength, probably have their emission spread out over a broader set of frequencies, and therefore have a lower flux density as measured in Janskys!
+\memoDS{Is this pointed out elsewhere in the literature?}
+
+Combining the expressions above for the dependence of radio emission on planetary magnetic field strength, we find that the radio spectral flux density observed at the Earth is:
 %%%

### 2015-05-26 ms.tex
fixed typo in B^{2/3}
Removed Tony from Acknowledgments
typo corrected. griesmeier2007a is added

@@
 stellar wind particles and particles from Io-like moons.
-Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001, griebmeier2007, hallinan_et_al2013, noyola2014}.
+Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001, griesmeier2007a, griesmeier2007b, hallinan_et_al2013, noyola2014}.
 Although the search for these radio signatures are being conducted, there is no clear detection claimed so far, while some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013}. 
@@
 \end{equation}
-where $v_{\odot} \sim 4.0 \times 10^5 $ km/sec.
+where $v_{\odot} \sim 4.0 \times 10^2 $ km/sec.
 
@@
 
-Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griebmeier2004} or \citet{christensen2010} for the summary).
+Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griesmeier2004} or \citet{christensen2010} for the summary).
 %
@@
 There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
-In particular, \citet{griebmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
+In particular, \citet{griesmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
 %%%%%%%%%% 
@@
 %
-Unlike usual hot jupiters, RGHJsEst are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
-Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr].
+Unlike canonical hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
+Without no physical insights of the typical spin rate, we could assume that of Jupiter: $\omega = 9.925$ [hr].
 %\memoYF{Would their spin rate become higher or lower??}
@@
 
-We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission with the input energy from stellar wind, in the same manner as \citet{griebmeier2007}.
+We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission with the input energy from stellar wind, in the same manner as \citet{griesmeier2007b}.
 %, following the procedure of \citet{griebmeier2007}. 
@@
 
-The band width, $\Delta f$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griebmeier2007}.
+The band width, $\Delta f$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griesmeier2007b}.
 
@@
 %%%
-\memoDS{Why scale canonical HJs distances to 5 AU?}
-\memoYF{??}
 Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
@@
 
-Per Eq.~(\ref{eq:Pkinp}), the total emitted power scales with $B^(2/3)$.
+According to Eq.~(\ref{eq:Pkinp}), the total emitted power scales with $B^{2/3}$.
 In detail, it is not obvious how the power spectral density scales with a planet's surface magnetic field, because the emission process involves electrons passing through a wide range of magnetic field conditions (dipolar field strength drops off as $r^{-3}$, and only in an idealized model is a planet a perfect magnetic dipole).
@@
 %%%
-Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}. 
+Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griesmeier2007b} \memoYF{cite original paper!}. 
 Therefore, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.
@@
 
-\memoYF{discussion about detectability}
+\memoYF{discussion about detectability... Figures 1-3 of \citet{griesmeier2007b} show $10^{-3}$ Jy limit for 10-100 MHz (LWA, LOFAR) and $10^{-5}-10^{-4}$ Jy for 100-1000 MHz (LOFAR, SKA). }
 
@@
 
-We thank many people for useful discussions, in particular Tony
-Mroczkowzki.  YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science. 
-DSS gratefully acknowledges support from a fellowship
-from the AMIAS group.  NM acknowledges support from [???].
+YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science.
+DSS gratefully acknowledges support from a fellowship from the AMIAS group.
+NM acknowledges support from [???].
 
@@
 
-Theoretically, the magnetic moment of gaseous planets are expressed with the following scaling relationship \citep{griebmeier2004}:
+Theoretically, the magnetic moment of gaseous planets are expressed with the following scaling relationship \citep{griesmeier2004}:
 %%%%%%%%%% 

### 2015-05-26 ms.tex
put end document before Dave's sketch.
Split Greater B => lower Fnu line
removed excess ()s

@@
 
-Based on the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows:
+Based on the assumption that the radio emission is proportional to the input kinetic energy (equation \ref{eq:Pinp_kin}), the scaling of the radio emission is expanded as follows:
 %%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Brighter Implies Harder to See: Greater $B$ Produces Lower $F_\nu$}
+\subsection{Brighter Implies Harder to See:\\
+Greater $B$ Produces Lower $F_\nu$}
 \label{ss:counterintuitive}
@@
 
-%\end{document}
+\end{document}
 

### 2015-05-26 ms.tex
Description of Section 4 is edited so as to be consistent with Figure 3

--- 2015-05-26 ms.tex
@@
 %%%
-Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity by specifying the magnetic field and orbital distance of a hypothetical planetary companion.
-Here, we consider two cases: (a) a Jupiter-twin at 5~AU whose cyclotron frequency is $\sim 30$~MHz, and (b) a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old at 5~AU whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).
+Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion.
+Here, we consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, and [B] a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).
 
-Figure \ref{fig:observability} displays the estimated radio intensity and the maximum frequency (i.e., cyclotron frequency) of red giants within 100~pc.  
+Figure \ref{fig:observability} displays the estimated radio intensity and the maximum frequency (i.e., cyclotron frequency) of Jupiters [A] and [B] around red giants within 100~pc. 
+Jupiters [A] and [B] are placed at 1 AU and at 5 AU for reference. 
 The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross).
+
+\memoYF{Up to where would the planet be engulfed by evolved stars? References?}
 

### 2015-05-26 ms.tex
redoing

@@
 %%%
-\begin{equation}
-r_s \sim \left( \frac{B^2}{2\pi m_{\rm p}nv^2}
-\right)^{1/6}   \label{eq:stand-off-radius}
-\end{equation}
+\begin{eqnarray}
+r_s &\sim & R_p \left( \frac{B^2}{2\pi m_{\rm p}nv^2}
+\right)^{1/6}  \\
+&=& 7.57 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_{\star }}{\dot M_{\odot }} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} 
+ \label{eq:stand-off-radius}
+\end{eqnarray}
 %%%
@@
 
-\end{document}
+%\end{document}
 

### 2015-05-29 ms.tex
Scaled magnetic stand-off radius. Converting to cgs unit except for eq.[8]
reformatting

@@
 \email{
-dave@ias.edu
+yuka.fujii@elsi.jp
 }
@@
 Although the search for these radio signatures are being conducted, there is no clear detection claimed so far, while some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013}.
-%In general, there are four proposed models for a planet to emit radio wave \citep{griebmeier2007}: 1) the magnetic energy model, 2) kinetic energy model, 3) CME model, and 4) the unipolar interaction model.
-%The search for these radio emissions from extrasolar Jovian planets has been performed.
 
-%It has been predicted that
-% fix
 When stars less than $\sim$8~$M_\sun$ evolve off the main sequence,
@@
 At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_{\odot }$/yr to $\sim  10^{-5} M_{\odot }$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_{\odot }$/yr.
-%\memoYF{to Jason: how these values are observationally obtained? Suggestions for relevant references?} 
-%stellar wind \citep{suzuki2008} \memoYF{To Jason: references?}. 
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could generate bright radio emission.
@@
 In this paper we estimate the potential to detect planetary companions around evolved stars through the brightness of their radio emission. 
-%The search for such emission could tell us the population of companions around evolved stars, including those were originally A or O stars. 
 In \S2, we describe our assumptions for the scaling of planetary radio emission, stellar wind, and planetary magnetosphere.
@@
 Finally, \S5 concludes the paper with a brief summary.
-% based on the number of targets in the observable volumes
-
-%Red giants lose their masses at a high rate, typically $\sim  10^{-5} M_{\odot }/yr $ through massive stellar wind. These stellar wind particle can
 
@@
 The number density of stellar wind, $n$, can be expressed as
-%%%
+%%%%%%%%%% 
 \begin{equation}
@@
 \end{equation}
-%%%
+%%%%%%%%%% 
 where $\dot M_{\star }$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.
@@
 Therefore, we have
-%\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
+%%%%%%%%%% 
 \begin{equation}
@@
 \end{equation}
+%%%%%%%%%%
 
@@
 Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_p/R}$ ($G$ is the gravitational constant, $M_p$ is the planetary mass, and $R$ is the planetary radius), a RG with radius $R=100R_{\odot}$ has 10 times as slow stellar wind as that at the main sequence.
-\memoYF{Estimate in more detail?} Thus,
+%\memoYF{Estimate in more detail?} 
+Thus, 
 \begin{equation}
@@
 \begin{equation}
-B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} % \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta } 
+B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
 \end{equation}
@@
 In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$.
-%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
 
@@
 \memoYF{Burrows et al. 2001 says $10^{-9} L_\odot $, but it looks to me like it is actually $10^{-8} L_\odot $}. 
-%We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$. 
-%The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}; this leads to the Jovian magnetic field $B_J \sim $
-is used for the scaling of planetary magnetic fields.
+We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$.
 
@@
 The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$.
-%In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}
+
 %
@@
 Without no physical insights of the typical spin rate, we could assume that of Jupiter: $\omega = 9.925$ [hr].
-%\memoYF{Would their spin rate become higher or lower??}
-%\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}
 
@@
 
-%Radio emission intensity of Solar System giant planets are empirically shown to be proportional to the kinetic energy or the magnetic energy of the solar wind,  which interacts with planetary magnetic field at the magnetic standoff cross section\citep[``radio Bode's law''; ][]{desch+kaiser1984}.
-%The detail of the mechanism of energy transport from the energy source into the radio emission.
-
-%\subsection{}
 The peak of the auroral radio emission is around the cyclotron frequency of the planetary magnetic field, $f_{\rm cyc}$: 
-%In our assumption, the frequency band width is assumed to be scaled with the cyclotron frequency, $f_{\rm cyc}$: 
-%%%
+%%%%%%%%%% 
 \begin{equation}
 f_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:cyc} 
-%\\
-%B &=& \frac{\mu_0}{2\pi}\frac{\mathcal{M}}{R_p^3} \\
-%&\sim & 9.1{\rm~G} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right) \left( \frac{R_p}{R_{p, J}} \right)^{-3}. 
 \end{equation}
-%%%
+%%%%%%%%%%
 where $e$ is the elementary charge ($=1.60\times10^{-19}$ C) and $m_e$ is the electron mass ($=9.10\times 10^{-31}$ kg).
 
-%where $\mathcal{M}_J = 1.56 \times 10^{27} \mbox{A m}^2$. 
-%For magnetic field strengths in the vicinity of $\sim$25-50~Gauss (G),
-%the cyclotron frequency will be in the range $\sim$75-150~MHz.
-
 Radio emission from the planet is observable from ground only when the maximum frequency is larger than the plasma frequency of Earth's ionosphere,
-%%%
+%%%%%%%%%%
 \begin{equation}
@@
 \end{equation}
-%%%
+%%%%%%%%%%
 {\it and} the maximum plasma frequency along the line of sight, $f_{\rm c2}$. 
@@
 The auroral radio spectral flux of exoplanets observed at the Earth, $F_{\nu}$ can be expressed by:
-%Assuming $P_{\rm inp, J} = 2.1\times 10^{11}$ W \citep{griebmeier2007}, observed RGHJ radio emission at distance $l$ is
 %%%
@@
 We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission with the input energy from stellar wind, in the same manner as \citet{griesmeier2007b}.
-%, following the procedure of \citet{griebmeier2007}. 
 This is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
@@
 \begin{equation}
-m_p n v ^2 \sim \frac{B^2}{2\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \label{eq:stand-off}
+m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \label{eq:stand-off}
 \end{equation}
@@
 \begin{eqnarray}
-r_s &\sim & R_p \left( \frac{B^2}{2\pi m_{\rm p}nv^2}
+r_s &\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2}
 \right)^{1/6}  \\
-&=& 7.57 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_{\star }}{\dot M_{\odot }} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} 
+&=& 42.0 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_{\star }}{\dot M_{\odot }} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
+&=& 6.16 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot }} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6} 
  \label{eq:stand-off-radius}
 \end{eqnarray}
-%%%
-%\begin{eqnarray}
-%r_s &\sim& \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2} \right)^{1/6} \\
-%&=& 4.6 R_J \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{1/3} \left( \frac{\dot M}{\dot M_{\odot }} \right)^{-1/6} \left( \frac{v}{v_{\odot }} \right)^{-1/6}  
-%\end{eqnarray}
 %%%
@@
 In the following, we describe our assumptions for these properties.
-
-%Thus, 
-%r_s = \left[ \frac{\mu_0 f_0^2 \mathcal{M}}{8\pi^2 (m_p n(d) v(d)^2 + 2 n(d) k_B T)} \right]^{1/6}. 
-%\end{equation}
-%%%
-%where $\mathcal{M}$ is the planetary magnetic moment and $m_p$ is the proton mass.
 
@@
 \begin{figure}[htbp]
-%   \plotoneh{r_c.pdf}
-%   \plotoneh{rho_c.pdf}
    \plotoneh{model_planetaryB.pdf}
@@
 Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
-Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission will be even weaker.
-\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
-\memoYF{what is the typical wind velocity of AGB stars?}
+Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be even weaker.
+%\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
 
@@
 \begin{figure*}[bp]
- %\begin{minipage}{0.5\hsize}
-  %\begin{center}
-   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
    \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
-  %\end{center}
- %\end{minipage}
- %\begin{minipage}{0.5\hsize}
-   %\begin{center}
-   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
    \plotonesc{radio_emission_Mdot1e-5_constRp_christensen.pdf}
-  %\end{center} 
- %\end{minipage}
    \caption{[{\bf New version: based on scaling relationship of Christensen 2010}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%If we consider an AGB star with mass loss rate $\dot M \sim 10^{-5} M_{\odot }\mbox{/yr}~ (=10^9 \dot M_{\odot})$, then the flux goes up to $\sim 1 \mbox{~mJy}$. 
-%As the current detection limit of radio wave at $\sim 30 \mbox{~MHz}$ with Long Wavelength Array (LWA), for instance, is $\sim 1\mbox{~mJy}$ \memoYF{cite something}, this indicates that as the Sun evolves to ARB stage our Jupiter will eventually become so brilliant in radio wave that it can be detected from 100 pc away!
-%\memoYF{only if $v \sim 10^{-1} v_{\odot}$. Is this validated???}
-% <---- No, in this case f_plasma > 30 MHz
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Observable spectral radio emission of RGHJs with varying mass and orbital distance}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
-%&=& P_{\rm radio,\,J} \\
 &\approx & 5.22\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
@@
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
-%\\
-%&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\
-%&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1} \left( \frac{R_p}{R_{p, J}} \right)^{3}
 \end{eqnarray}
@@
 Therefore, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.
-
-%Note that the spectral radio flux increases as the magnetic moment decreases.
 
@@
 %%%
-% 
-% \left( \frac{a}{5~\mbox{[AU]}} \right)  \\
-%&&> 2.2 \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
-%\end{eqnarray}
-%%%
 Therefore, given any orbital distance, there is a lower mass limit for a planet to be able to release the  radio wave out of the system.
@@
 %%%
-%Since the dependence of the mass-loss rate is weak, even for evolved stars with significant mass loss rate (e.g.
-AGB stars), the upper limit of the stellar flux would not be changed by orders of magnitude.
-%Thus, we may consider that the radio-brightest planetary systems at 10 pc would emit $\sim 10^{-2}$ Jy.
 
@@
 
-\memoYF{Up to where would the planet be engulfed by evolved stars? References?}
+%\memoYF{Up to where would the planet be engulfed by evolved stars? References?}
+%I wondered this because if planets at 1 AU would be engulfed anyway it would not be worth discussing here.
+According to e.g.
+Nordhaus and Spiegel (2013) it is the case--however, some planets may migrate inward within 1 AU after evolution.
+So it should be ok.
+In any case this is not the main point of this paper and I would leave it out.
 
 \memoYF{discussion about detectability... Figures 1-3 of \citet{griesmeier2007b} show $10^{-3}$ Jy limit for 10-100 MHz (LWA, LOFAR) and $10^{-5}-10^{-4}$ Jy for 100-1000 MHz (LOFAR, SKA). }
-
-%Figure \ref{fig:} displays the detection limit of current and near-future radio wave detectors.
-Between 10~MHz and 100~MHz the detection limit is $\sim 10^{-3}$~Jy.
-Therefore, Jovian planets around the nearest evolved stars would be within reach.
-%On the other hand, between 100~MHz and 1~GHz where the cyclotron frequency of massive Jovian planets resides, SKA potentially achieve $10^{-5}$ Jy.
-In this range, massive planetary companion as far as 100 pc away would be marginally within the scope.
-%We estimate the population of RGHJs within 100 pc to be order of 1000, based on the photometric dataset of Hipparcos. Thus,
 
@@
 To estimate the strength of this effect, consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$, spiraling along the initial magnetic field.
-%The particles make a spiral motion inside the magnetic field and partially cancel the initial field. 
-%The canceling field $B_c$ can be estimated as follows. 
 A single charged particle moving perpendicular to the magnetic field moves in a circular orbit of radius 
@@
 
-%\acknowledgements
+\acknowledgements
 
@@
 
-%\newpage
-
-%mehrdad
-
-%\newpage
-
 \bibliography{biblio.bib}

### 2015-05-31 ms.tex
reference is added

@@
 Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
-It has been known that Jupiter emits radio emission from the radiation belt and auroral region due to the acceleration of the plasmas. \memoYF{?}.
+It has been known that Jupiter emits radio emission from the radiation belt and auroral region due to cyclotron-maser instability \citep{zarka1998}.
+% due to the acceleration of the plasmas.
+\memoYF{?}.
 Potentially, large exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
@@
 
-Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griesmeier2004} or \citet{christensen2010} for the summary).
+Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} %\memoYF{check!}
+(see \citet{griesmeier2004} or \citet{christensen2010} for the summary). 
 %
 They are compared with numerical simulations in \citet{christensen2010}.
-We employ the following relationship from \citet{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
+We employ the following relationship from \citet{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space
+%\memoYF{describe in more detail}:
 %%%%%%%%%% 
@@
 %%%%%%%%%%
-We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}.
+We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006}.
 The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
-In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$.
+%In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$.
 
@@
 \begin{equation}
-L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{1~M_J} \right)^{2.64} \, .
+L \sim 10^{-8} L_\odot \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{1~M_J} \right)^{2.64} \, .
 \label{eq:burrowsLum}
@@
 %%%%%%%%%%
-\memoYF{Burrows et al. 2001 says $10^{-9} L_\odot $, but it looks to me like it is actually $10^{-8} L_\odot $}. 
-We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$.
+We estimate the convected heat flux by dividing this luminosity by the surface area of the core region, i.e., $4 \pi r_c^2$.
 
-\memoYF{I am not sure if the following paragraph is needed.}
-There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
-In particular, \citet{griesmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
+%\memoYF{I am not sure if the following paragraph is needed.}
+%There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
+%In particular, \citet{griesmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
 %%%%%%%%%% 
-\begin{equation}
-\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
-\end{equation}
+%\begin{equation}
+%\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
+%\end{equation}
 %%%%%%%%%%
-where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
-The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$.
-
+%where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
+%The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
 %
-Unlike canonical hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
+%Unlike canonical hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
 Without no physical insights of the typical spin rate, we could assume that of Jupiter: $\omega = 9.925$ [hr].
@@
 It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both.
-Because... \memoYF{I want to justify not to consider the magnetic case.}, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.
+
+In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.
+
+Magnetic field of evolved stars are not well constrained \citep{konstantinova2010}. 
+If the correlation with input magnetic energy is the case, the radio emission would be rather weaker than the Jupiter, because the magnetic field of evolved stars
 
@@
 For a planet with the same magnetic moment as Jupiter, the maximum radio emission from the planets which can penetrate through the surrounding plasma is $\sim 10^{-3}$ Jy or $\sim 10^{-5}$ Jy at 10 pc and 100 pc, respectively.
-\memoYF{comment on observability!!}
+\memoYF{comment on observability...}
 

### 2015-05-31 ms.tex
Rewrote section on plasma frequency. Minor: Also changed _{\star } to _\star and _{\odot } to _\odot

@@
 Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass \citep{spiegel+madhusudhan2012}.
-At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_{\odot }$/yr to $\sim  10^{-5} M_{\odot }$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_{\odot }$/yr.
+At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_\odot$/yr.
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could generate bright radio emission.
@@
 \begin{equation}
-n = \frac{\dot M_{\star }}{4\pi a^2 m_p v}
+n = \frac{\dot M_\star}{4\pi a^2 m_p v}
+\label{eq:n}
 \end{equation}
 %%%%%%%%%% 
-where $\dot M_{\star }$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.
+where $\dot M_\star$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.
 
-While the solar mass loss rate, $\dot M_{\odot }$, is $\dot M_{\odot } \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is typically $\dot M_{\star } \sim 10^{-8}-10^{-7} M_{\odot}$/yr, ant the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
+While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr, ant the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
 Therefore, we have
@@
 \begin{equation}
-\frac{\dot M_{\star }}{\dot M_{\odot}} \sim 10^6 - 10^9
+\frac{\dot M_\star}{\dot M_{\odot}} \sim 10^6 - 10^9
 \end{equation}
@@
 %%%%%%%%%%
-where $e$ is the elementary charge ($=1.60\times10^{-19}$ C) and $m_e$ is the electron mass ($=9.10\times 10^{-31}$ kg).
+where $e$ and $m_e$ are the charge and mass of the electron, respectively.
 
-Radio emission from the planet is observable from ground only when the maximum frequency is larger than the plasma frequency of Earth's ionosphere,
-%%%%%%%%%%
-\begin{equation}
-f_{\rm c1}\sim 10~\mbox{MHz}
-\end{equation}
-%%%%%%%%%%
-{\it and} the maximum plasma frequency along the line of sight, $f_{\rm c2}$. 
-At the favorable condition where the planet is in the near side of the spherical plane, the maximum plasma frequency corresponds to that in the vicinity of the planet. Therefore, 
+Radio emission from the planet is observable from ground only when the maximum frequency is larger than the plasma frequency of Earth's ionosphere $f_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $f_{\rm plasma}^{\rm los}$.
+The plasma frequency may be expressed as
+\begin{eqnarray}
+f_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
+ & = & 8979 {\rm~Hz} \times \left( \frac{n_e}{\rm cm^{-3}} \right)^{1/2} \, .
+\label{eq:fplasma}
+\end{eqnarray}
+In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $f_{\rm plasma}^\oplus \lsim 10$~MHz.
+At the favorable viewing condition, when the planet is on the near side of its star to the Earth, the maximum plasma frequency along the line of sight corresponds to that in the vicinity of the planet.
+Therefore, combining Eq.~(\ref{eq:n}) and Eq.~(\ref{eq:fplasma}), we have
 %%%
 \begin{eqnarray}
-f_{\rm c2} &=& \frac{1}{2\pi} \sqrt{\frac{ne^2}{\epsilon _0 m_e}} \\
-&=& \frac{1}{2\pi} \sqrt{\frac{\dot M_{\star } }{4\pi a^2 m_p v}\frac{e^2}{\epsilon _0 m_e}} 
+\label{eq:fplasmalos} f_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \cdot \frac{1}{\rm cm^{-3}} \right)^{1/2} \\
+\label{eq:fplasmalos_scaled} & = & 14.7{\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{0.1 v_{\odot}}  \right)^{-1/2} \notag \\
+ & & \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}}\right)^{1/2} \, ,
 \end{eqnarray}
 %%%
-where $\epsilon _0$ is the permittivity of vacuum ($=8.85$~F/m). 
-%
-Using solar mass $M_{\odot } = 1.99\times 10^{30}$~kg, solar mass-loss rate $\dot M_{\odot } = 2.0 \times 10^{-14}~M_{\odot }$/yr, and the typical velocity  of solar wind $v_{\odot }=400 $~km/sec, we scale this frequency as
-%%%
-\begin{eqnarray}
-f_{\rm c2} &\approx & 14.7{\rm~MHz} \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \notag \\
-&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}}\right)^{1/2} \left(\frac{v}{10^{-1} v_{\odot}}  \right)^{-1/2}
-\end{eqnarray}
-%%%
+where in Eq.~(\ref{eq:fplasmalos_scaled}) we have taken the solar mass-loss rate $\dot M_\odot$ to be $2.0 \times 10^{-14}~M_\odot$/yr and the typical solar wind velocity $v_{\odot }$ to be 400~km/sec.
 
@@
 \right)^{1/6}  \\
-&=& 42.0 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_{\star }}{\dot M_{\odot }} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
-&=& 6.16 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot }} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6} 
+&=& 42.0 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
+&=& 6.16 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6} 
  \label{eq:stand-off-radius}
@@
 &=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.20~\mbox{AU}} \right)^{-4/3}  \notag \\
-&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
+&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
 \end{eqnarray}
@@
 &\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
+&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
 &\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M_{\star }}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
+&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
 &\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
@@
 &&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
+&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
@@
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
+&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
@@
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M_{\star }}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
+&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
@@
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
+&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
@@
  \left( \frac{B}{10~\mbox{G}} \right) &>& 2.2 \left( \frac{a}{5~\mbox{AU}} \right)^{-1} \\
- && \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
+ && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
 \end{eqnarray}
@@
  \left( \frac{M_p}{M_{p,J}} \right) &> & 1.8 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
- && \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
+ && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
 \end{eqnarray}
@@
 F_{\nu} &<& 8 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right) \\
-&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{-1}  \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{1/6} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
+&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{-1}  \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/6} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
 \end{eqnarray}
@@
 \begin{equation}
-\dot M_{\star } [M_{\odot }{\rm /yr}] \sim 4 \times 10^{-13} \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_{\star }}{M_{\odot }} \right)^{-1}
+\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
 \end{equation}
@@
 \begin{equation}
-v \propto \sqrt{\frac{2GM_{\star }}{R_{\star }}}
+v \propto \sqrt{\frac{2GM_\star}{R_{\star }}}
 \end{equation}
@@
 DSS gratefully acknowledges support from a fellowship from the AMIAS group.
+We thank David Hogg for encouraging us to pursue calculations of explanetary radio emission.
 NM acknowledges support from [???].

### 2015-05-31 ms.tex
Added several memos: * Change figure to cgs * Is the section on Brighter -> Dimmer still needed?  Is it even accurate?

@@
 F_{\nu} = \frac{P_{\rm radio}}{\Omega l^2 \Delta f}
+\label{eq:Fnu}
 \end{equation}
 %%%
-where $P_{\rm radio}$ is the energy that is deposited as radio emission of considered frequency range, $\Omega $ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta f$ is frequency band width.
+where $P_{\rm radio}$ is the energy that is deposited as radio emission of considered frequency range, $\Omega $ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta f$ is frequency bandwidth.
 
@@
 
-The band width, $\Delta f$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griesmeier2007b}.
+The bandwidth, $\Delta f$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griesmeier2007b}.
 
@@
 Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_c$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_c$), as functions of planetary mass and the age.
+\memoDS{previously, we referred to $f_{\rm cyc}$.
+We should be consistent.}
 Because $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
@@
    \plotoneh{model_planetaryB.pdf}
-   \caption{Planetary magnetic field as a function of age and planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of internal heat of \citet{burrows_et_al2001}.
-}
+   \caption{Planetary magnetic field as a function of age and planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of internal heat of \citet{burrows_et_al2001}.} \memoDS{Can we change density to cgs in this figure?}
   \label{fig:planetaryB}
@@
 
+\memoDS{Is this section needed anymore, since this is already in the Griesmeier paper?
+Does the Griesmeier paper make the point explicit enough, or is this still somewhat valuable?
+Also, are we 100\% sure that this section is right?
+A planet with larger surface field achieves an equivalent field to a planet with a smaller surface field at a larger radius, and captures a larger wind flux.
+Should we think more about the spectrum?}
+
 According to Eq.~(\ref{eq:Pkinp}), the total emitted power scales with $B^{2/3}$.
@@
 Nevertheless, a reasonable ansatz is that the radio emission is spread over a range of wavelengths in an approximately scale-independent way.
-In other words, the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.
-Since $f_{\rm cyclotron}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
+In other words, the frequency bandwidth $\Delta f$ of Eq.~(\ref{eq:Fnu}) is proportional to $f_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
+This means that the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.
+Since $f_{\rm cyc}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
 Planets that are intrinsically brighter, owing to a greater magnetic field strength, probably have their emission spread out over a broader set of frequencies, and therefore have a lower flux density as measured in Janskys!

### 2015-06-01 ms.tex
cgs unit

@@
 
-While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr, ant the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
+While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr, ant the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
 Therefore, we have
@@
 Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} %\memoYF{check!}
-(see \citet{griesmeier2004} or \citet{christensen2010} for the summary). 
-%
-They are compared with numerical simulations in \citet{christensen2010}.
-We employ the following relationship from \citet{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space
+(see \citet{griesmeier2004} or \citet{christensen2010} for the summary), which are compared with numerical simulations in \citet{christensen2010}. 
+We employ the following relationship from \citet{christensen2006}, which is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space:
 %\memoYF{describe in more detail}:
@@
 %%%%%%%%%%
-We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006}.
+We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006, griesmeier2007b}.
 The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
-%In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$.
+In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$.
 
-The convected heat flux, $q_c$, is estimated by dividing the time-dependent net planetary luminosity by the surface area of the core region ($4\pi r_c^2$). 
+The scaling of convected heat flux, $q_c$, is obtained by dividing the time-dependent net planetary luminosity by the surface area of the core region i.e., $4\pi r_c^2$. 
 The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
@@
 \begin{equation}
-L \sim 10^{-8} L_\odot \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{1~M_J} \right)^{2.64} \, .
+L \sim 1.4^{-9} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
 \label{eq:burrowsLum}
@@
 %%%%%%%%%%
-We estimate the convected heat flux by dividing this luminosity by the surface area of the core region, i.e., $4 \pi r_c^2$.
+Therefore, we have
+%%%%%%%%%%
+\begin{equation}
+q_c \sim q_{c, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
+\label{eq:burrowsLum}
+\end{equation}
+%%%%%%%%%%
+%We estimate the convected heat flux by dividing this luminosity by the surface area of the core region, i.e., $4 \pi r_c^2$.
 
@@
 First, we estimate the strength of planetary magnetic field based on the scaling relation of equation (\ref{eq:Bscaling}) and assumptions described in \S\ref{ss:magneticfield}. 
-Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_c$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_c$), as functions of planetary mass and the age.
-\memoDS{previously, we referred to $f_{\rm cyc}$.
-We should be consistent.}
+Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_c$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age.
 Because $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
@@
    \plotoneh{model_planetaryB.pdf}
-   \caption{Planetary magnetic field as a function of age and planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of internal heat of \citet{burrows_et_al2001}.} \memoDS{Can we change density to cgs in this figure?}
+   \caption{Planetary magnetic field as a function of age and planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of internal heat of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
   \label{fig:planetaryB}
@@
 \memoDS{Is this pointed out elsewhere in the literature?}
+
+\newpage
 

### 2015-06-01 ms.tex
figure 1 is replaced by cgs-version figure
scaling of radius of magnetic stand-off point is updated

@@
 
-The radius of the magnetic stand-off point, $r_s$, is determined by the balance between the stellar wind pressure and the planetary magnetic pressure: 
+The radius of the magnetic stand-off point, $r_s$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
 %%%
@@
 %%%
-and therefore
+The radius obtained for Jupiter from this equality is about a half of actual radius of Magnetosphere \citep[][]{griesmeier2005}.
+We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$][]{joy2002} according to equation (\ref{eq:stand-off}), i.e.,
 %%%
 \begin{eqnarray}
-r_s &\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2}
-\right)^{1/6}  \\
-&=& 42.0 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
-&=& 6.16 R_p \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6} 
+r_s 
+%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
+&=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot a}{5.2\mbox{AU}} \right)^{-1/3}  \\
+&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
+&=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{\dot a}{5\mbox{AU}} \right)^{-1/3} \\
+&& \times \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
  \label{eq:stand-off-radius}
@@
 
-Thus, the radio emission, $P_{\rm radio}$, or equivalently the input kinetic energy, $P_{\rm k,\,inp}$, are estimated with $n$, $v$, and $\mathcal{M}$, which should be specified by assuming the properties of the stellar wind and the planetary magnetic field.
-In the following, we describe our assumptions for these properties.
+%Thus, the radio emission, $P_{\rm radio}$, or equivalently the input kinetic energy, $P_{\rm k,\,inp}$, are estimated with $n$, $v$, and $\mathcal{M}$, which should be specified by assuming the properties of the stellar wind and the planetary magnetic field.
+%In the following, we describe our assumptions for these properties.
 
@@
 \begin{figure}[htbp]
-   \plotoneh{model_planetaryB.pdf}
+   \plotoneh{model_planetaryB_cgs.pdf}
    \caption{Planetary magnetic field as a function of age and planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of internal heat of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Number of particle which is trapped by planetary magnetosphere is
+\begin{equation}
+n \propto \pi r_s^2
+\end{equation}
+
+\newpage
 

### 2015-06-01 ms.tex
scaling of radius of magnetic stand-off point is corrected
consideration of radio spectra

@@
 %&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
-&=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot a}{5.2\mbox{AU}} \right)^{-1/3}  \\
+&=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
 && \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
-&=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{\dot a}{5\mbox{AU}} \right)^{-1/3} \\
+&=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
 && \times \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
@@
 
-Number of particle which is trapped by planetary magnetosphere is
+The cyclotron frequency at radius $r$ is:
+%%%
 \begin{equation}
-n \propto \pi r_s^2
+f_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
 \end{equation}
+%%
+Therefore, 
+%%%
+\begin{equation}
+\frac{dP}{df_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
+\end{equation}
+%%%
+Employing Larmor formula, power emitted from a thin shell at $r\sim r+dr$, $dP/dr$ is 
+%%%
+\begin{equation}
+\frac{dP}{dr} \propto 4\pi r^2 N_{\rm plasma}(r) v_{\bot }^2(r) B^2(r) \label{eq:larmor}
+\end{equation}
+%%%
+where $N_{\rm plasma}(r) $ represents the number density of plasma in the planetary magnetosphere at radius $r$.
+
+We assume that $N_{\rm plasma}(r_s) $  is proportional to the squared radius of the magnetic stand-off point:
+%%%
+\begin{equation}
+N_{\rm plasma}(r_s) \propto \pi r_s^2 \;\;(\propto B_p^{2/3}) \label{eq:N0_plasma}
+\end{equation}
+%%%
+Due the the mass flux conservation,
+%%%
+\begin{equation}
+4 \pi r^2 N_{\rm plasma}(r) v_{\|} = const.
+\end{equation}
+%%%
+Combining with equation (\ref{eq:N0_plasma}),
+%%%
+\begin{equation}
+N_{\rm plasma}(r) \propto  r_s^2 \frac{v_{\|}(r)}{r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
+\end{equation}
+%%%
+
+Because the magnetic dipole moment
+%%%
+\begin{equation}
+\mu = \frac{mv_{\bot}(r)}{eB(r)}
+\end{equation}
+%%%
+is approximately to be constant while the plasma falls down along the magnetic field, 
+%%%
+\begin{eqnarray}
+v_{\bot }(r) \propto \frac{1}{r^3} \label{eq:v_bot} \\
+B(r) \propto \frac{B_p}{r^3} 
+\end{eqnarray}
+%%%
+On the other hand, conservation of energy ensures that
+%%%
+\begin{equation}
+\mathcal{E} = -\frac{GM_p}{r} + \frac{v_{\bot }^2}{2} + \frac{v_{\|}^2}{2}=const.
+\end{equation}
+%%%
+Assuming that the initial energy (at $r=r_s$) is negligible compared to those near the surface, $\mathcal{E}=0$, 
+%%%
+\begin{equation}
+v_{\|}^2 \sim \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \label{eq:v_||}
+\end{equation}
+%%%
+
+Substituting equations (\ref{eq:N0_plasma}),  (\ref{eq:v_bot}) and (\ref{eq:v_||}) into equation (\ref{eq:larmor}) leads to
+%%%
+\begin{equation}
+\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{12}} \left( \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \right)^{1/2}  
+\end{equation}
+%%%
+The right-hand side has the maximum value $\sqrt{5GM_p/6\tilde r} $ at radius $\tilde r=(6v_{\bot ,0}^2/GM_p)^{1/5}$. 
+At $r>>\tilde r$, 
+%%%
+\begin{equation}
+\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{25/2}}
+\end{equation}
+%%%
+and
+%%%
+\begin{equation}
+\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{17/2}} \propto \frac{\nu^{17/6}}{B_p^{7/6}}
+\end{equation}
+%%%
+
+At $r<<\tilde r$, 
+%%%
+\begin{equation}
+\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{15}}
+\end{equation}
+%%%
+and
+%%%
+\begin{equation}
+\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{11}} \propto \frac{\nu^{11}}{B_p^{28/3}}
+\end{equation}
+%%%
 

### 2015-06-01 ms.tex
Explanation for the magnetic case is added

@@
 
-In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.
-
-Magnetic field of evolved stars are not well constrained \citep{konstantinova2010}. 
-If the correlation with input magnetic energy is the case, the radio emission would be rather weaker than the Jupiter, because the magnetic field of evolved stars
+In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$, because as indicated earlier, the kinetic energy of the stellar wind of evolved stars are much larger than the main-sequence stars and thus may lead to brighter radio emission.
+On the other hand, if the correlation with input magnetic energy is more fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars have not be well constrained for most of the highly evolved stars.
+Recently there are some observations for M giants, which measured surface magnetic field $\sim 0.1-10 $G for a M-type star EK Boo  \citep{konstantinova2010}.
+In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus also may also increase the planetary radio emission.
+However, because of the lack of universal understanding of the stellar magnetic field, we leave the magnetic model of radio emission for evolved stars for future work.
+
+the radio emission could be rather weaker than the Jupiter, 
+We note that, if the correlation with input magnetic energy is the case, the radio emission could be rather weaker than the Jupiter, because the magnetic field of evolved stars
 

### 2015-06-02 ms.tex
references for the canonical values of total power of Jovian auroral emission

@@
 In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$, because as indicated earlier, the kinetic energy of the stellar wind of evolved stars are much larger than the main-sequence stars and thus may lead to brighter radio emission.
-On the other hand, if the correlation with input magnetic energy is more fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars have not be well constrained for most of the highly evolved stars.
+On the other hand, if the correlation with input magnetic energy is more fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars have not be well constrained for most of the highly evolved stars \memoYF{Some observations: \citet[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}}.
 Recently there are some observations for M giants, which measured surface magnetic field $\sim 0.1-10 $G for a M-type star EK Boo  \citep{konstantinova2010}.
@@
 %%%
-Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griesmeier2007b} \memoYF{cite original paper!}. 
+The total power of Jovian auroral emission highly varies in time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
+Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
+%\memoYF{cite original paper!}. 
 Therefore, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.

### 2015-06-02 ms.tex
references for theory and observations for exoplanet radio emission are added

--- 2015-06-01 ms.tex
@@
 \memoYF{?}.
-Potentially, large exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
+Potentially, exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.
-Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001, griesmeier2007a, griesmeier2007b, hallinan_et_al2013, noyola2014}.
-Although the search for these radio signatures are being conducted, there is no clear detection claimed so far, while some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013}.
+In particular, those in close orbit to the host stars have attracted attention because they are subjected to strong stellar wind and/or strong magnetic interstellar magnetic field, and thus acquire larger input energy.
+Radio emission from known exoplanets have been roughly estimated based on the the empirical scaling of the radio intensity with the solar wind flux known as ``radiometric Bode's law'' \citep{farrell1999,zarka2001,Lazio2004,griesmeier2004,griesmeier2005,griesmeier2007a,griesmeier2007b,reiners2010}.
+Although the search for these radio signatures are being conducted, there is no clear detection claimed so far
+\citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
+while some indications were obtained \citep{lecavelier_et_al2013,sirothia2014}.
 
@@
 
-We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission with the input energy from stellar wind, in the same manner as \citet{griesmeier2007b}.
-This is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
+We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}.
+The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
 %Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
@@
 
-In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.
-
-Magnetic field of evolved stars are not well constrained \citep{konstantinova2010}. 
-If the correlation with input magnetic energy is the case, the radio emission would be rather weaker than the Jupiter, because the magnetic field of evolved stars
+In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$, because as indicated earlier, the kinetic energy of the stellar wind of evolved stars are much larger than the main-sequence stars and thus may lead to brighter radio emission.
+
+On the other hand, if the correlation with input magnetic energy is more fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well known for highly evolved stars; many of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}.
+In the case of M-type giant EK boo, surface magnetic field $\sim 0.1-10 $G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus also may also increase the planetary radio emission.
+However, because of the lack of universal understanding of the stellar magnetic field, we leave the magnetic model of radio emission for evolved stars for future work.
+
+In reality, the total power of Jovian auroral emission highly varies in time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
+Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
 
@@
 The bandwidth, $\Delta f$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griesmeier2007b}.
+
+We estimate the radio brightness of RGHJs by simply scaling
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Brighter Implies Harder to See:\\
-Greater $B$ Produces Lower $F_\nu$}
-\label{ss:counterintuitive}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The cyclotron frequency at radius $r$ is:
-%%%
-\begin{equation}
-f_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
-\end{equation}
-%%
-Therefore, 
-%%%
-\begin{equation}
-\frac{dP}{df_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
-\end{equation}
-%%%
-Employing Larmor formula, power emitted from a thin shell at $r\sim r+dr$, $dP/dr$ is 
-%%%
-\begin{equation}
-\frac{dP}{dr} \propto 4\pi r^2 N_{\rm plasma}(r) v_{\bot }^2(r) B^2(r) \label{eq:larmor}
-\end{equation}
-%%%
-where $N_{\rm plasma}(r) $ represents the number density of plasma in the planetary magnetosphere at radius $r$.
-
-We assume that $N_{\rm plasma}(r_s) $  is proportional to the squared radius of the magnetic stand-off point:
-%%%
-\begin{equation}
-N_{\rm plasma}(r_s) \propto \pi r_s^2 \;\;(\propto B_p^{2/3}) \label{eq:N0_plasma}
-\end{equation}
-%%%
-Due the the mass flux conservation,
-%%%
-\begin{equation}
-4 \pi r^2 N_{\rm plasma}(r) v_{\|} = const.
-\end{equation}
-%%%
-Combining with equation (\ref{eq:N0_plasma}),
-%%%
-\begin{equation}
-N_{\rm plasma}(r) \propto  r_s^2 \frac{v_{\|}(r)}{r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
-\end{equation}
-%%%
-
-Because the magnetic dipole moment
-%%%
-\begin{equation}
-\mu = \frac{mv_{\bot}(r)}{eB(r)}
-\end{equation}
-%%%
-is approximately to be constant while the plasma falls down along the magnetic field, 
-%%%
-\begin{eqnarray}
-v_{\bot }(r) \propto \frac{1}{r^3} \label{eq:v_bot} \\
-B(r) \propto \frac{B_p}{r^3} 
-\end{eqnarray}
-%%%
-On the other hand, conservation of energy ensures that
-%%%
-\begin{equation}
-\mathcal{E} = -\frac{GM_p}{r} + \frac{v_{\bot }^2}{2} + \frac{v_{\|}^2}{2}=const.
-\end{equation}
-%%%
-Assuming that the initial energy (at $r=r_s$) is negligible compared to those near the surface, $\mathcal{E}=0$, 
-%%%
-\begin{equation}
-v_{\|}^2 \sim \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \label{eq:v_||}
-\end{equation}
-%%%
-
-Substituting equations (\ref{eq:N0_plasma}),  (\ref{eq:v_bot}) and (\ref{eq:v_||}) into equation (\ref{eq:larmor}) leads to
-%%%
-\begin{equation}
-\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{12}} \left( \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \right)^{1/2}  
-\end{equation}
-%%%
-The right-hand side has the maximum value $\sqrt{5GM_p/6\tilde r} $ at radius $\tilde r=(6v_{\bot ,0}^2/GM_p)^{1/5}$. 
-At $r>>\tilde r$, 
-%%%
-\begin{equation}
-\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{25/2}}
-\end{equation}
-%%%
-and
-%%%
-\begin{equation}
-\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{17/2}} \propto \frac{\nu^{17/6}}{B_p^{7/6}}
-\end{equation}
-%%%
-
-At $r<<\tilde r$, 
-%%%
-\begin{equation}
-\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{15}}
-\end{equation}
-%%%
-and
-%%%
-\begin{equation}
-\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{11}} \propto \frac{\nu^{11}}{B_p^{28/3}}
-\end{equation}
-%%%
-
-\newpage
-
-\memoDS{Is this section needed anymore, since this is already in the Griesmeier paper?
-Does the Griesmeier paper make the point explicit enough, or is this still somewhat valuable?
-Also, are we 100\% sure that this section is right?
-A planet with larger surface field achieves an equivalent field to a planet with a smaller surface field at a larger radius, and captures a larger wind flux.
-Should we think more about the spectrum?}
-
-According to Eq.~(\ref{eq:Pkinp}), the total emitted power scales with $B^{2/3}$.
-In detail, it is not obvious how the power spectral density scales with a planet's surface magnetic field, because the emission process involves electrons passing through a wide range of magnetic field conditions (dipolar field strength drops off as $r^{-3}$, and only in an idealized model is a planet a perfect magnetic dipole).
-Nevertheless, a reasonable ansatz is that the radio emission is spread over a range of wavelengths in an approximately scale-independent way.
-In other words, the frequency bandwidth $\Delta f$ of Eq.~(\ref{eq:Fnu}) is proportional to $f_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
-This means that the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.
-Since $f_{\rm cyc}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
-Planets that are intrinsically brighter, owing to a greater magnetic field strength, probably have their emission spread out over a broader set of frequencies, and therefore have a lower flux density as measured in Janskys!
-\memoDS{Is this pointed out elsewhere in the literature?}
-
-\newpage
-
 Combining the expressions above for the dependence of radio emission on planetary magnetic field strength, we find that the radio spectral flux density observed at the Earth is:
@@
 %%% 
-Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griesmeier2007b} \memoYF{cite original paper!}. 
-Therefore, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.
+%\memoYF{cite original paper!}. 
+Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.
 
@@
 
-\end{document}
+%\end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Brighter Implies Harder to See:\\
+Greater $B$ Produces Lower $F_\nu$}
+\label{ss:counterintuitive}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The cyclotron frequency at radius $r$ is:
+%%%
+\begin{equation}
+f_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
+\end{equation}
+%%
+Therefore, 
+%%%
+\begin{equation}
+\frac{dP}{df_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
+\end{equation}
+%%%
+Employing Larmor formula, power emitted from a thin shell at $r\sim r+dr$, $dP/dr$ is 
+%%%
+\begin{equation}
+\frac{dP}{dr} \propto 4\pi r^2 N_{\rm plasma}(r) v_{\bot }^2(r) B^2(r) \label{eq:larmor}
+\end{equation}
+%%%
+where $N_{\rm plasma}(r) $ represents the number density of plasma in the planetary magnetosphere at radius $r$.
+
+We assume that $N_{\rm plasma}(r_s) $  is proportional to the squared radius of the magnetic stand-off point:
+%%%
+\begin{equation}
+N_{\rm plasma}(r_s) \propto \pi r_s^2 \;\;(\propto B_p^{2/3}) \label{eq:N0_plasma}
+\end{equation}
+%%%
+Due the the mass flux conservation,
+%%%
+\begin{equation}
+4 \pi r^2 N_{\rm plasma}(r) v_{\|} = const.
+\end{equation}
+%%%
+Combining with equation (\ref{eq:N0_plasma}),
+%%%
+\begin{equation}
+N_{\rm plasma}(r) \propto  r_s^2 \frac{v_{\|}(r)}{r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
+\end{equation}
+%%%
+
+Because the magnetic dipole moment
+%%%
+\begin{equation}
+\mu = \frac{mv_{\bot}(r)}{eB(r)}
+\end{equation}
+%%%
+is approximately to be constant while the plasma falls down along the magnetic field, 
+%%%
+\begin{eqnarray}
+v_{\bot }(r) \propto \frac{1}{r^3} \label{eq:v_bot} \\
+B(r) \propto \frac{B_p}{r^3} 
+\end{eqnarray}
+%%%
+On the other hand, conservation of energy ensures that
+%%%
+\begin{equation}
+\mathcal{E} = -\frac{GM_p}{r} + \frac{v_{\bot }^2}{2} + \frac{v_{\|}^2}{2}=const.
+\end{equation}
+%%%
+Assuming that the initial energy (at $r=r_s$) is negligible compared to those near the surface, $\mathcal{E}=0$, 
+%%%
+\begin{equation}
+v_{\|}^2 \sim \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \label{eq:v_||}
+\end{equation}
+%%%
+
+Substituting equations (\ref{eq:N0_plasma}),  (\ref{eq:v_bot}) and (\ref{eq:v_||}) into equation (\ref{eq:larmor}) leads to
+%%%
+\begin{equation}
+\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{12}} \left( \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \right)^{1/2}  
+\end{equation}
+%%%
+The right-hand side has the maximum value $\sqrt{5GM_p/6\tilde r} $ at radius $\tilde r=(6v_{\bot ,0}^2/GM_p)^{1/5}$. 
+At $r>>\tilde r$, 
+%%%
+\begin{equation}
+\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{25/2}}
+\end{equation}
+%%%
+and
+%%%
+\begin{equation}
+\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{17/2}} \propto \frac{\nu^{17/6}}{B_p^{7/6}}
+\end{equation}
+%%%
+
+At $r<<\tilde r$, 
+%%%
+\begin{equation}
+\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{15}}
+\end{equation}
+%%%
+and
+%%%
+\begin{equation}
+\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{11}} \propto \frac{\nu^{11}}{B_p^{28/3}}
+\end{equation}
+%%%
+
+\newpage
+
+\memoDS{Is this section needed anymore, since this is already in the Griesmeier paper?
+Does the Griesmeier paper make the point explicit enough, or is this still somewhat valuable?
+Also, are we 100\% sure that this section is right?
+A planet with larger surface field achieves an equivalent field to a planet with a smaller surface field at a larger radius, and captures a larger wind flux.
+Should we think more about the spectrum?}
+
+According to Eq.~(\ref{eq:Pkinp}), the total emitted power scales with $B^{2/3}$.
+In detail, it is not obvious how the power spectral density scales with a planet's surface magnetic field, because the emission process involves electrons passing through a wide range of magnetic field conditions (dipolar field strength drops off as $r^{-3}$, and only in an idealized model is a planet a perfect magnetic dipole).
+Nevertheless, a reasonable ansatz is that the radio emission is spread over a range of wavelengths in an approximately scale-independent way.
+In other words, the frequency bandwidth $\Delta f$ of Eq.~(\ref{eq:Fnu}) is proportional to $f_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
+This means that the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.
+Since $f_{\rm cyc}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
+Planets that are intrinsically brighter, owing to a greater magnetic field strength, probably have their emission spread out over a broader set of frequencies, and therefore have a lower flux density as measured in Janskys!
+\memoDS{Is this pointed out elsewhere in the literature?}
 

### 2015-06-02 ms.tex
introduction is updated

@@
 stellar wind particles and particles from Io-like moons.
-In particular, those in close orbit to the host stars have attracted attention because they are subjected to strong stellar wind and/or strong magnetic interstellar magnetic field, and thus acquire larger input energy.
-Radio emission from known exoplanets have been roughly estimated based on the the empirical scaling of the radio intensity with the solar wind flux known as ``radiometric Bode's law'' \citep{farrell1999,zarka2001,Lazio2004,griesmeier2004,griesmeier2005,griesmeier2007a,griesmeier2007b,reiners2010}.
-Although the search for these radio signatures are being conducted, there is no clear detection claimed so far
+Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is known as  ``radiometric Bode's law'' \citep{desch+kaiser1984}.
+Based on this law, exoplanets in close-in orbits have been attracted attention as possible bright radio wave emitters because they are subjected to strong stellar wind and/or strong interstellar magnetic field, and thus can gain larger energy input.
+Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,Lazio2004,griesmeier2004,griesmeier2007a,griesmeier2007b,reiners2010}.
+In addition, young planetary systems where the stellar wind activity is stronger are also taken into consideration \citep{griesmeier2005}. 
+Although the observational search for these radio signatures are being conducted, there is no clear detection claimed so far
 \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
-while some indications were obtained \citep{lecavelier_et_al2013,sirothia2014}.
+while some indications have been obtained \citep{lecavelier_et_al2013,sirothia2014}.
 
@@
 At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_\odot$/yr.
-On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could generate bright radio emission.
+On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.
 
@@
 \S3 presents a simple estimate of the spectral radio intensity of RGHJs and compares them with what might be expected from canonical hot Jupiters.
-\S3 also describes the surprising result that, although the planetary magnetic field is crucial to the generation of radio emission at all, there might be an important region in parameter space in which planets with stronger magnetic fields are less easily observable.
+%\S3 also describes the surprising result that, although the planetary magnetic field is crucial to the generation of radio emission at all, there might be an important region in parameter space in which planets with stronger magnetic fields are less easily observable.
 \S4 discusses possible obstacles to detect radio emission from RGHJs, in particular the effects of intrinsic radio emission of evolved stars and the offsetting effect of the electrons spiraling down along the planetary magnetic field.

### 2015-06-02 ms.tex
some () for functions changed to []
while editing S5.2...

@@
 Magnetic field of planets are estimated by scaling Jovian magnetic field $B_J \sim 10$~G by equation (\ref{eq:Bscaling}). 
+\memoYF{need to cite \citet{reiners2010} somewhere.}
 
@@
 Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them. 
+Note that, within this framework, the {\it spectral} radio flux has  necessarily negative correlation with the planetary magnetic field, as pointed out by \citet{griesmeier2005}.
 
@@
 %%%
+
+---
+
+%%%
 Hence, for a number density $n$ of these charged particles, the fraction of canceling field to the background magnetic field is
@@
 therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.
+
+\memoYF{$\ast \ast \ast$ How about the following argument instead? $\ast \ast \ast$}
+
+%%%
+\begin{equation}
+r=\frac{mv_{\bot }}{eB}.
+\end{equation}
+%%%
+which creates a magnetic dipole
+%%%
+\begin{equation}
+\mu = \frac{e}{2\pi r/v_{\bot }} \pi r^2 = \frac{1}{2} e r v_{\bot } = \frac{mv_{\bot }^2}{2B}.
+\end{equation}
+%%%
+The volume integral of the canceling magnetic field $B_c$ generated by a single dipole $\mu$ is
+%%%
+\begin{equation}
+\int d^3{\boldsymbol r} B_c = \frac{8\pi}{3} \mu.
+\end{equation}
+%%%
+
+At the magnetic stand-off point, 
+%%%
+\begin{equation}
+\left. \frac{B_c}{B}\right|_{r=r_s} = \frac{8\pi n \mu}{3B} = \frac{4\pi nmv_{\bot }^2}{3 B^2}
+\end{equation}
+%%%
+but because
+%%%
+\begin{equation}
+m_p n v^2 \sim \frac{B^2}{2\pi }
+\end{equation}
+%%%
+and because $v_{\bot }^2 < v^2$, we have $|B_c/B| < 2/3$. 
+When the particles are spiraling down along the magnetic field line, the magnetic dipole moment are approximately constant. 
+On the other hand, the ambient magnetic field strength increase as $\propto r^{-3}$ where $r$ is the distance from the center of a planet.
+
+where $B_s$ is the magnetic field at the magnetic stand-off point. 
+Because $v_{\bot }^2 < v^2$, 
+%%%
+\begin{equation}
+\left. \frac{B_c}{B}\right|_{r=r_s} = \frac{4\pi n(mv_{\bot }^2)}{3 B^2}= \frac{\rho_K}{3\rho_B},
+\end{equation}
+%%%
+
+%%%
+Hence, for a number density $n$ of these charged particles, the fraction of canceling field to the background magnetic field is
+%%%
+\begin{equation}
+\frac{B_c}{B} = \frac{n(mv^2/2)}{3 B^2/8\pi}= \frac{\rho_K}{3\rho_B},
+\end{equation}
+%%%
+where $\rho_K$ and $\rho_B$ are the kinetic energy density and the magnetic energy density, respectively.
+If the initial velocity is not perpendicular to the magnetic field, $v$ must everywhere be replaced by its perpendicular component.
+
+%
+At the magnetic stand-off point, 
+%%%
+\begin{equation}
+m_p n(r_s) v^2 = \frac{B(r_s)^2}{2\pi }
+\end{equation}
+%%%
+and thus $\rho_K \sim \rho _B$. When the particle spirals into the planet, the kinetic energy of the moment is
+%%%
+\begin{equation}
+\frac{mv^2}{2} \propto \frac{1}{r}
+\end{equation}
+%%%
+while magnetic pressures increases (by beaming?) by 
+%%%
+\begin{equation}
+\frac{B^2}{8\pi } \propto \frac{1}{r^6}
+\end{equation}
+%%%
+therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.
+
+---
 
@@
 
+\section{Memo}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{equation}
-N_{\rm plasma}(r) \propto  r_s^2 \frac{v_{\|}(r)}{r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
+N_{\rm plasma}(r) \propto  \frac{r_s^2 }{v_{\|}(r) r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
 \end{equation}

### 2015-06-03 ms.tex
while editing S5.2...
changed a few () to [] for functions
all f_c -> f_cyc

@@
 B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
-f_c &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
+f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
 \end{eqnarray}
@@
 \begin{eqnarray}
-F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
+F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyc}} \\
 &\approx & 5.22\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
@@
 \begin{equation}
-m_p n(r_s) v^2 = \frac{B(r_s)^2}{2\pi }
+m_p n[r_s] v^2 = \frac{B[r_s]^2}{2\pi }
 \end{equation}
@@
 
-where $B_s$ is the magnetic field at the magnetic stand-off point. 
-Because $v_{\bot }^2 < v^2$, 
-%%%
-\begin{equation}
-\left. \frac{B_c}{B}\right|_{r=r_s} = \frac{4\pi n(mv_{\bot }^2)}{3 B^2}= \frac{\rho_K}{3\rho_B},
-\end{equation}
-%%%
-
-%%%
-Hence, for a number density $n$ of these charged particles, the fraction of canceling field to the background magnetic field is
-%%%
-\begin{equation}
-\frac{B_c}{B} = \frac{n(mv^2/2)}{3 B^2/8\pi}= \frac{\rho_K}{3\rho_B},
-\end{equation}
-%%%
-where $\rho_K$ and $\rho_B$ are the kinetic energy density and the magnetic energy density, respectively.
-If the initial velocity is not perpendicular to the magnetic field, $v$ must everywhere be replaced by its perpendicular component.
-
-%
-At the magnetic stand-off point, 
-%%%
-\begin{equation}
-m_p n(r_s) v^2 = \frac{B(r_s)^2}{2\pi }
-\end{equation}
-%%%
-and thus $\rho_K \sim \rho _B$. When the particle spirals into the planet, the kinetic energy of the moment is
-%%%
-\begin{equation}
-\frac{mv^2}{2} \propto \frac{1}{r}
-\end{equation}
-%%%
-while magnetic pressures increases (by beaming?) by 
-%%%
-\begin{equation}
-\frac{B^2}{8\pi } \propto \frac{1}{r^6}
-\end{equation}
-%%%
-therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.
-
 ---
@@
 
-Note that that for a plasma of protons and electrons in solar wind the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.
+It is interesting to note that, for a plasma of protons and electrons in a stellar wind, the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.
 \memoYF{necessary to mention?}

### 2015-06-03 ms.tex
while revising...
some very simple updates to affiliations and a duplicate equation label.

@@
 %
-Aaron Parsons\altaffilmark{5} \\
-%
-Tony Mroczkowski\altaffilmark{6} \\
+Aaron Parsons\altaffilmark{4} \\
+%
+Tony Mroczkowski\altaffilmark{5,6} \\
 %
@@
 
-\affil{$^4$Astronomy Department, UC Berkeley}
-
-\affil{$^5$Naval Research Laboratory}
-
-\affil{$^6$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
+\affil{$^4$Astronomy Department, University of California Berkeley}
+
+\affil{$^5$National Research Council Fellow}
+
+\affil{$^6$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
+
+\affil{$^7$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
 
@@
 q_c \sim q_{c, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
-\label{eq:burrowsLum}
+\label{eq:burrowsHeatFlux}
 \end{equation}

### 2015-06-03 ms.tex
f_{c2} -> f_{plasma}

@@
 
-We estimate the radio brightness of RGHJs by simply scaling
+We estimate the radio brightness of RGHJs by simply scaling \memoDS{stray sentence fragment?}
 
@@
 
-Note that the cyclotron frequency Jovian planets older than 1~Gyr is typically larger than 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
+Note that the cyclotron frequency of Jovian planets older than 1~Gyr is typically larger than 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
 In this regime, there are a number of current and near-future radio wave detectors including UTR-2, LOFAR, LWA, and SKA.
@@
 
-However, observed energy flux is limited by the plasma cut-off frequency in the vicinity of the planets. 
+However, observed energy flux is limited by the plasma cut-off frequency in the vicinity of the planets, given by Eq.~(\ref{eq:fplasmalos}).
 This condition is:
@@
 \begin{equation}
- f_{cyc} > f_{c2}
+\label{eq:fcyc>fplasma} f_{\rm cyc} > f_{\rm plasma}^{\rm los}
 \end{equation} 

### 2015-06-03 ms.tex
Added memo about fcyc>fplasma equation, and slightly modified surrounding text.

@@
 \begin{equation}
-f_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:cyc} 
+f_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
 \end{equation}
@@
 \begin{eqnarray}
-\label{eq:fplasmalos} f_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \cdot \frac{1}{\rm cm^{-3}} \right)^{1/2} \\
+\label{eq:fplasmalos} f_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
 \label{eq:fplasmalos_scaled} & = & 14.7{\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{0.1 v_{\odot}}  \right)^{-1/2} \notag \\
@@
 
-However, observed energy flux is limited by the plasma cut-off frequency in the vicinity of the planets, given by Eq.~(\ref{eq:fplasmalos}).
-This condition is:
+However, observed energy flux is limited by the plasma cut-off frequency in the vicinity of the planets, given by Eq.~(\ref{eq:fplasmalos_scaled}).
+We can see emission only from where the cyclotron frequency (Eq.~\ref{eq:fcyc}) exceeds the plasma frequency:
 %%%
@@
 %%%
-or,
+or, \memoDS{Is this arithmetic right?  Shouldn't the 2.2 actually be 0.5, based on the 14.7MHz in eq. 12 and the 27.9MHz in eq. 8?}
 %%%

### 2015-06-11 ms.tex

--- 2015-06-03 ms.tex
@@
 %
-Aaron Parsons\altaffilmark{4} \\
-%
-Tony Mroczkowski\altaffilmark{5,6} \\
+Aaron Parsons\altaffilmark{5} \\
+%
+Tony Mroczkowski\altaffilmark{6} \\
 %
@@
 
-\affil{$^4$Astronomy Department, University of California Berkeley}
-
-\affil{$^5$National Research Council Fellow}
-
-\affil{$^6$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
-
-\affil{$^7$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
+\affil{$^4$Astronomy Department, UC Berkeley}
+
+\affil{$^5$Naval Research Laboratory}
+
+\affil{$^6$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
 
@@
 q_c \sim q_{c, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
-\label{eq:burrowsHeatFlux}
+\label{eq:burrowsLum}
 \end{equation}
@@
 It is interesting to note that, for a plasma of protons and electrons in a stellar wind, the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.
-\memoYF{necessary to mention?}
 

### 2015-06-16 ms.tex
eqs.35-40 are corrected
figures for 70MHz and 200MHz

--- 2015-06-03 ms.tex
@@
 
-We estimate the radio brightness of RGHJs by simply scaling \memoDS{stray sentence fragment?}
+%We estimate the radio brightness of RGHJs by simply scaling \memoDS{stray sentence fragment?}
 
@@
 %%%
-or, \memoDS{Is this arithmetic right?  Shouldn't the 2.2 actually be 0.5, based on the 14.7MHz in eq. 12 and the 27.9MHz in eq. 8?}
-%%%
-\begin{eqnarray}
- \left( \frac{B}{10~\mbox{G}} \right) &>& 2.2 \left( \frac{a}{5~\mbox{AU}} \right)^{-1} \\
+or, \memoDS{Is this arithmetic right?  Shouldn't the 2.2 actually be 0.5, based on the 14.7MHz in eq. 12 and the 27.9MHz in eq. 8?}\memoYF{Corrected. }
+%%%
+\begin{eqnarray}
+ \left( \frac{B}{10~\mbox{G}} \right) &>& 0.526 \left( \frac{a}{5~\mbox{AU}} \right)^{-1} \\
  && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
@@
 \begin{eqnarray}
- \left( \frac{M_p}{M_{p,J}} \right) &> & 1.8 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
+ \left( \frac{M_p}{M_{p,J}} \right) &> & 0.627 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
  && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
@@
 \begin{eqnarray}
-F_{\nu} &<& 8 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right) \\
-&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{-1}  \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/6} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
+F_{\nu} &<& 1.30 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}}^{-2} \right) \\
+&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{1/3}  \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
 \end{eqnarray}
@@
    \plotoneh{radio_1Mp_5AU.pdf}
-   \plotoneh{radio_5Mp_5AU.pdf}
-   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$ and 5$M_J$ at 1 AU and 5AU.
+%   \plotoneh{radio_5Mp_5AU.pdf}
+   \plotoneh{radio_2Mp_4-5Gyr.pdf}
+   \plotoneh{radio_4Mp_4-5Gyr.pdf}   
+   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$, 2$M_J$, and 4$M_J$ at 1 AU and 5AU.
 Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet.
@@
 Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion.
-Here, we consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, and [B] a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).
-
-Figure \ref{fig:observability} displays the estimated radio intensity and the maximum frequency (i.e., cyclotron frequency) of Jupiters [A] and [B] around red giants within 100~pc. 
-Jupiters [A] and [B] are placed at 1 AU and at 5 AU for reference. 
+Here, we consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, [B] a larger Jovian planet with $M_p\sim 2M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 70$~MHz, and [C] a larger Jovian planet with $M_p\sim 4M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 200$~MHz
+  (equation (\ref{eq:scalingfc})).
+
+Figure \ref{fig:observability} displays the estimated radio intensity and the maximum frequency (i.e., cyclotron frequency) of Jupiters [A], [B], and [C]  around red giants within 100~pc. 
+Jupiters are placed at 1 AU and at 5 AU for reference. 
 The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross).

### 2015-06-21 ms.tex
trivial change as a test
abstract is modified

@@
 \begin{abstract}
-  Red-giant hot Jupiters (RGHJs) are jovian planets orbiting red-giant-branch or asymptotic-giant-branch (AGB) stars.
-  Post-main-sequence stars lose mass at much higher rates than main-sequence stars.
-  A jovian planet passing through the dense winds of its RGB or AGB host can capture stellar wind in its magnetosphere, leading to cyclotron emission from electrons spiraling in the magnetic field.
-  The cyclotron frequency of electrons from the stellar wind accreting onto the planet scales as 100~MHz~$(B/30 {\rm~Gauss})$.
-  Counterintuitively, a plausible toy model suggests that a stronger planetary magnetic field leads to lower spectral flux density, and might therefore make objects more challenging to observe.
-  Still, for a range of planetary and stellar parameters, a RGHJ might generate a radio luminosity that would be visible from kiloparsec distances.
+%%%
+Magnetized planets emit radio wave in the interaction with stellar wind. 
+When the host stars evolve off the main sequence and go through red-giant branch (RGB), the stars become orders-of-magnitudes more luminous and at the same time lose mass at much higher rate than their main-sequence counterparts.
+Accordingly, planetary companions around them, if exist, are heated up to the level of canonical hot Jupiters and also subjected to the massive stellar wind. 
+Such ``Red-Giant Hot Jupiters'' (RGHJs) are therefore candidates of bright radio emitters. 
+We estimate the spectral auroral radio intensity of RGHJs employing the ``radio Bode's law'' and proposed scaling of planetary magnetic fields. 
+We find that RGHJs would be as bright as the predicted radio emission from canonical hot Jupiters, and can be even brighter depending on the configurations.
+Thus radio emission from a RGHJ might be visible from a hundred parsec distances with current/future detectors \memoYF{check}.
+
+%Red-giant hot Jupiters (RGHJs) are jovian planets orbiting red-giant-branch (RGB) or asymptotic-giant-branch (AGB) stars. 
+%Red-giant hot Jupiters (RGHJs) are jovian planets orbiting red-giant-branch (RGB) or asymptotic-giant-branch (AGB) stars.
+%Post-main-sequence stars lose mass at much higher rates than main-sequence stars.
+%A jovian planet passing through the dense winds of its RGB or AGB host can capture stellar wind in its magnetosphere, leading to radio emission from electrons spiraling in the magnetic field.
+%The cyclotron frequency of electrons from the stellar wind accreting onto the planet scales as 100~MHz~$(B/30 {\rm~Gauss})$.
+%The cyclotron frequency of electrons from the stellar wind accreting onto the planet scales as 100~MHz~$(B/30 {\rm~Gauss})$.
+%Counterintuitively, a plausible toy model suggests that a stronger planetary magnetic field leads to lower spectral flux density, and might therefore make objects more challenging to observe.
+%Still, for a range of planetary and stellar parameters, a RGHJ might generate a radio luminosity that would be visible from kiloparsec distances.
 \end{abstract}
@@
 \keywords{planets and satellites: Jupiter --- Sun: evolution ---
-  planetary systems --- radiative transfer --- stars: evolution ---
+  planetary systems --- stars: evolution ---
   stars: AGB and post-AGB}

### 2015-06-21 ms.tex
slight change

@@
 %\usepackage[dvipdfmx]{graphicx}
+
+% trivial change as a test
 
@@
 When the host stars evolve off the main sequence and go through red-giant branch (RGB), the stars become orders-of-magnitudes more luminous and at the same time lose mass at much higher rate than their main-sequence counterparts.
-Accordingly, planetary companions around them, if exist, are heated up to the level of canonical hot Jupiters and also subjected to the massive stellar wind. 
+Accordingly, planetary companions around them at a few AU orbits, if exist, are heated up to the level of canonical hot Jupiters and also subjected to the massive stellar wind. 
 Such ``Red-Giant Hot Jupiters'' (RGHJs) are therefore candidates of bright radio emitters. 

### 2015-06-22 ms.tex
Text edits in various places

@@
 %
-Jason Nordhaus\altaffilmark{3} \\
-%
-Nikku Madhusudhan\altaffilmark{4} \\
+Jason Nordhaus\altaffilmark{3,4} \\
+%
+Nikku Madhusudhan\altaffilmark{5} \\
 %
@@
 %
-Aaron Parsons\altaffilmark{4} \\
-%
-Tony Mroczkowski\altaffilmark{5,6} \\
-%
-Neil Zimmerman\altaffilmark{7}
+Aaron Parsons\altaffilmark{6} \\
+%
+Tony Mroczkowski\altaffilmark{7,8} \\
+%
+Neil Zimmerman\altaffilmark{9}
 }
@@
 
-\affil{$^2$Department of Mathematics, Rochester Institute of Technology}
-
-\affil{$^3$Astronomy Department, University of Cambridge, UK}
-
-\affil{$^4$Astronomy Department, University of California Berkeley}
-
-\affil{$^5$National Research Council Fellow}
-
-\affil{$^6$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
-
-\affil{$^7$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
+\affil{$^3$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^4$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^5$Astronomy Department, University of Cambridge, UK}
+
+\affil{$^6$Astronomy Department, University of California Berkeley}
+
+\affil{$^7$National Research Council Fellow}
+
+\affil{$^8$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
+
+\affil{$^9$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
 
@@
 %%%
-Magnetized planets emit radio wave in the interaction with stellar wind. 
-When the host stars evolve off the main sequence and go through red-giant branch (RGB), the stars become orders-of-magnitudes more luminous and at the same time lose mass at much higher rate than their main-sequence counterparts.
+Magnetized planets emit radio waves in the interaction with stellar winds. 
+When the host stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders-of-magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
 Accordingly, planetary companions around them at a few AU orbits, if exist, are heated up to the level of canonical hot Jupiters and also subjected to the massive stellar wind. 
@@
 \memoYF{?}.
-Potentially, exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
+Potentially, exoplanets can also emit radio waves through similar mechanisms, depending on their intrinsic magnetic fields and the density of the surrounding plasma, e.g.
 stellar wind particles and particles from Io-like moons.
 Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is known as  ``radiometric Bode's law'' \citep{desch+kaiser1984}.
-Based on this law, exoplanets in close-in orbits have been attracted attention as possible bright radio wave emitters because they are subjected to strong stellar wind and/or strong interstellar magnetic field, and thus can gain larger energy input.
+Based on this law, exoplanets in close-in orbits have attracted attention as possible bright radio wave emitters because they are subjected to strong stellar winds and/or strong interstellar magnetic fields, and thus can gain larger energy input.
 Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,Lazio2004,griesmeier2004,griesmeier2007a,griesmeier2007b,reiners2010}.
 In addition, young planetary systems where the stellar wind activity is stronger are also taken into consideration \citep{griesmeier2005}. 
-Although the observational search for these radio signatures are being conducted, there is no clear detection claimed so far
+Although the observational search for these radio signatures are underway, there is no clear detection claimed so far
 \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
@@
 Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass \citep{spiegel+madhusudhan2012}.
-At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_\odot$/yr.
+At the same time, they are subject to a massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_\odot$/yr.
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.
@@
 %\footnote{Escape velocity is $\sqrt{2GM/r}$.}
-Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_p/R}$ ($G$ is the gravitational constant, $M_p$ is the planetary mass, and $R$ is the planetary radius), a RG with radius $R=100R_{\odot}$ has 10 times as slow stellar wind as that at the main sequence.
+Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_p/R}$ ($G$ is the gravitational constant, $M_p$ is the planetary mass, and $R$ is the planetary radius), a RG with radius $R=100R_{\odot}$ encounters 10 times as slow a stellar wind as that at the main sequence.
 %\memoYF{Estimate in more detail?} 

### 2015-06-22 ms.tex
scaling of B is slightly updated. Now it is not based on Christensen+ 2006 but Christensen+ 2009

--- 2015-06-21 ms.tex
@@
 Such ``Red-Giant Hot Jupiters'' (RGHJs) are therefore candidates of bright radio emitters. 
-We estimate the spectral auroral radio intensity of RGHJs employing the ``radio Bode's law'' and proposed scaling of planetary magnetic fields. 
-We find that RGHJs would be as bright as the predicted radio emission from canonical hot Jupiters, and can be even brighter depending on the configurations.
-Thus radio emission from a RGHJ might be visible from a hundred parsec distances with current/future detectors \memoYF{check}.
+We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and proposed scaling of planetary magnetic fields. 
+We find that RGHJs might be as bright as canonical hot Jupiters as predicted so far, and thus radio emission from a RGHJ would be visible from a hundred parsec distances with current/future detectors \memoYF{check}.
 
@@
 Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
-It has been known that Jupiter emits radio emission from the radiation belt and auroral region due to cyclotron-maser instability \citep{zarka1998}.
-% due to the acceleration of the plasmas.
-\memoYF{?}.
+It has been known that Jupiter emits radio emission from the auroral region due to cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
 Potentially, exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
@@
 Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is known as  ``radiometric Bode's law'' \citep{desch+kaiser1984}.
-Based on this law, exoplanets in close-in orbits have been attracted attention as possible bright radio wave emitters because they are subjected to strong stellar wind and/or strong interstellar magnetic field, and thus can gain larger energy input.
+Based on this law, it has been proposed that exoplanets in close-in orbits may be bright radio wave emitters because they are subjected to strong stellar wind and/or strong interstellar magnetic field, and thus can gain larger energy input.
 Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,Lazio2004,griesmeier2004,griesmeier2007a,griesmeier2007b,reiners2010}.
@@
 asymptotic-giant branch (AGB) where their radii and luminosities increase by orders of magnitude. 
-Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass \citep{spiegel+madhusudhan2012}.
+Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) \citep{spiegel+madhusudhan2012}.
 At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_\odot$/yr.
@@
 
-In this paper we estimate the potential to detect planetary companions around evolved stars through the brightness of their radio emission. 
+In this paper, we estimate the potential to detect planetary companions around evolved stars through the brightness of their radio emission. 
 In \S2, we describe our assumptions for the scaling of planetary radio emission, stellar wind, and planetary magnetosphere.
@@
 
-While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr, ant the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
+While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
 Therefore, we have
@@
 %\footnote{Escape velocity is $\sqrt{2GM/r}$.}
-Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_p/R}$ ($G$ is the gravitational constant, $M_p$ is the planetary mass, and $R$ is the planetary radius), a RG with radius $R=100R_{\odot}$ has 10 times as slow stellar wind as that at the main sequence.
+Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_{\star}/R_{\star}}$ ($G$ is the gravitational constant, $M_{\star}$ is the stellar mass, and $R_{\star}$ is the stellar radius), a RG with radius $R_{\star}=100R_{\odot}$ has 10 times as slow stellar wind as that at the main sequence.
 %\memoYF{Estimate in more detail?} 
@@
 
-Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} %\memoYF{check!}
-(see \citet{griesmeier2004} or \citet{christensen2010} for the summary), which are compared with numerical simulations in \citet{christensen2010}. 
-We employ the following relationship from \citet{christensen2006}, which is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space:
+Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006,christensen_et_al2009} %\memoYF{check!}
+%(see \citet{griesmeier2004} or \citet{christensen2010} for the summary), 
+which are compared with numerical simulations in \citet{christensen2010}. 
+We employ the relationship proposed in \citet{christensen_et_al2009}, which is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space:
 %\memoYF{describe in more detail}:
 %%%%%%%%%% 
-\begin{equation}
-B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
-\end{equation}
-%%%%%%%%%%
-where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
-Magnetic field of planets are estimated by scaling Jovian magnetic field $B_J \sim 10$~G by equation (\ref{eq:Bscaling}). 
-\memoYF{need to cite \citet{reiners2010} somewhere.}
-
-In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
+%\begin{equation}
+%B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
+%\end{equation}
+\begin{equation}
+\langle B_c \rangle ^2 \propto f_{\rm ohm} \langle \rho_c \rangle ^{1/3} (Fq_o)^{2/3} \label{eq:Bscaling} 
+\end{equation}
+%%%%%%%%%%
+%where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
+where $\langle B_c \rangle$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\langle \rho_c \rangle$ is the mean density in the dynamo region, $F$ is the efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
+Dipole magnetic field strength at the planetary surface, denoted by $B$, is then scaled by
+%%%%%%%%%%
+\begin{equation}
+B \propto B_c \left( \frac{r_c}{R_p} \right)^3 \label{eq:Bscaling2}
+\end{equation}
+%%%%%%%%%%
+Magnetic field of planets are estimated by scaling Jovian magnetic field $B_J \sim 10$~G with equations (\ref{eq:Bscaling}) and (\ref{eq:Bscaling2}) assuming that $f_{\rm ohm}$ and $F$ are roughly constant.
+
+In order to evaluate $\rho _c $ and $q_o$, we need a model of internal structure of planets. 
 In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, because the numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
@@
 
-The scaling of convected heat flux, $q_c$, is obtained by dividing the time-dependent net planetary luminosity by the surface area of the core region i.e., $4\pi r_c^2$. 
+The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the time-dependent net planetary luminosity by the surface area of the core region, i.e., $4\pi r_c^2$. 
 The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
@@
 \begin{equation}
-L \sim 1.4^{-9} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
+L \sim 1.4\times 10^{-9} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
 \label{eq:burrowsLum}
@@
 \begin{equation}
-q_c \sim q_{c, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
+q_o \sim q_{o, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
 \label{eq:burrowsHeatFlux}
@@
 %%%%%%%%%%
+
+We note that the scaling relation based on \citet{christensen_et_al2009}, or equation (\ref{eq:Bscaling}), has also been adopted in \citet{reiners2010}.
+While the detailed treatment of $\rho _c$ and $q_o$ are different, two estimates of planetary magnetic field strength are fairly close, as shown in \S3 below.
+
 %We estimate the convected heat flux by dividing this luminosity by the surface area of the core region, i.e., $4 \pi r_c^2$.
@@
 
-The peak of the auroral radio emission is around the cyclotron frequency of the planetary magnetic field, $f_{\rm cyc}$: 
+Planetary auroral radio wave are emitted at the local cyclotron frequency along the motion of the plasmas.
+The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $f_{\rm cyc}$:
 %%%%%%%%%% 
@@
 The radius obtained for Jupiter from this equality is about a half of actual radius of Magnetosphere \citep[][]{griesmeier2005}.
-We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$][]{joy2002} according to equation (\ref{eq:stand-off}), i.e.,
+We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e.,
 %%%
@@
 First, we estimate the strength of planetary magnetic field based on the scaling relation of equation (\ref{eq:Bscaling}) and assumptions described in \S\ref{ss:magneticfield}. 
-Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_c$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age.
+Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_o$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age.
 Because $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
@@
 %%%
-or, \memoDS{Is this arithmetic right?  Shouldn't the 2.2 actually be 0.5, based on the 14.7MHz in eq. 12 and the 27.9MHz in eq. 8?}\memoYF{Corrected. }
+or, 
 %%%

### 2015-06-22 ms.tex

@@
 %
-Jason Nordhaus\altaffilmark{3} \\
+Jason Nordhaus\altaffilmark{3,4} \\
 %
-Nikku Madhusudhan\altaffilmark{4} \\
+Nikku Madhusudhan\altaffilmark{5} \\
 %
@@
 %
-Aaron Parsons\altaffilmark{4} \\
+Aaron Parsons\altaffilmark{6} \\
 %
-Tony Mroczkowski\altaffilmark{5,6} \\
+Tony Mroczkowski\altaffilmark{7,8} \\
 %
-Neil Zimmerman\altaffilmark{7}
+Neil Zimmerman\altaffilmark{9}
 }
@@
 In addition, young planetary systems where the stellar wind activity is stronger are also taken into consideration \citep{griesmeier2005}. 
-Although the observational search for these radio signatures are being conducted, there is no clear detection claimed so far
+Although the observational search for these radio signatures are underway, there is no clear detection claimed so far
 \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
@@
 Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_{\star}/R_{\star}}$ ($G$ is the gravitational constant, $M_{\star}$ is the stellar mass, and $R_{\star}$ is the stellar radius), a RG with radius $R_{\star}=100R_{\odot}$ has 10 times as slow stellar wind as that at the main sequence.
+
 %\memoYF{Estimate in more detail?} 

### 2015-06-23 ms.tex
text brush up

@@
 %%%
-Magnetized planets emit radio waves in the interaction with stellar winds. 
 When the host stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders-of-magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
 Accordingly, planetary companions around them at a few AU orbits, if exist, are heated up to the level of canonical hot Jupiters and also subjected to the massive stellar wind. 
-Such ``Red-Giant Hot Jupiters'' (RGHJs) are therefore candidates of bright radio emitters. 
+Given that magnetized planets emit radio waves in the interaction with stellar winds, such ``Red-Giant Hot Jupiters'' (RGHJs) may be candidates of bright radio emitters. 
 We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and proposed scaling of planetary magnetic fields. 
@@
 Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
-It has been known that Jupiter emits radio emission from the auroral region due to cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
-Potentially, exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
+It has been known that Jupiter emits radio wave from the auroral region due to cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
+Potentially, exoplanets can also generate radio emission through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.
@@
 Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) \citep{spiegel+madhusudhan2012}.
-At the same time, they are subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significantly higher than the main-sequence counterparts, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, significantly larger than solar mass-loss rate $\sim 10^{-14}M_\odot$/yr.
+They are also subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, much higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr .
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.
 
-In this paper, we estimate the potential to detect planetary companions around evolved stars through the brightness of their radio emission. 
-In \S2, we describe our assumptions for the scaling of planetary radio emission, stellar wind, and planetary magnetosphere.
-\S3 presents a simple estimate of the spectral radio intensity of RGHJs and compares them with what might be expected from canonical hot Jupiters.
+In this paper, we estimate the radio emission from RGHJs and examine the potential to detect planetary them. 
+In \S2, we describe our assumptions for stellar wind, planetary magnetosphere, frequency of radio emission, and the scaling of planetary radio emission.
+\S3 presents an estimate of the spectral radio intensity of RGHJs and compares them with what might be expected from canonical hot Jupiters.
 %\S3 also describes the surprising result that, although the planetary magnetic field is crucial to the generation of radio emission at all, there might be an important region in parameter space in which planets with stronger magnetic fields are less easily observable.
@@
 
-One important factor in modeling the radio emission due to the interaction with stellar wind and the planetary magnetic field is the density and velocity of stellar wind. 
+One important factor in modeling the radio emission due to the interaction between stellar wind and the planetary magnetic field is the density and velocity of stellar wind. 
 The number density of stellar wind, $n$, can be expressed as
@@
 
-While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase.
+While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr
+\citep{reimers1975}
+, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase
+\citep{schild1989, vassiliadis1993, schoier2001, vanloon2005}.
 Therefore, we have
@@
 \begin{equation}
-\frac{\dot M_\star}{\dot M_{\odot}} \sim 10^6 - 10^9
-\end{equation}
-%%%%%%%%%%
-
-On the other hand, the stellar wind velocity becomes smaller because of the small escape velocity (due to expanded stellar radius).
+\frac{\dot M_\star}{\dot M_{\odot}} \sim 10^6 - 10^9 . 
+\end{equation}
+%%%%%%%%%%
+
+On the other hand, the stellar wind velocity becomes smaller because of the small escape velocity (due to the expanded stellar radius).
 %\footnote{Escape velocity is $\sqrt{2GM/r}$.}
-Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_{\star}/R_{\star}}$ ($G$ is the gravitational constant, $M_{\star}$ is the stellar mass, and $R_{\star}$ is the stellar radius), a RG with radius $R_{\star}=100R_{\odot}$ has 10 times as slow stellar wind as that at the main sequence.
-
-%\memoYF{Estimate in more detail?} 
+Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_{\star}/R_{\star}}$ ($G$ is the gravitational constant, $M_{\star}$ is the stellar mass, and $R_{\star}$ is the stellar radius), a Solar-mass red giant with radius $R_{\star}=100R_{\odot}$ has 10 times as slow stellar wind as that at the Sun, $v_{\odot}$.
 Thus,
 \begin{equation}
-\frac{v}{v_{\odot}} \sim 10^{-1}
-\end{equation}
-where $v_{\odot} \sim 4.0 \times 10^2 $ km/sec.
+\frac{v}{v_{\odot}} \sim 10^{-1} . 
+\end{equation}
+%where $v_{\odot} \sim 4.0 \times 10^2 $ km/sec.
 
@@
 
-In order to estimate the planetary magnetic field of general planets, we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.
-
-Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006,christensen_et_al2009} %\memoYF{check!}
+We estimate the planetary magnetic field of general planets  
+simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G according to the planetary mass and age, based on the predicted scaling relation described below. 
+% we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.
+
+So far, several scaling relations for the planetary magnetic field strength  
+have been proposed \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006,christensen_et_al2009} %\memoYF{check!}
 %(see \citet{griesmeier2004} or \citet{christensen2010} for the summary), 
-which are compared with numerical simulations in \citet{christensen2010}. 
-We employ the relationship proposed in \citet{christensen_et_al2009}, which is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space:
+which are summarized and compared with numerical simulations in \citet{christensen2010}. 
+We employ the scaling law proposed in \citet{christensen_et_al2009}, which is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
 %\memoYF{describe in more detail}:
@@
 \begin{equation}
-\langle B_c \rangle ^2 \propto f_{\rm ohm} \langle \rho_c \rangle ^{1/3} (Fq_o)^{2/3} \label{eq:Bscaling} 
+B_{\rm dynamo} ^2 \propto f_{\rm ohm}\;\rho_{\rm dynamo}  ^{1/3} \;  (Fq_o)^{2/3} \label{eq:Bscaling} 
 \end{equation}
@@
 %where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
-where $\langle B_c \rangle$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\langle \rho_c \rangle$ is the mean density in the dynamo region, $F$ is the efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
+where $B_{\rm dynamo}$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\rho_{\rm dynamo} $ is the mean density in the dynamo region, $F$ is the efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
+Here, $f_{\rm ohm}$ and $F$ are assumed to be constant for the bodies considered in this paper. 
 Dipole magnetic field strength at the planetary surface, denoted by $B$, is then scaled by
@@
 \begin{equation}
-B \propto B_c \left( \frac{r_c}{R_p} \right)^3 \label{eq:Bscaling2}
-\end{equation}
-%%%%%%%%%%
-Magnetic field of planets are estimated by scaling Jovian magnetic field $B_J \sim 10$~G with equations (\ref{eq:Bscaling}) and (\ref{eq:Bscaling2}) assuming that $f_{\rm ohm}$ and $F$ are roughly constant.
-
-In order to evaluate $\rho _c $ and $q_o$, we need a model of internal structure of planets. 
+B \propto B_{\rm dynamo} \left( \frac{r_{\rm dynamo}}{R_p} \right)^3.  \label{eq:Bscaling2}
+\end{equation}
+%%%%%%%%%%
+where $r_{\rm dynamo}$ is the radius of the outer boundary of the dynamo region.
+
+Note that the scaling law, equation (\ref{eq:Bscaling}), would be reasonable only for the rapidly rotating objects.
+Indeed, unlike canonical hot Jupiters, RGHJs are not subjected to tidal lock and we do not have to assume slow spin rotation rate for them \citep{spiegel+madhusudhan2012}.
+Thus, we implicitly assume that RGHJs we consider are rapidly rotating so that they generate  planetary magnetic fields through the same mechanism as Jupiter.
+
+In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need a model of internal structure of planets. 
 In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, because the numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
@@
 %%%%%%%%%%
-We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006, griesmeier2007b}.
-The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
-In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$.
-
-The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the time-dependent net planetary luminosity by the surface area of the core region, i.e., $4\pi r_c^2$. 
+We determine the radius of outer boundary of the dynamo region, $r_{\rm dynamo}$, by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006, griesmeier2007b}.
+The density of the metallic core, $\rho _{\rm dynamo}$ is obtained by averaging the density in the core.
+In the case of Jupiter, $r_{\rm dynamo, J} = 0.85 R_{\rm J}$ and $\rho_{\rm dynamo, J} = 1.899~{\rm g/cm}^3$  .
+
+The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
 The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
@@
 \begin{equation}
-L \sim 1.4\times 10^{-9} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
+L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
 \label{eq:burrowsLum}
@@
 %%%%%%%%%%
-Therefore, we have
+\memoYF{dependence on Rossland mean opacity} Therefore, we have
 %%%%%%%%%%
@@
 %%%
-where in Eq.~(\ref{eq:fplasmalos_scaled}) we have taken the solar mass-loss rate $\dot M_\odot$ to be $2.0 \times 10^{-14}~M_\odot$/yr and the typical solar wind velocity $v_{\odot }$ to be 400~km/sec.
+%where in Eq.~(\ref{eq:fplasmalos_scaled}) we have taken the solar mass-loss rate $\dot M_\odot$ to be $2.0 \times 10^{-14}~M_\odot$/yr and the typical solar wind velocity $v_{\odot }$ to be 400~km/sec.
 
@@
 
-The auroral radio spectral flux of exoplanets observed at the Earth, $F_{\nu}$ can be expressed by:
+The auroral radio spectral flux of exoplanets observed at the Earth, $F_{\nu}$, can be expressed by:
 %%%
@@
 We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}.
-The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
+The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
 %Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
@@
 where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
-%
-In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
+%In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
 It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
-
-In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$, because as indicated earlier, the kinetic energy of the stellar wind of evolved stars are much larger than the main-sequence stars and thus may lead to brighter radio emission.
-
-On the other hand, if the correlation with input magnetic energy is more fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well known for highly evolved stars; many of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}.
+In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$ and consider the possible effects of massive stellar wind.
+
+On the other hand, in the case that the correlation with input magnetic energy is fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well constrained for highly evolved stars; most of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}.
 In the case of M-type giant EK boo, surface magnetic field $\sim 0.1-10 $G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus also may also increase the planetary radio emission.
@@
 Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
+\memoYF{reconsidering...}
 
@@
 The radius obtained for Jupiter from this equality is about a half of actual radius of Magnetosphere \citep[][]{griesmeier2005}. 
-We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e.,
+By scaling this radius with equations (\ref{eq:n}) and (\ref{eq:stand-off}), the radius of magnetosphere of planets would be estimated as:
+%If the radius of magnetosphere is estimated by scaling that of Jupiter according to equations (\ref{eq:n}) and (\ref{eq:stand-off}), 
+%We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
 %%%
@@
 
-First, we estimate the strength of planetary magnetic field based on the scaling relation of equation (\ref{eq:Bscaling}) and assumptions described in \S\ref{ss:magneticfield}. 
-Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_o$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age.
-Because $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
+Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($f_{\rm cyc}$), as well as the core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_o$), as functions of planetary mass and the age.
+Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
 %%%%%%%%%% 
@@
 
-Note that the cyclotron frequency of Jovian planets older than 1~Gyr is typically larger than 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
+Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
 In this regime, there are a number of current and near-future radio wave detectors including UTR-2, LOFAR, LWA, and SKA.
@@
 
-Now, we compare radio emission power of canonical hot Jupiters and that of red giant hot Jupiters.
-Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}.
+We may compare radio emission power of canonical hot Jupiters set at 0.05 AU  and that of RGHJs at 5 AU.
+%Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}. 
 Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows.
@@
 %%%
-Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
+Here we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
 Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be even weaker.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htdp]
-\caption{Canonical Parameters of 2 types of hot jupiters.}
-\begin{center}
-\begin{tabular}{c|cccc} \hline \hline
-& mass & magnetic field & orbit &  spin period \\ 
-& $M_p$ & B & $a$ &  \\ \hline
-canonical HJ & $M_J$ & $B_J$ & 0.05 AU & 4 days \\
-RGHJ & $M_J$ & $B_J$ & 5 AU &  0.4 days \\ \hline
-\end{tabular}
-\end{center}
-\label{tab:comp_HJ}
-\end{table}%
+%\begin{table}[htdp]
+%\caption{Canonical Parameters of 2 types of hot jupiters.}
+%\begin{center}
+%\begin{tabular}{c|cccc} \hline \hline
+%& mass & magnetic field & orbit &  spin period \\ 
+%& $M_p$ & B & $a$ &  \\ \hline
+%canonical HJ & $M_J$ & $B_J$ & 0.05 AU & 4 days \\
+%RGHJ & $M_J$ & $B_J$ & 5 AU &  0.4 days \\ \hline
+%\end{tabular}
+%\end{center}
+%\label{tab:comp_HJ}
+%\end{table}%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
    \plotonesc{radio_emission_Mdot1e-5_constRp_christensen.pdf}
-   \caption{[{\bf New version: based on scaling relationship of Christensen 2010}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
+   \caption{[{\bf New version: based on scaling relationship of Christensen 2010}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 10 pc.
 The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere.
@@
 
-Combining the expressions above for the dependence of radio emission on planetary magnetic field strength, we find that the radio spectral flux density observed at the Earth is:
+Combining the expressions above, we find that the radio spectral flux density observed at the Earth is:
 %%%
@@
 
-However, observed energy flux is limited by the plasma cut-off frequency in the vicinity of the planets, given by Eq.~(\ref{eq:fplasmalos_scaled}).
-We can see emission only from where the cyclotron frequency (Eq.~\ref{eq:fcyc}) exceeds the plasma frequency:
+Using the model for planetary magnetic field strength, we may consider the  radio spectral intensity and maximum frequency of given planetary mass and age. 
+Figure \ref{fig:radio} shows the contours of spectral radio flux of planetary companions at 4.5~Gyr with varying masses and orbital distances. 
+The target system is located at a distance of 10~pc from the Earth; the flux can be scaled by the distance as a quadratic function. 
+The spectral radio emission from RGHJs at around 5-10 AU is found to be $\sim 10^{-6}-10^{-3}$ Jy when observed from 10-100 pc away.
+
+Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by Eq.~(\ref{eq:fplasmalos_scaled}).
+We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency:
 %%%
@@
 %%%
-or, 
+The hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where this criteria is not satisfied and thus the radio emission from the planet cannot be observed from the Earth.
+
+Equation (\ref{eq:fcyc>fplasma}) can also be rewritten as: 
 %%%
@@
 %%%
-Therefore, given any orbital distance, there is a lower mass limit for a planet to be able to release the  radio wave out of the system.
-
+In other words, given any orbital distance, there is a lower mass limit for a planet to be able to release the  radio wave out of the system. 
 Substituting equation (\ref{eq:Ba_limit}) into equation (\ref{eq:F_nu_RGHJ}) leads to the maximum spectral radio flux at given orbital period:
@@
 \begin{eqnarray}
-F_{\nu} &<& 1.30 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}}^{-2} \right) \\
+F_{\nu} &<& 1.30 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right)^{-2} \\
 && \times \left( \frac{a}{5~\mbox{AU}} \right)^{1/3}  \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
@@
 %%%
-
-Figure \ref{fig:radio} shows the contours of spectral radio flux of planetary companions at 4.5~Gyr with varying masses and orbital distances.
-Here we assumed that the target system is located at a distance of 10~pc from the Earth.
-The flux can be scaled by the distance as a quadratic function.
-The hashed regions indicate the parameter spaces where the radio emission from the planet cannot be observed due to the plasma cut-off frequency of the Earth's ionosphere as well as that of the target planetary system.
 
@@
 
-In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from actual red giants in the case that they have planetary companions around them.
-For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the values of mass, radius, and effective temperature, and also obtained the values of parallax from the original Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS} to compute thes distance.
-
+In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
+For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
 For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
@@
 %%%
-Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion.
-Here, we consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, [B] a larger Jovian planet with $M_p\sim 2M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 70$~MHz, and [C] a larger Jovian planet with $M_p\sim 4M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 200$~MHz
+We also obtained the data of parallax from the original Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS} to compute the distance.
+
+Using these estimates for stellar wind for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can calculate the maximum frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion.
+We consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, [B] a larger Jovian planet with $M_p\sim 2M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 70$~MHz, and [C] a larger Jovian planet with $M_p\sim 4M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 200$~MHz
   (equation (\ref{eq:scalingfc})).
@@
 \begin{equation}
-r=\frac{mv}{eB}.
+r=\frac{mv_\bot }{eB}.
 \end{equation}
@@
 \begin{equation}
-\mu = \frac{e}{2\pi r/v} \pi r^2 = \frac{1}{2} e r v = \frac{mv^2}{2B}.
+\mu = \frac{e}{2\pi r/v_\bot} \pi r^2 = \frac{1}{2} e r v_\bot = \frac{mv_\bot^2}{2B}.
 \end{equation}
@@
 
----
-
-%%%
 Hence, for a number density $n$ of these charged particles, the fraction of canceling field to the background magnetic field is
@@
 \begin{equation}
-\frac{B_c}{B} = \frac{n(mv^2/2)}{3 B^2/8\pi}= \frac{\rho_K}{3\rho_B},
+\frac{B_c}{B} = \frac{n(mv_\bot^2/2)}{3 B^2/8\pi} < \frac{\rho_K}{3\rho_B},
 \end{equation}
@@
 where $\rho_K$ and $\rho_B$ are the kinetic energy density and the magnetic energy density, respectively. 
-If the initial velocity is not perpendicular to the magnetic field, $v$ must everywhere be replaced by its perpendicular component.
-
-%
-At the magnetic stand-off point, 
-%%%
-\begin{equation}
-m_p n[r_s] v^2 = \frac{B[r_s]^2}{2\pi }
-\end{equation}
-%%%
-and thus $\rho_K \sim \rho _B$. When the particle spirals into the planet, the kinetic energy of the moment is
-%%%
-\begin{equation}
-\frac{mv^2}{2} \propto \frac{1}{r}
-\end{equation}
-%%%
-while magnetic pressures increases (by beaming?) by 
+%If the initial velocity is not perpendicular to the magnetic field, $v$ must everywhere be replaced by its perpendicular component.
+
+Just inside the stand-off point, 
+%%%
+\begin{equation}
+m_p n[r_s] v^2 < \frac{B[r_s]^2}{2\pi }
+\end{equation}
+%%%
+and thus $\rho_K/\rho _B < 1$. 
+When the particle spirals into the planet, 
+the magnetic pressures increases (by beaming?) by 
 %%%
@@
 %%%
-therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.
-
-\memoYF{$\ast \ast \ast$ How about the following argument instead? $\ast \ast \ast$}
-
-%%%
-\begin{equation}
-r=\frac{mv_{\bot }}{eB}.
-\end{equation}
-%%%
-which creates a magnetic dipole
-%%%
-\begin{equation}
-\mu = \frac{e}{2\pi r/v_{\bot }} \pi r^2 = \frac{1}{2} e r v_{\bot } = \frac{mv_{\bot }^2}{2B}.
-\end{equation}
-%%%
-The volume integral of the canceling magnetic field $B_c$ generated by a single dipole $\mu$ is
-%%%
-\begin{equation}
-\int d^3{\boldsymbol r} B_c = \frac{8\pi}{3} \mu.
-\end{equation}
-%%%
-
-At the magnetic stand-off point, 
-%%%
-\begin{equation}
-\left. \frac{B_c}{B}\right|_{r=r_s} = \frac{8\pi n \mu}{3B} = \frac{4\pi nmv_{\bot }^2}{3 B^2}
-\end{equation}
-%%%
-but because
-%%%
-\begin{equation}
-m_p n v^2 \sim \frac{B^2}{2\pi }
-\end{equation}
-%%%
-and because $v_{\bot }^2 < v^2$, we have $|B_c/B| < 2/3$. 
-When the particles are spiraling down along the magnetic field line, the magnetic dipole moment are approximately constant. 
-On the other hand, the ambient magnetic field strength increase as $\propto r^{-3}$ where $r$ is the distance from the center of a planet.
-
----
-
-%Since by definition $\rho_K/\rho_B < 1$ inside the magnetic stand-off point where the auroral emission is from, the canceling magnetic field is much smaller than the canceling magnetic field.
-
-It is interesting to note that, for a plasma of protons and electrons in a stellar wind, the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.
+On the other hand, the kinetic energy of the moment increases at most
+%%%
+\begin{equation}
+%\frac{mv^2}{2} \propto \frac{1}{r}
+\rho _K \propto \frac{1}{r}
+\end{equation}
+%%%
+Therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.
+
+%It is interesting to note that, for a plasma of protons and electrons in a stellar wind, the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.
 
@@
 In this paper, we propose that ``hot Jupiters'' around evolved stars (RGHJ) may be bright radio wave emitters, on the assumption of the simple empirical correlation between the radio emission and the kinetic input energy.
-Massive stellar wind of red giants and AGB stars would put the kinetic energy into magnetospheres of distant Jovian planets, which could lead to the intrinsic bright radio emission, which is comparable to or by far greater than canonical hot Jupiters in close-in orbits.
+Massive stellar wind of red giants and AGB stars would put the kinetic energy into magnetospheres of distant Jovian planets, which could lead to the intrinsic bright radio emission, comparable to or greater than canonical hot Jupiters in close-in orbits.
 
@@
 
-Admittedly, uncertainties exist both in the scaling of planetary magnetic field  and the scaling of radio emission of Jovian planets in relation to the input energy. 
+Admittedly, uncertainties exist in the relation between radio emission of Jovian planets and the input energy from stellar wind, as well as in the scaling of planetary magnetic field. 
 Alternatively, once we detect both the gravitational perturbation and radio emission of Jovian planets, these models will be contested.

### 2015-06-24 ms.tex
beginnings of a sensitivity table, and comments on introductory material

@@
 \def\memoDS#1{\color{blue}$[${\bf #1}$]$ \color{black}}
+
+\definecolor{DarkGreen}{rgb}{0.0, 0.6, 0.0}
+\def\memoTM#1{\color{DarkGreen}$[${\bf #1}$]$ \color{black}}
 
@@
 One important factor in modeling the radio emission due to the interaction between stellar wind and the planetary magnetic field is the density and velocity of stellar wind. 
-The number density of stellar wind, $n$, can be expressed as
+The number density of \memoTM{electrons in the (?)} stellar wind, $n$, can be expressed as
 %%%%%%%%%% 
@@
 \end{eqnarray}
+\memoTM{Somekind of plot of the typical ranges of these quantities might be useful/illustrative.}
 %%%
@@
 
-In reality, the total power of Jovian auroral emission highly varies in time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
+In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
 Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htdp]
+\caption{Detectability of Hot Jupiters with Current and Future Radio Telescopes.}
+\begin{center}
+\begin{tabular}{c|ccc} \hline \hline\\[-0.5pc]
+Instrument & Band & Sensitivity & Time  \\[.25pc]
+ &  & $\mu$Jy~hr$^{1/2}$ &  hr \\[0.25pc] 
+\hline\\[-0.5pc]
+GMRT & 220~MHz &  \\
+HERA  & 70~MHz  &  &  \\
+LOFAR  & 120~MHz  &  &  \\
+LWA  & 70~MHz  &  &  \\
+SKA  & 200~MHz  &  &  \\
+UTR-2 & & & \\
+VLA  & P-band (270-430~MHz)  \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:sens}
+\tablecomments{Time estimates to reach 10~$\mu$Jy RMS.  We consider only
+telescopes that can reach this in less than XX hours without
+being confusion limited.}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{deluxetable}{l|lll}
+%\tablecolumns{4}
+%\tablewidth{0pt}
+%\tabletypesize{\scriptsize}
+%\tablecaption{Detectability of Hot Jupiters with Current and Future Radio Telescopes}
+%\tablehead{ Instrument & Band & Sensitivity & Time  \\ 
+% &  & $\mu$Jy~hr$^{1/2}$ &  hr} 
+%\startdata 
+%GMRT & 220~MHz   &  & \\
+%SKA  & 200~MHz)  &  &  \\
+%VLA  & P-band (270-430~MHz)  &  & 
+%\enddata
+%\tablecomments{Time estimates to reach 10~$\mu$Jy RMS.  We consider only
+%telescopes that can reach this in less than XX hours without
+%being confusion limited.}
+%\label{tab:sens}
+%\end{deluxetable}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-06-24 ms.tex
minor table update

@@
 \hline\\[-0.5pc]
+ASKAP & 700-1700~MHz & 37 & 3.4 \\ % table 3 of http://www.atnf.csiro.au/projects/askap/config.html
 GMRT & 220~MHz &  \\

### 2015-06-24 ms.tex
figure 1 is updated

--- 2015-06-23 ms.tex
@@
 \begin{figure}[htbp]
-   \plotoneh{model_planetaryB_cgs.pdf}
+   \plotoneh{fig1_linear.pdf}
    \caption{Planetary magnetic field as a function of age and planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of internal heat of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
+  \label{fig:planetaryB_pre}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{fig2_Christensen.pdf}
+   \caption{Planetary magnetic field as a function of age for different planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of luminosity of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
   \label{fig:planetaryB}
@@
 %%%
-On the other hand, the kinetic energy of the moment increases at most
-%%%
-\begin{equation}
-%\frac{mv^2}{2} \propto \frac{1}{r}
-\rho _K \propto \frac{1}{r}
+On the other hand, the kinetic energy of the moment increases
+%%%
+\begin{equation}
+\frac{mv^2}{2} \propto \frac{1}{r}
+%\rho _K \propto \frac{1}{r}
 \end{equation}

### 2015-06-25 ms.tex
estimate for radio flux from RGs is updated

@@
 It has been known that Jupiter emits radio wave from the auroral region due to cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
-Potentially, exoplanets can also generate radio emission through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
+Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.
@@
 Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) \citep{spiegel+madhusudhan2012}.
-They are also subject to massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, much higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr .
+They are also subject to a massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, much higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr .
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.
@@
 %\footnote{Escape velocity is $\sqrt{2GM/r}$.}
-Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_{\star}/R_{\star}}$ ($G$ is the gravitational constant, $M_{\star}$ is the stellar mass, and $R_{\star}$ is the stellar radius), a Solar-mass red giant with radius $R_{\star}=100R_{\odot}$ has 10 times as slow stellar wind as that at the Sun, $v_{\odot}$.
+Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_{\star}/R_{\star}}$ ($G$ is the gravitational constant, $M_{\star}$ is the stellar mass, and $R_{\star}$ is the stellar radius), a Solar-mass red giant with radius $R_{\star}=100R_{\odot}$ encounters 10 times as slow stellar wind as that at the Sun, $v_{\odot}$.
 Thus,
@@
 
+---
+
+\memoYF{Before}
+
 In the radio range, the brightness source of the radio emission is Rayleigh-Jeans tail of the Planck function, i.e., $S_{\nu } = 2kT\nu^2/c^2$.
@@
 
+---
+
+\memoYF{After}
+
+The radio intensity of evolved stars in the range of 10~MHz and 1~GHz is not constrained through observation\memoYF{?}. 
+Above 1~GHz, there are several observations.
+For example, \citet{gorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
+
+We estimate the thermal radio flux from the host star to be consistent with these observed data and by extrapolating to the lower frequency range with a simple power law:
+%%%
+\begin{eqnarray}
+f_{\star }(\nu ) &\sim & (0.4-1.375) \times 10^{-3} ~\mbox{Jy} \\
+&& \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
+\end{eqnarray}
+%%%
+If we assume $\alpha = 0.6$ based on constant property wind model, radio flux at 10~pc at 10~MHz-1~GHz is $\sim$ 25 $\mu$Jy-1 mJy, which is below the estimated radio flux of RGHJs. 
+Note that it has also been suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}, in which case the radio flux from the host star would be even lower.
+
 \newpage
@@
 
+\end{document}
+
 \clearpage
-
-%\end{document}
 

### 2015-06-27 ms.tex
equation 23, 24 are modified to be consistent with equation 4

@@
 
+\memoYF{comments on ionized fraction??}
+
+\citet{drake1983}
+%\citet{}
+
 %The temperature of stellar wind of RGs is expected to be 2 orders of magnitude lower than their main sequence counterparts, mainly because the sound speed of hot corona exceeds the escape speed, i.e., hot corona cannot be confined in the stellar atmosphere \citep{suzuki2008}.
@@
 \begin{eqnarray}
-B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
-f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
+%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
+B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
+%f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
+f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
 \end{eqnarray}
@@
 (Jason?)
-
----
-
-\memoYF{Before}
-
-In the radio range, the brightness source of the radio emission is Rayleigh-Jeans tail of the Planck function, i.e., $S_{\nu } = 2kT\nu^2/c^2$.
-Recent observations revealed that this dependence on $\nu$ ($f \propto \nu^{\alpha }$ where $\alpha $ is 2) can approximately be extended as low frequency as 1 GHz \citep{gorman2013}, presumably as a result of the wavelength dependence of the opacity (at longer wavelength we see the region further from the center of the stars) and the decreased temperature as the distance from the stars increases.
-In this paper, we simply assume that the radio emission from the red giants themselves is approximated as a black body radiation at 1000~GHz and proportional to $\nu ^{5/3}$. 
-Thus, the flux from the giants is:
-%%%
-\begin{eqnarray}
-f_{\star } (\nu ) &=& \frac{2R_{\star }^2 k_B T \nu^2}{c^2 d^2}  \\
-&\approx & 1.56 \times 10^{-6} ~\mbox{Jy} \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2} \\
-&& \times \left( \frac{R_{\star }}{10 R_{\odot }} \right)^2 \left( \frac{T_{\star }}{10^{4}~\mbox{K}} \right) \left( \frac{\nu}{1~\mbox{GHz}} \right)^{5/3} 
-\end{eqnarray}
-%%%
-The brightest emission due to interaction with planetary companion to the RGB stars would therefore overwhelm the radio emission from their host stars in the 10-100~MHz range (in the 100-1000~MHz range) unless the stellar radius $R_{\star }$ is larger than $\sim 2000R_{\odot }$ ($\sim 300R_{\odot }$).
-
----
-
-\memoYF{After}
 
@@
 %%%
-If we assume $\alpha = 0.6$ based on constant property wind model, radio flux at 10~pc at 10~MHz-1~GHz is $\sim$ 25 $\mu$Jy-1 mJy, which is below the estimated radio flux of RGHJs. 
+If we assume $\alpha = 0.6$ based on constant property wind model \citep{wright1975,panagia1975,olnon1975}, radio flux at 10~pc from 10~MHz to 1~GHz is $\sim$ 25 $\mu$Jy-1 mJy, which is below the estimated radio flux of RGHJs.
 Note that it has also been suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}, in which case the radio flux from the host star would be even lower.
-
-\newpage
 

### 2015-07-09 ms2.tex
add a cartoon plot, added ms2.tex which is based on ms.tex but includes sabstantial modification after Ignace et al 2010 was found.

--- 2015-06-27 ms.tex
@@
 We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and proposed scaling of planetary magnetic fields. 
-We find that RGHJs might be as bright as canonical hot Jupiters as predicted so far, and thus radio emission from a RGHJ would be visible from a hundred parsec distances with current/future detectors \memoYF{check}.
+We find that RGHJs might be as bright as canonical hot Jupiters as predicted so far, and thus radio emission from a RGHJ would be visible from a hundred parsec distances with current/future detectors \memoYF{need to rewrite}.
 
@@
 
-In this paper, we estimate the radio emission from RGHJs and examine the potential to detect planetary them. 
+Based on this speculation, \citet{ignace2010} examined radio emission from known substellar-mass companions around cool evolved stars.
+They found that the low ionization fraction of the stellar wind of evolved stars suppresses their radio emission and leads to weak radio emission, probably below the detection limit.
+
+\color{red}
+In this paper, we argue that the accretion of massive stellar wind onto the planets would emit strong X-ray, which would ionize the hydrogen atoms around the planets.
+The ionized stellar wind could then interact with the planetary magnetic field in the same way as Solar System planets do.
+We therefore provide optimistic estimates for highly evolved stars, simply extrapolating the radiometric Bode's law. 
+We do not constrain ourselves to the systems known to have sub-stellar companions, given that the survey of exoplanets around highly evolved stars is not complete; rather, we investigate the parameter space where we can search for radio emission and examine the possibility to detect them with current and future instruments.
+\color{black}
+
 In \S2, we describe our assumptions for stellar wind, planetary magnetosphere, frequency of radio emission, and the scaling of planetary radio emission. 
-\S3 presents an estimate of the spectral radio intensity of RGHJs and compares them with what might be expected from canonical hot Jupiters.
-%\S3 also describes the surprising result that, although the planetary magnetic field is crucial to the generation of radio emission at all, there might be an important region in parameter space in which planets with stronger magnetic fields are less easily observable.
+Then, we present an estimate of the spectral radio intensity.
+Then, we present  an estimate of the spectral radio intensity of RGHJs and compares them with what might be expected from canonical hot Jupiters.
+%
+\S3 discusses the observability of these radio emission from these targets with current and near-future instruments, based on the demographics of 
+%
 \S4 discusses possible obstacles to detect radio emission from RGHJs, in particular the effects of intrinsic radio emission of evolved stars and the offsetting effect of the electrons spiraling down along the planetary magnetic field.
-Observability with current and near-future instruments is also examined in \S4. 
+%
 Finally, \S5 concludes the paper with a brief summary.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Assumptions for Planetary Magnetic Field}
+\label{ss:magneticfield}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We estimate the planetary magnetic field of general planets  
+simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G. 
+So far, several scaling relations for the planetary magnetic field strength  
+have been proposed \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006,christensen_et_al2009} %\memoYF{check!}
+%(see \citet{griesmeier2004} or \citet{christensen2010} for the summary), 
+which are summarized and compared with numerical simulations in \citet{christensen2010}. 
+We write the scaling laws as follows:
+%%%%%%%%%%
+\begin{equation}
+B^2 \propto \omega ^\alpha M_p^\beta t^\gamma \label{eq:Bscaling0}
+\end{equation}
+%%%%%%%%%%
+where $\omega $ is the spin rotation rate, $M_p$ is the planetary mass, and $t$ is the age of the planet. 
+Fiducial values we employ are $\alpha = 0$, $\beta \sim 1$, and $\gamma \sim -0.43$, which are obtained based on the following assumptions.
+
+First, we adopt the scaling law proposed in \citet{christensen_et_al2009} \citep[see also][]{reiners2010}, which is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
+%\memoYF{describe in more detail}:
+%%%%%%%%%% 
+%\begin{equation}
+%B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
+%\end{equation}
+\begin{equation}
+B_{\rm dynamo} ^2 \propto f_{\rm ohm}\;\rho_{\rm dynamo}  ^{1/3} \;  (Fq_o)^{2/3} \label{eq:Bscaling} 
+\end{equation}
+%%%%%%%%%%
+%where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
+where $B_{\rm dynamo}$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\rho_{\rm dynamo} $ is the mean density in the dynamo region, $F$ is the efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
+Here, $f_{\rm ohm}$ and $F$ are assumed to be constant for the bodies considered in this paper. 
+Dipole magnetic field strength at the planetary surface, denoted by $B$, is then scaled by
+%%%%%%%%%%
+\begin{equation}
+B \propto B_{\rm dynamo} \left( \frac{r_{\rm dynamo}}{R_p} \right)^3.  \label{eq:Bscaling2}
+\end{equation}
+%%%%%%%%%%
+where $r_{\rm dynamo}$ is the radius of the outer boundary of the dynamo region. 
+%
+Note that the scaling law, equation (\ref{eq:Bscaling}), would be reasonable only for the rapidly rotating objects.
+Indeed, unlike canonical hot Jupiters, RGHJs are not subjected to tidal lock and we do not have to assume slow spin rotation rate for them \citep{spiegel+madhusudhan2012}.
+Thus, we implicitly assume that RGHJs we consider are rapidly rotating so that they generate  planetary magnetic fields through the same mechanism as Jupiter.
+
+In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need a model of internal structure of planets. 
+In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, because the numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
+For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
+%%%%%%%%%% 
+\begin{equation}
+\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
+\end{equation}
+%%%%%%%%%%
+We determine the radius of outer boundary of the dynamo region, $r_{\rm dynamo}$, by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006, griesmeier2007b}.
+The density of the metallic core, $\rho _{\rm dynamo}$ is obtained by averaging the density in the core.
+In the case of Jupiter, $r_{\rm dynamo, J} = 0.85 R_{\rm J}$ and $\rho_{\rm dynamo, J} = 1.899~{\rm g/cm}^3$  .
+
+The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
+The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}.
+Ignoring the relatively weak dependence on  average atmospheric Rosseland mean opacity, the result leads to:
+%%%%%%%%%%
+\begin{equation}
+L \sim 1.84\times10^{-10} L_\odot \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3}  \, 	
+\label{eq:burrowsLum}
+\end{equation}
+%%%%%%%%%%
+Therefore, we have
+%%%%%%%%%%
+\begin{equation}
+q_o \sim q_{o, J} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3}  \left( \frac{r_{\rm dynamo}}{r_{{\rm dynamo},\,J}} \right)^{-2}\, .
+\label{eq:burrowsHeatFlux}
+\end{equation}
+%%%%%%%%%%
+
+Substituting equation (\ref{eq:burrowsHeatFlux}) into equation (\ref{eq:Bscaling2}) and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is roughly, we find that:
+%%%%%%%%%% 
+\begin{equation}
+%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
+B   \sim   10~{\rm G} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
+\end{equation}
+%%%%%%%%%%
+under this model.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Assumptions for Stellar Wind}
@@
 One important factor in modeling the radio emission due to the interaction between stellar wind and the planetary magnetic field is the density and velocity of stellar wind. 
-The number density of \memoTM{electrons in the (?)} stellar wind, $n$, can be expressed as
+The number density of electrons in the stellar wind, $n$, can be expressed as
 %%%%%%%%%% 
@@
 
-While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr
-\citep{reimers1975}
-, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase
+The mass-loss rate, $\dot M_{\star }$, may be expressed in terms of the stellar radius in unit of solar radius, $R_{\star }$, the stellar luminosity in unit of solar luminosity, $L_{\star }$, and the stellar mass in unit of solar mass, $M_{\star }$ \citep{reimers1975}:
+%%%%%%%%%%
+\begin{equation}
+\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \eta \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
+\end{equation}
+%%%%%%%%%%
+where $\eta \sim 0.3-3$. 
+For example, for a star with $R_\star = 100 R_\odot $, $T_{\rm eff} = 4000 K$ (and thus $L_\star  = R_{\star }^2 T_{\star }^4 \sim 2262 L_\odot $) and $M_\star = M_\odot $ gives $\dot M_\star \sim 10^{-7} M_{\odot }$/yr.
+This is about 7 orders of magnitude larger than the solar mass loss rate, $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}. 
+The mass loss rate can be even as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase
 \citep{schild1989, vassiliadis1993, schoier2001, vanloon2005}.
-Therefore, we have
-%%%%%%%%%% 
-\begin{equation}
-\frac{\dot M_\star}{\dot M_{\odot}} \sim 10^6 - 10^9 . 
-\end{equation}
-%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Assumptions for Planetary Magnetic Field}
-\label{ss:magneticfield}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We estimate the planetary magnetic field of general planets  
-simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G according to the planetary mass and age, based on the predicted scaling relation described below. 
-% we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.
-
-So far, several scaling relations for the planetary magnetic field strength  
-have been proposed \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006,christensen_et_al2009} %\memoYF{check!}
-%(see \citet{griesmeier2004} or \citet{christensen2010} for the summary), 
-which are summarized and compared with numerical simulations in \citet{christensen2010}. 
-We employ the scaling law proposed in \citet{christensen_et_al2009}, which is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
-%\memoYF{describe in more detail}:
-%%%%%%%%%% 
-%\begin{equation}
-%B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
-%\end{equation}
-\begin{equation}
-B_{\rm dynamo} ^2 \propto f_{\rm ohm}\;\rho_{\rm dynamo}  ^{1/3} \;  (Fq_o)^{2/3} \label{eq:Bscaling} 
-\end{equation}
-%%%%%%%%%%
-%where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
-where $B_{\rm dynamo}$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\rho_{\rm dynamo} $ is the mean density in the dynamo region, $F$ is the efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
-Here, $f_{\rm ohm}$ and $F$ are assumed to be constant for the bodies considered in this paper. 
-Dipole magnetic field strength at the planetary surface, denoted by $B$, is then scaled by
-%%%%%%%%%%
-\begin{equation}
-B \propto B_{\rm dynamo} \left( \frac{r_{\rm dynamo}}{R_p} \right)^3.  \label{eq:Bscaling2}
-\end{equation}
-%%%%%%%%%%
-where $r_{\rm dynamo}$ is the radius of the outer boundary of the dynamo region.
-
-Note that the scaling law, equation (\ref{eq:Bscaling}), would be reasonable only for the rapidly rotating objects.
-Indeed, unlike canonical hot Jupiters, RGHJs are not subjected to tidal lock and we do not have to assume slow spin rotation rate for them \citep{spiegel+madhusudhan2012}.
-Thus, we implicitly assume that RGHJs we consider are rapidly rotating so that they generate  planetary magnetic fields through the same mechanism as Jupiter.
-
-In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need a model of internal structure of planets. 
-In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, because the numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
-For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
-%%%%%%%%%% 
-\begin{equation}
-\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
-\end{equation}
-%%%%%%%%%%
-We determine the radius of outer boundary of the dynamo region, $r_{\rm dynamo}$, by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006, griesmeier2007b}.
-The density of the metallic core, $\rho _{\rm dynamo}$ is obtained by averaging the density in the core.
-In the case of Jupiter, $r_{\rm dynamo, J} = 0.85 R_{\rm J}$ and $\rho_{\rm dynamo, J} = 1.899~{\rm g/cm}^3$  .
-
-The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
-The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
-%%%%%%%%%%
-\begin{equation}
-L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
-\label{eq:burrowsLum}
-\end{equation}
-%%%%%%%%%%
-\memoYF{dependence on Rossland mean opacity} Therefore, we have
-%%%%%%%%%%
-\begin{equation}
-q_o \sim q_{o, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
-\label{eq:burrowsHeatFlux}
-\end{equation}
-%%%%%%%%%%
-
-We note that the scaling relation based on \citet{christensen_et_al2009}, or equation (\ref{eq:Bscaling}), has also been adopted in \citet{reiners2010}.
-While the detailed treatment of $\rho _c$ and $q_o$ are different, two estimates of planetary magnetic field strength are fairly close, as shown in \S3 below.
-
-%We estimate the convected heat flux by dividing this luminosity by the surface area of the core region, i.e., $4 \pi r_c^2$.
-
-%\memoYF{I am not sure if the following paragraph is needed.}
-%There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
-%In particular, \citet{griesmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
-%%%%%%%%%% 
-%\begin{equation}
-%\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
-%\end{equation}
-%%%%%%%%%%
-%where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
-%The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
-%
-%Unlike canonical hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
-Without no physical insights of the typical spin rate, we could assume that of Jupiter: $\omega = 9.925$ [hr].
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Cut-off frequency}
-%\label{ss:cutoff}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Frequency of Radio Emission}
@@
 where $e$ and $m_e$ are the charge and mass of the electron, respectively.
+Using equation (\ref{eq:scalingB}), 
+%%%%%%%%%% 
+\begin{equation}
+f_{\rm cyc} \sim  28~{\rm MHz} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} . \label{eq:scalingfc} 
+\end{equation}
+%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Estimates}
 \label{s:result}
@@
 Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($f_{\rm cyc}$), as well as the core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_o$), as functions of planetary mass and the age.
-Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
-%%%%%%%%%% 
-\begin{eqnarray}
-%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
-B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
-%f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
-f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
-\end{eqnarray}
-%%%%%%%%%%
-under this model.
 

### 2015-07-09 ms2.tex
cartoon figure is inserted

@@
 
-(Jason?)
-
 The radio intensity of evolved stars in the range of 10~MHz and 1~GHz is not constrained through observation\memoYF{?}. 
@@
 %%%
-If we assume $\alpha = 0.6$ based on constant property wind model \citep{wright1975,panagia1975,olnon1975}, radio flux at 10~pc from 10~MHz to 1~GHz is $\sim$ 25 $\mu$Jy-1 mJy, which is below the estimated radio flux of RGHJs.
-Note that it has also been suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}, in which case the radio flux from the host star would be even lower.
+Constant property wind model \citep{wright1975,panagia1975,olnon1975} predicts $\alpha = 0.6$, while observations suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}. 
+Figure \ref{fig:cartoon} show a cartoon for a radio spectrum of a Jovian-mass RGHJs and that of the host red giant stars with 100 $R_{\odot }$, both of which is placed at 10 pc away.  
+As this figure indicates, the radio emission from RGHJs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{cartoon.pdf}
+   \caption{A cartoon of radio emission spectra of a Jovian-mass RGHJ and the host red giants with 100 $R_{\odot }$.
+The spectrum of RGHJ is modeled after Jovian radio spectra \citep[][e.g.]{zarka2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law.
+}
+  \label{fig:cartoon}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-07-19 ms.tex
removed extra eq #s
Arguemnt for ionization fraction is added

@@
 
-In this paper, we estimate the radio emission from RGHJs and examine the potential to detect planetary them. 
+Based on this speculation, \citet{ignace2010} examined radio emission from known substellar-mass companions around cool evolved stars.
+They found that the low ionization fraction of the stellar wind of evolved stars suppresses their radio emission and leads to weak radio emission, probably below the detection limit.
+
+\color{red}
+In this paper, we argue that the accretion of massive stellar wind onto the planets would emit strong X-ray, which can ionize the hydrogen atoms around the planets.
+The ionized stellar wind could then interact with the planetary magnetic field in the same way as Solar System planets do.
+We therefore provide optimistic estimates for highly evolved stars, simply extrapolating the radiometric Bode's law. 
+We do not constrain ourselves to the systems known to have sub-stellar companions, given that the survey of exoplanets around highly evolved stars is not complete; rather, we investigate the parameter space where we can search for radio emission and examine the possibility to detect them with current and future instruments.
+\color{black}
+
 In \S2, we describe our assumptions for stellar wind, planetary magnetosphere, frequency of radio emission, and the scaling of planetary radio emission.
@@
 
-Before estimating the frequency of planetary radio emission and the spectral radio intensity, we specify the property of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}, and that of planetary magnetic field in \S\ref{ss:magneticfield}.
+Before estimating the frequency of planetary radio emission and the spectral radio intensity, we specify the property of the planetary magnetic field in \S\ref{ss:magneticfield}, and that of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}.
 Then, we discuss the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Assumptions for Planetary Magnetic Field}
+\label{ss:magneticfield}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We estimate the planetary magnetic field of general planets  
+simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G according to the planetary mass and age, based on the predicted scaling relation described below. 
+% we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.
+
+So far, several scaling relations for the planetary magnetic field strength  
+have been proposed \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006,christensen_et_al2009} %\memoYF{check!}
+%(see \citet{griesmeier2004} or \citet{christensen2010} for the summary), 
+which are summarized and compared with numerical simulations in \citet{christensen2010}. 
+We employ the scaling law proposed in \citet{christensen_et_al2009}, which has already been used in \citet{reiners2010} to explore the evolution of planetary magnetic fields.
+This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
+%\memoYF{describe in more detail}:
+%%%%%%%%%% 
+%\begin{equation}
+%B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
+%\end{equation}
+\begin{equation}
+B_{\rm dynamo} ^2 \propto f_{\rm ohm}\;\rho_{\rm dynamo}  ^{1/3} \;  (Fq_o)^{2/3} \label{eq:Bscaling} 
+\end{equation}
+%%%%%%%%%%
+%where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
+where $B_{\rm dynamo}$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\rho_{\rm dynamo} $ is the mean density in the dynamo region, $F$ is the efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
+Here, $f_{\rm ohm}$ and $F$ are assumed to be constant for the bodies considered in this paper. 
+Dipole magnetic field strength at the planetary surface, denoted by $B$, is then scaled by
+%%%%%%%%%%
+\begin{equation}
+B \propto B_{\rm dynamo} \left( \frac{r_{\rm dynamo}}{R_p} \right)^3.  \label{eq:Bscaling2}
+\end{equation}
+%%%%%%%%%%
+where $r_{\rm dynamo}$ is the radius of the outer boundary of the dynamo region.
+
+Note that the scaling law, equation (\ref{eq:Bscaling}), would be reasonable only for the rapidly rotating objects.
+Indeed, unlike canonical hot Jupiters, RGHJs are not subjected to tidal lock and we do not have to assume slow spin rotation rate for them \citep{spiegel+madhusudhan2012}.
+Thus, we implicitly assume that RGHJs we consider are rapidly rotating so that they generate  planetary magnetic fields through the same mechanism as Jupiter.
+
+In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need a model of internal structure of planets. 
+In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, because the numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
+For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
+%%%%%%%%%% 
+\begin{equation}
+\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
+\end{equation}
+%%%%%%%%%%
+We determine the radius of outer boundary of the dynamo region, $r_{\rm dynamo}$, by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006, griesmeier2007b}.
+The density of the metallic core, $\rho _{\rm dynamo}$ is obtained by averaging the density in the core.
+In the case of Jupiter, $r_{\rm dynamo, J} = 0.85 R_{\rm J}$ and $\rho_{\rm dynamo, J} = 1.899~{\rm g/cm}^3$  .
+
+The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
+The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
+Ignoring the relatively weak dependence on  average atmospheric Rosseland mean opacity, the result leads to:
+%%%%%%%%%%
+\begin{equation}
+L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
+\label{eq:burrowsLum}
+\end{equation}
+%%%%%%%%%%
+Therefore, we have
+%%%%%%%%%%
+\begin{equation}
+q_o \sim q_{o, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
+\label{eq:burrowsHeatFlux}
+\end{equation}
+%%%%%%%%%%
+
+Substituting equation (\ref{eq:burrowsHeatFlux}) into equation (\ref{eq:Bscaling2}) and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is roughly, we find that:
+%%%%%%%%%% 
+\begin{equation}
+%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
+B   \sim   10~{\rm G} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
+\end{equation}
+%%%%%%%%%%
+under this model.
+
+%We note that the scaling relation based on \citet{christensen_et_al2009}, or equation (\ref{eq:Bscaling}), has also been adopted in \citet{reiners2010}.
+While the detailed treatment of $\rho _c$ and $q_o$ are different, two estimates of planetary magnetic field strength are fairly close, as shown in \S3 below.
 
@@
 
-One important factor in modeling the radio emission due to the interaction between stellar wind and the planetary magnetic field is the density and velocity of stellar wind. 
+Another ingredient needed for modeling the radio emission from the interaction between the planetary magnetic field and the stellar wind is the density and velocity of the stellar wind. 
 The number density of \memoTM{electrons in the (?)} stellar wind, $n$, can be expressed as
@@
 \begin{equation}
-\frac{\dot M_\star}{\dot M_{\odot}} \sim 10^6 - 10^9 . 
+\frac{\dot M_\star}{\dot M_{\odot}} \sim 10^6 - 10^9 . \label{eq:scale_Mdot}
 \end{equation}
@@
 Thus,
-\begin{equation}
-\frac{v}{v_{\odot}} \sim 10^{-1} . 
-\end{equation}
+%%%%%%%%%% 
+\begin{equation}
+\frac{v}{v_{\odot}} \sim 10^{-1} . \label{eq:scale_v}
+\end{equation}
+%%%%%%%%%% 
 %where $v_{\odot} \sim 4.0 \times 10^2 $ km/sec.
 
-\memoYF{comments on ionized fraction??}
-
-\citet{drake1983}
+Based on equations (\ref{eq:scale_Mdot}) and (\ref{eq:scale_v}), the number density of the stellar wind (equation (\ref{eq:n})) are normalized as follows:
+%%%%%%%%%% 
+\begin{equation}
+n = 1.80 \times 10^6 \; {\rm cm^{-3}} \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30\; {\rm km}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \label{eq:n_normalized}
+\end{equation}
+%%%%%%%%%%
+
+\memoYF{check from here}
+As discussed in \citet{ignace2010}, one potential problem of the stellar wind of evolved stars which is unfavorable for radio emission is that their ionization fraction is usually as low as $10^{-3}$ \memoYF{cite something}, which would lead to inefficient interaction with planetary magnetosphere and hence low input energy for radio emission.
+However, at this stage the velocity of stellar wind becomes slower than the escape velocity of planetary companion and hence the stellar wind particles are expected to accrete onto the planets. 
+Based on \citet{spiegel+madhusudhan2012}, the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ are: 
+%%%%%%%%%
+\begin{eqnarray}
+L_{\rm acc} \sim &&  10^{29} \; {\rm erg\;s}^{-1} \\
+&& \times \left( \frac{\dot M_*}{10^{-7} M_{\odot }\;{\rm yr}} \right) \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \\
+%
+T_{\rm acc} \sim && 2 \times 10^6 \left( \frac{M_p}{10 M_J} \right)
+\end{eqnarray}
+%%%%%%%%%
+The accretion disks around planets therefore emit X-ray radiation. 
+We estimate the scale of the ionized region by computing Stromgren radius of the accretion disk: 
+%%%%%%%%%
+\begin{equation}
+R_{\rm stromgren} = \frac{3}{4\pi} \left( \frac{S}{n^2 \beta } \right)^{1/3}
+\end{equation}
+%%%%%%%%%
+where $S$ is the source rate of ionizing photons, $n$ is the density of hydrogen, and $\beta $ is the coefficient for recombination \memoYF{need to check}:
+% http://www.tapir.caltech.edu/~chirata/ay102/Photoionized.pdf
+% T \propto 4.3e-13 ( T /10^4 K )^-0.7
+%%%%%%%%%
+\begin{eqnarray}
+\beta &=& 4.3? \times 10^{-13} \; \left( \frac{T}{10^4 \;{\rm K}} \right) ^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} \\
+&\sim& 5.28 \times 10^{-14} \; \left( \frac{M_p}{M_J} \right)^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} 
+\end{eqnarray}
+%%%%%%%%%
+The source rate is obtained by counting the number of photons whose energy is higher than 13.6 eV, the energy needed to ionize hydrogen atoms. Thus\memoYF{need to check},  
+%%%%%%%%%
+\begin{eqnarray}
+S_* = 
+  \left\{
+    \begin{array}{ll}
+      1.18 \times 10^{42} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
+      2.66 \times 10^{44} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
+    \end{array}
+  \right.
+\end{eqnarray}
+%%%%%%%%%
+and the number density of hydrogen atoms are given by equation (\ref{eq:n_normalized}). 
+These values give \memoYF{need to check}
+%%%%%%%%%
+\begin{eqnarray}
+R_{\rm stromgren} = 
+  \left\{
+    \begin{array}{ll}
+      3 \;{\rm AU} & \;\;\;(M_p = M_J) \\
+      30 \;{\rm AU} & \;\;\;(M_p = 10 M_J)
+    \end{array}
+  \right.
+\end{eqnarray}
+%%%%%%%%%
+
+Thus, we expect that the X-ray emission from the accretion disk is enough to ionize the stellar wind.
+Therefore, we assume that the stellar wind particles represented by (equation (\ref{eq:n})) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
+
+%\citet{drake1983}
 %\citet{}
+%\color{black}
 
@@
 %%%
-The radius obtained for Jupiter from this equality is about a half of actual radius of Magnetosphere \citep[][]{griesmeier2005}. 
+The radius obtained for Jupiter from this equality is about a half of actual radius of magnetosphere \citep[][]{griesmeier2005}. 
 By scaling this radius with equations (\ref{eq:n}) and (\ref{eq:stand-off}), the radius of magnetosphere of planets would be estimated as:
@@
 \begin{eqnarray}
-r_s 
+\nonumber r_s 
 %&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
@@
 && \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
-&=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
+\nonumber &=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
 && \times \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
@@
 
-Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($f_{\rm cyc}$), as well as the core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_o$), as functions of planetary mass and the age.
-Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
-%%%%%%%%%% 
-\begin{eqnarray}
+Figure \ref{fig:planetaryB_pre} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region, and Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age.
+%Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
+Reasonably, the resultant values are in a good agreement with \citet{reiners2010}, which adopted the same scaling law for planetary magnetic field; we show this figure just for self-completeness.
+
+%%%%%%%%%% 
+%\begin{eqnarray}
 %B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
-B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
+%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
 %f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
-f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
-\end{eqnarray}
-%%%%%%%%%%
-under this model.
-
+%f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
+%\end{eqnarray}
+%%%%%%%%%%
+%under this model. 
 Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
@@
 
-Based on the assumption that the radio emission is proportional to the input kinetic energy (equation \ref{eq:Pinp_kin}), the scaling of the radio emission is expanded as follows:
+Based on the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows:
 %%%

### 2015-07-21 ms.tex
small updates to table

--- 2015-06-27 ms.tex
@@
 
-In this paper, we estimate the radio emission from RGHJs and examine the potential to detect planetary them. 
+In this paper, we estimate radio emission from RGHJs and examine the potential to detect planetary them. 
 In \S2, we describe our assumptions for stellar wind, planetary magnetosphere, frequency of radio emission, and the scaling of planetary radio emission.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htdp]
+\begin{table*}[htdp]
 \caption{Detectability of Hot Jupiters with Current and Future Radio Telescopes.}
 \begin{center}
-\begin{tabular}{c|ccc} \hline \hline\\[-0.5pc]
-Instrument & Band & Sensitivity & Time  \\[.25pc]
- &  & $\mu$Jy~hr$^{1/2}$ &  hr \\[0.25pc] 
+\begin{tabular}{c|ccccc} \hline \hline\\[-0.5pc]
+Instrument & Band & Sensitivity & Time  & Resolution & Confusion limit\\[.25pc]
+ &  & $\mu$Jy~hr$^{1/2}$ &  hr & \arcsec\ & $\mu$Jy \\[0.25pc] 
 \hline\\[-0.5pc]
-ASKAP & 700-1700~MHz & 37 & 3.4 \\ % table 3 of http://www.atnf.csiro.au/projects/askap/config.html
-GMRT & 220~MHz &  \\
-HERA  & 70~MHz  &  &  \\
-LOFAR  & 120~MHz  &  &  \\
-LWA  & 70~MHz  &  &  \\
+%ASKAP & 700-1700~MHz & 37 & 342.3 \\ % table 3 of http://www.atnf.csiro.au/projects/askap/config.html
+GMRT  & 235~MHz &  165.6 & 6860 & 13 \\ % http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html
+HERA  & 70~MHz  &  &  \\ % http://reionization.org/wp-content/uploads/2015/05/HERA0_imaging.pdf
+% https://www.astron.nl/~heald/test/sens.php; 
+% 24 core stations, 16 remote, 8 international, 488 subbands
+LOFAR & ~45~MHz  &  833!! &  &  & \\
+LOFAR & ~60~MHz  &  648!! &  &  & \\
+LOFAR & 120~MHz  &  51.73 &  &  & \\  
+LOFAR & 150~MHz  &  40.97 &  &  & \\  
+LWA   & ~70~MHz  &  &  \\
 SKA   & 200~MHz  &  &  \\
 UTR-2 & & & \\
-VLA  & P-band (270-430~MHz)  \\ \hline
+VLA P-band & (270-470~MHz)  & 138  & 4760 & \\
+\hline
 \end{tabular}
@@
 \label{tab:sens}
-\tablecomments{Time estimates to reach 10~$\mu$Jy RMS.  We consider only
+\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.  We consider only
 telescopes that can reach this in less than XX hours without
 being confusion limited.}
-\end{table}
+\end{table*}
 

### 2015-07-24 ms.tex
note for additional discussion on time variability, cartoon replaced

@@
 \label{s:observability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Intrinsic radio emission of red giants stars}
+\label{ss:RGradio}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The radio intensity of evolved stars in the range of 10~MHz and 1~GHz is not constrained through observation\memoYF{?}. 
+Above 1~GHz, there are several observations.
+For example, \citet{gorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
+
+We estimate the thermal radio flux from the host star to be consistent with these observed data and by extrapolating to the lower frequency range with a simple power law:
+%%%
+\begin{eqnarray}
+f_{\star }(\nu ) &\sim & (0.4-1.375) \times 10^{-3} ~\mbox{Jy} \\
+&& \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
+\end{eqnarray}
+%%%
+Constant property wind model \citep{wright1975,panagia1975,olnon1975} predicts $\alpha = 0.6$, while observations suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}. 
+Figure \ref{fig:cartoon} show a cartoon for a radio spectrum of a Jovian-mass RGHJs and that of the host red giant stars with 100 $R_{\odot }$, both of which is placed at 10 pc away.  
+As this figure indicates, the radio emission from RGHJs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{cartoon2.pdf}
+   \caption{A cartoon of radio emission spectra of a Jovian-mass RGHJ and the host red giants with 100 $R_{\odot }$.
+The spectrum of RGHJ is modeled after Jovian radio spectra \citep[][e.g.]{zarka2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law.
+}
+  \label{fig:cartoon}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Radio Flux from Nearby Evolved Stars}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Discriminating from Background:\\Time Variability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+(from short to long)
+\begin{itemize}
+\item Modulation due to planetary spin rotation (condition: misalignment of spin axis and magnetic axis) 
+\item modulation due to the presence of satellites??
+\item Modulation due to orbital motion of the planet (condition: near edge-on orbit)
+\item Variability of stellar wind due to stellar oscillation 
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussions}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Intrinsic radio emission of red giants stars}
-\label{ss:RGradio}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-(Jason?)
-
-The radio intensity of evolved stars in the range of 10~MHz and 1~GHz is not constrained through observation\memoYF{?}. 
-Above 1~GHz, there are several observations.
-For example, \citet{gorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
-
-We estimate the thermal radio flux from the host star to be consistent with these observed data and by extrapolating to the lower frequency range with a simple power law:
-%%%
-\begin{eqnarray}
-f_{\star }(\nu ) &\sim & (0.4-1.375) \times 10^{-3} ~\mbox{Jy} \\
-&& \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
-\end{eqnarray}
-%%%
-Constant property wind model \citep{wright1975,panagia1975,olnon1975} predicts $\alpha = 0.6$, while observations suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}. 
-Figure \ref{fig:cartoon} show a cartoon for a radio spectrum of a Jovian-mass RGHJs and that of the host red giant stars with 100 $R_{\odot }$, both of which is placed at 10 pc away.  
-As this figure indicates, the radio emission from RGHJs.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-   \plotoneh{cartoon.pdf}
-   \caption{A cartoon of radio emission spectra of a Jovian-mass RGHJ and the host red giants with 100 $R_{\odot }$.
-The spectrum of RGHJ is modeled after Jovian radio spectra \citep[][e.g.]{zarka2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law.
-}
-  \label{fig:cartoon}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-07-26 ms.tex
adding discussion about time variability...(halfway)

--- 2015-07-21 ms.tex
@@
 
+In this section, we discuss the observability of the estimated radio emission. 
+An obvious obstacle is the intrinsic radio emission from host red giant stars themselves; if they are larger than radio flux from the planets, there is no way to identify the latter.
+We will see in \S\ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range.
+Then, we estimate the radio emission of Jupiter-twin around known M giants in \S\ref{ss:actualMgiants}. 
+Finally, \S\ref{ss:timevariability} discusses the expected time variability of the radio emission as a mean to discern the signals from the background noise.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Intrinsic radio emission of red giants stars}
+\label{ss:RGradio}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The radio intensity of evolved stars in the range of 10~MHz and 1~GHz is not constrained through observation\memoYF{?}. 
+Above 1~GHz, there are several observations.
+For example, \citet{gorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
+
+We estimate the thermal radio flux from the host star to be consistent with these observed data and by extrapolating to the lower frequency range with a simple power law:
+%%%
+\begin{eqnarray}
+f_{\star }(\nu ) &\sim & (0.4-1.375) \times 10^{-3} ~\mbox{Jy} \\
+&& \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
+\end{eqnarray}
+%%%
+Constant property wind model \citep{wright1975,panagia1975,olnon1975} predicts $\alpha = 0.6$, while observations suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}.
+
+Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10M_J$ and that of the host red giant stars with 100 $R_{\odot }$, both of which is placed at 10 pc away. 
+As this figure indicates, even if the radio emission from the red giant itself has relatively low spectral index, the radio emission from RGHJs still dominate in the 10-200~MHz range. 
+Therefore, in the following, we ignore the radio emission from the red giant as a noise source.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{cartoon2.pdf}
+   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.
+The spectrum of RGHJ is modeled after Jovian radio spectra \citep[e.g.][]{zarka_et_al2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law.
+}
+  \label{fig:cartoon}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Radio Flux from Nearby Evolved Stars}
+\label{ss:actualMgiants}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
+
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
@@
 %%%
-We also obtained the data of parallax from the original Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS} to compute the distance.
-
-Using these estimates for stellar wind for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can calculate the maximum frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion.
+The age of the system is assumed to roughly same as the lifetime of their main-sequence stage, which depends on the stellar mass:
+%%%
+\begin{equation}
+test
+\end{equation}
+%%%
+In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}.
+
+Using these data, we can now calculate the maximum frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion. 
 We consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, [B] a larger Jovian planet with $M_p\sim 2M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 70$~MHz, and [C] a larger Jovian planet with $M_p\sim 4M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 200$~MHz
-  (equation (\ref{eq:scalingfc})).
+  (equation (\ref{eq:scalingfc})). \memoYF{no!!}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Discriminating from Background:\\Time Variability}
+\label{ss:timevariability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%In order to identify radio emission from exoplanets in the galactic background noise, it is
+
+In order to identify radio emission from exoplanets, it is critical to discern it from the galactic background. 
+An important feature useful for this purpose is the time variability of radio emission. 
+Indeed, several processes cause the time variability of radio emission from exoplanets at different timescales; they are listed below from the ones typically with shorter timescales to those with longer timescales.
+
+\paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)} 
+If the planetary spin axis is misaligned to the planetary magnetic axis, like Jupiter, the radio intensity  will display sinusoidal modulation synchronously to the spin period. 
+%
+
+\memoYF{Modulation due to the presence of satellites (a few hours $\sim $)?} 
+%
+
+\paragraph{Variability of stellar wind due to stellar oscillation (day $\sim $)?}
+Based on the correlation between the planetary radio emission and the solar wind plasma density also suggest that the radio emission from the planet around the evolved stars, which typically oscillate, are time variable.
+%
+\paragraph{Modulation due to orbital motion of the planet (a few years $\sim $)}
+If the planetary orbit is close to the edge-on configuration, the radio emission disappears synchronously to the orbital period, due to the increased plasma cut-off frequency along the path and/or secondary eclipse.
+The former is because when the planet is behind the star the path of the radio emission toward the Earth comes through the vicinity of the star where the plasma density is high.
+The probability of the latter one, secondary eclipse, is $\sim a/R_\star \sim 9$\% (in the case that $a=5~\mathrm{AU}$ and $R_{\star}=100R_{\odot }$).
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussions}

### 2015-07-28 ms.tex
In section 4.2, radio emission is now re-estimated taking into account of the stellar age.

@@
 Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is known as  ``radiometric Bode's law'' \citep{desch+kaiser1984}.
-Based on this law, it has been proposed that exoplanets in close-in orbits may be bright radio wave emitters because they are subjected to strong stellar wind and/or strong interstellar magnetic field, and thus can gain larger energy input.
-Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,Lazio2004,griesmeier2004,griesmeier2007a,griesmeier2007b,reiners2010}.
+Extrapolating this law to exoplanets, radio emission from exoplanetary system has been estimated \citep{farrell1999,zarka2001,lazio2004,griesmeier2004,griesmeier2005,stevens2005,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010}.
+\memoYF{in more detail}
+%Based on this law, it has been proposed that exoplanets in close-in orbits may be bright radio wave emitters because they are subjected to strong stellar wind and/or strong interstellar magnetic field, and thus can gain larger energy input.
+Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,lazio2004,griesmeier2004,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010,}.
 In addition, young planetary systems where the stellar wind activity is stronger are also taken into consideration \citep{griesmeier2005}. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Radio Flux from Nearby Evolved Stars}
+\subsection{Radio Flux from Nearby M giants}
 \label{ss:actualMgiants}
@@
 \begin{figure}[tbhp]
-   \plotoneh{radio_1Mp_5AU.pdf}
+   \plotoneh{radio_1Mp.pdf}
+   \plotoneh{radio_10Mp.pdf}
+%   \plotoneh{radio_1Mp_5AU.pdf}
 %   \plotoneh{radio_5Mp_5AU.pdf}
-   \plotoneh{radio_2Mp_4-5Gyr.pdf}
-   \plotoneh{radio_4Mp_4-5Gyr.pdf}   
+%   \plotoneh{radio_2Mp_4-5Gyr.pdf}
+%   \plotoneh{radio_4Mp_4-5Gyr.pdf}   
    \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$, 2$M_J$, and 4$M_J$ at 1 AU and 5AU.
@@
 \begin{equation}
-\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
+\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \eta \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
 \end{equation}
@@
 where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are radius, luminosity, and mass of the star. 
+The factor $\eta $ is $\sim 0.3-3$, and we assume $\eta =1$ here. 
 The velocity of stellar wind is assumed to scale with the escape velocity, hence
@@
 %%%
-The age of the system is assumed to roughly same as the lifetime of their main-sequence stage, which depends on the stellar mass:
-%%%
-\begin{equation}
-test
+The age of the system is assumed to roughly same as the lifetime of their main-sequence stage, which depends on the stellar mass. We assume \memoYF{validation}:
+%%%
+\begin{equation}
+t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5}
 \end{equation}
@@
 Using these data, we can now calculate the maximum frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion. 
-We consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, [B] a larger Jovian planet with $M_p\sim 2M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 70$~MHz, and [C] a larger Jovian planet with $M_p\sim 4M_p$ of 4.5 Gyrs old whose cyclotron frequency is $\sim 200$~MHz
-  (equation (\ref{eq:scalingfc})). \memoYF{no!!}
-
-Figure \ref{fig:observability} displays the estimated radio intensity and the maximum frequency (i.e., cyclotron frequency) of Jupiters [A], [B], and [C]  around red giants within 100~pc. 
+We consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, and [B] a larger Jovian planet with $M_p\sim 10M_p$ whose cyclotron frequency is $\sim 300$~MHz (equations (\ref{eq:scalingB}) and (\ref{eq:fcyc})).
+
+Figure \ref{fig:observability} displays the estimated radio intensity (i.e., cyclotron frequency) of Jupiters [A] and [B] around M-type red giants within 100~pc. 
 Jupiters are placed at 1 AU and at 5 AU for reference. 
@@
 Based on the correlation between the planetary radio emission and the solar wind plasma density also suggest that the radio emission from the planet around the evolved stars, which typically oscillate, are time variable.
+\memoYF{To Jason: time variability?}
 %
@@
 \bibliography{biblio.bib}
+
+\newpage
+
+\appendix
+
+\section{Comparison with previous work}
+
+There are rather wide variety of estimation for radio emission of Jovian exoplanets and it is worth noting how the different models return different answers.
+
+A common part is the scaling relationship between the planetary magnetic field strength and the input kinetic energy. Combining equation (\ref{eq:Pinp_kin}), i.e.,
+%%%
+\begin{equation}
+P_{\rm inp,k}=nv^3 r_s^2 \propto \dot M_{\star} v^2 a^{-2} r_s^2 s
+\end{equation}
+%%%
+and the scaling between the radius of the magnetic stand-off point, $r_s$, and the planetary magnetic field $B$ (see equation (\ref{eq:stand-off-radius})):
+%%%
+\begin{equation}
+r_s \propto B^{1/3} a^{1/3} \dot M_{\star }^{-1/6} \dot v^{-1/6}
+\end{equation}
+%%%
+under the constant stellar wind, we obtain:
+%%%
+\begin{equation}
+P_{\rm inp, k} \propto B^{2/3} a^{-4/3} \dot M_{\star }^{2/3} \dot v^{5/3}
+\end{equation}
+%%%
+
+%equation (\ref{eq:stand-off-radius})
+%%%
+%\begin{equation}
+%r_s = 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
+%\end{equation}
+%%%
+Aside from this common part, the differences originate mainly from:
+\renewcommand{\theenumi}{\roman{enumi}}
+%%%
+\begin{enumerate}
+\item Assumptions for the scaling law of radio power in terms of input energy. 
+\item Assumptions for the scaling law of planetary magnetic field strength. 
+\item Different normalization (assumptions for Jovian radio emission). 
+\item Assumptions for band width (either $f_{\rm cyc}$ or $0.5f_{\rm cyc}$). 
+\item Modeling of stellar wind
+\end{enumerate}
+%%%
+
+As for i., ii. and iii., the scaling laws are summarized in Table \ref{tab:comp}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}[htdp]
+\caption{Comparison for assumed scaling relationships.}
+\begin{center}
+\begin{tabular}{c|l|llcc} \hline \hline
+%
+& Paper & Radio power & Magnetic moment  & norm [W] & band width \\\hline
+%
+\#1 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{0.88} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^9$ & $ 0.5 f_{\rm cyc}$ \\ \hline
+%
+\#2 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{1.2} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^{11}$ & $ 0.5 f_{\rm cyc}$ \\
+& \citet{lazio2004} & & $\mathcal{M} \propto \omega M_p^{2}$?? & & \\
+& \citet{ignace2010} & & & & \\ \hline
+\#3 & \citet{stevens2005} & $P_{\rm radio} \propto P_{\rm sw} $ & $\mathcal{M} \propto M_p$ & - & - \\ \hline
+\#4 & \citet{griesmeier2005,griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^4 $ & $2.1 \times 10^{11}$ & $ 0.5 f_{\rm cyc}$ \\
+\#5 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega^{1/2} r_c^3 \sigma ^{-1/2} $ & & \\
+\#6 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega^{3/4} r_c^{7/2} \sigma ^{-1/4} $ & \\
+\#7 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^{7/2}$ & & \\ \hline
+%\#8 & \citet{griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & same as above & $2.1 \times 10^{11}$ & $ f_{\rm cyc}$ \\ \hline
+\#8 & \citet{reiners2010} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto M_p^{1/6} L^{1/3} R_p^{25/6}$ \\ 
+ & this work & & \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:comp}
+\tablecomments{}
+\end{table*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+If we use the assumptions that $R_p \sim R_J\;\;(const.)$, $\rho _c\sim R_p\sim const.$, and $\sigma = const.$, then the assumptions are reduced to:
+%%%%%%%%%
+\begin{eqnarray}
+\mbox{[\#1]} \; P_{\rm rad} &\sim & 4 \times 10^9 \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{0.58} \left( \frac{M_p}{M_J} \right)^{0.98} \left( \frac{a}{a_J} \right)^{-1.17} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{0.586} \left( \frac{v}{v_{\odot}} \right)^{1.46} \\
+%
+\mbox{[\#2]} \; P_{\rm rad} &\sim & 4 \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _J} \right)^{0.79} \left( \frac{M_p}{M_J} \right)^{1.33} \left( \frac{a}{a_J} \right)^{-1.60} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{0.8} \left( \frac{v}{v_{\odot}} \right)^{2.0} \\
+%
+\mbox{[\#3]} \; P_{\rm rad} &\sim & ?
+\times 10^{11} \,{\rm W}\,\left( \frac{M_p}{M_J} \right)^{2/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+%
+\mbox{[\#4]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{2/3} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+%
+\mbox{[\#5]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{1/3} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+%
+\mbox{[\#6]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{1/2} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+%
+\mbox{[\#7]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{2/3} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+%
+\mbox{[\#8]} \; P_{\rm rad} &\sim & ?
+\times 10^{11} \,{\rm W}\, \left( \frac{M_p}{M_J} \right)^{0.69}  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-0.288}  \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+\end{eqnarray}
+%%%%%%%%%
+For the last equation, we used the scaling of the luminosity $L$, equation (\ref{eq:burrowsLum}):
+%%%
+\begin{equation}
+L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \tag{\ref{eq:burrowsLum}}
+\end{equation} 
+%%%
+\memoYF{Note that in \citet{ignace2010} the dependence on mass-loss rate and stellar wind velocity is not taken account consistently; in that paper, $P_{\rm rad} \propto \dot M_{\star } v^2$.}
+
+In summary, we write down the scaling of the radio emission as below, 
+%%%
+\begin{equation}
+P_{\rm rad} \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _J} \right)^{\alpha } \left( \frac{M_p}{M_J} \right)^{\beta }  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-\gamma }  \left( \frac{a}{a_J} \right)^{-\delta }  \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{\epsilon } \left( \frac{v}{v_{\odot}} \right)^{\phi } \, \\
+\end{equation} 
+%%%
+with $\alpha = 0.5-0.8$, $\beta = 0.33-1.33$, $\gamma = 0-0.288$, $\gamma = 1.17-1.60$, $\epsilon = 0.58-0.8$, $\phi = 1.46-2.0$.
 

### 2015-07-28 code/sensitivity.py
Added simple script for calculating sensitivity in code/sensitivity.py

@@ -1,0 +1,11 @@
+#! /usr/bin/env python
+import numpy as n
+
+k_b = 1.380658e-16
+
+def Tsky(nu):
+    return 237 * (nu/.150)**-2.5
+
+def sense(d, N, nu, B=100e6, t=3600):
+    return 2 * k_b * Tsky(nu) / (N * d**2 * n.sqrt(B*t) * 1e-23)
+

### 2015-08-07 ms.tex
Moved cartoon to top of column and made it full width. (Might want to undo full width?)
minor table edits

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{table}[htdp]
+%\begin{table}[htp]
 %\caption{Canonical Parameters of 2 types of hot jupiters.}
@@
 \begin{eqnarray}
-f_{\star }(\nu ) &\sim & (0.4-1.375) \times 10^{-3} ~\mbox{Jy} \\
+\nonumber f_{\star }(\nu ) &\sim & (0.4-1.375) \times 10^{-3} ~\mbox{Jy} \\
 && \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-   \plotoneh{cartoon2.pdf}
+\begin{figure*}[tbp]
+   \plotonesc{cartoon2.pdf}
    \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.
@@
   \label{fig:cartoon}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %   \plotoneh{radio_4Mp_4-5Gyr.pdf}   
-   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$, 2$M_J$, and 4$M_J$ at 1 AU and 5AU.
+   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$ and 10$M_J$ at 1 AU and 5AU.
 Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}[htdp]
+\begin{table*}[htp]
 \caption{Detectability of Hot Jupiters with Current and Future Radio Telescopes.}
@@
 \begin{tabular}{c|ccccc} \hline \hline\\[-0.5pc]
-Instrument & Band & Sensitivity & Time  & Resolution & Confusion limit\\[.25pc]
- &  & $\mu$Jy~hr$^{1/2}$ &  hr & \arcsec\ & $\mu$Jy \\[0.25pc] 
+Instrument & Band & Sensitivity & Time  & Resolution & Confusion limit\\
+ & MHz & $\mu$Jy~hr$^{1/2}$ &  hr & \arcsec\ & $\mu$Jy \\[0.25pc] 
 \hline\\[-0.5pc]
@@
 % 24 core stations, 16 remote, 8 international, 488 subbands
-LOFAR & ~45~MHz  &  833!! &  &  & \\
-LOFAR & ~60~MHz  &  648!! &  &  & \\
-LOFAR & 120~MHz  &  51.73 &  &  & \\  
-LOFAR & 150~MHz  &  40.97 &  &  & \\  
-LWA   & ~70~MHz  &  &  \\
-SKA   & 200~MHz  &  &  \\
+LOFAR & ~45  &  833!! &  &  & \\
+LOFAR & ~60  &  648!! &  &  & \\
+LOFAR & 120  &  51.73 &  &  & \\  
+LOFAR & 150  &  40.97 &  &  & \\  
+LWA   & ~70  &  &  \\
+SKA   & 200  &  &  \\
 UTR-2 & & & \\
-VLA P-band & (270-470~MHz)  & 138  & 4760 & \\
+VLA P-band & 270-470  & 138  & 4760 & \\
 \hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}[htdp]
+\begin{table*}[htp]
 \caption{Comparison for assumed scaling relationships.}

### 2015-08-16 ms.tex
cartoon is modified to ignore Io-DAM based on griesmeier 2007

--- 2015-07-28 ms.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-   \plotoneh{cartoon2.pdf}
+\begin{figure*}[tbp]
+   \plotonesc{fig5_10Mj_2.pdf}
    \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.
-The spectrum of RGHJ is modeled after Jovian radio spectra \citep[e.g.][]{zarka_et_al2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law.
+The spectrum of RGHJ is modeled after Jovian radio spectra, e.g.
+figure 8 of \citet{zarka_et_al2004} and figure 2 of \citet{griesmeier2007a}; contribution from Io is not shown here.
+The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law.
 }
   \label{fig:cartoon}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-08-16 ms.tex

--- 2015-08-07 ms.tex
@@
 \begin{figure*}[tbp]
-   \plotonesc{cartoon2.pdf}
+   \plotonesc{fig5_10Mj_2.pdf}
    \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.
-The spectrum of RGHJ is modeled after Jovian radio spectra \citep[e.g.][]{zarka_et_al2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law.
+The spectrum of RGHJ is modeled after Jovian radio spectra, e.g.
+figure 8 of \citet{zarka_et_al2004} and figure 2 of \citet{griesmeier2007a}; contribution from Io is not shown here.
+The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law.
 }

### 2015-08-24 code/sensitivity.py
some notebook updates

@@ -1,5 +1,5 @@
 #! /usr/bin/env python
-import numpy as n
+import numpy as np
 
 k_b = 1.380658e-16
 
@@ -7,5 +7,5 @@ def Tsky(nu):
     return 237 * (nu/.150)**-2.5
 
 def sense(d, N, nu, B=100e6, t=3600):
-    return 2 * k_b * Tsky(nu) / (N * d**2 * n.sqrt(B*t) * 1e-23)
-
+    return 2 * 1.22**2 * np.pi / (4 *np.log(2)) *  k_b * Tsky(nu) / (N * d**2 * np.sqrt(B*t) * 1e-23)
+#    return 2 * k_b * Tsky(nu) / (N * d**2 * np.sqrt(B*t) * 1e-23)

### 2015-08-25 ms.tex
starting to finish the sensitivity section

--- 2015-08-07 ms.tex
@@
 \usepackage{color}
+\usepackage{url}
 %\usepackage[dvipdfmx]{color}
@@
 Then, we estimate the radio emission of Jupiter-twin around known M giants in \S\ref{ss:actualMgiants}. 
+In \S\ref{ss:detectability}, we estimate the sensitivities and limitations of several current and future
+radio instruments at lower frequencies.
 Finally, \S\ref{ss:timevariability} discusses the expected time variability of the radio emission as a mean to discern the signals from the background noise.
@@
 
-\memoYF{discussion about detectability... Figures 1-3 of \citet{griesmeier2007b} show $10^{-3}$ Jy limit for 10-100 MHz (LWA, LOFAR) and $10^{-5}-10^{-4}$ Jy for 100-1000 MHz (LOFAR, SKA). }
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Detectability with Current and Near Future Low Frequency Radio Instrumentation}
+\label{ss:detectability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{discussion about detectability... Figures 1-3 of \citet{griesmeier2007b} show $10^{-3}$ Jy limit for 10-100 MHz (LWA, LOFAR) and $10^{-5}-10^{-4}$ Jy for 100-1000 MHz (LOFAR, SKA).}
+
+We consider in this section several current and near future radio observatories that 
+operate at frequencies $\nu \lesssim 300~\rm MHz$ and can reach continuum 
+sensitivities less than 1~mJy in a few hours.  The results are summarized
+in Table~\ref{tab:sens}.
+The primary limitations to detectability are noise, characterized by the sky
+and system equivalent blackbody temperatures $T_{\rm sky}$ and $T_{\rm sys}$,
+resolution, and source confusion.  
+To estimate the source confusion $\sigma_c$ (in mJy beam$^{-1}$) reported in Table~\ref{tab:sens}, 
+we use equations provided by \cite{condon+ransom2016}, reproduced below:
+\begin{eqnarray}
+\sigma_c & \approx & 0.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^2\!\!,~(\theta > 10\arcsec) \\
+\sigma_c & \approx & 2.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^{10/3}\!\!,~(\theta < 10\arcsec)
+\end{eqnarray}
+The confusion limit is dominated by active galactic nuclei, which have low polarization 
+fractions $<2.5\%$ \citep{Stil2014} and slowly vary with time \citep{Condon1974,Condon2012}.
+Therefore both the circularly polarized nature of the emission from hot Jupiters 
+and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate 
+the source confusion limit.
+
+The LOw-Frequency ARray (LOFAR) operates in the 10-240~MHz range, split in two arrays
+using a low band and high band antenna design (LOFAR-LBA and LOFAR-HBA), 
+and different pad configuration \cite{vanHaarlem2013}.  
+LOFAR's two most sensitive bands are centered at 60~MHz for LOFAR-LBA and 150~MHz 
+for LOFAR-HBA respectively.  Given the strong frequency dependence of
+the effective aperture of a dipole antenna, and that the system noise temperature 
+$T_{\rm sys}$ for LOFAR is not fully determined by the sky noise $T_{\rm sky}$, 
+we use the LOFAR Image Noise calculator\footnote{
+Heald; \url{http://www.astron.nl/~heald/test/sens.php}} for simplicity, which 
+is based on SKA Memo 113\footnote{
+ Nijboer, Pandey-Pommier, \& de Bruyn; SKA Memo 113; 
+\url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for
+our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
 
@@
 Instrument & Band & Sensitivity & Time  & Resolution & Confusion limit\\
- & MHz & $\mu$Jy~hr$^{1/2}$ &  hr & \arcsec\ & $\mu$Jy \\[0.25pc] 
+ & MHz & $\mu$Jy~hr$^{1/2}$ &  hr & \arcsec\ & $\mu$Jy bm$^{-1}$ \\[0.25pc] 
 \hline\\[-0.5pc]
@@
 % 24 core stations, 16 remote, 8 international, 488 subbands
-LOFAR & ~45  &  833!! &  &  & \\
-LOFAR & ~60  &  648!! &  &  & \\
-LOFAR & 120  &  51.73 &  &  & \\  
-LOFAR & 150  &  40.97 &  &  & \\  
-LWA   & ~70  &  &  \\
+LOFAR &  30-80  & 700 &  & 8.3 & 120 \\
+LOFAR & 110-200 &  35 &  & 3.3 & 2.6\\  
+LWA   &  30-80  &  &  \\
 SKA   & 200  &  &  \\
@@
 \label{tab:sens}
-\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.  We consider only
-telescopes that can reach this in less than XX hours without
-being confusion limited.}
+\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.}
 \end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{deluxetable}{l|lll}
-%\tablecolumns{4}
-%\tablewidth{0pt}
-%\tabletypesize{\scriptsize}
-%\tablecaption{Detectability of Hot Jupiters with Current and Future Radio Telescopes}
-%\tablehead{ Instrument & Band & Sensitivity & Time  \\ 
-% &  & $\mu$Jy~hr$^{1/2}$ &  hr} 
-%\startdata 
-%GMRT & 220~MHz   &  & \\
-%SKA  & 200~MHz)  &  &  \\
-%VLA  & P-band (270-430~MHz)  &  & 
-%\enddata
-%\tablecomments{Time estimates to reach 10~$\mu$Jy RMS.  We consider only
-%telescopes that can reach this in less than XX hours without
-%being confusion limited.}
-%\label{tab:sens}
-%\end{deluxetable}
 

### 2015-08-25 ms.tex
inserted all of my additions to section 4.1

@@
 \def\memoDS#1{\color{blue}$[${\bf #1}$]$ \color{black}}
+
+\def\memoNZ#1{\color{green}$[${\bf #1}$]$ \color{black}}
 
@@
 %
-Neil Zimmerman\altaffilmark{9}
+Neil T. Zimmerman\altaffilmark{9}
 }
@@
 
-\affil{$^9$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
+\affil{$^9$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
 
@@
 Therefore, in the following, we ignore the radio emission from the red giant as a noise source.
+
+% Neil's addition
+
+Over the last four decades there have been numerous radio continuum observations of nearby red giants, many with the aim of understanding the extended atmospheres and mass-loss mechanisms of K- and M-type giants~\citep[e.g.,][]{Newell1982, Knapp1995, Skinner1997, Lim1998, OGorman2013}.
+Almost all observations have been carried out at wavelengths of 6 cm and below, probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.
+The spectral index of this emission is of order unity, with a range of reported values for various sources between 0.8 and 1.6~\citep{OGorman2013}.
+
+Only two published studies describe attempts to detect continuum emission from single (non-binary) red giant stars at wavelengths above 20 cm ($L$ band); both yielded null results.
+First, a program that observed a sample of nine M-type giants at 430 MHz with the Arecibo Telescope failed to detect any of the sources down to flux density 10 mJy~\citep{Fix1976}.
+Later, with the Molonglo Observatory Synthesis Telescope (MOST), a sample of eight K- and M-type giants were observed at 843 MHz; the upper limits of their flux densities were placed at approximately 1 mJy~\citep{Beasley1992}.
+Current facilities could achieve far deeper sensitivity on similar targets.
+For example, as listed in Table~\ref{tab:sens}, at 235 MHz the GMRT reaches a sensitivity of under 0.2 mJy in under a half hour \memoNZ{is this projected or current performance of GMRT?}.
+However, any re-attempts to detect single red giants at wavelengths near 1 meter remain to be presented in the literature.
+
+The only red giants that have been detected at meter wavelengths are those in interacting binary systems like those of the RS CVn type.
+For example, van den Oord and de Bruyn detected plasma maser emission from II Pegasi at 360 MHz and 609 MHz with the WSRT~\citep{vandenOord1994}.
+Although single dwarf-type main sequence stars are also known to exhibit bright, coherent radio flares~\citep{Bastian1990}, no analog to this non-thermal emission process has been proposed to exist for evolved stars.
+
+Altogether, we lack firm observational constraints on the brightnesses of M giants near 1-m wavelengths.
+However, assuming thermal Bremsstrahlung emission continues to dominate in this wavelength regime, we can extrapolate down from the reported centimeter flux densities, using the specific spectral index when available.
+In this case, for example, extrapolating from the 0.4 mJy flux density of $\alpha$ Ori at 1.46 GHz, and using its spectral index 1.32~\citep{Newell1982}, we arrive at an estimated flux density of 0.04 mJy at 300 MHz.
 

### 2015-08-26 ms.tex
Neil's section, 1 sentence per line.
further refinements to the sens and conf estimates

@@
 We consider in this section several current and near future radio observatories that 
-operate at frequencies $\nu \lesssim 300~\rm MHz$ and can reach continuum 
+operate at frequencies $\nu \lesssim 200~\rm MHz$ and can reach continuum 
 sensitivities less than 1~mJy in a few hours.  The results are summarized
@@
 \begin{eqnarray}
-\sigma_c & \approx & 0.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^2\!\!,~(\theta > 10\arcsec) \\
-\sigma_c & \approx & 2.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^{10/3}\!\!,~(\theta < 10\arcsec)
-\end{eqnarray}
-The confusion limit is dominated by active galactic nuclei, which have low polarization 
-fractions $<2.5\%$ \citep{Stil2014} and slowly vary with time \citep{Condon1974,Condon2012}.
+\sigma_c & \approx & 0.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^2\!\!\!\!,~(\theta > 10\arcsec) \\
+\sigma_c & \approx & 2.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^{10/3}\!\!\!\!\!\!\!\!\!\!,~(\theta < 10\arcsec).
+\end{eqnarray}
+The source confusion limit is dominated by active galactic nuclei, which have low polarization 
+fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time \citep{Condon1974,Condon2012}.
 Therefore both the circularly polarized nature of the emission from hot Jupiters 
@@
 
-The LOw-Frequency ARray (LOFAR) operates in the 10-240~MHz range, split in two arrays
-using a low band and high band antenna design (LOFAR-LBA and LOFAR-HBA), 
-and different pad configuration \cite{vanHaarlem2013}.  
-LOFAR's two most sensitive bands are centered at 60~MHz for LOFAR-LBA and 150~MHz 
-for LOFAR-HBA respectively.  Given the strong frequency dependence of
+The LOw-Frequency ARray (LOFAR) operates as two separate arrays defined by their 
+high and low bands, differing configurations, and antenna designs.  
+LOFAR-LBA operates in the 10-90~MHz range, and LOFAR-HBA operates in the 
+100-240~MHz range \cite{vanHaarlem2013}.  We consider it as two separate
+instruments here.
+LOFAR-LBA's most sensitive band is centered at 60~MHz, and at 150~MHz 
+for LOFAR-HBA.  Given the strong frequency dependence of
 the effective aperture of a dipole antenna, and that the system noise temperature 
@@
 we use the LOFAR Image Noise calculator\footnote{
-Heald; \url{http://www.astron.nl/~heald/test/sens.php}} for simplicity, which 
+Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which 
 is based on SKA Memo 113\footnote{
- Nijboer, Pandey-Pommier, \& de Bruyn; SKA Memo 113; 
+Nijboer, Pandey-Pommier, \& de Bruyn; 
 \url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for
 our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
+
+The Giant Metre-wave Radio Telescope (GMRT) is an array comprising thirty 
+25-meter antennas, operating at frequencies 130-2000~MHz. The lowest
+band (130-190~MHz) exhibits receiver noise comparable to the sky noise, and
+hence we use their online calculator.\footnote{
+\href{http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html}}
+
+For the rest of the instruments considered, we assume $T_{\rm sys}\approx T_{\rm sky}$,
+and use the fit from \cite{Rogers+Bowman2008} to data taken in the 100-200~MHz range:
+\begin{equation}
+T_{\rm sky} = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + T_{\rm CMB} 
+\end{equation}
+where $T_{150} = 283.2~\rm K$ is the $T_{\rm sky}$ at 150~MHz, $\beta=2.47$,
+and $T_{\rm CMB} = 2.73~\rm K$ is the contribution from the cosmic microwave 
+background (CMB).
+The RMS noise ${\sigma}$ in an interferometric observation, 
+integration time $\tau$, bandwidth $\Delta\nu$, effective area $A_{\rm eff}$ 
+($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$),
+and $N$ elements is \citep[see e.g.][]{condon+ransom2016} 
+\begin{equation}
+\sigma = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta\nu \, \tau N (N-1)}} 
+\left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right)
+\end{equation}
 
@@
 \begin{tabular}{c|ccccc} \hline \hline\\[-0.5pc]
-Instrument & Band & Sensitivity & Time  & Resolution & Confusion limit\\
+Instrument & Band & Sensitivity & $\tau$  & Resolution & $5\sigma_c$\\
  & MHz & $\mu$Jy~hr$^{1/2}$ &  hr & \arcsec\ & $\mu$Jy bm$^{-1}$ \\[0.25pc] 
 \hline\\[-0.5pc]
-%ASKAP & 700-1700~MHz & 37 & 342.3 \\ % table 3 of http://www.atnf.csiro.au/projects/askap/config.html
-GMRT  & 235~MHz &  165.6 & 6860 & 13 \\ % http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html
-HERA  & 70~MHz  &  &  \\ % http://reionization.org/wp-content/uploads/2015/05/HERA0_imaging.pdf
-% https://www.astron.nl/~heald/test/sens.php; 
-% 24 core stations, 16 remote, 8 international, 488 subbands
-LOFAR &  30-80  & 700 &  & 8.3 & 120 \\
-LOFAR & 110-200 &  35 &  & 3.3 & 2.6\\  
-LWA   &  30-80  &  &  \\
-SKA   & 200  &  &  \\
+GMRT      & 130-190 & 430   &  460             &  20  & 1070 \\ 
+HERA      &  30-80  & 540   &  730             & 880  & $1.4\times10^6$\\ 
+LOFAR-LBA &  30-80  & 700   & 1225             & 8.3  & 120 \\ 
+LOFAR-HBA & 110-200 &  35   &    3             & 3.3  & 2.6\\  
+LWA       &  30-80  & 36000 &  3.2$\times10^6$ & 10.3 & 211\\
+MWA       &  30-80  & 18000 &  8.1$\times10^5$ & 1030 & $1.4\times10^6$ \\
+SKA-Low   & 50-350 &  3.5   &  0.03            & 7.9  & 57 \\
 UTR-2 & & & \\
@@
 \label{tab:sens}
-\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.}
+\tablecomments{Time estimates to reach 20~$\mu$Jy RMS.}
 \end{table*}
+
+% HERA
+% http://reionization.org/wp-content/uploads/2015/05/HERA0_imaging.pdf
+%
+% LOFAR
+% https://www.astron.nl/~heald/test/sens.php; 
+% 24 core stations, 16 remote, 8 international, 488 subbands
+%
+% GMRT
+% http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html
+%
 

### 2015-08-26 ms.tex
incremental updates, not longer just assuming 70 MHz.

@@
 Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
-In this regime, there are a number of current and near-future radio wave detectors including UTR-2, LOFAR, LWA, and SKA.
+In this regime, there are a number of current and near-future radio wave detectors including GMRT, LOFAR, LWA, MWA, Hera, SKA, and upgrades to the VLA.
 
@@
 
-For the rest of the instruments considered, we assume $T_{\rm sys}\approx T_{\rm sky}$,
-and use the fit from \cite{Rogers+Bowman2008} to data taken in the 100-200~MHz range:
+The low frequency component of the  Square Kilometer Array (SKA), recently rebaselined 
+to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending
+to 65~km, will operate from 50-350~MHz.\footnote{
+\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
+We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$) assuming
+$T_{\rm sys} \approx T_{\rm sky}$, and use the fit from \cite{Rogers+Bowman2008}:
 \begin{equation}
@@
 background (CMB).
+While this relation was fit to data taken in the 100-200~MHz range, the authors
+found it to be consistent with published measurements from 10-408~MHz.
+
+For the rest of the instruments considered, we also assume $T_{\rm sys} \approx T_{\rm sky}$,
+and adopt the \cite{Rogers+Bowman2008} relation.  We caution that is assumption is 
+optimistic, and the time estimates could in reality be a factor of a few worse.
+
 The RMS noise ${\sigma}$ in an interferometric observation, 
@@
 \hline\\[-0.5pc]
-GMRT      & 130-190 & 430   &  460             &  20  & 1070 \\ 
-HERA      &  30-80  & 540   &  730             & 880  & $1.4\times10^6$\\ 
-LOFAR-LBA &  30-80  & 700   & 1225             & 8.3  & 120 \\ 
-LOFAR-HBA & 110-200 &  35   &    3             & 3.3  & 2.6\\  
-LWA       &  30-80  & 36000 &  3.2$\times10^6$ & 10.3 & 211\\
-MWA       &  30-80  & 18000 &  8.1$\times10^5$ & 1030 & $1.4\times10^6$ \\
-SKA-Low   & 50-350 &  3.5   &  0.03            & 7.9  & 57 \\
-UTR-2 & & & \\
-VLA P-band & 270-470  & 138  & 4760 & \\
+GMRT      & 130-190 & 430   &  460             & 16.5 & 280 \\ 
+HERA      &  30-80  & 790   &  730             & 1030 & $2.1\times10^6$\\ 
+LOFAR-LBA &  30-80  & 700   & 1225             & 8.3  & 211 \\ 
+LOFAR-HBA & 110-200 &  35   &    3             & 3.3  & 5.5 \\  
+LWA       &  30-80  & 53000 &  3.2$\times10^6$ & 10.3 & 211 \\
+MWA       &  30-80  & 27000 &  8.1$\times10^5$ & 1030 & $2.1\times10^6$ \\
+SKA-Low   & 50-350  &  4.9   &  0.03            & 7.9  & 57 \\
+VLA       & 30-80   & 138  & 4760 & \\
 \hline

### 2015-08-29 ms.tex
ready to read sensitivity section

--- 2015-08-26 ms.tex
@@
-\documentclass{emulateapj}
+\documentclass[iop,numberedappendix,apj]{emulateapj}
 
@@
 \usepackage{url}
+\usepackage{hyperref}
 %\usepackage[dvipdfmx]{color}
@@
 Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
-In this regime, there are a number of current and near-future radio wave detectors including GMRT, LOFAR, LWA, MWA, Hera, SKA, and upgrades to the VLA.
+In this regime, there are a number of current and near-future radio wave detectors including GMRT, 
+LOFAR, Hera, SKA, and upgrades to the VLA.
 
@@
 
-\memoYF{discussion about detectability... Figures 1-3 of \citet{griesmeier2007b} show $10^{-3}$ Jy limit for 10-100 MHz (LWA, LOFAR) and $10^{-5}-10^{-4}$ Jy for 100-1000 MHz (LOFAR, SKA).}
+%\memoYF{discussion about detectability... Figures 1-3 of \citet{griesmeier2007b} show $10^{-3}$ Jy limit for 10-100 MHz (LWA, LOFAR) and $10^{-5}-10^{-4}$ Jy for 100-1000 MHz (LOFAR, SKA).}
 
 We consider in this section several current and near future radio observatories that 
-operate at frequencies $\nu \lesssim 200~\rm MHz$ and can reach continuum 
+operate at frequencies $\nu \lesssim 350~\rm MHz$ and can reach continuum 
 sensitivities less than 1~mJy in a few hours.  The results are summarized
 in Table~\ref{tab:sens}.
-The primary limitations to detectability are noise, characterized by the sky
-and system equivalent blackbody temperatures $T_{\rm sky}$ and $T_{\rm sys}$,
-resolution, and source confusion.  
+The primary limitations to detectability are noise, characterized by the
+system equivalent blackbody temperature $T_{\rm sys}$, resolution, and source confusion.  
 To estimate the source confusion $\sigma_c$ (in mJy beam$^{-1}$) reported in Table~\ref{tab:sens}, 
-we use equations provided by \cite{condon+ransom2016}, reproduced below:
+we use the relations provided by \cite{condon+ransom2016}, reproduced below:
 \begin{eqnarray}
@@
 and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate 
-the source confusion limit.
-
-The LOw-Frequency ARray (LOFAR) operates as two separate arrays defined by their 
-high and low bands, differing configurations, and antenna designs.  
-LOFAR-LBA operates in the 10-90~MHz range, and LOFAR-HBA operates in the 
-100-240~MHz range \cite{vanHaarlem2013}.  We consider it as two separate
-instruments here.
-LOFAR-LBA's most sensitive band is centered at 60~MHz, and at 150~MHz 
-for LOFAR-HBA.  Given the strong frequency dependence of
-the effective aperture of a dipole antenna, and that the system noise temperature 
-$T_{\rm sys}$ for LOFAR is not fully determined by the sky noise $T_{\rm sky}$, 
-we use the LOFAR Image Noise calculator\footnote{
-Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which 
-is based on SKA Memo 113\footnote{
-Nijboer, Pandey-Pommier, \& de Bruyn; 
-\url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for
-our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
-
-The Giant Metre-wave Radio Telescope (GMRT) is an array comprising thirty 
-25-meter antennas, operating at frequencies 130-2000~MHz. The lowest
-band (130-190~MHz) exhibits receiver noise comparable to the sky noise, and
-hence we use their online calculator.\footnote{
-\href{http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html}}
-
-The low frequency component of the  Square Kilometer Array (SKA), recently rebaselined 
-to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending
-to 65~km, will operate from 50-350~MHz.\footnote{
-\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
-We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$) assuming
-$T_{\rm sys} \approx T_{\rm sky}$, and use the fit from \cite{Rogers+Bowman2008}:
-\begin{equation}
-T_{\rm sky} = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + T_{\rm CMB} 
-\end{equation}
-where $T_{150} = 283.2~\rm K$ is the $T_{\rm sky}$ at 150~MHz, $\beta=2.47$,
-and $T_{\rm CMB} = 2.73~\rm K$ is the contribution from the cosmic microwave 
-background (CMB).
-While this relation was fit to data taken in the 100-200~MHz range, the authors
-found it to be consistent with published measurements from 10-408~MHz.
-
-For the rest of the instruments considered, we also assume $T_{\rm sys} \approx T_{\rm sky}$,
-and adopt the \cite{Rogers+Bowman2008} relation.  We caution that is assumption is 
-optimistic, and the time estimates could in reality be a factor of a few worse.
+the source confusion limit, allowing hot Jupiters, like other time-variable sources,
+to be detected below the imaging confusion limit.
 
@@
 GMRT       & 130-190 & 430   &  460             & 16.5 & 280 \\ 
-HERA      &  30-80  & 790   &  730             & 1030 & $2.1\times10^6$\\ 
-LOFAR-LBA &  30-80  & 700   & 1225             & 8.3  & 211 \\ 
+HERA       &  30-80  & 790   &  870             & 1030 & $2.1\times10^6$\\ 
+LOFAR-LBA  &  30-80  & 700   & 1225             & 8.3  & 210 \\ 
 LOFAR-HBA  & 110-200 &  35   &    3             & 3.3  & 5.5 \\  
-LWA       &  30-80  & 53000 &  3.2$\times10^6$ & 10.3 & 211 \\
-MWA       &  30-80  & 27000 &  8.1$\times10^5$ & 1030 & $2.1\times10^6$ \\
-SKA-Low   & 50-350  &  4.9   &  0.03            & 7.9  & 57 \\
-VLA       & 30-80   & 138  & 4760 & \\
+%LWA        &  30-80  & 53000 &  3.2$\times10^6$ & 10.3 & 211 \\
+%MWA        &  30-80  & 27000 &  8.1$\times10^5$ & 1030 & $2.1\times10^6$ \\
+SKA-Low (part) & 50-200 & 7.8 &  0.15           & 7.8  & 48 \\
+SKA-Low (full) & 50-350 & 2.2 &  0.012          & 2.2  & 7.2 \\
+%VLA 4-Band & 30-80   & 3300  & 1100             & 28.6 & 1600 \\
+VLA-LOBO   &  50-350 &  92   &  21              & 8.6  & 52 \\
 \hline
@@
 %
+
+The LOw-Frequency ARray (LOFAR) operates as two separate arrays defined by their 
+high and low bands, differing configurations, and antenna designs, which
+are called respectively the Low Band Antennas (LBA) and High Band Antennas (HBA).  
+LOFAR-LBA operates in the 10-90~MHz range, and LOFAR-HBA operates in the 
+100-240~MHz range \citep{vanHaarlem2013}.  We consider it as two separate
+instruments here.
+LOFAR-LBA's most sensitive band is centered at 60~MHz, and LOFAR-HBA's is at 150~MHz. 
+Given the strong frequency dependence of
+the effective aperture of a dipole antenna, and that the system noise temperature 
+$T_{\rm sys}$ for LOFAR is not fully determined by the sky noise $T_{\rm sky}$, 
+we use the LOFAR Image Noise calculator\footnote{
+Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which 
+is based on SKA Memo 113\footnote{
+Nijboer, Pandey-Pommier, \& de Bruyn; 
+\url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for
+our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
+
+The Giant Metre-wave Radio Telescope (GMRT) is an array comprising thirty 
+25-meter antennas, operating at frequencies 130-2000~MHz. The lowest
+band (130-190~MHz) exhibits receiver noise $T_{\rm rx}$ comparable to the sky noise.
+To be conservative, we use the GMRT online calculator.\footnote{
+\url{http://gmrt.ncra.tifr.res.in/~astrosupp/obs\_setup/sensitivity.html}
+}
+
+For the low frequency receivers (28-80~MHz; 4-Band) in the % Long Wavelength Array (LWA) and the 
+Very Large Array (VLA), the receiver noise temperature $T_{\rm rx}\approx 260~\rm K$ 
+\citep{Hicks2012} and is subdominant to $T_{\rm sky}$ by at least -6~dB.  Future
+upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU},
+We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly
+from $T_{\rm rx}\approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to
+$T_{\rm rx}\approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion
+of the full 30-470~MHz band.
+
+We compute $T_{\rm sys} = T_{\rm rx}+ T_{\rm sky}$ using the low frequency sky 
+noise temperature fit from \cite{Rogers+Bowman2008}:
+\begin{equation}
+T_{\rm sky} = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + T_{\rm CMB} 
+\end{equation}
+where $T_{150} = 283.2~\rm K$ is the $T_{\rm sky}$ at 150~MHz, $\beta=2.47$,
+and $T_{\rm CMB} = 2.73~\rm K$ is the contribution from the cosmic microwave 
+background (CMB).
+While this relation was fit to data taken in the 100-200~MHz range, the authors
+found it to be consistent with published measurements from 10-408~MHz.
+
+The low frequency component of the  Square Kilometer Array (SKA), recently rebaselined 
+to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending
+to 65~km, will operate from 50-350~MHz.\footnote{
+\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
+We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate
+for lower mass ($\lesssim 10 M_J$) separately from the full band, which could be used
+to detect $\sim 30 M_J$ hot Jupiters.
+We adopt the \cite{Rogers+Bowman2008} relation for $T_{\rm sys}$ as above, and assume
+$T_{\rm rx}\approx 60~\rm K$.
+We caution that these assumptions are optimistic, and the time estimates could in reality 
+be a factor of a few worse.
 

### 2015-08-31 ms.tex
Discussions -> Discussion

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussions}
+\section{Discussion}
 \label{s:discussion}

### 2015-08-31 ms.tex
updated HERA integration time

--- 2015-08-29 ms.tex
@@
 GMRT       & 130-190 & 430   &  460             & 16.5 & 280 \\ 
-HERA       &  30-80  & 790   &  870             & 1030 & $2.1\times10^6$\\ 
+HERA       &  30-80  & 870   & 1900             & 1030 & $2.1\times10^6$\\ 
 LOFAR-LBA  &  30-80  & 700   & 1225             & 8.3  & 210 \\ 
@@
 Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which 
-is based on SKA Memo 113\footnote{
+is based on {\it SKA Memo 113}\footnote{
 Nijboer, Pandey-Pommier, \& de Bruyn; 
@@
 our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
+
+The Hydrogen Epoch of Reionization Array (HERA\footnote{
+\url{http://reionization.org/}}) \ldots
 

### 2015-08-31 ms.tex
some updates to the sensitivies, and questions about what fiducial RGHJ to use

@@
 \begin{equation}
-F_{\nu} = \frac{P_{\rm radio}}{\Omega l^2 \Delta f}
+F_{\nu} = \frac{P_{\rm radio}}{\Omega l^2 \Delta \nu}
 \label{eq:Fnu}
@@
 %%%
-where $P_{\rm radio}$ is the energy that is deposited as radio emission of considered frequency range, $\Omega $ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta f$ is frequency bandwidth.
+where $P_{\rm radio}$ is the energy that is deposited as radio emission of considered frequency range, $\Omega$ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta \nu$ is frequency bandwidth.
 
@@
 On the other hand, in the case that the correlation with input magnetic energy is fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well constrained for highly evolved stars; most of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}.
-In the case of M-type giant EK boo, surface magnetic field $\sim 0.1-10 $G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus also may also increase the planetary radio emission.
+In the case of M-type giant EK boo, surface magnetic field $\sim 0.1-10 $G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus may also increase the planetary radio emission.
 However, because of the lack of universal understanding of the stellar magnetic field, we leave the magnetic model of radio emission for evolved stars for future work.
@@
 
-The bandwidth, $\Delta f$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griesmeier2007b}.
+The bandwidth, $\Delta \nu$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griesmeier2007b}.
 
@@
 
-Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10M_J$ and that of the host red giant stars with 100 $R_{\odot }$, both of which is placed at 10 pc away. 
-As this figure indicates, even if the radio emission from the red giant itself has relatively low spectral index, the radio emission from RGHJs still dominate in the 10-200~MHz range. 
+Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant stars with 100~$R_{\odot }$, both of which is placed at 10 pc away. 
+As this figure indicates, even if the radio emission from the red giant itself has a relatively shallow spectral index, the radio emission from the RGHJ still dominates in the 10-200~MHz range. 
 Therefore, in the following, we ignore the radio emission from the red giant as a noise source.
@@
 Current facilities could achieve far deeper sensitivity on similar targets.
-For example, as listed in Table~\ref{tab:sens}, at 235 MHz the GMRT reaches a sensitivity of under 0.2 mJy in under a half hour \memoNZ{is this projected or current performance of GMRT?}.
+For example, as listed in Table~\ref{tab:sens}, the Giant Metrewave Radio Telescope (GMRT) at 150 MHz reaches a 
+sensitivity better than 0.5~mJy in under an hour.
 However, any re-attempts to detect single red giants at wavelengths near 1 meter remain to be presented in the literature.
@@
    \plotonesc{cartoon2.pdf}
-   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.
-The spectrum of RGHJ is modeled after Jovian radio spectra \citep[e.g.][]{zarka_et_al2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law.
+   \caption{A cartoon spectrum of the radio emission of a RGHJ with 10~$M_J$ and the host red giant with 100 $R_{\odot }$.
+The spectrum of RGHJ is modeled after Jovian radio spectra \citep[e.g.][]{zarka_et_al2004}, while that of the host red giant is obtained simply by extrapolating the radio spectrum observed above 1~GHz to lower ffrequencies assuming a power law.
 }
@@
 The RMS noise ${\sigma}$ in an interferometric observation, 
-integration time $\tau$, bandwidth $\Delta\nu$, effective area $A_{\rm eff}$ 
+integration time $\tau$, bandwidth $\Delta \nu$, effective area $A_{\rm eff}$ 
 ($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$),
@@
 \begin{equation}
-\sigma = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta\nu \, \tau N (N-1)}} 
+\sigma = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
 \left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right)
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}[htp]
-\caption{Detectability of Hot Jupiters with Current and Future Radio Telescopes.}
-\begin{center}
-\begin{tabular}{c|ccccc} \hline \hline\\[-0.5pc]
-Instrument & Band & Sensitivity & $\tau$  & Resolution & $5\sigma_c$\\
- & MHz & $\mu$Jy~hr$^{1/2}$ &  hr & \arcsec\ & $\mu$Jy bm$^{-1}$ \\[0.25pc] 
-\hline\\[-0.5pc]
-GMRT       & 130-190 & 430   &  460             & 16.5 & 280 \\ 
-HERA       &  30-80  & 870   & 1900             & 1030 & $2.1\times10^6$\\ 
-LOFAR-LBA  &  30-80  & 700   & 1225             & 8.3  & 210 \\ 
-LOFAR-HBA  & 110-200 &  35   &    3             & 3.3  & 5.5 \\  
+%\begin{center}
+\begin{deluxetable*}{cccccc}
+\tabletypesize{\scriptsize}
+\tablecolumns{6}
+\tablecaption{Detectability of Hot Jupiters with Current 
+and Future Radio Telescopes.\label{tab:sens}}
+\tablehead{
+Instrument & Band  & Sensitivity\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
+           & (MHz) & ($\mu$Jy~hr$^{1/2}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
+\startdata
+GMRT       & 130-190 & 430   &  460             & 16.5 & 56.9 \\ 
+HERA       &  30-80  & 870   & 1900             & 1030 & 4.2$\times10^5$\\ 
+LOFAR-LBA  &  30-80  & 700   & 1225             & 8.3  & 42 \\ 
+LOFAR-HBA  & 110-200 &  35   &    3             & 3.3  & 1.1 \\  
 %LWA        &  30-80  & 53000 &  3.2$\times10^6$ & 10.3 & 211 \\
 %MWA        &  30-80  & 27000 &  8.1$\times10^5$ & 1030 & $2.1\times10^6$ \\
-SKA-Low (part) & 50-200 & 7.8 &  0.15           & 7.8  & 48 \\
-SKA-Low (full) & 50-350 & 2.2 &  0.012          & 2.2  & 7.2 \\
-%VLA 4-Band & 30-80   & 3300  & 1100             & 28.6 & 1600 \\
-VLA-LOBO   &  50-350 &  92   &  21              & 8.6  & 52 \\
-\hline
-\end{tabular}
-\end{center}
-\label{tab:sens}
+SKA-Low (part) & 50-200 & 7.8 &  0.15           & 7.8  & 9.7 \\
+SKA-Low (full) & 50-350 & 2.2 &  0.012          & 2.2  & 1.5 \\
+%VLA 4-Band & 30-80   & 3300  & 1100             & 28.6 & 330 \\
+VLA-LOBO   &  50-350 &  92   &  21              & 8.6  & 10
+\enddata
 \tablecomments{Time estimates to reach 20~$\mu$Jy RMS.}
-\end{table*}
+\tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported in this table.}
+\tablenotetext{b}{The integration time in hours required to reach an RMS of 20~$\mu$Jy (i.e.\ 5-$\sigma$ detection
+of a typical source with 100~$\mu$Jy bm$^{-1}$ average flux) \memoTM{Should we compute this instead for a 5-sigma detection
+of a $\sim$400~$\mu$Jy bm$^{-1}$ average flux, like in Figure \ref{fig:cartoon}?  Going to 80~$\mu$Jy RMS would be $16\times$ shorter.}.}
+\tablenotetext{c}{Source confusion limit RMS contribution.}
+\end{deluxetable*}
+%\end{center}
 
@@
 The maximum radio emission we can expect to observe is limited by the plasma cut-off frequency of the stellar wind in the vicinity of the planets. 
-For a planet with the same magnetic moment as Jupiter, the maximum radio emission from the planets which can penetrate through the surrounding plasma is $\sim 10^{-3}$ Jy or $\sim 10^{-5}$ Jy at 10 pc and 100 pc, respectively.
-\memoYF{comment on observability...}
+For a planet with the same magnetic moment as Jupiter, the maximum radio emission from the planets which can penetrate through the surrounding plasma is $\sim 10^{-3}$ Jy or $\sim 10^{-5}$ Jy at 10~pc and 100~pc, respectively.
+As we showed in \S\ref{ss:detectability}, the upper end of this range is detectable with the current generation of radio facilities, while farther hot Jupiters should soon be detectable using the next generation of instruments.
 
@@
 NM acknowledges support from [???].
+The portion of this research for which TM is responsible was performed while he
+held a National Research Council Research Associateship Award at the Naval 
+Research Laboratory (NRL).  Basic research in radio astronomy at NRL 
+is supported by 6.1 Base funding.
 
@@
 Nevertheless, a reasonable ansatz is that the radio emission is spread over a range of wavelengths in an approximately scale-independent way.
-In other words, the frequency bandwidth $\Delta f$ of Eq.~(\ref{eq:Fnu}) is proportional to $f_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
+In other words, the frequency bandwidth $\Delta \nu$ of Eq.~(\ref{eq:Fnu}) is proportional to $f_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
 This means that the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.

### 2015-09-01 ms.tex
Text editing

@@
 Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
-It has been known that Jupiter emits radio wave from the auroral region due to cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
+It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
 Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.
-Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is known as  ``radiometric Bode's law'' \citep{desch+kaiser1984}.
-Extrapolating this law to exoplanets, radio emission from exoplanetary system has been estimated \citep{farrell1999,zarka2001,lazio2004,griesmeier2004,griesmeier2005,stevens2005,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010}.
+Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984}.
+Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems have been estimated \citep{farrell1999,zarka2001,lazio2004,griesmeier2004,griesmeier2005,stevens2005,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010}.
 \memoYF{in more detail}
 %Based on this law, it has been proposed that exoplanets in close-in orbits may be bright radio wave emitters because they are subjected to strong stellar wind and/or strong interstellar magnetic field, and thus can gain larger energy input.
-Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,lazio2004,griesmeier2004,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010,}.
-In addition, young planetary systems where the stellar wind activity is stronger are also taken into consideration \citep{griesmeier2005}. 
-Although the observational search for these radio signatures are underway, there is no clear detection claimed so far
-\citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
-while some indications have been obtained \citep{lecavelier_et_al2013,sirothia2014}.
+Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,lazi o2004,griesmeier2004,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010,}.
+In addition, young planetary systems where stellar wind activity is strong have also been considered \citep{griesmeier2005}. 
+Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
+though there are some promising intial results \citep{lecavelier_et_al2013,sirothia2014}.
 
 When stars less than $\sim$8~$M_\sun$ evolve off the main sequence,
-they go through stages on the red-giant branch (RGB) and the
-asymptotic-giant branch (AGB) where their radii and luminosities increase by orders of magnitude. 
-Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) \citep{spiegel+madhusudhan2012}.
-They are also subject to a massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, much higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr .
+they evolve through the red-giant branch (RGB) and the
+asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude. 
+Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) but refer to planets orbiting RGB and AGB stars \citep{spiegel+madhusudhan2012}.
+Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr .
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.

### 2015-09-01 ms.tex
More editing

@@
 
-\color{red}
-In this paper, we argue that the accretion of massive stellar wind onto the planets would emit strong X-ray, which can ionize the hydrogen atoms around the planets.
-The ionized stellar wind could then interact with the planetary magnetic field in the same way as Solar System planets do.
-We therefore provide optimistic estimates for highly evolved stars, simply extrapolating the radiometric Bode's law. 
-We do not constrain ourselves to the systems known to have sub-stellar companions, given that the survey of exoplanets around highly evolved stars is not complete; rather, we investigate the parameter space where we can search for radio emission and examine the possibility to detect them with current and future instruments.
-\color{black}
-
-In \S2, we describe our assumptions for stellar wind, planetary magnetosphere, frequency of radio emission, and the scaling of planetary radio emission.
-\S3 presents an estimate of the spectral radio intensity of RGHJs and compares them with what might be expected from canonical hot Jupiters.
+In this paper, we argue that the accretion of the massive stellar wind onto the planet would emit strong X-rays, thereby ionizing the hydrogen atoms around the planet.
+The ionized stellar wind would then interact with the planetary magnetic field in the same way as Solar System planets do.
+Thus, by extrapolating the radiometric Bode's law, we provide more optimistic estimates for highly evolved stars compared to previous results.
+Given that the survey of exoplanets around highly evolved stars is not complete, we do not constrain ourselves to the systems known to have sub-stellar companions.
+Instead, we investigate the parameter space where we can search for radio emission and examine the possibility to detect them with current and future instruments.
+
+In \S2, we describe our assumptions for the stellar wind, planetary magnetosphere, frequency of radio emission, and scaling of planetary radio emission.
+\S3 presents an estimate of the spectral radio intensity of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters.
 %\S3 also describes the surprising result that, although the planetary magnetic field is crucial to the generation of radio emission at all, there might be an important region in parameter space in which planets with stronger magnetic fields are less easily observable.

### 2015-09-01 ms.tex
More textual edits

@@
 %
-David S. Spiegel\altaffilmark{1, 2} \\
+David S. Spiegel\altaffilmark{1,2} \\
 %
@@
 %where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
-where $B_{\rm dynamo}$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\rho_{\rm dynamo} $ is the mean density in the dynamo region, $F$ is the efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
+where $B_{\rm dynamo}$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\rho_{\rm dynamo} $ is the mean density in the dynamo region, $F$ is an efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
 Here, $f_{\rm ohm}$ and $F$ are assumed to be constant for the bodies considered in this paper. 
@@
 
-Note that the scaling law, equation (\ref{eq:Bscaling}), would be reasonable only for the rapidly rotating objects.
-Indeed, unlike canonical hot Jupiters, RGHJs are not subjected to tidal lock and we do not have to assume slow spin rotation rate for them \citep{spiegel+madhusudhan2012}.
-Thus, we implicitly assume that RGHJs we consider are rapidly rotating so that they generate  planetary magnetic fields through the same mechanism as Jupiter.
-
-In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need a model of internal structure of planets. 
-In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, because the numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
+Note that the scaling law, Equation (\ref{eq:Bscaling}), would be reasonable only for rapidly rotating objects.
+Indeed, unlike canonical hot Jupiters, RGHJs are not subjected to tidal lock and as such, we do not have to assume slow spin rotation rates \citep{spiegel+madhusudhan2012}.
+Therefore, we implicitly assume that the RGHJs we consider in this paper are rapidly rotating so that they generate planetary magnetic fields through the same mechanism as Jupiter.
+
+In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need models of the internal planetary structure. 
+We consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
 For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
@@
 
-The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
-The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
-Ignoring the relatively weak dependence on  average atmospheric Rosseland mean opacity, the result leads to:
+The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net-planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
+The time-dependence luminosity is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
+Ignoring the relatively weak dependence on average atmospheric Rosseland mean opacity leads to:
 %%%%%%%%%%
@@
 
-Substituting equation (\ref{eq:burrowsHeatFlux}) into equation (\ref{eq:Bscaling2}) and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is roughly, we find that:
+Substituting Equation~\ref{eq:burrowsHeatFlux} into Equation~\ref{eq:Bscaling2} and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is roughly, we find that:
 %%%%%%%%%% 

### 2015-09-02 ms.tex

--- 2015-09-01 ms.tex
@@
 Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
-It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
+It has been known that Jupiter emits radio wave from the auroral region due to cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
 Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.
-Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984}.
-Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems have been estimated \citep{farrell1999,zarka2001,lazio2004,griesmeier2004,griesmeier2005,stevens2005,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010}.
+Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is known as  ``radiometric Bode's law'' \citep{desch+kaiser1984}.
+Extrapolating this law to exoplanets, radio emission from exoplanetary system has been estimated \citep{farrell1999,zarka2001,lazio2004,griesmeier2004,griesmeier2005,stevens2005,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010}.
 \memoYF{in more detail}
 %Based on this law, it has been proposed that exoplanets in close-in orbits may be bright radio wave emitters because they are subjected to strong stellar wind and/or strong interstellar magnetic field, and thus can gain larger energy input.
-Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,lazi o2004,griesmeier2004,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010,}.
-In addition, young planetary systems where stellar wind activity is strong have also been considered \citep{griesmeier2005}. 
-Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
-though there are some promising intial results \citep{lecavelier_et_al2013,sirothia2014}.
+Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,lazio2004,griesmeier2004,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010,}.
+In addition, young planetary systems where the stellar wind activity is stronger are also taken into consideration \citep{griesmeier2005}. 
+Although the observational search for these radio signatures are underway, there is no clear detection claimed so far
+\citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
+while some indications have been obtained \citep{lecavelier_et_al2013,sirothia2014}.
 
 When stars less than $\sim$8~$M_\sun$ evolve off the main sequence,
-they evolve through the red-giant branch (RGB) and the
-asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude. 
-Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) but refer to planets orbiting RGB and AGB stars \citep{spiegel+madhusudhan2012}.
-Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr .
+they go through stages on the red-giant branch (RGB) and the
+asymptotic-giant branch (AGB) where their radii and luminosities increase by orders of magnitude. 
+Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) \citep{spiegel+madhusudhan2012}.
+They are also subject to a massive (but slow) stellar wind, as the mass-loss rate of such evolved stars are significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, much higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr .
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.
@@
 \begin{figure*}[tbp]
-   \plotonesc{cartoon2.pdf}
-   \caption{A cartoon spectrum of the radio emission of a RGHJ with 10~$M_J$ and the host red giant with 100 $R_{\odot }$.
-The spectrum of RGHJ is modeled after Jovian radio spectra \citep[e.g.][]{zarka_et_al2004}, while that of the host red giant is obtained simply by extrapolating the radio spectrum observed above 1~GHz to lower ffrequencies assuming a power law.
+   \plotonesc{fig5_10Mj_2.pdf}
+   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.
+The spectrum of RGHJ is modeled after Jovian radio spectra, e.g.
+figure 8 of \citet{zarka_et_al2004} and figure 2 of \citet{griesmeier2007a}; contribution from Io is not shown here.
+The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law.
 }

### 2015-09-02 ms.tex
edited Section 4.3

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\memoYF{--- how about the following? ---}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{center}
+\begin{deluxetable*}{cccccc}
+\tabletypesize{\scriptsize}
+\tablecolumns{6}
+\tablecaption{Detectability of Hot Jupiters with Current 
+and Future Radio Telescopes.\label{tab:sens}}
+\tablehead{
+Instrument & Band  & Sensitivity\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
+           & (MHz) & ($\mu$Jy~hr$^{1/2}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
+\startdata
+LOFAR-LBA  &  30-80  & 700   & 122500             & 8.3  & 42 \\ 
+LOFAR-HBA  & 110-200 &  35   &    300             & 3.3  & 1.1 \\  
+HERA       &  30-80  & 870   & 190000             & 1030 & 4.2$\times10^5$\\ 
+GMRT       & 130-190 & 430   &  46000             & 16.5 & 56.9 \\ 
+%LWA        &  30-80  & 53000 &  3.2$\times10^6$ & 10.3 & 211 \\
+%MWA        &  30-80  & 27000 &  8.1$\times10^5$ & 1030 & $2.1\times10^6$ \\
+SKA-Low (part) & 50-200 & 7.8 &  15           & 7.8  & 9.7 \\
+SKA-Low (full) & 50-350 & 2.2 &  1.2          & 2.2  & 1.5 \\
+%VLA 4-Band & 30-80   & 3300  & 1100             & 28.6 & 330 \\
+VLA-LOBO   &  50-350 &  92   &  2100              & 8.6  & 10
+\enddata
+%\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.}
+\tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported in this table.}
+\tablenotetext{b}{The integration time in hours required to reach an RMS of 2~$\mu$Jy (i.e.\ 5-$\sigma$ detection
+of a typical source with 10~$\mu$Jy bm$^{-1}$ average flux)}
+\tablenotetext{c}{Source confusion limit RMS contribution.}
+\end{deluxetable*}
+%\end{center}
+
+% HERA
+% http://reionization.org/wp-content/uploads/2015/05/HERA0_imaging.pdf
+%
+% LOFAR
+% https://www.astron.nl/~heald/test/sens.php; 
+% 24 core stations, 16 remote, 8 international, 488 subbands
+%
+% GMRT
+% http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html
+%
+
+We consider in this section several current and near future radio observatories that 
+operate at frequencies $\nu \lesssim 350~\rm MHz$ and can reach continuum 
+sensitivities less than 1~mJy in a few hours.  The results are summarized
+in Table~\ref{tab:sens}.
+
+The primary limitations to detectability are the noise characterized by the root mean square (RMS) of the sky background, and source confusion, i.e., the noise associated with other radio sources in the beam.
+\memoYF{Is this right?
+If not, please correct.
+}
+
+The RMS noise, ${\sigma}_{\rm RMS}$, in an interferometric observation, 
+integration time $\tau$, bandwidth $\Delta \nu$, effective area $A_{\rm eff}$ 
+($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$),
+and $N$ elements is \citep[see e.g.][]{condon+ransom2016}
+%%%
+\begin{equation}
+\sigma_{\rm RMS} = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
+\left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right)
+\end{equation}
+%%%
+We compute $T_{\rm sys} = T_{\rm rx}+ T_{\rm sky}$ using the low frequency sky 
+noise temperature fit from \cite{Rogers+Bowman2008}:
+%%%
+\begin{equation}
+T_{\rm sky} = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + T_{\rm CMB} 
+\end{equation}
+%%%
+where $T_{150} = 283.2~\rm K$ is the $T_{\rm sky}$ at 150~MHz, $\beta=2.47$,
+and $T_{\rm CMB} = 2.73~\rm K$ is the contribution from the cosmic microwave 
+background (CMB).
+While this relation was fit to data taken in the 100-200~MHz range, the authors
+found it to be consistent with published measurements from 10-408~MHz.
+
+The confusion limit, $\sigma_c$, is defined as the standard deviation of the background radio sources. \memoYF{give me better explanation... } 
+To estimate $\sigma_c$ (in mJy beam$^{-1}$) reported in Table~\ref{tab:sens}, 
+we use the relations provided by \cite{condon+ransom2016}, reproduced below:
+%%%
+\begin{eqnarray}
+\sigma_c & \approx & 0.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^2\!\!\!\!,~(\theta > 10\arcsec) \\
+\sigma_c & \approx & 2.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^{10/3}\!\!\!\!\!\!\!\!\!\!,~(\theta < 10\arcsec).
+\end{eqnarray}
+%%%
+The source confusion limit is dominated by active galactic nuclei, which have low polarization fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time \citep{Condon1974,Condon2012}. 
+Therefore both the circularly polarized nature of the emission from hot Jupiters 
+and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate 
+the source confusion limit, allowing hot Jupiters, like other time-variable sources,
+to be detected below the imaging confusion limit.
+
+% LOFAR
+The LOw-Frequency ARray (LOFAR) operates as two separate arrays defined by their 
+high and low bands, differing configurations, and antenna designs, which
+are called respectively the Low Band Antennas (LBA) and High Band Antennas (HBA).  
+LOFAR-LBA operates in the 10-90~MHz range, and LOFAR-HBA operates in the 
+100-240~MHz range \citep{vanHaarlem2013}.  We consider it as two separate
+instruments here.
+LOFAR-LBA's most sensitive band is centered at 60~MHz, and LOFAR-HBA's is at 150~MHz. 
+Given the strong frequency dependence of
+the effective aperture of a dipole antenna, and that the system noise temperature 
+$T_{\rm sys}$ for LOFAR is not fully determined by the sky noise $T_{\rm sky}$, 
+we use the LOFAR Image Noise calculator\footnote{
+Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which 
+is based on {\it SKA Memo 113}\footnote{
+Nijboer, Pandey-Pommier, \& de Bruyn; 
+\url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for
+our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
+
+% HERA
+The Hydrogen Epoch of Reionization Array (HERA\footnote{
+\url{http://reionization.org/}}) \ldots
+
+% GMRT
+The Giant Metre-wave Radio Telescope (GMRT) is an array comprising thirty 
+25-meter antennas, operating at frequencies 130-2000~MHz. The lowest
+band (130-190~MHz) exhibits receiver noise $T_{\rm rx}$ comparable to the sky noise.
+To be conservative, we use the GMRT online calculator.\footnote{
+\url{http://gmrt.ncra.tifr.res.in/~astrosupp/obs\_setup/sensitivity.html}
+}
+
+% VLA
+For the low frequency receivers (28-80~MHz; 4-Band) in the % Long Wavelength Array (LWA) and the 
+Very Large Array (VLA), the receiver noise temperature $T_{\rm rx}\approx 260~\rm K$ 
+\citep{Hicks2012} and is subdominant to $T_{\rm sky}$ by at least -6~dB.  Future
+upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU},
+We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly
+from $T_{\rm rx}\approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to
+$T_{\rm rx}\approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion
+of the full 30-470~MHz band.
+
+% SKA
+The low frequency component of the  Square Kilometer Array (SKA), recently rebaselined 
+to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending
+to 65~km, will operate from 50-350~MHz.\footnote{
+\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
+We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate
+for lower mass ($\lesssim 10 M_J$) separately from the full band, which could be used
+to detect $\sim 30 M_J$ hot Jupiters.
+We adopt the \cite{Rogers+Bowman2008} relation for $T_{\rm sys}$ as above, and assume
+$T_{\rm rx}\approx 60~\rm K$.
+We caution that these assumptions are optimistic, and the time estimates could in reality 
+be a factor of a few worse.
+
+The estimates of the noises shown in Table \ref{tab:sens}, together with Figure \ref{fig:observability}, indicate that, at the frequency relevant to the radio emission from Jupiter-size planets,  the sensitivity is too low to detect them (LOFAR-LBA, HERA).
+On the other hand, for more massive exoplanets ($M_p\sim 10 M_J$) where the bulk of the radio emission would exist above 50 MHz, there is hope to detect radio emission from nearby systems. 
+LOFAR-HBA has reasonable sensitivity to $M_p =10M_p$ planets at 5 AU around a few closest systems as well as those around further stars but orbiting closer to the stars. 
+More promising is SKA, which will be able to detect the signal, within 1 day, from a planet with $M_p =10M_p$ at 5 AU around M stars within 100 pc,
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-09-02 ms.tex
in Section 4.3, the order of descriptions for SKA and VLA are switched in order to be consistent with the Table
updates including comments from Yuka on the sensitivity section

--- 2015-09-02 ms.tex
@@
 
-%\memoYF{discussion about detectability... Figures 1-3 of \citet{griesmeier2007b} show $10^{-3}$ Jy limit for 10-100 MHz (LWA, LOFAR) and $10^{-5}-10^{-4}$ Jy for 100-1000 MHz (LOFAR, SKA).}
-
-We consider in this section several current and near future radio observatories that 
-operate at frequencies $\nu \lesssim 350~\rm MHz$ and can reach continuum 
-sensitivities less than 1~mJy in a few hours.  The results are summarized
-in Table~\ref{tab:sens}.
-The primary limitations to detectability are noise, characterized by the
-system equivalent blackbody temperature $T_{\rm sys}$, resolution, and source confusion.  
-To estimate the source confusion $\sigma_c$ (in mJy beam$^{-1}$) reported in Table~\ref{tab:sens}, 
-we use the relations provided by \cite{condon+ransom2016}, reproduced below:
-\begin{eqnarray}
-\sigma_c & \approx & 0.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^2\!\!\!\!,~(\theta > 10\arcsec) \\
-\sigma_c & \approx & 2.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^{10/3}\!\!\!\!\!\!\!\!\!\!,~(\theta < 10\arcsec).
-\end{eqnarray}
-The source confusion limit is dominated by active galactic nuclei, which have low polarization 
-fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time \citep{Condon1974,Condon2012}.
-Therefore both the circularly polarized nature of the emission from hot Jupiters 
-and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate 
-the source confusion limit, allowing hot Jupiters, like other time-variable sources,
-to be detected below the imaging confusion limit.
-
-The RMS noise ${\sigma}$ in an interferometric observation, 
-integration time $\tau$, bandwidth $\Delta \nu$, effective area $A_{\rm eff}$ 
-($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$),
-and $N$ elements is \citep[see e.g.][]{condon+ransom2016} 
-\begin{equation}
-\sigma = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
-\left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right)
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{center}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{deluxetable*}{cccccc}
-\tabletypesize{\scriptsize}
+\tabletypesize{\footnotesize}
 \tablecolumns{6}
@@
 \startdata
-GMRT       & 130-190 & 430   &  460             & 16.5 & 56.9 \\ 
-HERA       &  30-80  & 870   & 1900             & 1030 & 4.2$\times10^5$\\ 
-LOFAR-LBA  &  30-80  & 700   & 1225             & 8.3  & 42 \\ 
-LOFAR-HBA  & 110-200 &  35   &    3             & 3.3  & 1.1 \\  
-%LWA        &  30-80  & 53000 &  3.2$\times10^6$ & 10.3 & 211 \\
-%MWA        &  30-80  & 27000 &  8.1$\times10^5$ & 1030 & $2.1\times10^6$ \\
-SKA-Low (part) & 50-200 & 7.8 &  0.15           & 7.8  & 9.7 \\
-SKA-Low (full) & 50-350 & 2.2 &  0.012          & 2.2  & 1.5 \\
-%VLA 4-Band & 30-80   & 3300  & 1100             & 28.6 & 330 \\
-VLA-LOBO   &  50-350 &  92   &  21              & 8.6  & 10
+LOFAR-LBA  &  30-80  & 700   & 120000             & 8.3  & 42 \\ 
+LOFAR-HBA  & 110-200 &  35   &    310             & 3.3  & 1.1 \\  
+HERA       &  30-80  & 870   & 160000             & 1030 & 4.2$\times10^5$\\ 
+GMRT       & 130-190 & 430   &  46000             & 16.5 & 56.9 \\ 
+%LWA       &  30-80  & 58000 &  702127141         & 10.3 & 42.2 \\
+%MWA       &  30-80  & 29000 &  176223211         & 1030 & 4.2$\times10^5$ \\
+SKA-Low (part) & 50-200 & 7.8 &  12.6             & 7.6  & 9.7 \\
+SKA-Low (full) & 50-350 & 2.2 &  1.0              & 4.8  & 1.5 \\
+%VLA 4-Band& 30-80   & 3300  & 2312058            & 28.6 & 330 \\
+VLA-LOBO   &  50-350 &  92   &  1800              & 8.6  & 10.4
 \enddata
-\tablecomments{Time estimates to reach 20~$\mu$Jy RMS.}
+%\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.}
 \tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported in this table.}
-\tablenotetext{b}{The integration time in hours required to reach an RMS of 20~$\mu$Jy (i.e.\ 5-$\sigma$ detection
-of a typical source with 100~$\mu$Jy bm$^{-1}$ average flux) \memoTM{Should we compute this instead for a 5-sigma detection
-of a $\sim$400~$\mu$Jy bm$^{-1}$ average flux, like in Figure \ref{fig:cartoon}?  Going to 80~$\mu$Jy RMS would be $16\times$ shorter.}.}
-\tablenotetext{c}{Source confusion limit RMS contribution.}
+\tablenotetext{b}{The integration time in hours required to reach an RMS of 2~$\mu$Jy (i.e.\ 5-$\sigma$ detection
+of a typical source at 100~pc with 10~$\mu$Jy bm$^{-1}$ average flux).}
+\tablenotetext{c}{Source confusion RMS contribution.}
 \end{deluxetable*}
-%\end{center}
-
+%
 % HERA
@@
 %
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We consider in this section several current and near future radio observatories that 
+operate at frequencies $\nu \lesssim 350~\rm MHz$ and can reach continuum 
+sensitivities less than 1~mJy in a few hours.  The results are summarized in Table~\ref{tab:sens}.
+
+The primary limitation to detectability is a telescope's sensitivity, characterized by the root mean 
+square (RMS) noise fluctuations in the sky and receiver.
+The RMS noise ${\sigma}_{\rm RMS}$ in an interferometric observation with 
+integration time $\tau$, bandwidth $\Delta \nu$, effective area $A_{\rm eff}$ 
+($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$),
+and $N$ antennas is \citep[see e.g.][]{condon+ransom2016}
+%%%
+\begin{equation}
+\sigma_{\rm RMS} = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
+\left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right).
+\end{equation}
+%%%
+Here, $T_{\rm sys}$ is the blackbody temperature equivalent of the total system noise, which is the sum
+of the instrument or receiver noise temperature $T_{\rm rx}$ and the noise contribution from the sky $T_{\rm sky}$.
+We estimate $T_{\rm sky}$ using the low frequency sky noise temperature fit from \cite{Rogers+Bowman2008}:
+%%%
+\begin{equation}
+T_{\rm sky} = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + T_{\rm CMB} 
+\end{equation}
+%%%
+where $T_{150} = 283.2~\rm K$ is the $T_{\rm sky}$ at 150~MHz, $\beta=2.47$,
+and $T_{\rm CMB} = 2.73~\rm K$ is the contribution from the cosmic microwave 
+background (CMB).
+While this relation was fit to data taken in the 100-200~MHz range, the authors
+found it to be consistent with published measurements from 10-408~MHz. 
+%The $T_{\rm rx}$ is the receiver noise temperature, which depends on the instruments and is described below.
+
+An additional contribution to the noise is due to source confusion, the imaging noise associated with 
+unresolved interloping radio sources in an observation.
+Source confusion is characterized by the standard deviation $\sigma_c$ in the surface brightness of an 
+image due to one or more unresolved sources in the beam solid angle (for a review, see \cite{Condon1974,Condon2012}).
+To estimate $\sigma_c$, reported in Table~\ref{tab:sens}, 
+we use the relations provided by \cite{condon+ransom2016}, reproduced below:
+%%%
+\begin{eqnarray}
+\sigma_c & \approx & 0.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^2\!\!\!\!,~(\theta > 10\arcsec) \\
+\sigma_c & \approx & 2.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^{10/3}\!\!\!\!\!\!\!\!\!\!,~(\theta < 10\arcsec).
+\end{eqnarray}
+%%%
+The source confusion limit is dominated by active galactic nuclei, which have low polarization 
+fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time. 
+Therefore both the circularly polarized nature of the emission from hot Jupiters 
+and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate 
+the source confusion limit, allowing hot jupiters, like other time-variable sources,
+to be detected below the imaging confusion limit.  Thus we expect not to be a strong
+limitation to detectability of hot jupiters.
+
+% LOFAR
 The LOw-Frequency ARray (LOFAR) operates as two separate arrays defined by their 
@@
 the effective aperture of a dipole antenna, and that the system noise temperature 
-$T_{\rm sys}$ for LOFAR is not fully determined by the sky noise $T_{\rm sky}$, 
+$T_{\rm sys}$ for LOFAR is not fully determined by the sky noise $T_{\rm sky}$ (i.e.\ $T_{\rm rx} \sim T_{\rm sky}$), 
 we use the LOFAR Image Noise calculator\footnote{
@@
 
+% HERA
 The Hydrogen Epoch of Reionization Array (HERA\footnote{
@@
 
+% GMRT
 The Giant Metre-wave Radio Telescope (GMRT) is an array comprising thirty 
@@
 
-For the low frequency receivers (28-80~MHz; 4-Band) in the % Long Wavelength Array (LWA) and the 
-Very Large Array (VLA), the receiver noise temperature $T_{\rm rx}\approx 260~\rm K$ 
-\citep{Hicks2012} and is subdominant to $T_{\rm sky}$ by at least -6~dB.  Future
-upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU},
-We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly
-from $T_{\rm rx}\approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to
-$T_{\rm rx}\approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion
-of the full 30-470~MHz band.
-
-We compute $T_{\rm sys} = T_{\rm rx}+ T_{\rm sky}$ using the low frequency sky 
-noise temperature fit from \cite{Rogers+Bowman2008}:
-\begin{equation}
-T_{\rm sky} = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + T_{\rm CMB} 
-\end{equation}
-where $T_{150} = 283.2~\rm K$ is the $T_{\rm sky}$ at 150~MHz, $\beta=2.47$,
-and $T_{\rm CMB} = 2.73~\rm K$ is the contribution from the cosmic microwave 
-background (CMB).
-While this relation was fit to data taken in the 100-200~MHz range, the authors
-found it to be consistent with published measurements from 10-408~MHz.
-
+% SKA
 The low frequency component of the  Square Kilometer Array (SKA), recently rebaselined 
@@
 be a factor of a few worse.
+
+% VLA
+For the low frequency receivers (28-80~MHz; 4-Band) in the % Long Wavelength Array (LWA) and the 
+Very Large Array (VLA), the receiver noise temperature $T_{\rm rx}\approx 260~\rm K$ 
+\citep{Hicks2012} and is subdominant to $T_{\rm sky}$ by at least -6~dB.  Future
+upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU}
+are being considered, and would cover the full 30-470~MHz band.  
+We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly
+from $T_{\rm rx}\approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to
+$T_{\rm rx}\approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion
+of the full 30-470~MHz band.
+
+The estimates of the noises shown in Table \ref{tab:sens}, together with Figure \ref{fig:observability}, indicate that, at the frequency relevant to the radio emission from Jupiter-size planets, current instrument sensitivities are too low for detection.
+On the other hand, for more massive exoplanets ($M_p\sim 10 M_J$) where the bulk of the radio emission would exist above 50~MHz, there is hope to detect radio emission from nearby systems with LOFAR-HBA or LOBO.
+LOFAR-HBA has reasonable sensitivity to $M_p =10~M_J$ planets at 5 AU around a few closest systems as well as those around further stars but orbiting closer to the stars. 
+More promising is the low frequency component of SKA, which will be able to detect the signal within one day from planets with $M_p \sim 10~M_J$ and orbital distances $\sim$5~AU around M stars $<$100~pc from Earth.
 

### 2015-09-02 ms.tex
ok, now i think we just need a few words about HERA.

@@
 \usepackage{comment}
-\usepackage{color}
+\usepackage{color,xcolor}
 \usepackage{url}
 \usepackage{hyperref}
+\hypersetup{colorlinks,linkcolor={blue!50!black},citecolor={blue!50!black},urlcolor={blue!50!black}}
 %\usepackage[dvipdfmx]{color}
@@
 \tablehead{
-Instrument & Band  & Sensitivity\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
+Instrument & Band  & $\sigma_{\rm RMS}$\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
            & (MHz) & ($\mu$Jy~hr$^{1/2}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
@@
 %\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.}
-\tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported in this table.}
+\tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported 
+in this table (Equation~\ref{eq:rms_sens}).}
 \tablenotetext{b}{The integration time in hours required to reach an RMS of 2~$\mu$Jy (i.e.\ 5-$\sigma$ detection
@@
 \left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right).
+\label{eq:rms_sens}
 \end{equation}
@@
 the source confusion limit, allowing hot jupiters, like other time-variable sources,
-to be detected below the imaging confusion limit.  Thus we expect not to be a strong
-limitation to detectability of hot jupiters.
+to be detected below the imaging confusion limit.  Thus we expect confusion not to be a 
+strong limitation to detectability of hot jupiters.
 

### 2015-09-03 ms.tex
1 line per sentence/1 sentence per line; and minor wording changes.

@@
 %%%
-When the host stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders-of-magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
+When planet-hosting stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders-of-magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
 Accordingly, planetary companions around them at a few AU orbits, if exist, are heated up to the level of canonical hot Jupiters and also subjected to the massive stellar wind.
@@
 Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) but refer to planets orbiting RGB and AGB stars \citep{spiegel+madhusudhan2012}.
-Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr .
+Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr.
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.
@@
 Note that the scaling law, Equation (\ref{eq:Bscaling}), would be reasonable only for rapidly rotating objects.
-Indeed, unlike canonical hot Jupiters, RGHJs are not subjected to tidal lock and as such, we do not have to assume slow spin rotation rates \citep{spiegel+madhusudhan2012}.
+Indeed, unlike canonical hot Jupiters, RGHJs are not tidal locked to their host stars, so we do not have to assume slow spin rotation rates \citep{spiegel+madhusudhan2012}.
 Therefore, we implicitly assume that the RGHJs we consider in this paper are rapidly rotating so that they generate planetary magnetic fields through the same mechanism as Jupiter.
@@
 The density of the metallic core, $\rho _{\rm dynamo}$ is obtained by averaging the density in the core. 
-In the case of Jupiter, $r_{\rm dynamo, J} = 0.85 R_{\rm J}$ and $\rho_{\rm dynamo, J} = 1.899~{\rm g/cm}^3$  .
+In the case of Jupiter, $r_{\rm dynamo, J} = 0.85 R_{\rm J}$ and $\rho_{\rm dynamo, J} = 1.899~{\rm g/cm}^3$.
 
@@
 
-While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr
-\citep{reimers1975}
-, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase
-\citep{schild1989, vassiliadis1993, schoier2001, vanloon2005}.
+While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr \citep{reimers1975}, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase \citep{schild1989, vassiliadis1993, schoier2001, vanloon2005}.
 Therefore, we have
@@
 \begin{equation}
-\frac{\dot M_\star}{\dot M_{\odot}} \sim 10^6 - 10^9 . \label{eq:scale_Mdot}
+\frac{\dot M_\star}{\dot M_{\odot}} \sim 10^6 - 10^9 \, . \label{eq:scale_Mdot}
 \end{equation}
@@
 Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_{\star}/R_{\star}}$ ($G$ is the gravitational constant, $M_{\star}$ is the stellar mass, and $R_{\star}$ is the stellar radius), a Solar-mass red giant with radius $R_{\star}=100R_{\odot}$ encounters 10 times as slow stellar wind as that at the Sun, $v_{\odot}$.
-Thus,
-%%%%%%%%%% 
-\begin{equation}
-\frac{v}{v_{\odot}} \sim 10^{-1} . \label{eq:scale_v}
+Therefore, 
+%%%%%%%%%% 
+\begin{equation}
+\frac{v}{v_{\odot}} \sim 10^{-1} \, . \label{eq:scale_v}
 \end{equation}
@@
 %%%%%%%%%
-The source rate is obtained by counting the number of photons whose energy is higher than 13.6 eV, the energy needed to ionize hydrogen atoms. Thus\memoYF{need to check},  
+The source rate is obtained by counting the number of photons whose energy is higher than 13.6~eV, the energy needed to ionize hydrogen atoms.
+As a result, \memoYF{need to check}
 %%%%%%%%%
@@
 
-Thus, we expect that the X-ray emission from the accretion disk is enough to ionize the stellar wind.
-Therefore, we assume that the stellar wind particles represented by (equation (\ref{eq:n})) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
+We therefore expect that the X-ray emission from the accretion disk is enough to ionize the stellar wind.
+This implies that the stellar wind particles represented by (equation~\ref{eq:n}) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
 
@@
 \label{eq:fplasmalos_scaled} & = & 14.7{\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{0.1 v_{\odot}}  \right)^{-1/2} \notag \\
- & & \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}}\right)^{1/2} \, ,
+ & & \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}}\right)^{1/2} \, .
 \end{eqnarray}
@@
 P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
-P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
-\end{eqnarray}
-\memoTM{Somekind of plot of the typical ranges of these quantities might be useful/illustrative.}
+P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag} \, ,
+\end{eqnarray}
+\memoTM{Some kind of plot of the typical ranges of these quantities might be useful/illustrative.}
 %%%
@@
 In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim 1.6$, $\sim $6.3, and $\sim $3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission.
-
-The bandwidth, $\Delta \nu$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following the assumption of \citet{griesmeier2007b}.
+The bandwidth, $\Delta \nu$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following \citet{griesmeier2007b}.
 
@@
 The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere. 
-The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion.
-Bottom panel: cyclotron frequency, i.e., the frequency of radio emission.
-}
+he hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion.
+Bottom panel: cyclotron frequency, i.e., the frequency of radio emission. }
   \label{fig:radio}
@@
    \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.
-The spectrum of RGHJ is modeled after Jovian radio spectra, e.g.
-figure 8 of \citet{zarka_et_al2004} and figure 2 of \citet{griesmeier2007a}; contribution from Io is not shown here.
-The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law.
-}
+The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. figure 8 of \citet{zarka_et_al2004} and figure 2 of \citet{griesmeier2007a}; contribution from Io is not shown here.
+The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law. }
   \label{fig:cartoon}
@@
    \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$ and 10$M_J$ at 1 AU and 5AU.
-Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet.
-}
+Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet. }
   \label{fig:observability}
@@
 In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
-
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
@@
 %%%
-The age of the system is assumed to roughly same as the lifetime of their main-sequence stage, which depends on the stellar mass. We assume \memoYF{validation}:
+The age of the system is assumed to roughly same as the lifetime of their main-sequence stage, which depends on the stellar mass.
+We assume \memoYF{validation}:
 %%%
@@
 
-We consider in this section several current and near future radio observatories that 
-operate at frequencies $\nu \lesssim 350~\rm MHz$ and can reach continuum 
-sensitivities less than 1~mJy in a few hours.  The results are summarized in Table~\ref{tab:sens}.
-
-The primary limitation to detectability is a telescope's sensitivity, characterized by the root mean 
-square (RMS) noise fluctuations in the sky and receiver.
-The RMS noise ${\sigma}_{\rm RMS}$ in an interferometric observation with 
-integration time $\tau$, bandwidth $\Delta \nu$, effective area $A_{\rm eff}$ 
-($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$),
-and $N$ antennas is \citep[see e.g.][]{condon+ransom2016}
+We consider in this section several current and near future radio observatories that operate at frequencies $\nu \lesssim 350~\rm MHz$ and can reach continuum sensitivities less than 1~mJy in a few hours.
+The results are summarized in Table~\ref{tab:sens}.
+
+The primary limitation to detectability is a telescope's sensitivity, characterized by the root mean square (RMS) noise fluctuations in the sky and receiver.
+The RMS noise ${\sigma}_{\rm RMS}$ in an interferometric observation with integration time $\tau$, bandwidth $\Delta \nu$, effective area $A_{\rm eff}$ ($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$), and $N$ antennas is \citep[see e.g.][]{condon+ransom2016}
 %%%
@@
 %%%
-Here, $T_{\rm sys}$ is the blackbody temperature equivalent of the total system noise, which is the sum
-of the instrument or receiver noise temperature $T_{\rm rx}$ and the noise contribution from the sky $T_{\rm sky}$.
+Here, $T_{\rm sys}$ is the blackbody temperature equivalent of the total system noise, which is the sum of the instrument or receiver noise temperature $T_{\rm rx}$ and the noise contribution from the sky $T_{\rm sky}$.
 We estimate $T_{\rm sky}$ using the low frequency sky noise temperature fit from \cite{Rogers+Bowman2008}:
@@
 %%%
-where $T_{150} = 283.2~\rm K$ is the $T_{\rm sky}$ at 150~MHz, $\beta=2.47$,
-and $T_{\rm CMB} = 2.73~\rm K$ is the contribution from the cosmic microwave 
-background (CMB).
-While this relation was fit to data taken in the 100-200~MHz range, the authors
-found it to be consistent with published measurements from 10-408~MHz. 
+where $T_{150} = 283.2~\rm K$ is the $T_{\rm sky}$ at 150~MHz, $\beta=2.47$, and $T_{\rm CMB} = 2.73~\rm K$ is the contribution from the cosmic microwave background (CMB).
+While this relation was fit to data taken in the 100-200~MHz range, the authors found it to be consistent with published measurements from 10-408~MHz. 
 %The $T_{\rm rx}$ is the receiver noise temperature, which depends on the instruments and is described below.
 
-An additional contribution to the noise is due to source confusion, the imaging noise associated with 
-unresolved interloping radio sources in an observation.
-Source confusion is characterized by the standard deviation $\sigma_c$ in the surface brightness of an 
-image due to one or more unresolved sources in the beam solid angle (for a review, see \cite{Condon1974,Condon2012}).
-To estimate $\sigma_c$, reported in Table~\ref{tab:sens}, 
-we use the relations provided by \cite{condon+ransom2016}, reproduced below:
+An additional contribution to the noise is due to source confusion, the imaging noise associated with unresolved interloping radio sources in an observation.
+Source confusion is characterized by the standard deviation $\sigma_c$ in the surface brightness of an image due to one or more unresolved sources in the beam solid angle (for a review, see \cite{Condon1974,Condon2012}).
+To estimate $\sigma_c$, reported in Table~\ref{tab:sens}, we use the relations provided by \cite{condon+ransom2016}, reproduced below:
 %%%
@@
 %%%
-The source confusion limit is dominated by active galactic nuclei, which have low polarization 
-fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time. 
-Therefore both the circularly polarized nature of the emission from hot Jupiters 
-and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate 
-the source confusion limit, allowing hot jupiters, like other time-variable sources,
-to be detected below the imaging confusion limit.  Thus we expect confusion not to be a 
-strong limitation to detectability of hot jupiters.
+The source confusion limit is dominated by active galactic nuclei, which have low polarization fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time.
+Therefore both the circularly polarized nature of the emission from hot Jupiters and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate the source confusion limit, allowing hot jupiters, like other time-variable sources, to be detected below the imaging confusion limit.
+We therefore expect confusion not to be a strong limitation to detectability of hot Jupiters.
 
 % LOFAR
-The LOw-Frequency ARray (LOFAR) operates as two separate arrays defined by their 
-high and low bands, differing configurations, and antenna designs, which
-are called respectively the Low Band Antennas (LBA) and High Band Antennas (HBA).  
-LOFAR-LBA operates in the 10-90~MHz range, and LOFAR-HBA operates in the 
-100-240~MHz range \citep{vanHaarlem2013}.  We consider it as two separate
-instruments here.
+The LOw-Frequency ARray (LOFAR) operates as two separate arrays defined by their high and low bands, differing configurations, and antenna designs, which are called respectively the Low Band Antennas (LBA) and High Band Antennas (HBA).
+LOFAR-LBA operates in the 10-90~MHz range, and LOFAR-HBA operates in the 100-240~MHz range \citep{vanHaarlem2013}.
+We consider it as two separate instruments here.
 LOFAR-LBA's most sensitive band is centered at 60~MHz, and LOFAR-HBA's is at 150~MHz.
-Given the strong frequency dependence of
-the effective aperture of a dipole antenna, and that the system noise temperature 
-$T_{\rm sys}$ for LOFAR is not fully determined by the sky noise $T_{\rm sky}$ (i.e.\ $T_{\rm rx} \sim T_{\rm sky}$), 
-we use the LOFAR Image Noise calculator\footnote{
-Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which 
-is based on {\it SKA Memo 113}\footnote{
-Nijboer, Pandey-Pommier, \& de Bruyn; 
-\url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for
-our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
+Given the strong frequency dependence of the effective aperture of a dipole antenna, and that the system noise temperature $T_{\rm sys}$ for LOFAR is not fully determined by the sky noise $T_{\rm sky}$ (i.e.\ $T_{\rm rx} \sim T_{\rm sky}$), we use the LOFAR Image Noise calculator\footnote{Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which is based on {\it SKA Memo 113}\footnote{Nijboer, Pandey-Pommier, \& de Bruyn; \url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
 
 % HERA
-The Hydrogen Epoch of Reionization Array (HERA\footnote{
-\url{http://reionization.org/}}) \ldots
+The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) \ldots
 
 % GMRT
-The Giant Metre-wave Radio Telescope (GMRT) is an array comprising thirty 
-25-meter antennas, operating at frequencies 130-2000~MHz. The lowest
-band (130-190~MHz) exhibits receiver noise $T_{\rm rx}$ comparable to the sky noise.
-To be conservative, we use the GMRT online calculator.\footnote{
-\url{http://gmrt.ncra.tifr.res.in/~astrosupp/obs\_setup/sensitivity.html}
-}
+The Giant Metre-wave Radio Telescope (GMRT) is an array comprising thirty 25-meter antennas, operating at frequencies 130-2000~MHz.
+The lowest band (130-190~MHz) exhibits receiver noise $T_{\rm rx}$ comparable to the sky noise.
+To be conservative, we use the GMRT online calculator.\footnote{\url{http://gmrt.ncra.tifr.res.in/~astrosupp/obs\_setup/sensitivity.html}}
 
 % SKA
-The low frequency component of the  Square Kilometer Array (SKA), recently rebaselined 
-to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending
-to 65~km, will operate from 50-350~MHz.\footnote{
-\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
-We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate
-for lower mass ($\lesssim 10 M_J$) separately from the full band, which could be used
-to detect $\sim 30 M_J$ hot Jupiters.
-We adopt the \cite{Rogers+Bowman2008} relation for $T_{\rm sys}$ as above, and assume
-$T_{\rm rx}\approx 60~\rm K$.
-We caution that these assumptions are optimistic, and the time estimates could in reality 
-be a factor of a few worse.
+The low frequency component of the Square Kilometer Array (SKA), recently rebaselined to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending to 65~km, will operate from 50-350~MHz.\footnote{\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
+We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_J$) separately from the full band, which could be used to detect $\sim 30 M_J$ hot Jupiters.
+We adopt the \cite{Rogers+Bowman2008} relation for $T_{\rm sys}$ as above, and assume $T_{\rm rx}\approx 60~\rm K$.
+We caution that these assumptions are optimistic, and the time estimates could in reality be a factor of a few worse.
 
 % VLA
-For the low frequency receivers (28-80~MHz; 4-Band) in the % Long Wavelength Array (LWA) and the 
-Very Large Array (VLA), the receiver noise temperature $T_{\rm rx}\approx 260~\rm K$ 
-\citep{Hicks2012} and is subdominant to $T_{\rm sky}$ by at least -6~dB.  Future
-upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU}
-are being considered, and would cover the full 30-470~MHz band.  
-We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly
-from $T_{\rm rx}\approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to
-$T_{\rm rx}\approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion
-of the full 30-470~MHz band.
+For the low frequency receivers (28-80~MHz; 4-Band) in the \memoDS{Long Wavelength Array (LWA) and the?} Very Large Array (VLA), the receiver noise temperature $T_{\rm rx}\approx 260~\rm K$ \citep{Hicks2012} and is subdominant to $T_{\rm sky}$ by at least -6~dB.
+Future upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU} are being considered, and would cover the full 30-470~MHz band.
+We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly from $T_{\rm rx}\approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to $T_{\rm rx}\approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion of the full 30-470~MHz band.
 
@@
 NM acknowledges support from [???].
-The portion of this research for which TM is responsible was performed while he
-held a National Research Council Research Associateship Award at the Naval 
-Research Laboratory (NRL).  Basic research in radio astronomy at NRL 
-is supported by 6.1 Base funding.
+The portion of this research for which TM is responsible was performed while he held a National Research Council Research Associateship Award at the Naval Research Laboratory (NRL).
+Basic research in radio astronomy at NRL is supported by 6.1 Base funding.
 
@@
 
-A common part is the scaling relationship between the planetary magnetic field strength and the input kinetic energy. Combining equation (\ref{eq:Pinp_kin}), i.e.,
+A common part is the scaling relationship between the planetary magnetic field strength and the input kinetic energy.
+Combining equation (\ref{eq:Pinp_kin}), i.e.,
 %%%

### 2015-09-03 ms.tex
introduction is edited to be consistent with the current organization

@@
 We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and proposed scaling of planetary magnetic fields.
-We find that RGHJs might be as bright as canonical hot Jupiters as predicted so far, and thus radio emission from a RGHJ would be visible from a hundred parsec distances with current/future detectors \memoYF{check}.
+We find that RGHJs might be as bright as canonical hot Jupiters as predicted so far, and thus radio emission from a RGHJ would be visible from a hundred parsec distances with current/future detectors such as LOFAR-HBA and SKA.
 
@@
 The ionized stellar wind would then interact with the planetary magnetic field in the same way as Solar System planets do.
-Thus, by extrapolating the radiometric Bode's law, we provide more optimistic estimates for highly evolved stars compared to previous results.
+Thus, by extrapolating the radiometric Bode's law, we provide more optimistic estimates for highly evolved stars compared to the previous result.
 Given that the survey of exoplanets around highly evolved stars is not complete, we do not constrain ourselves to the systems known to have sub-stellar companions.
@@
 In \S2, we describe our assumptions for the stellar wind, planetary magnetosphere, frequency of radio emission, and scaling of planetary radio emission.
-\S3 presents an estimate of the spectral radio intensity of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters.
-%\S3 also describes the surprising result that, although the planetary magnetic field is crucial to the generation of radio emission at all, there might be an important region in parameter space in which planets with stronger magnetic fields are less easily observable.
-\S4 discusses possible obstacles to detect radio emission from RGHJs, in particular the effects of intrinsic radio emission of evolved stars and the offsetting effect of the electrons spiraling down along the planetary magnetic field.
-Observability with current and near-future instruments is also examined in \S4. 
-Finally, \S5 concludes the paper with a brief summary.
+\S3 presents an estimate of the spectral radio intensity of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters as well as those from Jupiter-twins.
+\S4 gives predictions for the signals from evolved systems within 400 pc, taking account of the intrinsic radio emission from the host evolved stars.
+Considering the sensitivity of the current and future radio instruments, we argue that SKA, and perhaps LOFAR-HBA as well, would be capable of detecting these signals within a reasonable integration time.
+%In \S5, we discuss the usefulness of radio emission in exploring Jupiter-like planets around evolved stars. 
+In \S5, we mention the effects of canceling magnetic fields resulting from the plasmas spiraling in the planetary magnetosphere.  
+Finally, \S6 concludes the paper with a brief summary.
 

### 2015-09-03 ms.tex
filename of cartoon figure is modified
response to Dave about LWA

--- 2015-09-03 ms.tex
@@
 
+\newcommand{\Tcmb}{\mbox{$T_{\mbox{\tiny CMB}}$}}
+\newcommand{\Tsky}{\mbox{$T_{\mbox{\tiny sky}}$}}
+\newcommand{\Tsys}{\mbox{$T_{\mbox{\tiny sys}}$}}
+\newcommand{\Trx}{\mbox{$T_{\mbox{\tiny rx}}$}}
+\newcommand{\sigRMS}{\mbox{$\sigma_{\mbox{\tiny RMS}}$}}
+
 % set formatting properties
@@
 Another ingredient needed for modeling the radio emission from the interaction between the planetary magnetic field and the stellar wind is the density and velocity of the stellar wind. 
-The number density of \memoTM{electrons in the (?)} stellar wind, $n$, can be expressed as
+The number density of electrons in the stellar wind, $n$, can be expressed as
 %%%%%%%%%% 
@@
 \end{eqnarray}
-\memoTM{Some kind of plot of the typical ranges of these quantities might be useful/illustrative.}
 %%%
@@
 \tablehead{
-Instrument & Band  & $\sigma_{\rm RMS}$\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
+Instrument & Band  & \sigRMS\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
            & (MHz) & ($\mu$Jy~hr$^{1/2}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
@@
 The primary limitation to detectability is a telescope's sensitivity, characterized by the root mean square (RMS) noise fluctuations in the sky and receiver.
-The RMS noise ${\sigma}_{\rm RMS}$ in an interferometric observation with integration time $\tau$, bandwidth $\Delta \nu$, effective area $A_{\rm eff}$ ($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$), and $N$ antennas is \citep[see e.g.][]{condon+ransom2016}
-%%%
-\begin{equation}
-\sigma_{\rm RMS} = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
+The RMS noise \sigRMS\ in an interferometric observation with integration time $\tau$, bandwidth $\Delta \nu$, effective area $A_{\rm eff}$ ($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$), and $N$ antennas is \citep[see e.g.][]{condon+ransom2016}
+%%%
+\begin{equation}
+\sigRMS = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
 \left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right).
@@
 %%%
-Here, $T_{\rm sys}$ is the blackbody temperature equivalent of the total system noise, which is the sum of the instrument or receiver noise temperature $T_{\rm rx}$ and the noise contribution from the sky $T_{\rm sky}$.
-We estimate $T_{\rm sky}$ using the low frequency sky noise temperature fit from \cite{Rogers+Bowman2008}:
-%%%
-\begin{equation}
-T_{\rm sky} = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + T_{\rm CMB} 
-\end{equation}
-%%%
-where $T_{150} = 283.2~\rm K$ is the $T_{\rm sky}$ at 150~MHz, $\beta=2.47$, and $T_{\rm CMB} = 2.73~\rm K$ is the contribution from the cosmic microwave background (CMB).
+Here, \Tsys\ is the blackbody temperature equivalent of the total system noise, which is the sum of the instrument or receiver noise temperature \Trx\ and the noise contribution from the sky \Tsky.
+We estimate \Tsky\ using the low frequency sky noise temperature fit from \cite{Rogers+Bowman2008}:
+%%%
+\begin{equation}
+\Tsky = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + \Tcmb 
+\end{equation}
+%%%
+where $T_{150} = 283.2~\rm K$ is the \Tsky\ at 150~MHz, $\beta=2.47$, and $\Tcmb = 2.73~\rm K$ is the contribution from the cosmic microwave background (CMB).
 While this relation was fit to data taken in the 100-200~MHz range, the authors found it to be consistent with published measurements from 10-408~MHz. 
-%The $T_{\rm rx}$ is the receiver noise temperature, which depends on the instruments and is described below.
+%The \Trx\ is the receiver noise temperature, which depends on the instruments and is described below.
 
@@
 LOFAR-LBA's most sensitive band is centered at 60~MHz, and LOFAR-HBA's is at 150~MHz.
-Given the strong frequency dependence of the effective aperture of a dipole antenna, and that the system noise temperature $T_{\rm sys}$ for LOFAR is not fully determined by the sky noise $T_{\rm sky}$ (i.e.\ $T_{\rm rx} \sim T_{\rm sky}$), we use the LOFAR Image Noise calculator\footnote{Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which is based on {\it SKA Memo 113}\footnote{Nijboer, Pandey-Pommier, \& de Bruyn; \url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
+Given the strong frequency dependence of the effective aperture of a dipole antenna, and that the reciever noise temperature for LOFAR $\Trx \sim \Tsky$, we use the LOFAR Image Noise calculator\footnote{Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which is based on {\it SKA Memo 113}\footnote{Nijboer, Pandey-Pommier, \& de Bruyn; \url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
 
@@
 We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_J$) separately from the full band, which could be used to detect $\sim 30 M_J$ hot Jupiters.
-We adopt the \cite{Rogers+Bowman2008} relation for $T_{\rm sys}$ as above, and assume $T_{\rm rx}\approx 60~\rm K$.
+We adopt the \cite{Rogers+Bowman2008} relation for \Tsys\ as above, and assume $\Trx \approx 60~\rm K$.
 We caution that these assumptions are optimistic, and the time estimates could in reality be a factor of a few worse.
@@
 % VLA
-For the low frequency receivers (28-80~MHz; 4-Band) in the \memoDS{Long Wavelength Array (LWA) and the?} Very Large Array (VLA), the receiver noise temperature $T_{\rm rx}\approx 260~\rm K$ \citep{Hicks2012} and is subdominant to $T_{\rm sky}$ by at least -6~dB.
+For the low frequency receivers (28-80~MHz; 4-Band) in the \memoDS{Long Wavelength Array (LWA) and the?}\memoTM{No need to mention LWA here.
+The receivers are the same in the VLA 4-band and the LWA, but the LWA is far too insensitive to consider here, as is VLA 4-band alone, so the reference just serves to place an upper limit on what \Trx\ will be for LOBO.} Very Large Array (VLA), the receiver noise temperature $\Trx \approx 260~\rm K$ \citep{Hicks2012} and is subdominant to \Tsky\ by at least -6~dB.
 Future upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU} are being considered, and would cover the full 30-470~MHz band.
-We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly from $T_{\rm rx}\approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to $T_{\rm rx}\approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion of the full 30-470~MHz band.
+We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly from $\Trx \approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to $\Trx \approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion of the full 30-470~MHz band.
 

### 2015-09-03 ms.tex

@@
 \begin{figure*}[tbp]
-   \plotonesc{fig5_10Mj_2.pdf}
+   \plotonesc{cartoon_10Mj_2.pdf}
    \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.

### 2015-09-04 ms.tex
minor edit
in introduction, descriptions of previous papers are elaborated

@@
 Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984}.
-Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems have been estimated \citep{farrell1999,zarka2001,lazio2004,griesmeier2004,griesmeier2005,stevens2005,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010}.
-\memoYF{in more detail}
-%Based on this law, it has been proposed that exoplanets in close-in orbits may be bright radio wave emitters because they are subjected to strong stellar wind and/or strong interstellar magnetic field, and thus can gain larger energy input.
-Motivated by such speculations, spectral radio intensity from known exoplanets have been estimated  \citep{farrell1999,zarka2001,lazi o2004,griesmeier2004,griesmeier2007a,griesmeier2007b,jardine2008,reiners2010,}.
-In addition, young planetary systems where stellar wind activity is strong have also been considered \citep{griesmeier2005}. 
+Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems have been examined. 
+\citet{farrell1999,zarka2001,lazio2004} pointed out that a few of the known exoplanetary systems may have radio flux of $\sim $1 mJy level, due to the small orbital distance of the planet and/or the larger planetary mass.
+%\citet{griesmeier2004} modeled in detail the evolution of atmosphere and magnetic field of the tidally-locked close-in stars and found that 
+\citet{stevens2005} gave improved estimates of the stellar mass-loss rate based on X-ray flux and re-evaluated the radio flux of known exoplanetary systems. 
+\citet{griesmeier2005} took account of the high stellar activity in the early stage of the planetary system and proposed that the young system would be good candidates to search for radio emission. 
+\citet{griesmeier2007a, griesmeier2007b} discussed the effects of the detailed model of stellar wind property in the proximity of the stars.
+They considered not only the kinetic energy of the stellar wind but also the magnetic energy of the stellar wind and coronal mass ejection (CME).
+Note that in these paperes, the scaling relation of planetary magnetic fields  differ from paper to paper.    
+In \citet{reiners2010}, the authors adopted new scaling relation of planetary magnetic field based on \citet{christensen2009}.
+\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission.  
 Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
-though there are some promising intial results \citep{lecavelier_et_al2013,sirothia2014}.
+though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
 
@@
 %In \S5, we discuss the usefulness of radio emission in exploring Jupiter-like planets around evolved stars. 
-In \S5, we mention the effects of canceling magnetic fields resulting from the plasmas spiraling in the planetary magnetosphere.  
+In \S5, we mention the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.  
 Finally, \S6 concludes the paper with a brief summary.
@@
 %%%%%%%%%% 
-\begin{equation}
-n = 1.80 \times 10^6 \; {\rm cm^{-3}} \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30\; {\rm km}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \label{eq:n_normalized}
-\end{equation}
+\begin{eqnarray}
+n &=& 1.80 \times 10^6 \; {\rm cm^{-3}} \\
+&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30\; {\rm km}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \label{eq:n_normalized}
+\end{eqnarray}
 %%%%%%%%%%
@@
 
-The radio intensity of evolved stars in the range of 10~MHz and 1~GHz is not constrained through observation\memoYF{?}. 
+The radio intensity of evolved stars in the range of 10~MHz and 1~GHz is not constrained through observation. 
 Above 1~GHz, there are several observations.
@@
 
-\memoYF{Modulation due to the presence of satellites (a few hours $\sim $)?} 
-%
+\paragraph{Modulation due to the presence of satellites (a few hours $\sim $)}
 

### 2015-09-04 ms.tex
Section 4.1 is cleaned up

@@
 In this section, we discuss the observability of the estimated radio emission. 
-An obvious obstacle is the intrinsic radio emission from host red giant stars themselves; if they are larger than radio flux from the planets, there is no way to identify the latter.
+An obvious potential obstacle is the intrinsic radio emission from host red giant stars themselves; if they are larger than radio flux from the planets, there is no way to identify the latter.
 We will see in \S\ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 
@@
 In \S\ref{ss:detectability}, we estimate the sensitivities and limitations of several current and future
-radio instruments at lower frequencies.
+radio instruments at relevant frequencies.
 Finally, \S\ref{ss:timevariability} discusses the expected time variability of the radio emission as a mean to discern the signals from the background noise.
@@
 
-The radio intensity of evolved stars in the range of 10~MHz and 1~GHz is not constrained through observation. 
-Above 1~GHz, there are several observations.
-For example, \citet{gorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
-
-We estimate the thermal radio flux from the host star to be consistent with these observed data and by extrapolating to the lower frequency range with a simple power law:
-%%%
-\begin{eqnarray}
-\nonumber f_{\star }(\nu ) &\sim & (0.4-1.375) \times 10^{-3} ~\mbox{Jy} \\
-&& \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
-\end{eqnarray}
-%%%
-Constant property wind model \citep{wright1975,panagia1975,olnon1975} predicts $\alpha = 0.6$, while observations suggested that the power index $\alpha $ is steeper than 0.6 \citep{gorman2013}.
-
-Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant stars with 100~$R_{\odot }$, both of which is placed at 10 pc away. 
-As this figure indicates, even if the radio emission from the red giant itself has a relatively shallow spectral index, the radio emission from the RGHJ still dominates in the 10-200~MHz range. 
-Therefore, in the following, we ignore the radio emission from the red giant as a noise source.
-
-% Neil's addition
-
 Over the last four decades there have been numerous radio continuum observations of nearby red giants, many with the aim of understanding the extended atmospheres and mass-loss mechanisms of K- and M-type giants~\citep[e.g.,][]{Newell1982, Knapp1995, Skinner1997, Lim1998, OGorman2013}.
-Almost all observations have been carried out at wavelengths of 6 cm and below, probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.
+Almost all observations have been carried out 
+%at wavelengths of 6 cm and below, 
+at frequency of 5 GHz or above, 
+probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.
 The spectral index of this emission is of order unity, with a range of reported values for various sources between 0.8 and 1.6~\citep{OGorman2013}.
 
-Only two published studies describe attempts to detect continuum emission from single (non-binary) red giant stars at wavelengths above 20 cm ($L$ band); both yielded null results.
+Only two published studies describe attempts to detect continuum emission from single (non-binary) red giant stars 
+%at wavelengths above 20 cm 
+at frequencies below 1 GHz ($L$ band); both yielded null results.
 First, a program that observed a sample of nine M-type giants at 430 MHz with the Arecibo Telescope failed to detect any of the sources down to flux density 10 mJy~\citep{Fix1976}.
@@
 Current facilities could achieve far deeper sensitivity on similar targets.
-For example, as listed in Table~\ref{tab:sens}, the Giant Metrewave Radio Telescope (GMRT) at 150 MHz reaches a 
-sensitivity better than 0.5~mJy in under an hour.
+For example, as listed in Table~\ref{tab:sens}, the Giant Metrewave Radio Telescope (GMRT) at 150 MHz reaches a sensitivity better than 0.5~mJy in under an hour.
 However, any re-attempts to detect single red giants at wavelengths near 1 meter remain to be presented in the literature.
@@
 
-Altogether, we lack firm observational constraints on the brightnesses of M giants near 1-m wavelengths.
+Altogether, we lack firm observational constraints on the brightnesses of M giants near %1-m wavelengths.
+30-300 MHz frequencies.
+
 However, assuming thermal Bremsstrahlung emission continues to dominate in this wavelength regime, we can extrapolate down from the reported centimeter flux densities, using the specific spectral index when available.
-In this case, for example, extrapolating from the 0.4 mJy flux density of $\alpha$ Ori at 1.46 GHz, and using its spectral index 1.32~\citep{Newell1982}, we arrive at an estimated flux density of 0.04 mJy at 300 MHz.
+%In this case, for example, extrapolating from the 0.4 mJy flux density of $\alpha$ Ori at 1.46 GHz, and using its spectral index 1.32~\citep{Newell1982}, we arrive at an estimated flux density of 0.04 mJy at 300 MHz.
+% YF: This is consistent with the following equation, so I removed it to avoid redundancy. 
+%
+\citet{OGorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
+Using these data, we extrapolate the radio flux from the host star to the lower frequency range with a simple power law as follows:
+%%%
+\begin{eqnarray}
+\nonumber f_{\star }(\nu ) &\sim & (0.4-1.4) \times 10^{-3} ~\mbox{Jy} \\
+&& \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
+\end{eqnarray}
+%%%
+where the power index $\alpha $ is order of unity.
+
+Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
+The spectral shape is modeled by simply scaling the Jovian radio spectra e.g. Figure 8 of \citet{zarka_et_al2004}. 
+The continuum from the star in the case of $\alpha =0.6$ is shown as an extreme case; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}. 
+As Figure \ref{fig:cartoon} indicates, with the reasonable range of spectral index, radio emission from the stars is by order of magnitude smaller than the expected radio flux from RGHJs at frequencies below 300~MHz.
+For less massive planets (with weaker magnetic fields), the distinction is even clearer, as the peak flux is larger and the peak frequencies is smaller.
+Therefore, in the following, we ignore the radio emission from the red giant as a noise source.
 

### 2015-09-04 ms.tex
cartoon is smoothe

@@
 n &=& 1.80 \times 10^6 \; {\rm cm^{-3}} \\
-&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30\; {\rm km}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \label{eq:n_normalized}
+&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \label{eq:n_normalized}
 \end{eqnarray}
@@
 \begin{eqnarray}
-L_{\rm acc} \sim &&  10^{29} \; {\rm erg\;s}^{-1} \\
-&& \times \left( \frac{\dot M_*}{10^{-7} M_{\odot }\;{\rm yr}} \right) \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \\
+L_{\rm acc} \sim &&  10^{28} \; {\rm erg\;s}^{-1} \\
+&& \times \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right) \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \\
 %
@@
 \label{eq:fplasmalos} f_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
-\label{eq:fplasmalos_scaled} & = & 14.7{\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{0.1 v_{\odot}}  \right)^{-1/2} \notag \\
- & & \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}}\right)^{1/2} \, .
-\end{eqnarray}
+\label{eq:fplasmalos_scaled} & = & 14.7{\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
+ & & \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}}\right)^{1/2} \, .
+\end{eqnarray}
+\memoYF{check numbers in above equation}
 %%%
@@
 \nonumber &=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
-&& \times \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
+&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
  \label{eq:stand-off-radius}
@@
 F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyc}} \\
-&\approx & 5.22\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 5.22\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
@@
 %%%
-&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 1.12 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
@@
 %%%
-&\approx & 1.12 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
@@
 %%%
-&\approx & 2.42 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 2.42 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
@@
 Note that, within this framework, the {\it spectral} radio flux has necessarily negative correlation with the planetary magnetic field, as pointed out by \citet{griesmeier2005}. 
+Equation (\ref{eq:F_nu_RGHJ}) gives the value which is by factor smaller than the prediction of equation (5) in \citet{ignace2010} in the case of $\eta = 1$.
+This originates from the different scaling laws for the planetary magnetic field and that their paper didn't incorporate the compression of the planetary magnetosphere due to massive stellar wind.
 
@@
 \begin{eqnarray}
-\nonumber f_{\star }(\nu ) &\sim & (0.4-1.4) \times 10^{-3} ~\mbox{Jy} \\
-&& \times \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
+\nonumber f_{\star }(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \\
+&& \times \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 ~R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
 \end{eqnarray}
@@
 \begin{figure*}[tbp]
-   \plotonesc{cartoon_10Mj_2.pdf}
+   \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
    \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.

### 2015-09-04 ms.tex
revising Section 2.2

@@
 n &=& 1.80 \times 10^6 \; {\rm cm^{-3}} \\
-&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \label{eq:n_normalized}
-\end{eqnarray}
-%%%%%%%%%%
-
-\memoYF{check from here}
-As discussed in \citet{ignace2010}, one potential problem of the stellar wind of evolved stars which is unfavorable for radio emission is that their ionization fraction is usually as low as $10^{-3}$ \memoYF{cite something}, which would lead to inefficient interaction with planetary magnetosphere and hence low input energy for radio emission.
-However, at this stage the velocity of stellar wind becomes slower than the escape velocity of planetary companion and hence the stellar wind particles are expected to accrete onto the planets. 
-Based on \citet{spiegel+madhusudhan2012}, the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ are: 
+&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2}. \label{eq:n_normalized}
+\end{eqnarray}
+%%%%%%%%%%
+
+As discussed in \citet{ignace2010}, the ionization fraction of the stellar wind of evolved stars are supposedly as low as $\sim 10^{-3}$\memoYF{cite something}.
+Since only charged particles interact with planetary magnetic field, this suggests the inefficient interaction with planetary magnetosphere and hence low input energy for radio emission.
+However, at this stage, the velocity of stellar wind becomes slower than the escape velocity of planetary companion and hence the stellar wind particles are expected to accrete onto the planets. 
+\citet{spiegel+madhusudhan2012} computed the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ are: 
 %%%%%%%%%
 \begin{eqnarray}
-L_{\rm acc} \sim &&  10^{28} \; {\rm erg\;s}^{-1} \\
-&& \times \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right) \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \\
-%
-T_{\rm acc} \sim && 2 \times 10^6 \left( \frac{M_p}{10 M_J} \right)
+L_{\rm acc} \sim &&  10^{28} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \\
+&& \times \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \\
+%
+T_{\rm acc} \sim && 2 \times 10^6 ~\mbox{K} \left( \frac{M_p}{10 M_J} \right) \\
+\sim && 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_J} \right). 
 \end{eqnarray}
@@
 The accretion disks around planets therefore emit X-ray radiation. 
-We estimate the scale of the ionized region by computing Stromgren radius of the accretion disk: 
+We estimate the scale of the ionized region by computing Stromgren radius of the accretion disk \citep{stromgren1939}: 
 %%%%%%%%%
@@
 %%%%%%%%%
-where $S$ is the source rate of ionizing photons, $n$ is the density of hydrogen, and $\beta $ is the coefficient for recombination \memoYF{need to check}:
+where $S$ is the source rate of ionizing photons, $n$ is the density of hydrogen, and $\beta $ is the coefficient for recombination \memoYF{cite something}:
 % http://www.tapir.caltech.edu/~chirata/ay102/Photoionized.pdf
@@
 \begin{eqnarray}
-\beta &=& 4.3? \times 10^{-13} \; \left( \frac{T}{10^4 \;{\rm K}} \right) ^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} \\
-&\sim& 5.28 \times 10^{-14} \; \left( \frac{M_p}{M_J} \right)^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} 
+%\beta &=& 4.3? \times 10^{-13} \; \left( \frac{T}{10^4 \;{\rm K}} \right) ^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} \\
+\beta &=& 2.6 \times 10^{-13} \; \left( \frac{T}{10^4 \;{\rm K}} \right) ^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} \\
+&\sim& 2.74 \times 10^{-14} \; \left( \frac{M_p}{M_J} \right)^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} 
 \end{eqnarray}
 %%%%%%%%%
-The source rate is obtained by counting the number of photons whose energy is higher than 13.6~eV, the energy needed to ionize hydrogen atoms.
-As a result, \memoYF{need to check}
+The source rate is obtained by counting the number of photons whose energy is higher than 13.6~eV ($\lambda = $), the energy needed to ionize hydrogen atoms.
+As a result, 
 %%%%%%%%%
 \begin{eqnarray}
-S_* = 
+S_* \sim  
   \left\{
     \begin{array}{ll}
-      1.18 \times 10^{42} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
-      2.66 \times 10^{44} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
+      2 \times 10^{42} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
+      3 \times 10^{44} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
+    \end{array}. 
+  \right.
+\end{eqnarray}
+%%%%%%%%%
+Using the number density of hydrogen atoms given by equation (\ref{eq:n_normalized}), 
+%%%%%%%%%
+\begin{eqnarray}
+R_{\rm stromgren} \sim  
+  \left\{
+    \begin{array}{ll}
+      4 \;{\rm AU} & \;\;\;(M_p = M_J) \\
+      40 \;{\rm AU} & \;\;\;(M_p = 10 M_J)
     \end{array}
@@
 %%%%%%%%%
-and the number density of hydrogen atoms are given by equation (\ref{eq:n_normalized}). 
-These values give \memoYF{need to check}
-%%%%%%%%%
-\begin{eqnarray}
-R_{\rm stromgren} = 
-  \left\{
-    \begin{array}{ll}
-      3 \;{\rm AU} & \;\;\;(M_p = M_J) \\
-      30 \;{\rm AU} & \;\;\;(M_p = 10 M_J)
-    \end{array}
-  \right.
-\end{eqnarray}
-%%%%%%%%%
+for a planet around a red giants at 5~AU.
 
@@
 
+% -
+% - the obstacle is not the ionization fraction but the plasma cut-off
+
 The maximum radio emission we can expect to observe is limited by the plasma cut-off frequency of the stellar wind in the vicinity of the planets. 

### 2015-09-04 ms.tex
christensen2009 => christensen_et_al_2009
I point out that it's not impossible to see planets that are dimmer than stars, just more difficult.

@@
 Note that in these paperes, the scaling relation of planetary magnetic fields  differ from paper to paper.    
-In \citet{reiners2010}, the authors adopted new scaling relation of planetary magnetic field based on \citet{christensen2009}.
+In \citet{reiners2010}, the authors adopted new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}.
 \citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission.  
@@
 In this section, we discuss the observability of the estimated radio emission. 
-An obvious potential obstacle is the intrinsic radio emission from host red giant stars themselves; if they are larger than radio flux from the planets, there is no way to identify the latter.
+An obvious potential obstacle is the intrinsic radio emission from host red-giant stars themselves; if they are bright relative to the radio flux from the planets, it is significantly more difficult identify the planets.
 We will see in \S\ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 

### 2015-09-05 ms.tex
included Madhu's note

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Luminosity function of planetary radio emission}
+\label{ss:Lfunc}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In principle, if the expected luminosity function (LF) and positional distribution of possible RGHJ emitters were known one could estimate the likelihood of detecting RGHJs in radio surveys.
+For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N(L) \propto L^{-\alpha}$, where, $N(L)$ is the number of objects per unit volume with a luminosity of L, and assume an isotropic distribution of sources in the observed volume.
+Under these assumptions, the observed flux from the brightest source in a volume limited sample will scale with distance as $f_{\rm max} \propto d^{\frac{3}{\alpha} - 2}$, implying that the likelihood of finding the brightest source increases with distance for $\alpha < 3/2$.
+Such a scenario would indeed be favorable to detect RGHJs given that AGB stars, which are good sources for bright RGHJs due to their high mass loss rates, are rare and would require probing out to larger distances for detection.
+For example, for an $N(L) \propto L^{-1}$ the brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects.
+Therefore, it is important to determine the LF for RGHJ emitters in order to estimate their detectability.
+
+Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in the local galaxy.
+In order to estimate the true luminosity function of RGHJ emitters one of the key factors is the distribution of mass-loss rates of giant host stars.
+As discussed in section~3.2, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate as $\dot{M}_\star^{1/2}$.
+Recent empirical studies of stellar mass-loss rates, including those for evolved giant stars, suggest $\dot{M}_\star \propto L_\star^{7.5/4} (R_\star/M_\star)(1+A/g_\star)$, where, $L_\star$,  $R_\star$, $M_\star$, and $g_\star$ are the stellar luminosity, radius, mass, and gravity, respectively, and $A  = g_\odot/4300$ is a constant (Schr\"{o}der \& Cuntz~2005,2007).
+Therefore, the luminosity of a RGHJ varies nearly linearly as the luminosity of the host star, and is given by $L \propto L_\star^{7.5/8} [(R_\star/M_\star)(1+A/g_\star)]^{1/2}$.
+Therefore, the LF of giant host stars is an essential ingredient for determining the LF for RGHJs which future surveys would need to consider.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Back-reaction of a plasma flowing into a magnetic field}

### 2015-09-05 ms.tex
editing discussion (halfway)

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Discriminating from Background:\\Time Variability}
+\subsection{Discriminating from Background}
 \label{ss:timevariability}
@@
 
-%In order to identify radio emission from exoplanets in the galactic background noise, it is
-
-In order to identify radio emission from exoplanets, it is critical to discern it from the galactic background. 
-An important feature useful for this purpose is the time variability of radio emission. 
-Indeed, several processes cause the time variability of radio emission from exoplanets at different timescales; they are listed below from the ones typically with shorter timescales to those with longer timescales.
+Since the confusion limit is on the same order as the signal (Table \ref{tab:sens}), it is crucial to consider the ways to discriminate the signal from the confusion sources.
+In this section, we discuss time variability and polarization as keys to identify the auroral radio emission from the planets.
+
+One of the key features that make planetary radio emission distinct is the almost complete polarization \citep[e.g.][]{dulk1994}. ...\memoYF{write here}
+s
+Another key is that auroral radio emission from planets is not a static source but it significantly varies in time. 
+The potential factors that cause time variability of the auroral radio emission are  listed below.
 
 \paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
-If the planetary spin axis is misaligned to the planetary magnetic axis, like Jupiter, the radio intensity will display sinusoidal modulation synchronously to the spin period.
-%
-
+... \memoYF{write here}
+%
 \paragraph{Modulation due to the presence of satellites (a few hours $\sim $)}
-
-\paragraph{Variability of stellar wind due to stellar oscillation (day $\sim $)?}
+... \memoYF{write here}
+
+\paragraph{Variability of stellar wind due to stellar oscillation (months $\sim $)?}
 Based on the correlation between the planetary radio emission and the solar wind plasma density also suggest that the radio emission from the planet around the evolved stars, which typically oscillate, are time variable.
@@
 \label{s:discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Implication for discovery and characterization of exoplanets}
+\label{ss:implication}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-09-05 ms.tex
discussion (S5.1) is added

@@
 
+\memoYF{Need to elaborate. References are needed. }
+
+For now, it is difficult to detect planetary-mass companions around low-mass evolved stars through other means.
+The major difficulty in radial velocity measurement is the stellar pulsation (rms of $>30m/s$ for K giants).
+If the orbital period is long enough compared to the period of pulsation, it is possible to average out the pulsation and detect radial velocity of planetary component, but this requires long period monitoring.
+For transit observation Pulsation also contributes to the noise in detecting transit signals \memoYF{?} and besides the transit signals would be as low as 1ppm.
+Due to the great luminosity of the host star, direct imaging is also difficult \memoYF{?}.
+Thus, for the time being, one would have to aim at discovering planetary companions around evolved stars, rather than targeting at known planetary systems.
+
+Once radio emission is detected, it provides some useful information through both time dependence and frequency dependence. 
+As mentioned in \S\ref{ss:timevariability}, auroral radio emission varies in association with several physical processes.
+In turn, radio emission could provide a unique pathway to get an idea of spin rotation period.
+(This is an advantage of searching for RGHJs rather than canonical hot Jupiters, because the latter is likely to be tidally locked to the stars.)
+%
+Also, if the system is near edge-on, we will observe the time variability corresponding to orbital period, which can tell us the orbital distance of the planets.
+
+Obviously, if the spectra could be obtained and the frequency cut-off is detected, it tells us the magnetic field strengths of the planetary surface. 
+Such information would be most useful if we could follow up the system by radial velocity to get constraints on the planetary mass, because with such information, we can contest the scaling laws of planetary magnetic field strength as a function of mass.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-09-05 ms.tex
conclusion updated

@@
 \label{sec:conc}
-
-In this paper, we propose that ``hot Jupiters'' around evolved stars (RGHJ) may be bright radio wave emitters, on the assumption of the simple empirical correlation between the radio emission and the kinetic input energy.
-Massive stellar wind of red giants and AGB stars would put the kinetic energy into magnetospheres of distant Jovian planets, which could lead to the intrinsic bright radio emission, comparable to or greater than canonical hot Jupiters in close-in orbits.
-
-% -
-% - the obstacle is not the ionization fraction but the plasma cut-off
-
-The maximum radio emission we can expect to observe is limited by the plasma cut-off frequency of the stellar wind in the vicinity of the planets. 
-For a planet with the same magnetic moment as Jupiter, the maximum radio emission from the planets which can penetrate through the surrounding plasma is $\sim 10^{-3}$ Jy or $\sim 10^{-5}$ Jy at 10~pc and 100~pc, respectively.
-As we showed in \S\ref{ss:detectability}, the upper end of this range is detectable with the current generation of radio facilities, while farther hot Jupiters should soon be detectable using the next generation of instruments.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between the radio emission and the kinetic input energy.
+Unlike the previous paper, we consider that X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise fairly neutral. 
+Based on such picture, massive stellar wind of red giants and AGB stars would interact with planetary magnetic field and puts the kinetic energy into magnetospheres of RGHJs.
+We found that the RGHJs would generate bright radio emission, comparable to or greater than canonical hot Jupiters in close-in orbits around main-sequence stars.
+
+A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind.
+Due to great density of the stellar wind, the cut-off frequency is as high as $\sim 15 MHz$ for typical red giants and $\sim 464 MHz$ for typical AGB stars.
+Therefore, massive planetary companions with magnetic field stronger than Jupiter should be targeted at.
+
+The radio flux from a system with an exoplanet at 5 AU at a distance of 100 pc would be typically on the order of $\sim 10 \mu $Jy. 
+Such signals would be detectable with SKA within a day or so. 
+For a few nearest systems, or for systems with exoplanets in closer orbit, LOFAR-HBA  would also work with a reasonable integration time. 
+In both cases, it is critical to consider the time variability of the flux, in order to identify the signal from confusion sources.
 

### 2015-09-06 ms.tex
Move comment to new line.
Figure 3 is updated

@@
 %
-Yuka Fujii\altaffilmark{0} \\
-%
-David S. Spiegel\altaffilmark{1,2} \\
-%
-{\bf and some order:} \\
-%
-Jason Nordhaus\altaffilmark{3,4} \\
-%
-Nikku Madhusudhan\altaffilmark{5} \\
-%
-Mehrdad Mirbabayi\altaffilmark{1} \\
-%
-Aaron Parsons\altaffilmark{6} \\
-%
-Tony Mroczkowski\altaffilmark{7,8} \\
-%
-Neil T. Zimmerman\altaffilmark{9}
+Yuka Fujii\altaffilmark{1} 
+%
+David S. Spiegel\altaffilmark{2,3}
+%
+Tony Mroczkowski\altaffilmark{4,5}
+%
+Jason Nordhaus\altaffilmark{6,7}\\
+%
+Neil T. Zimmerman\altaffilmark{8}
+%
+Aaron Parsons\altaffilmark{9}
+%
+Nikku Madhusudhan\altaffilmark{10}
+%
+Mehrdad Mirbabayi\altaffilmark{2}
 }
 
-\affil{$^0$Earth-Life Science Institute, Tokyo Institute of Technology, 
+\affil{$^1$Earth-Life Science Institute, Tokyo Institute of Technology, 
   Tokyo, JAPAN, 152-8550}
 
-\affil{$^1$Astrophysics Department, Institute for Advanced Study,
+\affil{$^2$Astrophysics Department, Institute for Advanced Study,
   Princeton, NJ 08540}
 
-\affil{$^2$Research \& Development, Sum Labs,
+\affil{$^3$Research \& Development, Sum Labs,
   New York, NY  10001}
 
-\affil{$^3$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}
-
-\affil{$^4$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}
-
-\affil{$^5$Astronomy Department, University of Cambridge, UK}
-
-\affil{$^6$Astronomy Department, University of California Berkeley}
-
-\affil{$^7$National Research Council Fellow}
-
-\affil{$^8$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
-
-\affil{$^9$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
+\affil{$^4$National Research Council Fellow}
+
+\affil{$^5$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
+
+\affil{$^6$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^7$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^8$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
+
+\affil{$^9$Astronomy Department, University of California Berkeley}
+
+\affil{$^10$Astronomy Department, University of Cambridge, UK}
 
@@
 %%%%%%%%%% 
+\memoYF{check the values above}
 
@@
 \begin{eqnarray}
-L_{\rm acc} \sim &&  10^{28} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \\
+L_{\rm acc} \sim &&  10^{28} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \notag \\
 && \times \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \\
@@
 
-Radio emission from the planet is observable from ground only when the maximum frequency is larger than the plasma frequency of Earth's ionosphere $f_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $f_{\rm plasma}^{\rm los}$.
+Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $f_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $f_{\rm plasma}^{\rm los}$.
 The plasma frequency may be expressed as
@@
 \begin{figure*}[bp]
-   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
-   \plotonesc{radio_emission_Mdot1e-5_constRp_christensen.pdf}
-   \caption{[{\bf New version: based on scaling relationship of Christensen 2010}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 10 pc.
-The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere. 
-he hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion.
-Bottom panel: cyclotron frequency, i.e., the frequency of radio emission. }
+%   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
+%   \plotonesc{radio_emission_Mdot1e-5_constRp_christesnsen.pdf}
+	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
+   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom).
+The systems are located at 100 pc away.
+The doubly hashed regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $f_{\rm cyc}$) is below the plasma frequency cut-off, $f_{\rm plasma}^{\rm los}$.
+The hashed regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1f_{\rm cyc}$, is below $f_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
+}
   \label{fig:radio}
@@
 
-One of the key features that make planetary radio emission distinct is the almost complete polarization \citep[e.g.][]{dulk1994}. ...\memoYF{write here}
-s
+One of the key features that make planetary radio emission distinct is the almost complete polarization \citep[e.g.][]{dulk1994}.
+...\memoYF{write here}
+
 Another key is that auroral radio emission from planets is not a static source but it significantly varies in time. 

### 2015-09-06 ms.tex
Elaborating the text

@@
 
-Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by Eq.~(\ref{eq:fplasmalos_scaled}).
+Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}).
 We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency:
@@
 %%%
-The hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where this criteria is not satisfied and thus the radio emission from the planet cannot be observed from the Earth.
-
-Equation (\ref{eq:fcyc>fplasma}) can also be rewritten as: 
-%%%
-\begin{eqnarray}
- \left( \frac{B}{10~\mbox{G}} \right) &>& 0.526 \left( \frac{a}{5~\mbox{AU}} \right)^{-1} \\
- && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
-\end{eqnarray}
-%%%
-or, 
-%%%
-\begin{eqnarray}
- \left( \frac{M_p}{M_{p,J}} \right) &> & 0.627 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
- && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
-\end{eqnarray}
-%%%
-In other words, given any orbital distance, there is a lower mass limit for a planet to be able to release the  radio wave out of the system. 
-Substituting equation (\ref{eq:Ba_limit}) into equation (\ref{eq:F_nu_RGHJ}) leads to the maximum spectral radio flux at given orbital period:
-%%%
-\begin{eqnarray}
-F_{\nu} &<& 1.30 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right)^{-2} \\
-&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{1/3}  \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
-\end{eqnarray}
-%%%
+The doubly hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where this criteria is not satisfied and thus the radio emission from the planet cannot be observed from the Earth. 
+In reality, the peak of the auroral radio emission does not always occur at the maximum frequency.
+Instead, it usually exits at lower frequencies.
+Here, we also consider a more conservative criteria, $0.1 f_{\rm cyc} > f_{\rm plasma}^{\rm los}$ as a measure for the observability of the bulk of radio emission.
+In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines.
+It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars.
+For a red-giant system, the most promising target if massive companion with $M_p \gtrsim 5M_J$.
+On the other hand, for a AGB-star system, it is very difficult to detect a signal from the planetary-mass companions within 100 AU.
 
@@
 % HERA
-The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) \ldots
+The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) \ldots \memoYF{write here (Aaron?)}
 
@@
 One of the key features that make planetary radio emission distinct is the almost complete polarization \citep[e.g.][]{dulk1994}.
-...\memoYF{write here}
+...\memoYF{write here (YF)}
 
@@
 \paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
-... \memoYF{write here}
+... \memoYF{write here (YF)}
 %
 \paragraph{Modulation due to the presence of satellites (a few hours $\sim $)}
-... \memoYF{write here}
+... \memoYF{write here (YF)}
 
@@
 Once radio emission is detected, it provides some useful information through both time dependence and frequency dependence. 
-As mentioned in \S\ref{ss:timevariability}, auroral radio emission varies in association with several physical processes.
-In turn, radio emission could provide a unique pathway to get an idea of spin rotation period.
-(This is an advantage of searching for RGHJs rather than canonical hot Jupiters, because the latter is likely to be tidally locked to the stars.)
-%
-Also, if the system is near edge-on, we will observe the time variability corresponding to orbital period, which can tell us the orbital distance of the planets.
-
-Obviously, if the spectra could be obtained and the frequency cut-off is detected, it tells us the magnetic field strengths of the planetary surface. 
-Such information would be most useful if we could follow up the system by radial velocity to get constraints on the planetary mass, because with such information, we can contest the scaling laws of planetary magnetic field strength as a function of mass.
+As mentioned in \S\ref{ss:timevariability}, auroral radio flux significantly varies in time in association with several physical processes.
+In turn, we could utilize the time variability to characterize the system.
+For example, if the system is near edge-on, we will observe the time variability corresponding to orbital period, which can tell us the orbital distance of the planets.
+It the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could also be detectable (This is an advantage of searching for RGHJs rather than canonical hot Jupiters, because the latter is likely to be tidally locked to the stars).
+
+If the spectra are obtained, the upper cut-off frequency of the radio spectra will imply us the magnetic field strengths of the planetary surface.
+Such information would be most useful if we could follow up the system by radial velocity to get constraints on the planetary mass, because once both magnetic field strength and the planetary mass is constrained, the proposed scaling law of planetary dynamo may be contested.
+On the other hand, the lower cut-off frequency indicates the plasma frequency in the vicinity of the planets, which might be used as a probe of the density of the stellar wind at the planetary orbit.
 
@@
 
-In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between the radio emission and the kinetic input energy.
-Unlike the previous paper, we consider that X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise fairly neutral. 
-Based on such picture, massive stellar wind of red giants and AGB stars would interact with planetary magnetic field and puts the kinetic energy into magnetospheres of RGHJs.
-We found that the RGHJs would generate bright radio emission, comparable to or greater than canonical hot Jupiters in close-in orbits around main-sequence stars.
+In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind.
+Unlike the previous paper, we consider that X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
+Based on such a picture, massive stellar wind of red giants and AGB stars would interact with planetary magnetic field and inputs kinetic energy into magnetospheres of RGHJs. 
+We found that the intrinsic brightness of radio emission from RGHJs would be comparable to or greater than canonical hot Jupiters in close-in orbits around main-sequence stars.
 
@@
 Due to great density of the stellar wind, the cut-off frequency is as high as $\sim 15 MHz$ for typical red giants and $\sim 464 MHz$ for typical AGB stars.
-Therefore, massive planetary companions with magnetic field stronger than Jupiter should be targeted at.
+The most promising targets are massive planetary ($M_p \gtrsim 5M_J$) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
 
@@
 For a few nearest systems, or for systems with exoplanets in closer orbit, LOFAR-HBA  would also work with a reasonable integration time. 
-In both cases, it is critical to consider the time variability of the flux, in order to identify the signal from confusion sources.
-
-Admittedly, uncertainties exist in the relation between radio emission of Jovian planets and the input energy from stellar wind, as well as in the scaling of planetary magnetic field. 
-Alternatively, once we detect both the gravitational perturbation and radio emission of Jovian planets, these models will be contested.
-The viability of these scaling relations will be examined in the future.
+In both cases, it is critical to consider polarization and/or time variability of planetary radio flux, in order to separate it from confusion sources.
+
+Once the planetary radio emission is detected, ...\memoYF{write here}.
+
+%Admittedly, uncertainties exist in the relation between radio emission of Jovian planets and the input energy from stellar wind, as well as in the scaling of planetary magnetic field. 
+%Alternatively, once we detect both the gravitational perturbation and radio emission of Jovian planets, these models will be contested.
+%The viability of these scaling relations will be examined in the future.
 
@@
 
+Equation (\ref{eq:fcyc>fplasma}) can also be rewritten as: 
+%%%
+\begin{eqnarray}
+ \left( \frac{B}{10~\mbox{G}} \right) &>& 0.526 \left( \frac{a}{5~\mbox{AU}} \right)^{-1} \\
+ && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
+\end{eqnarray}
+%%%
+or, 
+%%%
+\begin{eqnarray}
+ \left( \frac{M_p}{M_{p,J}} \right) &> & 0.627 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
+ && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
+\end{eqnarray}
+%%%
+In other words, given any orbital distance, there is a lower mass limit for a planet to be able to release the  radio wave out of the system. 
+Substituting equation (\ref{eq:Ba_limit}) into equation (\ref{eq:F_nu_RGHJ}) leads to the maximum spectral radio flux at given orbital period:
+%%%
+\begin{eqnarray}
+F_{\nu} &<& 1.30 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right)^{-2} \\
+&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{1/3}  \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
+\end{eqnarray}
+%%%
+
 \end{document}

### 2015-09-07 ms.tex
Stromgren radius is revised. Text is edited

@@
     \begin{array}{ll}
-      2 \times 10^{42} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
-      3 \times 10^{44} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
+      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
+      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
     \end{array}. 
@@
     \begin{array}{ll}
-      4 \;{\rm AU} & \;\;\;(M_p = M_J) \\
-      40 \;{\rm AU} & \;\;\;(M_p = 10 M_J)
+      40 ~R_J & \;\;\;(M_p = M_J) \\
+      400 ~R_J & \;\;\;(M_p = 10 M_J)
     \end{array}
@@
 Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
-\memoYF{reconsidering...}
 
@@
 Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
+Note that the thermal contribution from accretion disk is negligible in this figure. 
 The spectral shape is modeled by simply scaling the Jovian radio spectra e.g. Figure 8 of \citet{zarka_et_al2004}. 
@@
 For less massive planets (with weaker magnetic fields), the distinction is even clearer, as the peak flux is larger and the peak frequencies is smaller.
+
 Therefore, in the following, we ignore the radio emission from the red giant as a noise source.
@@
 \paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
-... \memoYF{write here (YF)}
-%
-\paragraph{Modulation due to the presence of satellites (a few hours $\sim $)}
-... \memoYF{write here (YF)}
-
-\paragraph{Variability of stellar wind due to stellar oscillation (months $\sim $)?}
+The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep{dessler1983} due to the misalignment between the magnetic axis and the spin axis. 
+%
+\paragraph{Modulation due to the presence of satellites (a few days $\sim $)}
+The occurrence probability of Jovian radio burst is affected by the location of Io as well \citep{dessler1983}, because the presence of Io inputs plasmas into the system. 
+Likewise, if the exoplanets have moons that emit plasmas, then the radio flux is  modulated by the orbital motion of the moon \citep[see e.g.,][]{noyola2014}.
+
+\paragraph{Variability of stellar wind (months $\sim $)?}
 Based on the correlation between the planetary radio emission and the solar wind plasma density also suggest that the radio emission from the planet around the evolved stars, which typically oscillate, are time variable.
@@
 
-For now, it is difficult to detect planetary-mass companions around low-mass evolved stars through other means.
-The major difficulty in radial velocity measurement is the stellar pulsation (rms of $>30m/s$ for K giants).
+So far, more than 60 exoplanets are found around evolved stars \citep[e.g.][and references therein]{trifonov2015}. 
+Therefore, one possible strategy is to target at the know planetary systems.  
+One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30 \mbox[m/s]$.
+Therefore, there are some parameter spaces where current radial velocity observations cannot survey.
+For this parameter space, radio emission would work as a  probe to discover the possible sub-stellar companions.
+
+%For now, it is difficult to detect planetary-mass companions around low-mass evolved stars through other means. 
+%The major difficulty in radial velocity measurement is the stellar pulsation (rms of $>30m/s$ for K giants).
 If the orbital period is long enough compared to the period of pulsation, it is possible to average out the pulsation and detect radial velocity of planetary component, but this requires long period monitoring.
@@
 For example, if the system is near edge-on, we will observe the time variability corresponding to orbital period, which can tell us the orbital distance of the planets.
-It the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could also be detectable (This is an advantage of searching for RGHJs rather than canonical hot Jupiters, because the latter is likely to be tidally locked to the stars).
+If the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could also be detectable (This is an advantage of searching for RGHJs rather than canonical hot Jupiters, because the latter is likely to be tidally locked to the stars).
 
@@
 As discussed in section~3.2, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate as $\dot{M}_\star^{1/2}$.
-Recent empirical studies of stellar mass-loss rates, including those for evolved giant stars, suggest $\dot{M}_\star \propto L_\star^{7.5/4} (R_\star/M_\star)(1+A/g_\star)$, where, $L_\star$,  $R_\star$, $M_\star$, and $g_\star$ are the stellar luminosity, radius, mass, and gravity, respectively, and $A  = g_\odot/4300$ is a constant (Schr\"{o}der \& Cuntz~2005,2007).
+Recent empirical studies of stellar mass-loss rates, including those for evolved giant stars, suggest $\dot{M}_\star \propto L_\star^{7.5/4} (R_\star/M_\star)(1+A/g_\star)$, where, $L_\star$,  $R_\star$, $M_\star$, and $g_\star$ are the stellar luminosity, radius, mass, and gravity, respectively, and $A  = g_\odot/4300$ is a constant \citep{schroder2005,schroder2007}.
 Therefore, the luminosity of a RGHJ varies nearly linearly as the luminosity of the host star, and is given by $L \propto L_\star^{7.5/8} [(R_\star/M_\star)(1+A/g_\star)]^{1/2}$.
@@
 NM acknowledges support from [???]. 
+YF greatly acknowledges insightful and helpful discussions with Tomoki Kimura and Hiroki Harakawa. 
 The portion of this research for which TM is responsible was performed while he held a National Research Council Research Associateship Award at the Naval Research Laboratory (NRL).
